### 2018-08-17 README.Rmd
layout project status

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/",
  warning = FALSE,
  message = FALSE
)
```

## Vision

Use more detailed Ag and soils data to improve predictive models of lake TP, TN, and Nitrate.

## Potential predictor variables

* LAGOS
    * Lake depth
    * IWS area
    * IWS/Lake area
* Cropland Data Layer
    * IWS pasture types (forage or not)
    * IWS specific crops (corn, wheat, etc.)
    * IWS crop frequency/rotation
* gSSURGO
    * IWS wetland potential (as a proxy for tile drainage)
    * IWS soil organic carbon
    * IWS root zone depth
    * IWS lithology (sand %, clay %, etc.)
* USGS
    * IWS from county - manure, fertilizer, and deposition of N,P

## Research questions

* Is ag intensification related to changes in lake water quality?
    * Maybe areas with reduced intensification have been improving?
* Do ag conservation practices affect lake water quality?
* Others?

## Timeline

## Issues

* Availability of data products through time is highly variable. How to align or decide to treat properties as constant?

```{r maps, echo=FALSE}
knitr::include_graphics("../../fig/rmd-hi_ag_iws_w_ep-1.png")
```

```{r echo=FALSE}
cdl_key <- read.csv("data/cdl/cdl_key.csv", stringsAsFactors = FALSE)
```

```{r lagos_v_cdl_v_usgs, echo=FALSE}
# tp vs lagos ag, cdl ag, usgs P inputs

# ---- setup ----

library(dplyr)
library(ggplot2)
library(magrittr)
library(LAGOSNE)
library(cowplot)
library(sf)

lg          <- lagosne_load("1.087.1")
ep          <- readRDS("data/ep.rds")
cdl_summary <- read.csv("data/cdl/cdl_summary.csv", stringsAsFactors = FALSE)
usgs        <- readRDS("data/usgs/usgs.rds")

lg_ep <- mutate(lg$iws.lulc, 
                lg_ag = rowSums(cbind(iws_nlcd2011_pct_81, 
                                      iws_nlcd2011_pct_82), na.rm = TRUE)) %>%
  select(lagoslakeid, lg_ag) %>%
  left_join(ep, by = "lagoslakeid") %>%
  filter(!is.na(tp))

cdl_ep <- filter(cdl_summary, variable == "ag") %>%
  left_join(
    filter(ep, !is.na(tp)), by = c("llid" = "lagoslakeid")) %>%
  mutate(cdl_ag = value)

usgs_ep <- filter(usgs, !is.na(tp))

# ---- plotting ----

plot_grid(
ggplot() +
  geom_point(data = lg_ep, aes(x = lg_ag, y = tp)) +
  xlab("LAGOS (NLCD 2011) Ag (%)"),
ggplot() +
  geom_point(data = cdl_ep, aes(x = cdl_ag, y = tp)) +
  xlab("CDL Ag (%)"),
ggplot() + 
  geom_point(data = usgs_ep, aes(x = phosphorus_input, y = tp)) + 
  scale_x_log10() + 
  xlab("log(P Input)"))

```

### 2018-08-17 README.Rmd
compare with 2006 not 2011 nlcd

@@
 lg_ep <- mutate(lg$iws.lulc, 
-                lg_ag = rowSums(cbind(iws_nlcd2011_pct_81, 
-                                      iws_nlcd2011_pct_82), na.rm = TRUE)) %>%
+                lg_ag = rowSums(cbind(iws_nlcd2006_pct_81, 
+                                      iws_nlcd2006_pct_82), na.rm = TRUE)) %>%
   select(lagoslakeid, lg_ag) %>%
@@
   geom_point(data = lg_ep, aes(x = lg_ag, y = tp)) +
-  xlab("LAGOS (NLCD 2011) Ag (%)"),
+  xlab("LAGOS (NLCD 2006) Ag (%)"),
 ggplot() +

### 2018-10-02 figures/01_county_extent.Rmd
add makefile figure infrastructure

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
```

```{r read_explore_chunk, echo=FALSE, eval=TRUE}
knitr::read_chunk("../scripts/explore_lagos_ag.R")
```

```{r lagos_setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE}

```

```{r mendota_oneida, echo=FALSE, message=TRUE, eval=FALSE}
llids <- lake_info(lg, 
                   name = c("Lake Mendota", "Oneida Lake"), 
                   state = c("Wisconsin", "New York"))$lagoslakeid

cat(paste(c("Lake Mendota", "Oneida Lake")[which(llids %in% ep$lagoslakeid)], "is included in the hi ag sites."))
```

<!-- * Find counties that intersect large numbers of hi ag iws with tp + tn data -->

```{r county_extent, eval=TRUE, echo=FALSE, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (> 40%) and water quality data in LAGOS measured at > 3 sampling events between 1995 and 2005.", warning=FALSE, fig.width = 5.5, fig.height = 3}

```

### 2018-10-02 manuscript/figures.Rmd
add makefile figure infrastructure

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6, dev = c("pdf"))
```

```{r fig.cap="Figure 1: Counties that overlap lake watersheds with high agricultural land-use cover that have water quality data in LAGOS.", echo = FALSE, fig.width = 1, out.height = "4in"}
knitr::include_graphics("../figures/01_county_extent.pdf")
```

### 2018-10-02 scripts/explore_lagos_ag.R

@@ -14,7 +14,7 @@ library(ggridges)
 library(tidyr)
 library(ggExtra)
 
-ep <- readRDS("lagos_ag/data/ep.rds")
+ep <- readRDS("../data/ep.rds")
 gdb_path <- path.expand("~/.local/share/LAGOS-GIS/lagos-ne_gis.gpkg")
 # st_layers(gdb_path)
 layer_name <- "COUNTY"
@@ -67,8 +67,8 @@ get_iws_polygon <- function(lagoslakeid, crs){
 }
 
 lg          <- lagosne_load("1.087.1")
-iws_lulc    <- readRDS("lagos_ag/data/iws_lulc.rds")
-county_lulc <- readRDS("lagos_ag/data/county_lulc.rds")
+iws_lulc    <- readRDS("../data/iws_lulc.rds")
+county_lulc <- readRDS("../data/county_lulc.rds")
 
 iws_vs_county_ag <- iws_lulc %>%
   left_join(dplyr::select(lg$locus, lagoslakeid, county_zoneid))  %>%
@@ -156,7 +156,7 @@ plot_grid(
     NULL,
   ncol = 1)
 
-# ---- hi_ag_iws_w_ep ----
+# ---- county_extent ----
 # counties that overlap hi ag iws with ep data
 # setwd("_episodes_rmd")
 
@@ -181,10 +181,11 @@ hi_ag_iws_w_ep$county <- hi_ag_iws_w_ep$county[
 ggplot() +
   geom_sf(data = state_intersects) +
   geom_sf(data = hi_ag_iws_w_ep$county, aes(fill = n_iws)) +
-  ggtitle(paste0("# of overlappling IWS with > 40% ag & epi nutrient data \n
-          where > 4 measurements between 1995 and 2005")) +
-  theme(title = element_text(size = 10))
+  # ggtitle(paste0("# of overlappling IWS with > 40% ag & epi nutrient data \n
+          # where > 4 measurements between 1995 and 2005")) +
+  theme(title = element_text(size = 10)) +
+  labs(fill = paste0("# lakes \n (", nrow(ep), " total)"))
 
 # mapview::mapview(hi_ag_iws_w_ep$county, zcol = "n_iws")
 
-cat(paste0(nrow(ep), " total lakes"))
+# cat(paste0(nrow(ep), " total lakes"))

### 2018-10-02 manuscript/figures.Rmd
fix captions and make paths

@@
 
-```{r fig.cap="Figure 1: Counties that overlap lake watersheds with high agricultural land-use cover that have water quality data in LAGOS.", echo = FALSE, fig.width = 1, out.height = "4in"}
-knitr::include_graphics("../figures/01_county_extent.pdf")
+```{r county_extent, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (greater than 40 percent) and water quality data in LAGOS from at least 3 sampling events between 1995 and 2005.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/01_county_extent-1.pdf")
 ```

### 2018-10-02 scripts/explore_lagos_ag.R

@@ -156,7 +156,7 @@ plot_grid(
     NULL,
   ncol = 1)
 
-# ---- county_extent ----
+# ---- 01_county_extent ----
 # counties that overlap hi ag iws with ep data
 # setwd("_episodes_rmd")
 

### 2018-10-03 tables/01_predictors.Rmd
add predictors table

---
output:
  pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
```

```{r summary_table, eval=TRUE}
library(kableExtra)
library(dplyr)
library(magrittr)

# setwd("tables")
dt <- readRDS("../data/dt.rds") %>%
  dplyr::select(tp:clay_pct, -hu4_zoneid) %>%
  tidyr::gather(key = "variable") %>%
  group_by(variable) %>%
  mutate(value = as.numeric(value)) %>%
  mutate(q10 = quantile(value, probs = c(0.1), na.rm = TRUE),
         q50 = quantile(value, probs = c(0.5), na.rm = TRUE),
         q90 = quantile(value, probs = c(0.9), na.rm = TRUE), 
         ratio = q90 / q10, 
         n = sum(!is.na(value), na.rm = TRUE)) %>%
  dplyr::distinct(signif(q10, 2), signif(q50, 2), signif(q90, 2), ratio, n) %>%
  dplyr::select(variable, 
         q10 = `signif(q10, 2)`,
         q50 = `signif(q50, 2)`, 
         q90 = `signif(q90, 2)`,
         q10_q90_ratio = ratio,
         n) %>%
  left_join(readRDS("../data/dt_units.rds"), by = "variable") %>%
  dplyr::select(variable, units, everything())

knitr::kable(dt, digits = 0, format = "markdown") 
#%>%
 # add_header_above(c(" ", " ", Ranges = 3, " ", " "))
```

### 2018-10-03 figures/01_county_extent.Rmd
caption and number cleanup

@@
 ---
-title: "Figures"
-output:
-  pdf_document:
-    fig_caption: yes
+output: pdf_document
+header-includes: 
+  - \pagenumbering{gobble}
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
+knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
 ```
@@
 ```{r read_explore_chunk, echo=FALSE, eval=TRUE}
+# setwd("figures")
 knitr::read_chunk("../scripts/explore_lagos_ag.R")
@@
 
-```{r county_extent, eval=TRUE, echo=FALSE, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (> 40%) and water quality data in LAGOS measured at > 3 sampling events between 1995 and 2005.", warning=FALSE, fig.width = 5.5, fig.height = 3}
+```{r 01_county_extent, eval=TRUE, echo=FALSE, fig.width = 5.5, fig.height = 3}
 

### 2018-10-03 README.Rmd
fix figure link
link to figures and tables

@@
 
-## Vision
+Code and data for:
 
-Use more detailed Ag and soils data to improve predictive models of lake TP, TN, and Nitrate.
+## The effect of crop type, fertilizer, and manure applications on lake nutrients in agriculture watersheds at regional scales
+
+> Journal Target: Ecosystems
+
+### Products
+
+Figures: [manuscript/figures.pdf](manuscript/figures.pdf)
+
+Tables: [manuscript/tables.pdf](manuscript/tables.pdf)
 
@@
 ```{r maps, echo=FALSE}
-knitr::include_graphics("../../fig/rmd-hi_ag_iws_w_ep-1.png")
+knitr::include_graphics("figures/rmd-hi_ag_iws_w_ep-1.png")
 ```
@@
 
-```{r lagos_v_cdl_v_usgs, echo=FALSE}
+```{r lagos_v_cdl_v_usgs, echo=FALSE, eval=FALSE}
 # tp vs lagos ag, cdl ag, usgs P inputs

### 2018-10-08 figures/02_hierarchical_demo.Rmd
towards a hierarchical demo

---
output: pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
```

```{r hu4_n, echo=FALSE, message=TRUE, eval=FALSE}
library(kableExtra)
library(dplyr)
library(magrittr)

library(LAGOSextra)
library(sf)
library(ggplot2)

# setwd("tables")
ids <- test <- readRDS("../data/dt.rds") %>%
  group_by(hu4_zoneid) %>% 
  tally()

hu4 <-  LAGOSextra::query_gis("HU4", "ZoneID", ids$hu4_zoneid) %>%
  st_cast(to = "MULTIPOLYGON") %>%
  left_join(ids, by = c("ZoneID" = "hu4_zoneid"))

ggplot() +
  geom_sf(data = hu4, aes(fill = n)) +
  theme_minimal()

# hist(hu4$n, n = 20)
# table(as.character(dt$hu4_zoneid))
```

```{r }

```

### 2018-10-11 figures/02_hierarchical_demo.Rmd
finish out hierarchical demo figure

@@
 
-```{r hu4_n, echo=FALSE, message=TRUE, eval=FALSE}
+```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
 library(kableExtra)
 library(dplyr)
+library(tidyr)
 library(magrittr)
 
+library(LAGOSNE)
 library(LAGOSextra)
@@
 library(ggplot2)
+library(cowplot)
 
-# setwd("tables")
+# setwd("figures")
 ids <- test <- readRDS("../data/dt.rds") %>%
@@
 
-ggplot() +
-  geom_sf(data = hu4, aes(fill = n)) +
-  theme_minimal()
-
 # hist(hu4$n, n = 20)
@@
 
-```{r }
+```{r 02_hierarchical_demo, fig.height=3}
+lg <- lagosne_load("1.087.1")
 
+dt <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
+                summarize(
+                  group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
+                           lagoslakeid), 
+                  tp = median(tp, na.rm = TRUE), 
+                  chla = median(chla, na.rm = TRUE))
+                ) %>%
+  tidyr::drop_na()
+
+# hist(as.vector(table(dt$hu4_zoneid)))  
+good_hu4s <- group_by(dt, hu4_zoneid) %>% 
+  tally() %>%
+  dplyr::filter(n > 220)  
+dt <- dplyr::filter(dt, hu4_zoneid %in% good_hu4s$hu4_zoneid)
+dt <- dplyr::filter(dt, tp < 500 & chla < 150)
+
+plot_grid(
+  ggplot(data = dt, aes(x = tp, y = chla, color = hu4_zoneid)) + 
+    geom_point(alpha = 0.5) +
+    geom_smooth(method = lm, se = FALSE) +
+    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
+                color = "black", linetype = "dashed") +
+    # scale_y_log10() + scale_x_log10() +
+    theme(legend.position = ""),
+  ggplot() +
+    geom_sf(data = hu4, aes(fill = n)) +
+    theme_minimal() + 
+    theme(legend.position = "bottom"), 
+  rel_heights = c(0.6, 1), labels = "AUTO"
+)
 ```

### 2018-10-11 figures/03_wetland_potential.Rmd
add 03_wetland_potential

---
output: pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
```

```{r 03_wetland_potential, fig.height=3, echo=FALSE}
library(kableExtra)
library(dplyr)
library(tidyr)
library(magrittr)

library(LAGOSNE)
library(sf)
library(ggplot2)
library(cowplot)
library(concaveman)

states <- st_as_sf(maps::map("state", fill = TRUE, plot = FALSE))
ep      <- coordinatize(readRDS("../data/ep.rds"))
ep_bbox <- concaveman(ep)$polygons
states  <- states[unlist(lapply(st_intersects(states, ep_bbox), 
                               function(x) length(x) > 0)),]

# setwd("figures")
gssurgo_raw <- readRDS("../data/gssurgo/gssurgo.rds")$res
gssurgo_raw$llid <- as.integer(gssurgo_raw$llid)
lg <- lagosne_load("1.087.1")

gssurgo <- left_join(gssurgo_raw, 
                         dplyr::select(lg$locus, 
                         lagoslakeid, nhd_long, nhd_lat), 
                         by = c("llid" = "lagoslakeid"))
gssurgo <- left_join(gssurgo, 
            dplyr::select(lg$iws.conn, 
              wl_dissolved = iws_wl_allwetlandsdissolved_overlapping_area_pct, 
              wl_undissolved = iws_wl_allwetlandsundissolved_overlapping_area_pct,
              lagoslakeid), by = c("llid" = "lagoslakeid")) %>% 
          mutate(diff = wetland_potential - wl_dissolved) 
gssurgo <- coordinatize(gssurgo)

plot_grid(
  ggplot(data = gssurgo) +
    geom_point(aes(x = wetland_potential, 
                   y = wl_dissolved, color = diff > 30)) + 
    xlab("gssurgo wetland potential (%)") + ylab("lagos nwi wetland pct (%)") + 
    labs(color = "difference (%)") +
    geom_abline(slope = 1, intercept = 0) + 
    theme(legend.position = "none"),
  ggplot() + 
    geom_sf(data = states, fill = "white") +
    geom_sf(data = gssurgo, aes(color = diff > 30), size = 0.8) +
    theme_minimal() +
    theme(legend.position = "none"), labels = "AUTO"
)

```

### 2018-10-11 manuscript/figures.Rmd
finish out hierarchical demo figure
add 03_wetland_potential

@@
 ```
+
+```{r hierarchical_demo, fig.cap = "A) Global (dashed line) and regional (solid lines) fits to the relationship between lake chlorophyll and lake phosphorus.
+B) Number of lakes per region.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/02_hierarchical_demo-1.pdf")
+```
+
+```{r wetland_potential, fig.cap = "A) gSSURGO wetland potential versus National Wetlands Inventory cover.
+B) Locations of lakes where these number differ by more than 30 percent.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/03_wetland_potential-1.pdf")
+```

### 2018-10-26 figures/04_nlcd-versus-cdl.Rmd
towards an nlcd versus cdl comparison

---
output: pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
```

```{r 04_nlcd-versus-cdl, fig.height=3, echo=FALSE}
library(LAGOSNE)
library(ggplot2)
library(HydroData)
library(dplyr)
library(tidyr)

cdl <- read.csv("../data/cdl/cdl_summary.csv", stringsAsFactors = FALSE) %>%
  dplyr::select(lagoslakeid = llid, cdl_ag_99 = ag, cdl_pasture_81 = pasture)

lg  <- lagosne_load("1.087.1")$iws.lulc %>%
  dplyr::filter(lagoslakeid %in% cdl$lagoslakeid) %>%
  dplyr::select(lagoslakeid, matches(".*nlcd2011.*")) %>%
  dplyr::select(lagoslakeid, 
                nlcd_pasture_81 = iws_nlcd2011_pct_81, 
                nlcd_rowcrop_82 = iws_nlcd2011_pct_82) %>% 
  dplyr::mutate(nlcd_ag_99 = nlcd_pasture_81 + nlcd_rowcrop_82)

res <- dplyr::left_join(cdl, lg, by = c("lagoslakeid")) %>%
  tidyr::gather(key = "variable", value = "value", -lagoslakeid) %>%
  separate(variable, c("source", "variable", "code")) %>%
  group_by(lagoslakeid) %>%
  tidyr::spread(source, value) %>%
  dplyr::filter(variable != "rowcrop")

ggplot(data = res, aes(x = nlcd, y = cdl)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  facet_wrap(~variable)
```

### 2018-10-26 figures/04_nlcd-versus-cdl.Rmd
include pasture in cdl total ag

@@
 library(tidyr)
-
+# setwd("data")
 cdl <- read.csv("../data/cdl/cdl_summary.csv", stringsAsFactors = FALSE) %>%
@@
   geom_abline(intercept = 0, slope = 1) +
-  facet_wrap(~variable)
+  facet_wrap(~variable) +
+  theme_minimal()
 ```

### 2018-10-26 scripts/01_process_cdl.R

@@ -16,7 +16,7 @@ cdl_summary <- function(llid){
   
   cdl_table <- as_data_frame(table(values(r)), stringsAsFactors = FALSE) %>%
     mutate(code = as.integer(Var1)) %>%
-    select(-Var1) %>%
+    dplyr::select(-Var1) %>%
     left_join(cdl_key, by = "code") 
   
   cdl_cat <- cdl_table %>%

### 2018-10-26 scripts/99_make_cdl_key.R

@@ -1,7 +1,7 @@
 library(cdlTools)
 library(tidyr)
-library(dplyr)
-library(magrittr)
+suppressMessages(library(dplyr))
+suppressMessages(library(magrittr))
 
 cdl_key <- data.frame(code = 0:255, description = cdlTools::updateNamesCDL(0:255),
                       stringsAsFactors = FALSE)
@@ -35,7 +35,7 @@ aggregate_categories <- function(cdl_key){
 
   res <- mutate(res,
                 is_ag = if_else(category %in% c("corn", "wheat", "other ag",
-                                          "soybeans", "mixed crop", "forage"), "ag", 
+                                          "soybeans", "mixed crop", "forage", "pasture"), "ag", 
                                 "nonag"))
   
   res <- mutate(res, is_forage = case_when(

### 2018-10-31 manuscript/figures.Rmd
towards an nlcd versus cdl comparison
add figure legend
towards systematic census data pull

@@
 ```
+
+```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD derived and CDL derived total watershed ag and watershed pasture cover.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
+```
+
+```{r cafos, fig.cap = "CAFOS", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/05_cafos-1.pdf")
+```

### 2018-10-31 scripts/00_get_census.R

@@ -21,12 +21,69 @@ iws <- LAGOSextra::query_wbd(ep$lagoslakeid, utm = FALSE)
 # mapview::mapview(dplyr::filter(iws, lagoslakeid == 34352))
 iws <- st_make_valid(iws)
 
+source_desc = "CENSUS"
+year <- 2007
+state_alpha <- "MI"
+agg_level_desc <- "COUNTY"
+census_key <- data.frame(commodity = c("CATTLE", "CATTLE", 
+                                       "CATTLE", "CHICKENS", "HOGS"), 
+                         domain = c("TOTAL", "SALES OF CATTLE, INCL CALVES", 
+                                    "INVENTORY OF MILK COWS", "TOTAL", "TOTAL"),
+                         domaincat_desc = c(NA, "SALES OF CATTLE, INCL CALVES: (500 OR MORE HEAD)", 
+                                            "INVENTORY OF MILK COWS: (500 OR MORE HEAD)", NA, NA),
+                         unit_desc = c(NA, "OPERATIONS", "OPERATIONS", "OPERATIONS", NA),
+                         short_desc = c("CATTLE, INCL CALVES - INVENTORY", NA, NA, NA, NA),
+                         ref_period_desc = c(NA, NA, NA, "YEAR", "YEAR"), 
+                         freq_desc = c(NA, NA, NA, "ANNUAL", NA),
+                         stringsAsFactors = FALSE)
+
+test <- apply(census_key[1:2,], 1, function(x){
+  # x <- census_key[4,]
+  params <- list("source_desc" = source_desc, 
+                 "commodity_desc" = as.character(x["commodity"]), 
+                 "year" = year, 
+                 "state_alpha" = state_alpha, 
+                 "domain_desc" = as.character(x["domain"]), 
+                 "domaincat_desc" = as.character(x["domaincat_desc"]),
+                 "unit_desc" = as.character(x["unit_desc"]),
+                 "short_desc" = as.character(x["short_desc"]), 
+                 "ref_period_desc" = as.character(x["ref_period_desc"]),
+                 "freq_desc" = as.character(x["freq_desc"]),
+                 "agg_level_desc" = agg_level_desc, 
+                 key = key)
+  params <- params[!is.na(params)]
+  raw <- nassqs(params)
+  raw
+  })
+
+
 params <- list("source_desc" = "CENSUS",
-               "commodity_desc" = c("CATTLE"),
-               "year" = 2007,
-               "domain_desc" = "TOTAL",
[…]

### 2018-10-31 scripts/rnassqs.R

@@ -19,7 +19,7 @@ params <- list("source_desc" = "CENSUS",
                "commodity_desc"="WHEAT",
                "year"=2007,
                "state_alpha"="MI",
-               "domain_des" = "TOTAL",
+               "domain_desc" = "TOTAL",
                "agg_level_desc" = "COUNTY",
                "unit_desc" = "ACRES",
                key = key)
@@ -56,7 +56,7 @@ params <- list("source_desc" = "CENSUS",
                "commodity_desc"="CATTLE",
                "year" = 2007,
                "state_alpha" = "MI",
-               "domain_des" = "TOTAL",
+               "domain_desc" = "TOTAL",
                "agg_level_desc" = "COUNTY",
                # "unit_desc" = "ACRES",
                key = key)

### 2018-11-02 figures/05_cafos.Rmd
infrastucture for plotting all census vars

---
output: pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
source("../scripts/utils.R")
```

```{r 05_cafos, fig.height=3, echo=FALSE, eval=TRUE}
library(LAGOSNE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(concaveman)
library(sf)
# setwd("data")

states <- st_as_sf(maps::map("state", fill = TRUE, plot = FALSE))
ep      <- coordinatize(readRDS("../data/ep.rds"))
ep_bbox <- concaveman(ep)$polygons
states  <- states[unlist(lapply(st_intersects(states, ep_bbox), 
                               function(x) length(x) > 0)),]

animals <- readRDS("../data/census/census.rds")
st_geometry(animals) <- NULL
animals <- left_join(ep, animals, by = "lagoslakeid")
animals <- dplyr::filter(animals, lagoslakeid != 401)

# mapview::mapview(states) +
#   mapview::mapview(animals, zcol = "hog_sales")

cowplot::plot_grid(
ggplot() +
  geom_sf(data = states) +
  geom_sf(data = animals, aes(color = hog_sales)) +
  theme(title = element_text(size = 10)) +
  labs(color = paste0("hog \n operations")),
ggplot() +
  geom_sf(data = states) +
  geom_sf(data = animals, aes(color = cattle_sales)) +
  theme(title = element_text(size = 10)) #+
  #labs(color = paste0("hog \n operations"))
)

# ---- debug ----
# library(mapview)
# llid <- 457
# t_iws <- dplyr::filter(iws, lagoslakeid == llid)
# t_county <- st_transform(county_sf(), st_crs(t_iws))
# t_county <- t_county[unlist(lapply(
#   st_intersects(t_county, t_iws), function(x) length(x) > 0)), ]
# t_raw <- animals_raw[unlist(lapply(
#   st_intersects(animals_raw, t_iws), function(x) length(x) > 0)), ]
# 
# mapview(t_raw) +
#   mapview(t_iws)
```

### 2018-11-02 scripts/00_get_census.R

@@ -18,7 +18,6 @@ Sys.setenv(NASSQS_TOKEN = key)
 # ---- census_get ----
 ep  <- readRDS("data/ep.rds")
 iws <- LAGOSextra::query_wbd(ep$lagoslakeid, utm = FALSE)
-# mapview::mapview(dplyr::filter(iws, lagoslakeid == 34352))
 iws <- st_make_valid(iws)
 states <- state_sf()[unlist(
   lapply(st_intersects(state_sf(), coordinatize(ep)), 
@@ -96,12 +95,27 @@ if(!file.exists("data/census/census_raw.rds")){
 }
 
 animals_raw <- readRDS("data/census/census_raw.rds")
-animals_raw <- dplyr::bind_rows(animals_raw)
-animals_raw <- mutate(animals_raw, state = tolower(state_name),
+animals_tidy <- dplyr::bind_rows(animals_raw)
+animals_tidy <- mutate(animals_tidy, state = tolower(state_name),
              county = gsub("\\.", "", gsub(" ", "", tolower(county_name))))
-animals_raw <- mutate_at(animals_raw, vars(matches("cattle|chicken|hog")), funs(as.numeric))
-animals_raw <- left_join(animals_raw, county_sf(), by = c("state", "county"))
-st_geometry(animals_raw) <- animals_raw$geometry
+clean_numeric <- function(x){
+  x <- gsub(",", "", x)
+  as.numeric(x)
+}
+animals_tidy <- mutate_at(animals_tidy, vars(matches("cattle|chicken|hog")), 
+                          funs(clean_numeric))
+# animals_tidy <- mutate_at(animals_tidy, vars(matches("cattle|chicken|hog")), 
+#                           funs(tidyr::replace_na(., 0)))
+animals_tidy <- left_join(animals_tidy, county_sf(), 
+                          by = c("state", "county"))
+st_geometry(animals_tidy) <- animals_tidy$geometry
+saveRDS(animals_tidy, "data/census/census_tidy.rds")
+
+# test <- dplyr::filter(animals_raw, state == "minnesota")
+# test2 <- dplyr::filter(iws, lagoslakeid == 401)
+# mapview::mapview(test, zcol = "hog_sales") +
+#   mapview::mapview(test2) +
+#   mapview::mapview(coordinatize(ep)) 
 
 # animals_raw$area <- units::set_units(
 #   st_area(animals_raw$geometry), "acres")
[…]

### 2018-11-02 scripts/utils.R

@@ -56,18 +56,31 @@ state_key <- function(){
              state_name = datasets::state.name)
 }
 
+# kg per ha is false, kg is true
 interp_to_iws <- function(raw, varname = "total", outname, is_extensive = TRUE){
-  # raw <- animals_raw
-  # varname = "nitrogen_livestock_manure"
-  iws <- iws[sapply(st_intersects(iws, raw), length) != 0,]
+  # raw <- animals_tidy
+  # varname = "hog_sales"
+  # is_extensive = TRUE
+  print(varname)
+  
+  # raw <- dplyr::filter(animals_raw, county_name %in% c("LYON", "MURRAY", "PIPESTONE", "LINCOLN", "REDWOOD", "YELLOW MEDICINE") & state == "minnesota")
+  
+  raw <- raw[!is.na(raw[,varname])[,1],]
+  raw <- raw[
+      unlist(lapply(st_intersects(raw, iws), function(x) length(x) > 0)),]
+  iws_sub <- iws[sapply(st_intersects(iws, raw), length) != 0,]
+  # mapview::mapview(raw, zcol = "hog_sales") +
+  #   mapview::mapview(iws)
+  # median(raw$hog_sales)
   
   # st_interpolate_aw
   iws_interp <- suppressWarnings(
-    st_interpolate_aw(raw[,varname], iws,
+    st_interpolate_aw(raw[,varname], iws_sub,
                       extensive = is_extensive)) # kg per ha is false, kg is true
   iws_interp <- data.frame(outname = iws_interp[,varname],
-                           lagoslakeid = iws$lagoslakeid,
+                           lagoslakeid = iws_sub$lagoslakeid,
                            stringsAsFactors = FALSE)
+  
   names(iws_interp)[1] <- outname
   iws_interp <- dplyr::select(iws_interp, lagoslakeid, everything())
   iws_interp <- dplyr::rename(iws_interp, geometry = outname.geometry)

### 2018-11-05 figures/05_cafos.Rmd
cleanup animal plots

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
+knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 7, fig.height = 7)
 source("../scripts/utils.R")
@@
 
-```{r 05_cafos, fig.height=3, echo=FALSE, eval=TRUE}
+```{r 05_cafos, echo=FALSE, eval=TRUE}
 library(LAGOSNE)
@@
 library(sf)
+library(cowplot)
 # setwd("data")
@@
 animals <- left_join(ep, animals, by = "lagoslakeid")
-animals <- dplyr::filter(animals, lagoslakeid != 401)
+animals <- dplyr::filter(animals, !(lagoslakeid %in% c(401, 6076)))
 
@@
 
+theme_opts <- theme(legend.position = "none", 
+                    axis.text = element_blank(), 
+                    axis.ticks = element_blank(), 
+                    title = element_text(size = 8), 
+                    plot.margin = unit(c(0, -2, 0, -2), "cm"))
+
 cowplot::plot_grid(
@@
       geom_sf(data = states) +
-  geom_sf(data = animals, aes(color = hog_sales)) +
-  theme(title = element_text(size = 10)) +
+      geom_sf(data = 
+                dplyr::filter(animals, ), 
+              aes(color = hog_sales), 
+              size = 0.2, alpha = 0.8) +
+      coord_sf(datum = NA) + 
+      theme_minimal() + theme_opts +
+      ggtitle("hog operations") +
       labs(color = paste0("hog \n operations")),
@@
       geom_sf(data = states) +
-  geom_sf(data = animals, aes(color = cattle_sales)) +
-  theme(title = element_text(size = 10)) #+
-  #labs(color = paste0("hog \n operations"))
-)
+      geom_sf(data = 
+                dplyr::filter(animals, cattle_sales <= 6 & 
+                                !is.na(cattle_sales)), 
+              aes(color = cattle_sales), 
+              size = 0.2, alpha = 0.8) +
+      coord_sf(datum = NA) + 
+      ggtitle("cattle operations") +
+      theme_minimal() + theme_opts,
+    ggplot() +
+      geom_sf(data = states) +
+      geom_sf(data = 
+                dplyr::filter(animals, !is.na(cattle_dairy)), 
+              aes(color = cattle_dairy), 
+              size = 0.2, alpha = 0.8) +
+      coord_sf(datum = NA) + 
+      theme_minimal() + theme_opts +
+      ggtitle("dairy operations") +
+      labs(color = paste0("dairy \n operations")),
+    ggplot() +
+      geom_sf(data = states) +
+      geom_sf(data = 
+                dplyr::filter(animals, chicken_sales <= 30), 
+              aes(color = chicken_sales), 
+              size = 0.2, alpha = 0.8) +
+      coord_sf(datum = NA) + 
+      theme_minimal() + theme_opts +
+      ggtitle("chicken operations") +
+      labs(color = paste0("chicken \n operations")),
+    ggplot() +
+      geom_sf(data = states) +
+      geom_sf(data = 
+                dplyr::filter(animals, cattle_total <= 20000), 
+              aes(color = cattle_total), 
+              size = 0.2, alpha = 0.8, pch = 19) +
+      coord_sf(datum = NA) + 
+      theme_minimal() + theme_opts +
+      ggtitle("cattle head") +
+      labs(color = paste0("cattle \n head")), 
+    ncol = 1)
 
@@
 # library(mapview)
+# mapview(animals, zcol = "cattle_total")
 # llid <- 457

### 2018-11-05 figures/01_county_extent.Rmd
pull ep from 2000-2010

@@
 
-```{r read_explore_chunk, echo=FALSE, eval=TRUE}
-# setwd("figures")
-knitr::read_chunk("../scripts/explore_lagos_ag.R")
-```
+```{r lagos_setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE}
+# setwd("_episodes_rmd")
+library(vapour)
+library(LAGOSNE)
+library(magrittr)
+library(dplyr)
+library(lme4)
+library(sf)
+library(units)
+library(merTools)
+library(ggplot2)
+library(cowplot)
+library(ggridges)
+library(tidyr)
+library(ggExtra)
 
-```{r lagos_setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE}
+ep <- readRDS("data/ep.rds")
+gdb_path <- path.expand("~/.local/share/LAGOS-GIS/lagos-ne_gis.gpkg")
+# st_layers(gdb_path)
+layer_name <- "COUNTY"
+county <- st_read(gdb_path, layer_name, quiet = TRUE)
+states <- st_as_sf(maps::map("state", fill = TRUE, plot = FALSE))
+
+pull_ag_polygons <- function(hi_ag_iws, county){
+  layer_name <- "IWS"
+  crs <- st_crs(county)
+  # system(paste("ogrinfo -so", gdb_path, layer_name))
+  query      <- paste0("SELECT * FROM ", layer_name,
+                       " WHERE lagoslakeid IN ('",
+                       paste0(hi_ag_iws$lagoslakeid,
+                              collapse = "', '"), "');")
+  iws <- st_as_sfc(vapour_read_geometry(gdb_path, sql = query))
+  iws <- st_sf(vapour_read_attributes(gdb_path, sql = query),
+               geometry = iws, crs = crs)
+  iws <- st_zm(iws)
+  iws <- st_cast(iws, "MULTIPOLYGON") # solves error: Unknown WKB type 12
+
+  ## filter counties that intersect hi ag iws
+  hi_ag_counties_intersects <- st_intersects(county, iws)
+  hi_ag_counties_intersects <- unlist(lapply(hi_ag_counties_intersects,
+                                             function(x) length(x > 0)))
+  county <- county[hi_ag_counties_intersects > 0,]
+
+  ## get number of counties intersecting hi ag iws
+  hi_ag_iws_intersects <- st_intersects(iws, county)
+  hi_ag_iws_intersects <- unlist(lapply(hi_ag_iws_intersects,
+                                        function(x) length(x > 0)))
+
+  list(iws = iws,
+       county = county,
+       counties_intersects = hi_ag_counties_intersects,
+       iws_intersects = hi_ag_iws_intersects)
+}
+
+get_iws_polygon <- function(lagoslakeid, crs){
+  layer_name <- "IWS"
+  # system(paste("ogrinfo -so", gdb_path, layer_name))
+  query      <- paste0("SELECT * FROM ", layer_name,
+                       " WHERE lagoslakeid IN ('",
+                       paste0(lagoslakeid,
+                              collapse = "', '"), "');")
+  iws <- st_as_sfc(vapour_read_geometry(gdb_path, sql = query))
+  iws <- st_sf(vapour_read_attributes(gdb_path, sql = query),
+               geometry = iws, crs = crs)
+  iws <- st_zm(iws)
+  st_cast(iws, "MULTIPOLYGON") # solves error: Unknown WKB type 12
+}
+
+lg          <- lagosne_load("1.087.1")
+iws_lulc    <- readRDS("data/iws_lulc.rds")
+county_lulc <- readRDS("data/county_lulc.rds")
+
+iws_vs_county_ag <- iws_lulc %>%
+  left_join(dplyr::select(lg$locus, lagoslakeid, county_zoneid))  %>%
+  left_join(dplyr::select(county_lulc, county_zoneid:county_ag_2011_pcent))
 
@@
 ```{r 01_county_extent, eval=TRUE, echo=FALSE, fig.width = 5.5, fig.height = 3}
+# counties that overlap hi ag iws with ep data
+# setwd("_episodes_rmd")
 
+hi_ag_iws_w_ep <- pull_ag_polygons(ep, county)
+
+n_iws <- unlist(lapply(
+  st_intersects(hi_ag_iws_w_ep$county, hi_ag_iws_w_ep$iws),
+  function(x) length(x)))
+
+hi_ag_iws_w_ep$county$n_iws <- n_iws
+
+states <- st_transform(states, st_crs(hi_ag_iws_w_ep$county))
+state_intersects <- st_intersects(states, hi_ag_iws_w_ep$county)
+state_intersects <- states[unlist(lapply(
+  state_intersects,
+  function(x) length(x) > 3)),]
+
+hi_ag_iws_w_ep$county <- hi_ag_iws_w_ep$county[
+  unlist(lapply(st_intersects(hi_ag_iws_w_ep$county, state_intersects), function(x) length(x) > 0)),]
+
+# color by number of iws intersections
+ggplot() +
+  geom_sf(data = state_intersects) +
+  geom_sf(data = hi_ag_iws_w_ep$county, aes(fill = n_iws)) +
+  # ggtitle(paste0("# of overlappling IWS with > 40% ag & epi nutrient data \n
+          # where > 4 measurements between 1995 and 2005")) +
+  theme(title = element_text(size = 10)) +
+  labs(fill = paste0("# lakes \n (", nrow(ep), " total)"))
+
+# mapview::mapview(hi_ag_iws_w_ep$county, zcol = "n_iws")
+
+# cat(paste0(nrow(ep), " total lakes"))
 ```

### 2018-11-05 scripts/00_get_ep.R

@@ -4,11 +4,12 @@ suppressMessages(library(magrittr))
 
 source("scripts/utils.R")
 
+# setwd("../")
 lg           <- lagosne_load("1.087.1")
 iws_lulc     <- readRDS("data/iws_lulc.rds")
 county_lulc  <- readRDS("data/county_lulc.rds")
-date_start   <- as.Date("1995-01-01")
-date_end     <- as.Date("2005-01-01")
+date_start   <- as.Date("2000-01-01")
+date_end     <- as.Date("2010-01-01")
 min_sample_n <- 3
 ag_cutoff    <- 0.4
 min_state_n  <- 4
@@ -53,20 +54,20 @@ ep_nutr <- lg$epi_nutr %>%
 iws_vs_county_ag <- iws_lulc %>%
   left_join(dplyr::select(lg$locus, lagoslakeid, county_zoneid), 
             by = "lagoslakeid")  %>%
-  left_join(dplyr::select(county_lulc, county_zoneid:county_ag_2001_pcent), 
+  left_join(dplyr::select(county_lulc, county_zoneid:county_ag_2011_pcent), 
             by = "county_zoneid")
 
 get_ag_cutoff <- function(cutoff){
   hi_ag_counties <- dplyr::filter(iws_vs_county_ag,
-                                  county_ag_2001_pcent >= cutoff &
-                                  iws_ag_2001_pcent >= cutoff) %>%
+                                  county_ag_2011_pcent >= cutoff &
+                                  iws_ag_2011_pcent >= cutoff) %>%
     group_by(county_zoneid) %>%
     summarize(n_lakes = n()) %>%
     dplyr::filter(n_lakes >= 1) %>%
     left_join(dplyr::select(lg$county, county_zoneid, county_state, county_name))
 
   hi_ag_iws <- dplyr::filter(iws_vs_county_ag,
-                             iws_ag_2001_pcent >= cutoff) %>%
+                             iws_ag_2011_pcent >= cutoff) %>%
     distinct(lagoslakeid)
 
   list(hi_ag_counties = hi_ag_counties, hi_ag_iws = hi_ag_iws)

### 2018-11-05 scripts/00_get_lulc.R

@@ -1,19 +1,19 @@
 library(LAGOSNE)
-library(dplyr)
+suppressMessages(library(dplyr))
 
 lg <- lagosne_load("1.087.1")
 
 # ---- get_iws_landcover ----
 
-iws_lulc <- select(lg$iws.lulc, contains("nlcd2001_pct"), lagoslakeid) %>%
+iws_lulc <- select(lg$iws.lulc, contains("nlcd2011_pct"), lagoslakeid) %>%
   group_by(lagoslakeid) %>%
-  mutate(ag_pct = sum(iws_nlcd2001_pct_81,
-                           iws_nlcd2001_pct_82, na.rm = TRUE),
-         iws_ag_2001_pcent = ag_pct / 100) %>%
-  select(row_crop_pct = iws_nlcd2001_pct_82, 
-         pasture_pct = iws_nlcd2001_pct_81,
+  mutate(ag_pct = sum(iws_nlcd2011_pct_81,
+                           iws_nlcd2011_pct_82, na.rm = TRUE),
+         iws_ag_2011_pcent = ag_pct / 100) %>%
+  select(row_crop_pct = iws_nlcd2011_pct_82, 
+         pasture_pct = iws_nlcd2011_pct_81,
          ag_pct,
-         iws_ag_2001_pcent,
+         iws_ag_2011_pcent,
          lagoslakeid) %>%
   data.frame()
 
@@ -21,12 +21,12 @@ saveRDS(iws_lulc, "data/iws_lulc.rds")
 
 # ---- get_county_landcover ----
 
-county_lulc <- dplyr::select(lg$county.lulc, contains("nlcd2001_ha"), county_zoneid) %>%
+county_lulc <- dplyr::select(lg$county.lulc, contains("nlcd2011_ha"), county_zoneid) %>%
   group_by(county_zoneid) %>%
-  mutate(county_ag_2001 = sum(county_nlcd2001_ha_81,
-                              county_nlcd2001_ha_82, na.rm = TRUE)) %>%
+  mutate(county_ag_2011 = sum(county_nlcd2011_ha_81,
+                              county_nlcd2011_ha_82, na.rm = TRUE)) %>%
   left_join(dplyr::select(lg$county, county_ha, county_zoneid)) %>%
-  mutate(county_ag_2001_pcent = county_ag_2001 / county_ha) %>%
+  mutate(county_ag_2011_pcent = county_ag_2011 / county_ha) %>%
   data.frame()
 
 saveRDS(county_lulc, "data/county_lulc.rds")

### 2018-11-05 scripts/02_aggregate_predictors.R
pull 2011 nlcd not 2001

@@ -6,7 +6,7 @@ ep <- readRDS("data/ep.rds")
 
 # predictors are at the iws level and are as close in time to 2000 as possible
 lg_lulc <- readRDS("data/iws_lulc.rds") %>%
-  select(-iws_ag_2001_pcent)
+  select(-iws_ag_2011_pcent)
 
 usgs <- readRDS("data/usgs/usgs.rds")
 

### 2018-11-05 figures/01_county_extent.Rmd
pull 2010 cdl not 2008

@@
 
-ep <- readRDS("data/ep.rds")
+ep <- readRDS("../data/ep.rds")
 gdb_path <- path.expand("~/.local/share/LAGOS-GIS/lagos-ne_gis.gpkg")
@@
 lg          <- lagosne_load("1.087.1")
-iws_lulc    <- readRDS("data/iws_lulc.rds")
-county_lulc <- readRDS("data/county_lulc.rds")
+iws_lulc    <- readRDS("../data/iws_lulc.rds")
+county_lulc <- readRDS("../data/county_lulc.rds")
 

### 2018-11-05 manuscript/figures.Rmd
cleanup animal plots
pull 2010 cdl not 2008

--- 2018-10-11 manuscript/figures.Rmd
@@
 
-```{r county_extent, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (greater than 40 percent) and water quality data in LAGOS from at least 3 sampling events between 1995 and 2005.", warning=FALSE, echo = FALSE}
+```{r county_extent, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (greater than 40 percent) and water quality data in LAGOS from at least 3 sampling events between 2000 and 2010.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/01_county_extent-1.pdf")
@@
 ```
+
+```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
+```
+
+```{r cafos, fig.cap = "Livestock data from the 2007 USDA Census of Agriculture.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/05_cafos-1.pdf")
+```

### 2018-11-05 scripts/00_get_cdl.R

@@ -1,6 +1,6 @@
 cmdargs <- commandArgs(trailingOnly = TRUE)
 cdl_path <- cmdargs[1]
-# cdl_path <- "data/cdl/"
+cdl_path <- "data/cdl/"
 
 library(LAGOSNE)
 library(LAGOSextra)
@@ -12,6 +12,7 @@ library(concaveman)
 
 source("scripts/utils.R")
 
+cdl_year <- 2010
 lg     <- lagosne_load("1.087.1")
 ep     <- readRDS("data/ep.rds")
 ep_bbox <- st_bbox(concaveman(coordinatize(ep)))
@@ -20,24 +21,26 @@ ep     <- distinct(ep, lagoslakeid)
 
 # ep <- filter(ep, lagoslakeid %in% c(23670, 5724))
 for(i in seq_len(length(ep$lagoslakeid))){
-  llid <- ep$lagoslakeid[i]
-  print(llid)
   # i <- 1
   # llid <- 4393
+  llid <- ep$lagoslakeid[i]
+  print(llid)
   boundary_iws <- get_iws(llid)
   bbox         <- get_bbox(boundary_iws)
   states       <- get_states(bbox)
 
   # pull each cdl
 
-  # 2008 might by minimum year with all states?
-  left_join(ep, select(lg$locus, lagoslakeid, state_zoneid)) %>%
-    left_join(select(lg$state, state_zoneid, state)) %>%
+  # use 2010 
+  left_join(ep, 
+            dplyr::select(lg$locus, lagoslakeid, state_zoneid)) %>%
+    left_join(
+      dplyr::select(lg$state, state_zoneid, state)) %>%
     mutate(state = as.character(state)) %>%
     distinct(state) %>%
     sapply(fips) # for manual downloading
 
-  cdl <- cdlTools::getCDL(x = states, year = 2008,
+  cdl <- cdlTools::getCDL(x = states, year = cdl_year,
                            ssl.verifypeer = FALSE,
                            location = cdl_path)
 

### 2018-11-05 figures/05_cafos.Rmd
add cafos map

@@
 
+cafos_epa <- st_read("../data/cafos/CAFOs_per_County.shp")
+cafos_epa <- cafos_epa[
+  unlist(lapply(
+    st_intersects(cafos_epa, states), function(x) length(x) > 0)),]
+
 animals <- readRDS("../data/census/census.rds")
@@
 animals <- left_join(ep, animals, by = "lagoslakeid")
-animals <- dplyr::filter(animals, !(lagoslakeid %in% c(401, 6076)))
+# animals <- dplyr::filter(animals, !(lagoslakeid %in% c(401, 6076)))
 
@@
 theme_opts <- theme(legend.position = "none", 
+                    legend.title=element_blank(),
                     axis.text = element_blank(), 
@@
 
+log_breaks <- function(x, l_out){
+  round(rev(exp(
+    seq(
+      log(min(x, na.rm = TRUE)), 
+      log(max(x, na.rm = TRUE)), 
+      length.out = l_out))), 1)
+}
+
 cowplot::plot_grid(
+
   ggplot() +
@@
       geom_sf(data = 
-                dplyr::filter(animals, ), 
+                dplyr::filter(animals, !is.na(hog_sales)), 
               aes(color = hog_sales), 
@@
       coord_sf(datum = NA) + 
+      labs(color = paste0("hog \n operations")) +
       theme_minimal() + theme_opts +
       ggtitle("hog operations") +
-      labs(color = paste0("hog \n operations")),
+      scale_color_gradient(breaks = log_breaks(animals$hog_sales, 8), 
+                           trans = "log")
+  ,
     ggplot() +
@@
       ggtitle("cattle operations") +
-      theme_minimal() + theme_opts,
+      labs(color = paste0("cattle \n operations")) +
+      theme_minimal() + theme_opts +
+      scale_color_gradient(breaks = log_breaks(animals$cattle_sales, 8), 
+                           trans = "log"),
     ggplot() +
@@
       coord_sf(datum = NA) + 
+      labs(color = paste0("dairy \n operations")) +
       theme_minimal() + theme_opts +
       ggtitle("dairy operations") +
-      labs(color = paste0("dairy \n operations")),
+      scale_color_gradient(breaks = log_breaks(animals$cattle_dairy, 8), 
+                           trans = "log"),
     ggplot() +
@@
       coord_sf(datum = NA) + 
+      labs(color = paste0("chicken \n operations")) +
       theme_minimal() + theme_opts +
       ggtitle("chicken operations") +
-      labs(color = paste0("chicken \n operations")),
+      scale_color_gradient(breaks = log_breaks(animals$chicken_sales, 8), 
+                           trans = "log"),
     ggplot() +
@@
       coord_sf(datum = NA) + 
+      labs(color = paste0("cattle \n head")) +
       theme_minimal() + theme_opts +
       ggtitle("cattle head") +
-      labs(color = paste0("cattle \n head")), 
+      scale_color_gradient(breaks = log_breaks(animals$cattle_total, 8), 
+                           trans = "log"), 
+  ggplot() +
+      geom_sf(data = cafos_epa, aes(fill = CAFOs), color = "transparent") +
+      geom_sf(data = states, fill = "transparent") +
+      coord_sf(datum = NA) + 
+      theme_minimal() + theme_opts +
+      ggtitle("CAFOS"),
     ncol = 1)

### 2018-11-07 figures/02_hierarchical_demo.Rmd
add 03_wetland_potential
use ag lulc for demo

--- 2018-10-08 figures/02_hierarchical_demo.Rmd
@@
 
-```{r }
+```{r 02_hierarchical_demo, fig.height=3, echo=FALSE}
+lg <- lagosne_load("1.087.1")
 
+ep <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
+                summarize(
+                  group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
+                           lagoslakeid), 
+                  tp = median(tp, na.rm = TRUE), 
+                  chla = median(chla, na.rm = TRUE)), 
+                by = "lagoslakeid") %>%
+  tidyr::drop_na()
+
+dt <- dplyr::select(readRDS("../data/dt.rds"), "lagoslakeid") %>% 
+  left_join(ep, by = "lagoslakeid")
+
+# hist(as.vector(table(dt$hu4_zoneid)))  
+# good_hu4s <- group_by(dt, hu4_zoneid) %>% 
+#   tally() %>%
+#   dplyr::filter(n > 220)  
+# dt <- dplyr::filter(dt, hu4_zoneid %in% good_hu4s$hu4_zoneid)
+# dt <- dplyr::filter(dt, tp < 500 & chla < 150)
+
+# create alpha sample size weightings
+dt <- left_join(dt, ungroup(count(group_by(dt, hu4_zoneid))), 
+                by = "hu4_zoneid") %>%
+  dplyr::filter(n >= 5) %>%
+  mutate(n = n / max(n, na.rm = TRUE))
+
+# join iws ag
+dt <- left_join(dt, ungroup(dplyr::select(mutate(
+  group_by(lg$iws.lulc, lagoslakeid), 
+  ag_pct = sum(iws_nlcd2011_pct_81,
+                           iws_nlcd2011_pct_82, na.rm = TRUE)), 
+  lagoslakeid, ag_pct))
+  )
+
+# create hu4 labels
+centroid_xy <- sf::st_as_text(sf::st_geometry(sf::st_centroid(hu4[,"ZoneID"])))
+extract_coords <- function(messy_centroid){
+  res <- stringr::str_split(messy_centroid, "\\(", simplify = TRUE)[2]
+  res <- stringr::str_split(res, "\\)", simplify = TRUE)[1]
+  stringr::str_split(res, " ", simplify = TRUE)
+}
+coords <- data.frame(matrix(
+            as.numeric(unlist(lapply(centroid_xy, extract_coords))),
+            ncol = 2, byrow = TRUE), stringsAsFactors = FALSE)
+names(coords) <- c("x", "y")
+coords$ZoneID <- gsub("HU4_", "", hu4[,"ZoneID"]$ZoneID)
+
+plot_grid(
+  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
+    geom_point() +
+    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
+    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
+                color = "black", linetype = "dashed") +
+    # scale_y_log10() + scale_x_log10() +
+    theme(legend.position = "") +
+    labs(x = "Ag. LULC (pct, NLCD 2011)", 
+         y = "TP")  +
+    ylim(0, 300),
+  ggplot() +
+    geom_sf(data = hu4, aes(fill = n)) +
+    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
+    theme_minimal() + 
+    theme(legend.position = "bottom", 
+          axis.title = element_blank()), 
+  rel_heights = c(0.6, 1), labels = "AUTO"
+)
 ```

### 2018-11-07 manuscript/figures.Rmd
use ag lulc for demo

@@
 
-```{r hierarchical_demo, fig.cap = "A) Global (dashed line) and regional (solid lines) fits to the relationship between lake chlorophyll and lake phosphorus.
+```{r hierarchical_demo, fig.cap = "A) Global (dashed line) and regional (solid lines) fits to the relationship between lake phosphorus and IWS Ag.
+land use cover from the 2011 NLCD.
+A hierarchical model would weight these relationships by sample size (darker lines = higher sample size).
 B) Number of lakes per region.", warning=FALSE, echo = FALSE}

### 2018-11-08 figures/06_lulc_buffer_demo.Rmd
add stream lulc figure

---
output: pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 7, fig.height = 7)
source("../scripts/utils.R")
```

```{r 06_lulc_buffer_demo, echo=FALSE, eval=TRUE}
# setwd("figures")
library(nhdR)
library(LAGOSextra)
library(mapview)
library(FedData)
library(dplyr)
library(ggplot2)
library(raster)
library(sf)
library(cowplot)

dt <- readRDS("../data/dt.rds")

llid <- dt$lagoslakeid[2]
ll_pnt <- st_coordinates(
  st_transform(
    query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", llid), 4326))
ll_lake <- st_transform(
  query_gis("LAGOS_NE_All_Lakes_4ha", "lagoslakeid", llid), 4326)
network <- extract_network(lon = ll_pnt[1], 
                                   lat = ll_pnt[2], 
                                   maxsteps = Inf)
network <- network[unlist(lapply(
  st_intersects(network, st_transform(ll_lake, st_crs(network))), 
  function(x) length(x) == 0)),]

network_buffer <- st_buffer(network, 100)
nlcd <- get_nlcd(template = as_Spatial(st_as_sfc(st_bbox(network_buffer))), 
                 label = llid)
network_buffer <- st_transform(network_buffer, projection(nlcd))

nlcd_df <- as.data.frame(nlcd, xy = TRUE) %>%
  dplyr::select(x, y, contains("Value"))
nlcd_df[,3] <- factor(nlcd_df[,3])
names(nlcd_df)[3] <- "value"
cols <- dplyr::filter(pal_nlcd(), code %in% unique(nlcd_df[,3]))

g_map <- ggplot() + 
  geom_raster(data = nlcd_df, aes(x = x, y = y, fill = value)) +
  scale_fill_manual(values = cols$color) +
  geom_sf(data = network_buffer) +
  coord_sf(datum = NULL) +
  theme(legend.position = "none", 
        axis.text = element_blank(), 
        axis.title = element_blank(), 
        line = element_blank(), 
        rect = element_blank(), 
        text = element_blank(), 
        panel.grid = element_blank())

join_key <- function(vals){
  res <- vals %>%
    data.frame(code = ., stringsAsFactors = FALSE) %>% 
    count(code) %>%
    left_join(FedData::pal_nlcd(), by = "code") %>%
    dplyr::filter(code != 11)
  res$description <- factor(res$description, 
                            levels = res$description)
  res
}

buffer_stats <- join_key(as.character(
  unlist(raster::extract(nlcd, network_buffer))))
nlcd_stats <- join_key(as.character(values(nlcd)))

theme_opts <- theme(axis.text.x = element_blank(), 
                    legend.title = element_blank(), 
                    axis.title.x = element_blank())

g_all <- ggplot() + 
  geom_col(data = nlcd_stats, aes(x = description, 
                             y = n, 
                             fill = description)) +
  scale_fill_manual(values = nlcd_stats$color) +
  theme(legend.direction = "horizontal") +
  theme_opts +
  guides(fill = guide_legend(ncol = 2)) +
  ggtitle("All LULC")

g_buffer <- ggplot() + 
  geom_col(data = buffer_stats, aes(x = description, 
                                  y = n, 
                                  fill = description)) +
  scale_fill_manual(values = buffer_stats$color) +
  theme(legend.position = "none") +
  theme_opts +
  ggtitle("Stream buffer LULC")

legend <- get_legend(g_all)

plot_grid(g_map, 
  plot_grid(g_all + theme(legend.position = "none"),
            g_buffer), 
  legend, ncol = 1)

```

### 2018-11-15 figures/02_hierarchical_demo.Rmd
rm points, recolor chloropleth

@@
 ```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
-library(kableExtra)
 library(dplyr)
-library(tidyr)
-library(magrittr)
-
-library(LAGOSNE)
 library(LAGOSextra)
@@
 library(cowplot)
+library(classInt)
 
@@
 
+n_cat  <- 6
+colors <- c("#FFFFFF", viridisLite::viridis(n_cat - 1))
+hu4    <- mutate(hu4, 
+                 n_cat = cut(hu4$n, breaks = classInt::classIntervals(hu4$n, n = n_cat)$brks))
+hu4 <- dplyr::filter(hu4, !is.na(n_cat))
+
 # hist(hu4$n, n = 20)
@@
 ```{r 02_hierarchical_demo, fig.height=3, echo=FALSE}
+library(tidyr)
+library(LAGOSNE)
+
 lg <- lagosne_load("1.087.1")
@@
   ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
-    geom_point() +
+    # geom_point() +
     geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
@@
          y = "TP")  +
-    ylim(0, 300),
+    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
   ggplot() +
-    geom_sf(data = hu4, aes(fill = n)) +
+    geom_sf(data = hu4, aes(fill = n_cat)) +
     # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
@@
     theme(legend.position = "bottom", 
-          axis.title = element_blank()), 
+          axis.title = element_blank(), 
+          legend.title = element_blank()) + 
+    scale_fill_manual(values = colors, levels(hu4$n_cat)), 
   rel_heights = c(0.6, 1), labels = "AUTO"

### 2018-12-14 figures/02_hierarchical_demo.Rmd
use lagosnegis not lagosextra

@@
 library(dplyr)
-library(LAGOSextra)
+library(LAGOSNEgis)
 library(sf)
@@
 
-hu4 <-  LAGOSextra::query_gis("HU4", "ZoneID", ids$hu4_zoneid) %>%
+hu4 <-  LAGOSNEgis::query_gis("HU4", "ZoneID", ids$hu4_zoneid) %>%
   st_cast(to = "MULTIPOLYGON") %>%

### 2018-12-14 figures/06_lulc_buffer_demo.Rmd
use lagosnegis not lagosextra

@@
 library(nhdR)
-library(LAGOSextra)
+library(LAGOSNEgis)
 library(mapview)

### 2018-12-14 scripts/00_get_cdl.R

@@ -3,7 +3,7 @@ cdl_path <- cmdargs[1]
 cdl_path <- "data/cdl/"
 
 library(LAGOSNE)
-library(LAGOSextra)
+library(LAGOSNEgis)
 library(sf)
 library(cdlTools)
 library(raster)

### 2018-12-14 scripts/00_get_census.R

@@ -3,7 +3,7 @@ suppressMessages(library(dplyr))
 suppressMessages(library(magrittr))
 
 library(LAGOSNE)
-library(LAGOSextra)
+library(LAGOSNEgis)
 library(sf)
 library(lwgeom)
 library(ggplot2)
@@ -17,7 +17,7 @@ Sys.setenv(NASSQS_TOKEN = key)
 
 # ---- census_get ----
 ep  <- readRDS("data/ep.rds")
-iws <- LAGOSextra::query_wbd(ep$lagoslakeid, utm = FALSE)
+iws <- LAGOSNEgis::query_wbd(ep$lagoslakeid, utm = FALSE)
 iws <- st_make_valid(iws)
 states <- state_sf()[unlist(
   lapply(st_intersects(state_sf(), coordinatize(ep)), 

### 2018-12-14 scripts/00_get_tillage.R

@@ -1,6 +1,6 @@
 library(macroag)
 library(LAGOSNE)
-library(LAGOSextra)
+library(LAGOSNEgis)
 library(dplyr)
 library(tidyr)
 library(ggplot2)
@@ -14,7 +14,7 @@ tc <- tillage_ctic %>%
   drop_na("hu8_zoneid") %>%
   dplyr::filter(year == 2004 & crop == "allcrops")
   
-hu8 <- LAGOSextra::query_gis("HU8", "ZoneID", unique(tc$hu8_zoneid))
+hu8 <- LAGOSNEgis::query_gis("HU8", "ZoneID", unique(tc$hu8_zoneid))
 hu8 <- dplyr::left_join(hu8, tc, by = c("ZoneID" = "hu8_zoneid"))
 
 write_sf(hu8, "data/macroag/tillage.gpkg")

### 2018-12-14 scripts/00_get_usgs.R

@@ -1,12 +1,11 @@
 library(LAGOSNE)
-library(LAGOSextra)
+library(LAGOSNEgis)
 library(sf)
 library(unpivotr)
 suppressMessages(library(tidyr))
 library(tidyxl)
 suppressMessages(library(dplyr))
 library(snakecase)
-library(janitor)
 library(lwgeom)
 suppressMessages(library(magrittr))
 
@@ -16,7 +15,7 @@ suppressMessages(library(magrittr))
 # Surface of the Conterminous United States, 1982–2001
 
 ep  <- readRDS("data/ep.rds")
-iws <- LAGOSextra::query_wbd(ep$lagoslakeid, utm = FALSE)
+iws <- LAGOSNEgis::query_wbd(ep$lagoslakeid, utm = FALSE)
 # mapview::mapview(dplyr::filter(iws, lagoslakeid == 34352))
 iws <- st_make_valid(iws)
 
@@ -62,7 +61,7 @@ if(!file.exists("data/usgs/usgs_raw.rds")){
     mutate(character = coalesce(character, as.character(numeric))) %>%
     select(row, value = character, key) %>%
     spread(key, value) %>%
-    clean_names()
+    janitor::clean_names()
 
   usgs_raw <- left_join(county_info, datasheet, by = "row") %>%
     rename(value = character)

### 2018-12-14 scripts/cdlTools.R

@@ -11,7 +11,7 @@ library(sf)
 library(ggplot2)
 library(LAGOSNE)
 library(gdalUtils)
-library(LAGOSextra)
+library(LAGOSNEgis)
 
 # ---- cdl_get_mi ----
 

### 2018-12-14 scripts/riparian_lulc.R

@@ -1,5 +1,5 @@
 library(nhdR)
-library(LAGOSextra)
+library(LAGOSNEgis)
 library(mapview)
 library(FedData)
 library(dplyr)

### 2018-12-14 figures/05_cafos.Rmd
make gis gpkg, use 99_utils not utils

@@
 knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 7, fig.height = 7)
-source("../scripts/utils.R")
+source("../scripts/99_utils.R")
 ```

### 2018-12-14 scripts/00_get_cdl.R

@@ -10,7 +10,7 @@ library(raster)
 library(dplyr)
 library(concaveman)
 
-source("scripts/utils.R")
+source("scripts/99_utils.R")
 
 cdl_year <- 2010
 lg     <- lagosne_load("1.087.1")

### 2018-12-14 scripts/00_get_census.R

@@ -11,7 +11,7 @@ library(rnassqs)
 library(maps)
 library(stringr)
 library(concaveman)
-source("scripts/utils.R")
+source("scripts/99_utils.R")
 key <- "E44D2FCF-E267-3DE1-950A-E6C54EEA7058"
 Sys.setenv(NASSQS_TOKEN = key)
 

### 2018-12-14 scripts/00_get_crp.R

@@ -1,4 +1,4 @@
-source("scripts/utils.R")
+source("scripts/99_utils.R")
 library(macroag)
 library(dplyr)
 

### 2018-12-14 scripts/00_get_ep.R

@@ -2,7 +2,7 @@ library(LAGOSNE)
 suppressMessages(library(dplyr))
 suppressMessages(library(magrittr))
 
-source("scripts/utils.R")
+source("scripts/99_utils.R")
 
 # setwd("../")
 lg           <- lagosne_load("1.087.1")

### 2018-12-14 scripts/00_get_gis.R

@@ -1,0 +1,69 @@
+#' 00_get_gis.R
+#' =======================================================
+#+ setup, include=FALSE
+knitr::opts_chunk$set(eval = FALSE)
+#+
+
+
+# setwd("../")
+source("scripts/99_utils.R")
+
+# ---- size_comparison ----
+lg   <- lagosne_load()
+gpkg_path <- "data/gis.gpkg"
+
+ep  <- readRDS("data/ep.rds") %>%
+  st_as_sf(coords = c("nhd_long", "nhd_lat"), crs = 4326)
+
+iws  <- LAGOSNEgis::query_gis("IWS", "lagoslakeid", ep$lagoslakeid)
+
+state_codes <- c("IL", "IN", "IA",
+                 "MI", "MN", "MO",
+                 "NY", "OH", "PA", "WI")
+states <- state_sf() %>%
+  dplyr::filter(., ABB %in% state_codes)
+
+counties <- dplyr::filter(county_sf(), state_abb %in% state_codes)
+cnty_lg <- lg$county %>%
+  mutate(county_name = gsub(" county", "", tolower(county_name))) %>%
+  left_join(lg$state, by = c("county_state" = "state")) %>%
+  mutate(county_name = gsub("\\.", "", gsub(" ", "", county_name))) %>%
+  mutate(county_name = gsub("'", "", gsub("saint", "st", county_name))) %>%
+  mutate(state_name = tolower(state_name)) %>%
+  select(state_zoneid, state_name, county_name, county_state, county_zoneid) %>%
+  # dplyr::filter(cnty_lg, str_detect(county_name, "brien"))
+  left_join(st_drop_geometry(counties), .,
+            by = c("state" = "state_name", "county" = "county_name")) %>%
+  select(state_abb, county, county_zoneid)
+counties <- left_join(counties, cnty_lg, by = c("state_abb", "county"))
+
+# add zoneids
+
+# use LAGOSNE to pull hu ids that correspond to states
+# lg <- lagosne_load()
+# pad states with NA to 10 characters
+hu4_zones <- lg$hu4 %>%
+  mutate(hu4_states = gsub("  ", "NA", sprintf("%-10s", hu4_states, "NA"))) %>%
+  tidyr::separate(hu4_states, into = paste0("state_", 1:5), sep = seq(2, 8, 2)) %>%
[…]

### 2018-12-14 scripts/00_get_ssurgo.R

@@ -2,7 +2,7 @@ library(sf)
 library(raster)
 library(progress)
 
-source("scripts/utils.R")
+source("scripts/99_utils.R")
 
 ep       <- readRDS("data/ep.rds")
 in_path  <- path.expand("~/Documents/Science/Data/gssurgo_data/tifs/")

### 2018-12-14 scripts/01_process_ssurgo.R

@@ -8,7 +8,7 @@ library(reticulate)
 use_condaenv("gSSURGO")
 gssurgo <- import("gssurgo")
 
-source("scripts/utils.R")
+source("scripts/99_utils.R")
 ep          <- readRDS("data/ep.rds")
 
 gpkg_path   <- path.expand("~/Documents/Science/Data/gssurgo_data/gpkgs/")

### 2018-12-14 scripts/99_utils.R

@@ -1,0 +1,248 @@
+#' 99_utils.R
+#' =======================================================
+#+ setup, include=FALSE
+knitr::opts_chunk$set(eval = FALSE)
+#+
+
+
+# ---- source_utils ----
+
+library(sp)
+suppressMessages(library(dplyr))
+library(gstat)
+library(ggplot2)
+library(sf)
+library(LAGOSNEgis)
+library(LAGOSNE)
+library(lwgeom)
+library(classInt)
+library(tidyr)
+library(stringr)
+library(cowplot)
+library(mapview)
+library(macroag)
+library(broom)
+library(ggsn)
+
+theme_opts <- theme(axis.text = element_blank(),
+                    axis.ticks = element_blank(),
+                    panel.background = element_blank(),
+                    legend.text = element_text(size = 8),
+                    legend.title = element_text(size = 10),
+                    legend.key.size = unit(0.7, "line"),
+                    plot.margin = unit(c(0, -0.13, 0, -0.13), "cm"))
+                    # plot.margin = unit(c(0, 0, -2, 0), "cm")) # t, r, b, l
+
+signif_star <- function(x){
+  if(!is.na(x)){
+    if(x){
+      "*"
+    }else{
+      ""
+    }
+  }else{
+    ""
+  }
+}
+
+county_sf <- function(){
+  county_sf        <- st_as_sf(maps::map("county", fill = TRUE, plot = FALSE))
+  county_sf        <- tidyr::separate(county_sf, ID, c("state", "county"), ",")
+  county_sf$county <- gsub("\\.", "", gsub(" ", "", county_sf$county))
+  county_sf        <- st_make_valid(county_sf)
+
+  county_key <- data.frame(state = tolower(state.name), state_abb = state.abb,
+                           stringsAsFactors = FALSE)
+  county_sf <- left_join(county_sf, county_key)
+  # county_sf <- county_sf[
+  #   unlist(lapply(
+  #     st_intersects(county_sf, iws),
+  #     function(x) length(x) > 0)),]
+  county_sf
+}
+
+state_sf <- function(){
+  state_sf <- st_as_sf(maps::map("state", fill = TRUE, plot = FALSE))
+  key <- data.frame(ID = tolower(state.name),
[…]

### 2018-12-14 scripts/riparian_lulc.R

@@ -7,7 +7,7 @@ library(ggplot2)
 library(raster)
 
 dt <- readRDS("data/dt.rds")
-source("scripts/utils.R")
+source("scripts/99_utils.R")
 
 llid <- dt$lagoslakeid[2]
 ll_pnt <- st_coordinates(

### 2018-12-14 scripts/rnassqs.R

@@ -6,7 +6,7 @@ library(sf)
 library(tidyr)
 library(stringr)
 
-source("scripts/utils.R")
+source("scripts/99_utils.R")
 
 county <- county_sf()
 

### 2018-12-14 scripts/utils.R

@@ -1,91 +1,0 @@
-suppressMessages(library(sf))
-suppressMessages(library(dplyr))
-library(lwgeom)
-
-# ---- basic_gis ----
-county_sf <- function(){
-  county_sf <- st_as_sf(maps::map("county", fill = TRUE, plot = FALSE))
-  county_sf <- tidyr::separate(county_sf, ID, c("state", "county"), ",")
-  county_sf$county <- gsub("\\.", "", gsub(" ", "", county_sf$county))
-  county_sf <- st_make_valid(county_sf)
-  # county_sf <- county_sf[
-  #   unlist(lapply(
-  #     st_intersects(county_sf, iws),
-  #     function(x) length(x) > 0)),]
-  county_sf
-}
-
-state_sf <- function(){
-  state_sf <- st_as_sf(maps::map("state", fill = TRUE, plot = FALSE))
-  key <- data.frame(ID = tolower(state.name),
-                    ABB = state.abb, stringsAsFactors = FALSE)
-  left_join(state_sf, key, by = "ID")
-}
-
-get_states <- function(bbox){
-  state_sf <- sf::st_as_sf(maps::map("state", fill = TRUE, plot = FALSE))
-  key <- data.frame(ID = tolower(state.name),
-                    ABB = state.abb, stringsAsFactors = FALSE)
-  state_sf <- left_join(state_sf, key, by = "ID")
-  bbox <- st_transform(st_as_sfc(bbox), st_crs(state_sf))
-
-  state_sf <- state_sf[unlist(lapply(
-    st_intersects(state_sf, bbox),
-    function(x) length(x) > 0)),]
-
-  state_sf$ABB
-}
-
-get_bbox <- function(boundary_iws){
-  st_bbox(boundary_iws)
-}
-
-clip_to_iws <- function(iws, r){
-  raster::mask(r, as_Spatial(iws))
-}
-
-get_raster_name <- function(r, path){
-  paste0(path, r@data@names)
-}
-
-get_iws <- function(lagoslakeid){
-  LAGOSextra::query_wbd(lagoslakeid, utm = FALSE)
-}
-
-state_key <- function(){
-  data.frame(state = datasets::state.abb, 
-             state_name = datasets::state.name)
-}
-
-# ---- advanced_gis ----
-
-# kg per ha is false, kg is true
-interp_to_iws <- function(raw, varname = "total", outname, is_extensive = TRUE){
-  # raw <- animals_tidy
[…]

### 2018-12-14 README.Rmd
rm old research qs
no figures in README
experiment with collapsible chunks

@@
 
-* LAGOS
-    * Lake depth
-    * IWS area
-    * IWS/Lake area
+<details><summary><b>Lake Characteristics</b> (`LAGOSNE`) </summary><p>
+
+* [x] Lake depth
+* [x] IWS area
+* [x] IWS/Lake area
+</p></details>
+
 * Cropland Data Layer
@@
 
-* Is ag intensification related to changes in lake water quality?
-    * Maybe areas with reduced intensification have been improving?
-* Do ag conservation practices affect lake water quality?
-* Others?
-
 ## Timeline
@@
 * Availability of data products through time is highly variable. How to align or decide to treat properties as constant?
-
-```{r maps, echo=FALSE}
-knitr::include_graphics("figures/rmd-hi_ag_iws_w_ep-1.png")
-```
 

### 2018-12-14 README.Rmd
fill out variable status chunks

@@
 
-<details><summary><b>Lake Characteristics</b> (`LAGOSNE`) </summary><p>
+<details><summary><b>Crop Types</b> (`CDL`) </summary><p>
+
+* [x] IWS pasture types (forage or not)
+* [x] IWS specific crops (corn, wheat, etc.)
+* [ ] IWS crop frequency/rotation
+</p></details>
+
+<details><summary>Soil types (`gSSURGO`) </summary><p>
+
+* [x] IWS wetland potential (as a proxy for tile drainage)
+* [x] IWS soil organic carbon
+* [ ] IWS root zone depth
+* [ ] IWS lithology (sand %, clay %, etc.)
+</p></details>
+
+<details><summary><b>Fertilizer and manure application data</b> (`USGS`) </summary><p>
+
+* [x] IWS from county - manure, fertilizer, and deposition of N,P
+</p></details>
+
+<details><summary>Land use cover (`LAGOSNE`) </summary><p>
+
+* [ ] Lake buffer LULC
+* [x] IWS LULC 
+</p></details>
+
+<details><summary><b>Lake Characteristics and WQ</b> (`LAGOSNE`) </summary><p>
 
@@
 * [x] IWS/Lake area
+* [x] TP, TN, NO3
 </p></details>
-
-* Cropland Data Layer
-    * IWS pasture types (forage or not)
-    * IWS specific crops (corn, wheat, etc.)
-    * IWS crop frequency/rotation
-* gSSURGO
-    * IWS wetland potential (as a proxy for tile drainage)
-    * IWS soil organic carbon
-    * IWS root zone depth
-    * IWS lithology (sand %, clay %, etc.)
-* USGS
-    * IWS from county - manure, fertilizer, and deposition of N,P
 

### 2018-12-18 README.Rmd
add todo chunk for animal data

@@
 * [x] IWS specific crops (corn, wheat, etc.)
-* [ ] IWS crop frequency/rotation
+* [ ] ~IWS crop frequency/rotation~ -AK says this is probably not needed
 </p></details>
@@
 * [x] IWS soil organic carbon
+* [ ] IWS bulk density - needed to compute soil carbon mass
+* [ ] IWS rock content - needed to compute soil carbon mass
 * [ ] IWS root zone depth
@@
 * [x] TP, TN, NO3
+* [ ] IWS precip variability
+  * the area of a given crop in year n-1 matters. Usually, dry years leave nutrients on the ground, and when followed up by a wet year you get the largest signal in year n.
+</p></details>
+
+<details><summary>Animal data</b> (`USDA Census`) </summary><p>
+
+* [ ] Animal units
 </p></details>

### 2019-02-07 scripts/99_utils.R
use smoothr to fill polygon holes

@@ -27,6 +27,7 @@ library(nhdR)
 library(FedData)
 suppressMessages(library(raster))
 library(progress)
+library(smoothr)
 
 theme_opts <- theme(axis.text = element_blank(),
                     axis.ticks = element_blank(),

### 2019-02-07 figures/06_lulc_buffer_demo.Rmd
linting

@@
                                    lat = ll_pnt[2], 
-                                   maxsteps = Inf)
+                                   maxsteps = Inf, 
+                           buffer_dist = units::as_units(5, "km"),
+                           quiet = TRUE)
 network <- network[unlist(lapply(

### 2019-02-13 scripts/00_get_buffers.R
recover from failed network extraction

@@ -32,9 +32,16 @@ get_buffer_stats <- function(llid){
   lake_buffer_area <- sum(st_area(lake_buffer))
   
   # pull stream network buffer
-  network <- suppressWarnings(suppressMessages(extract_network(lon = ll_pnt[1], 
-                                                               lat = ll_pnt[2], 
-                                                               maxsteps = Inf)))
+  tryCatch(network <- suppressWarnings(
+    suppressMessages(
+      extract_network(lon = ll_pnt[1], 
+                            lat = ll_pnt[2], 
+                            maxsteps = Inf))), 
+           error = function(e){network <- NA})
+  if(!exists("network")){
+    network <- NA
+  }
+  
   if(all(class(network) != "logical")){
     network <- network[unlist(lapply(
       st_intersects(network, st_transform(ll_lake, st_crs(network))), 
@@ -131,6 +138,7 @@ get_buffer_stats <- function(llid){
 }
 
 # llid <- ep$lagoslakeid[5]
+# llid <- 6874
 # test <- get_buffer_stats(llid)
 
 pb <- progress_bar$new(format = "  pulling buffer lulc for :llid [:bar]", 
@@ -138,7 +146,7 @@ pb <- progress_bar$new(format = "  pulling buffer lulc for :llid [:bar]",
                        clear = FALSE)
 invisible(pb$tick(0))
 res <- list()
-for(i in seq_along(ep$lagoslakeid)){
+for(i in seq_along(ep$lagoslakeid[15:nrow(ep)])){
   llid          <- ep$lagoslakeid[i]
   pb$tick(tokens = list(llid = llid))
   res[[i]]      <- get_buffer_stats(llid)

### 2019-04-23 manuscript/figures.Rmd
add stream lulc figure
suppress cafos figure

@@
 
-```{r cafos, fig.cap = "Livestock data from the 2007 USDA Census of Agriculture.", warning=FALSE, echo = FALSE}
+```{r cafos, fig.cap = "Livestock data from the 2007 USDA Census of Agriculture.", warning=FALSE, echo = FALSE, eval=FALSE}
 knitr::include_graphics("../figures/05_cafos-1.pdf")
 ```
+
+```{r lulc_buffers, fig.cap = "Landuse cover in stream buffers.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/06_lulc_buffer_demo-1.pdf")
+```

### 2019-04-23 scripts/02_aggregate_predictors.R
write predictors to csv

@@ -60,6 +60,7 @@ dt <- ep %>%
   left_join(stream_buffer_lulc, by = c("lagoslakeid" = "llid"))
 
 saveRDS(dt, "data/dt.rds")
+write.csv(dt, "data/dt.csv", row.names = FALSE)
 # dt <- readRDS("data/dt.rds")
 
 dt_units <- data.frame(variable = names(dt), stringsAsFactors = FALSE) %>%

### 2019-04-24 figures/06_lulc_buffer_demo.Rmd
lulc demo figure changes, closes #7

@@
 knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 7, fig.height = 7)
+# setwd("figures")
 source("../scripts/99_utils.R")
@@
 # setwd("figures")
-library(nhdR)
-library(LAGOSNEgis)
-library(mapview)
-library(FedData)
-library(dplyr)
-library(ggplot2)
-library(raster)
-library(sf)
-library(cowplot)
 
@@
         rect = element_blank(), 
-        text = element_blank(), 
-        panel.grid = element_blank())
+        panel.grid = element_blank()) +
+    ggtitle(paste0("llid: ", llid))
 
@@
 
-buffer_stats <- join_key(as.character(
-  unlist(raster::extract(nlcd, network_buffer))))
+buffer_stats <- read.csv("../data/buffer_lulc.csv") %>%
+  dplyr::filter(llid == 2745) %>%
+  rename(total_n_lake = total_n, 
+         n_lake = n) %>%
+  mutate(total_n_stream = stream_buffer_area / 1000, 
+         n_stream = round((percent_stream / 100) * total_n_stream, 0))
+
+# create a vector of nlcd codes of length n_lake or n_stream
+expand_nlcd_codes <- function(x, n_col){
+  x_filtered <- x %>%
+    dplyr::filter(!is.na(UQ(rlang::sym(n_col))))
+  Map(rep, x_filtered$code, x_filtered[,n_col])  
+}
+
+lake_buffer_stats   <- join_key(as.character(unlist(
+  expand_nlcd_codes(buffer_stats, "n_lake"))))
+stream_buffer_stats <- join_key(as.character(unlist(
+  expand_nlcd_codes(buffer_stats, "n_stream"))))
 nlcd_stats          <- join_key(as.character(values(nlcd)))
@@
   guides(fill = guide_legend(ncol = 2)) +
-  ggtitle("All LULC")
+  ggtitle("Viewport LULC")
 
-g_buffer <- ggplot() + 
-  geom_col(data = buffer_stats, aes(x = description, 
+g_stream_buffer <- ggplot() + 
+  geom_col(data = stream_buffer_stats, aes(x = description, 
                                   y = n, 
                                   fill = description)) +
-  scale_fill_manual(values = buffer_stats$color) +
+  scale_fill_manual(values = stream_buffer_stats$color) +
   theme(legend.position = "none") +
@@
   ggtitle("Stream buffer LULC")
+
+g_lake_buffer <- ggplot() + 
+  geom_col(data = lake_buffer_stats, aes(x = description, 
+                                  y = n, 
+                                  fill = description)) +
+  scale_fill_manual(values = lake_buffer_stats$color) +
+  theme(legend.position = "none") +
+  theme_opts +
+  ggtitle("Lake buffer LULC")
 
@@
   plot_grid(g_all + theme(legend.position = "none"),
-            g_buffer), 
+            g_lake_buffer, ggplot(),
+            g_stream_buffer), 
   legend, ncol = 1)

### 2019-04-24 figures/08_exploratory_dotplot.Rmd
stash completed dotplot, closes #8

---
output: pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 6.5, fig.height = 4.5)
# setwd("figures")
source("../scripts/99_utils.R")
```

```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE}
dt     <- readRDS("../data/dt.rds")
dt_sub <- dplyr::select(dt, tp, tn, lake_area_ha:wheat, -other.non.ag, 
                        -mixed.crop) %>%
  dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  data.frame(stringsAsFactors = FALSE)

dt_tp <- dt_sub %>%
  corrr::correlate() %>%
  corrr::shave() %>%
  janitor::remove_empty(c("rows", "cols")) %>%
  mutate_if(is.numeric, round, 2) %>%
  arrange(desc(abs(tp))) %>%
  data.frame() %>%
  dplyr::select(rowname, tp, tn)

dt_tn <- dt_tp %>% 
  arrange(desc(abs(tn))) %>% 
  data.frame()

dt_tp_rows <- dt_tp$rowname
dt_tp <- dt_tp %>%
  dplyr::select(-rowname) %>%
  mutate_all(abs)
row.names(dt_tp) <- dt_tp_rows

dt_tn_rows <- dt_tn$rowname
dt_tn <- dt_tn %>%
  dplyr::select(-rowname) %>%
  mutate_all(abs)
row.names(dt_tn) <- dt_tn_rows

# pheatmap::pheatmap(
#   t(dt_tp),  
#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
#                                             "Reds"))(100),
#   cluster_cols = FALSE, cluster_rows = FALSE, 
#   na.col = "grey", 
#   cellheight = 7)
# 
# pheatmap::pheatmap(
#   t(dt_tn),  
#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
#                                                       "Reds"))(100),
#   cluster_cols = FALSE, cluster_rows = FALSE, 
#   na.col = "grey", 
#   cellheight = 7)

prep_dotplot <- function(x, col_name){
  dplyr::select(x, UQ(rlang::sym(col_name))) %>% 
    dplyr::mutate(var = factor(row.names(x), 
                            levels = rev(row.names(x)))) %>%
    dplyr::filter(!(var %in% c("tp", "tn")))
}

plot_opts <- theme(axis.title.y = element_blank(), 
                   axis.text = element_text(size = 8))
plot_grid(
  ggplot(data = prep_dotplot(dt_tp, "tp")) + 
    geom_point(aes(x = tp, y = var)) + 
    plot_opts, 
  ggplot(data = prep_dotplot(dt_tn, "tn")) + 
    geom_point(aes(x = tn, y = var)) +
    plot_opts
)

```

### 2019-04-24 scripts/03_model.R

@@ -22,52 +22,6 @@ library(ggeffects)
 library(ggplot2)
 
 dt     <- readRDS("data/dt.rds")
-dt_sub <- dplyr::select(dt, tp, tn, lake_area_ha:wheat, -other.non.ag, 
-                        -mixed.crop) %>%
-  dplyr::filter(complete.cases(.)) %>%
-  mutate_all(as.numeric) %>%
-  data.frame(stringsAsFactors = FALSE)
-
-dt_tp <- dt_sub %>%
-  corrr::correlate() %>%
-  corrr::shave() %>%
-  janitor::remove_empty(c("rows", "cols")) %>%
-  mutate_if(is.numeric, round, 2) %>%
-  arrange(desc(abs(tp))) %>%
-  data.frame() %>%
-  dplyr::select(rowname, tp, tn)
-
-dt_tn <- dt_tp %>% 
-  arrange(desc(abs(tn))) %>% 
-  data.frame()
-
-dt_tp_rows <- dt_tp$rowname
-dt_tp <- dt_tp %>%
-  dplyr::select(-rowname) %>%
-  mutate_all(abs)
-row.names(dt_tp) <- dt_tp_rows
-
-dt_tn_rows <- dt_tn$rowname
-dt_tn <- dt_tn %>%
-  dplyr::select(-rowname) %>%
-  mutate_all(abs)
-row.names(dt_tn) <- dt_tn_rows
-
-pheatmap::pheatmap(
-  t(dt_tp),  
-  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
-                                            "Reds"))(100),
-  cluster_cols = FALSE, cluster_rows = FALSE, 
-  na.col = "grey", 
-  cellheight = 7)
-
-pheatmap::pheatmap(
-  t(dt_tn),  
-  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
-                                                      "Reds"))(100),
-  cluster_cols = FALSE, cluster_rows = FALSE, 
-  na.col = "grey", 
-  cellheight = 7)
 
 # table(
 #   cbind(row.names(dt_tp), row.names(dt_tn))[1:15,]

### 2019-04-24 figures/02_hierarchical_demo.Rmd
linting
use library calls from utils script

@@
 knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
+source("../scripts/99_utils.R")
 ```
@@
 ```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
-library(dplyr)
-library(LAGOSNEgis)
-library(sf)
-library(ggplot2)
-library(cowplot)
-library(classInt)
-
 # setwd("figures")
@@
 hu4    <- mutate(hu4, 
-                 n_cat = cut(hu4$n, breaks = classInt::classIntervals(hu4$n, n = n_cat)$brks))
+            n_cat = cut(hu4$n, breaks = 
+                          classInt::classIntervals(hu4$n, n = n_cat)$brks))
 hu4 <- dplyr::filter(hu4, !is.na(n_cat))

### 2019-04-24 figures/02_hierarchical_demo.Rmd
solve mystery rendering issue

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
+knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 6.5, fig.height = 4.5)
+# setwd("figures")
 source("../scripts/99_utils.R")
@@
 
-```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
+```{r 02_hierarchical_demo, echo=FALSE, message=TRUE, eval=TRUE}
 # setwd("figures")
@@
 # table(as.character(dt$hu4_zoneid))
-```
-
-```{r 02_hierarchical_demo, fig.height=3, echo=FALSE}
-library(tidyr)
-library(LAGOSNE)
 
@@
 
-plot_grid(
+cowplot::plot_grid(
   ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 

### 2019-04-26 figures/07_model-selection.Rmd
model exploration

--- 2018-12-14 figures/02_hierarchical_demo.Rmd
@@
 knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
+# setwd("figures")
+source("../scripts/99_utils.R")
 ```
 
-```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
-library(dplyr)
-library(LAGOSNEgis)
-library(sf)
-library(ggplot2)
-library(cowplot)
-library(classInt)
+```{r ```{r 07_model_selection, fig.height=3, echo=FALSE}
 
@@
 
-ep <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
-                summarize(
-                  group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
-                           lagoslakeid), 
-                  tp = median(tp, na.rm = TRUE), 
-                  chla = median(chla, na.rm = TRUE)), 
-                by = "lagoslakeid") %>%
-  tidyr::drop_na()
+# ep <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
+#                 summarize(
+#                   group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
+#                            lagoslakeid), 
+#                   tp = median(tp, na.rm = TRUE), 
+#                   chla = median(chla, na.rm = TRUE)), 
+#                 by = "lagoslakeid") %>%
+#   tidyr::drop_na()
 
-dt <- dplyr::select(readRDS("../data/dt.rds"), "lagoslakeid") %>% 
-  left_join(ep, by = "lagoslakeid")
+dt <- readRDS("../data/dt.rds") %>%
+  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", "ag_pct", "phosphorus_fertilizer_use")
 
@@
 # join iws ag
-dt <- left_join(dt, ungroup(dplyr::select(mutate(
-  group_by(lg$iws.lulc, lagoslakeid), 
-  ag_pct = sum(iws_nlcd2011_pct_81,
-                           iws_nlcd2011_pct_82, na.rm = TRUE)), 
-  lagoslakeid, ag_pct))
-  )
+# dt <- left_join(dt, ungroup(dplyr::select(mutate(
+#   group_by(lg$iws.lulc, lagoslakeid), 
+#   ag_pct = sum(iws_nlcd2011_pct_81,
+#                            iws_nlcd2011_pct_82, na.rm = TRUE)), 
+#   lagoslakeid, ag_pct))
+#   )
 
@@
 ```
+
+```{r brms_stan}
+library(brms)
+
+names(dt) <- gsub("_", "v", names(dt))
+
+# linear
+model_form <- bf(tp ~ agvpct)
+
+# linear re
+model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))
+
+# non-linear re
+model_form <- bf(tp ~ bagvpct * agvpct, 
+                 bagvpct ~ 1 + 
+                   (1|hu4vzoneid), 
+                 nl = TRUE)
+nlprior <- c(prior(norma(0, 100), nlpar = "bagvpct"))
+
+fit <- brm(formula = model_form, data = dt, 
+           family = gaussian(), prior = nlprior)
+
+summary(fit)
+marginal_effects(fit)
+conditions <- data.frame(hu4vzoneid = unique(dt$hu4vzoneid)[1])
+rownames(conditions) <- unique(dt$hu4vzoneid)[1]
+me_zone <- marginal_effects(fit, conditions = conditions, 
+                            re_formula = NULL, method = "predict")
+ran_ef <- as.data.frame(ranef(fit)$hu4vzoneid) %>%
+  mutate(zoneid = rownames(.)) %>%
+  dplyr::filter(zoneid == unique(dt$hu4vzoneid)[1])
+
+plot(me_zone, ncol = 1)$agvpct + 
+  ggtitle(unique(dt$hu4vzoneid)[1]) +
+  geom_abline(intercept = 0, slope = 0.6899723 + 1.25)
+# ranef slope + fixed slope
+
+ranef(fit)
+
+get_prior(formula = model_form, data = dt)
+
+model_prior <- prior()
+
+fit <- brm(formula = model_form, data = dt, prior = model_prior)
+
+```

### 2019-04-26 figures/07_model-selection.Rmd
add 2nd level coefficents

@@
 dt <- readRDS("../data/dt.rds") %>%
-  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", "ag_pct", "phosphorus_fertilizer_use")
+  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", 
+                "ag_pct", "phosphorus_fertilizer_use", "soybeans")
 
@@
 names(dt) <- gsub("_", "v", names(dt))
+dt <- dplyr::filter(dt, !is.na(phosphorusvfertilizervuse), 
+                    !is.na(soybeans))
 
@@
                  nl = TRUE)
-nlprior <- c(prior(norma(0, 100), nlpar = "bagvpct"))
+fit1 <- brm(formula = model_form, data = dt, 
+           family = gaussian())
+
+# non-linear re w/ 2nd level coeffs
+model_form2 <- bf(tp ~ bagvpct * agvpct, 
+                 bagvpct ~ 1 + phosphorusvfertilizervuse + soybeans +
+                   (1|hu4vzoneid), 
+                 nl = TRUE)
+fit2 <- brm(formula = model_form2, data = dt, 
+           family = gaussian())
+---
+loo1 <- loo(fit1)
+loo2 <- loo(fit2)
+loo_compare(loo1, loo2)
 
 fit <- brm(formula = model_form, data = dt, 
-           family = gaussian(), prior = nlprior)
+           family = gaussian())
 
-summary(fit)
-marginal_effects(fit)
+summary(fit2)
+marginal_effects(fit2)
 conditions <- data.frame(hu4vzoneid = unique(dt$hu4vzoneid)[1])
@@
   ggtitle(unique(dt$hu4vzoneid)[1]) +
-  geom_abline(intercept = 0, slope = 0.6899723 + 1.25)
-# ranef slope + fixed slope
-
-ranef(fit)
-
-get_prior(formula = model_form, data = dt)
-
-model_prior <- prior()
-
-fit <- brm(formula = model_form, data = dt, prior = model_prior)
+  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
+                broom::tidy(fit)$estimate[1])
 

### 2019-04-29 figures/07_model-selection.Rmd
towards posterior summaries

@@
 
+dt        <- readRDS("../data/dt.rds") %>% 
+  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", 
+                "ag_pct", "phosphorus_fertilizer_use", "soybeans")
+
 names(dt) <- gsub("_", "v", names(dt))
@@
 # linear
-model_form <- bf(tp ~ agvpct)
+# model_form <- bf(tp ~ agvpct)
 
@@
 model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))
+fit <- brm(formula = model_form, data = dt, 
+           family = gaussian())
 
@@
 ---
+
+# plot(fit1, pars = "bagvpct")
+
+get_variables(fit)
+spread_draws(fit, b_Intercept)
+
+test <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
+  dplyr::filter(term == "agvpct" & hu4vzoneid == "HU4_40")
+
+m <- add_fitted_draws(dt, b_)
+
+spread_draws(fit, Intercept)
+spread_draws(fit1, bagvpct[hu4vzoneid,])
+
+ggplot() + 
+    stat_lineribbon(data = m, 
+                             aes(x = retention_time_yr, 
+                                 y = estimate), .prob = c(0.95), 
+                    fill = "grey", color = "black", alpha = 0.5)
+
++ 
+    geom_point(data = nes, aes(x = retention_time_yr, 
+                               y = p_percent_retention), 
+               size = 0.6, color = "black") + 
+    scale_x_log10() + ylim(0, 1) +
+    scale_fill_discrete("grey") + 
+    theme_pred() + 
+ylab("P retention") + xlab("Residence time (yr)") + ggtitle("A.")
+
+stat_lineribbon()
+stancode(fit1)
+
+m <- tidybayes::recover_types(fit1)
+
+bayes_results = m %>%
+  spread_draws()
+%>%
+  median_qi(estimate = condition_mean) %>%
+  to_broom_names() %>%
+  mutate(model = "Bayes")
+bayes_result
+
+---
 loo1 <- loo(fit1)
@@
 loo_compare(loo1, loo2)  
+---
 

### 2019-04-30 figures/07_model-selection.Rmd
summarize posteriors

@@
 library(brms)
+library(tidybayes)
 
@@
                 "ag_pct", "phosphorus_fertilizer_use", "soybeans")
-
 names(dt) <- gsub("_", "v", names(dt))
@@
 # linear
-# model_form <- bf(tp ~ agvpct)
+model_form <- bf(tp ~ agvpct)
+fit0 <- brm(formula = model_form, data = dt, 
+           family = gaussian())
+
+get_variables(fit0)
+plot(fit0, pars = "agvpct")
 
@@
 
-# plot(fit1, pars = "bagvpct")
+# pull global distribution (lower, mean, upper)
+# get_variables(fit0)
+global_dist <- spread_draws(fit0, b_agvpct) %>%
+    mutate(hu4vzoneid = "global") %>%
+    group_by(hu4vzoneid) %>%
+    do(tibble::as_tibble(t(quantile(.$b_agvpct, c(0.05, 0.5, 0.95)))))
 
-get_variables(fit)
-spread_draws(fit, b_Intercept)
+# pull hu4 distribution (lower, mean, upper)
+hu4_dist <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
+  dplyr::filter(term == "agvpct") %>%
+  group_by(hu4vzoneid) %>%
+  do(tibble::as_tibble(t(quantile(.$r_hu4vzoneid, c(0.05, 0.5, 0.95))))) %>%
+  mutate(signif = case_when(`5%` > 0 ~ TRUE))
+
+all_dist <- bind_rows(global_dist, hu4_dist)
+
+ggplot(data = all_dist) +
+  geom_point(aes(x = hu4vzoneid, y = `50%`)) +
+  geom_errorbar(aes(ymin = `5%`, ymax = `95%`, x = hu4vzoneid, color = signif)) +
+  geom_hline(yintercept = 0) +
+  coord_flip()
+
+hu4_signif <-  LAGOSNEgis::query_gis(
+  "HU4", "ZoneID", dplyr::filter(hu4_dist, signif)$hu4vzoneid) %>% 
+  st_cast(to = "MULTIPOLYGON")
+
+# pull 2nd level covariate distributions
+get_variables(fit2)
+# spread_draws(fit, b_Intercept)
+
+plot(fit, pars = "agvpct")
 
 test <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
-  dplyr::filter(term == "agvpct" & hu4vzoneid == "HU4_40")
+  dplyr::filter(term == "agvpct") %>%
+  group_by(hu4vzoneid) %>%
+  summarise(agvpct_effect = median(r_hu4vzoneid))
+quantile(test$agvpct_effect, c(0.05, 0.5, 0.95))
 

### 2019-04-30 figures/07_model-selection.Rmd
more posterior exploration

@@
 library(tidybayes)
+library(modelr)
 
@@
 ggplot(data = all_dist) +
-  geom_point(aes(x = hu4vzoneid, y = `50%`)) +
-  geom_errorbar(aes(ymin = `5%`, ymax = `95%`, x = hu4vzoneid, color = signif)) +
+  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
+                      ymin = `5%`, ymax = `95%`, color = signif)) +
   geom_hline(yintercept = 0) +
@@
 # pull 2nd level covariate distributions
-get_variables(fit2)
-# spread_draws(fit, b_Intercept)
+coef_signif <- bind_rows(
+  spread_draws(fit2, b_bagvpct_soybeans) %>%
+    do(tibble::as_tibble(t(quantile(.$b_bagvpct_soybeans, 
+                                    c(0.05, 0.5, 0.95))))), 
+  spread_draws(fit2, b_bagvpct_phosphorusvfertilizervuse) %>%
+    do(tibble::as_tibble(t(quantile(.$b_bagvpct_phosphorusvfertilizervuse, 
+                                    c(0.05, 0.5, 0.95)))))
+  )
+coef_signif$var <- c("soybeans", "pfertilizer")
 
-plot(fit, pars = "agvpct")
+ggplot(data = coef_signif) +
+  geom_pointrange(aes(x = var, y = `50%`, ymin = `5%`, ymax = `95%`)) +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  coord_flip()
 
-test <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
-  dplyr::filter(term == "agvpct") %>%
-  group_by(hu4vzoneid) %>%
-  summarise(agvpct_effect = median(r_hu4vzoneid))
-quantile(test$agvpct_effect, c(0.05, 0.5, 0.95))
+# plot prediction lines
+# hu4_signif$ZoneID
+hu4_id               <- hu4_signif$ZoneID[3]
+conditions           <- data.frame(hu4vzoneid = hu4_id)
+rownames(conditions) <- hu4_id
 
-m <- add_fitted_draws(dt, b_)
+me_zone <- marginal_effects(fit1, conditions = conditions, 
+                            re_formula = NULL, method = "predict")
 
-spread_draws(fit, Intercept)
-spread_draws(fit1, bagvpct[hu4vzoneid,])
+ran_ef <- as.data.frame(ranef(fit1)$hu4vzoneid) %>%
+  mutate(zoneid = rownames(.)) %>%
+  dplyr::filter(zoneid == hu4_id)
+
+plot(me_zone, ncol = 1)$agvpct + 
+  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
+                broom::tidy(fit)$estimate[3]) + 
+  ggtitle(hu4_id)
 
 ggplot() + 
-    stat_lineribbon(data = m, 
-                             aes(x = retention_time_yr, 
-                                 y = estimate), .prob = c(0.95), 
-                    fill = "grey", color = "black", alpha = 0.5)
+    geom_point(data = dplyr::filter(dt, 
+                                  hu4vzoneid == hu4_id), 
+             aes(x = agvpct, y = tp)) + 
+  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
+                broom::tidy(fit)$estimate[3])
 
-+ 
-    geom_point(data = nes, aes(x = retention_time_yr, 
-                               y = p_percent_retention), 
-               size = 0.6, color = "black") + 
-    scale_x_log10() + ylim(0, 1) +
-    scale_fill_discrete("grey") + 
-    theme_pred() + 
-ylab("P retention") + xlab("Residence time (yr)") + ggtitle("A.")
+dt %>%
+  modelr::data_grid(agvpct = seq_range(agvpct, n = 101)) %>%
+  mutate(hu4vzoneid = hu4_id[1]) %>%
+  add_predicted_draws(fit) %>%
+  ggplot(aes(x = agvpct, y = tp)) +
+  stat_lineribbon(aes(y = .prediction), .width = c(.99, .95, .8, .5), color = "#08519C") +
+  geom_point(data = dplyr::filter(dt, hu4vzoneid == hu4_id[1]), 
+                                  size = 2) +
+  scale_fill_brewer()
 
-stat_lineribbon()
-stancode(fit1)
-
-m <- tidybayes::recover_types(fit1)
-
-bayes_results = m %>%
-  spread_draws()
-%>%
-  median_qi(estimate = condition_mean) %>%
-  to_broom_names() %>%
-  mutate(model = "Bayes")
-bayes_result
-
----
+----
+# loo significance testing
+loo0 <- loo(fit)
 loo1 <- loo(fit1)
@@
 loo_compare(loo1, loo2)
----
-
-fit <- brm(formula = model_form, data = dt, 
-           family = gaussian())
-
-summary(fit2)
-marginal_effects(fit2)
-conditions <- data.frame(hu4vzoneid = unique(dt$hu4vzoneid)[1])
-rownames(conditions) <- unique(dt$hu4vzoneid)[1]
-me_zone <- marginal_effects(fit, conditions = conditions, 
-                            re_formula = NULL, method = "predict")
-ran_ef <- as.data.frame(ranef(fit)$hu4vzoneid) %>%
-  mutate(zoneid = rownames(.)) %>%
-  dplyr::filter(zoneid == unique(dt$hu4vzoneid)[1])
-
-plot(me_zone, ncol = 1)$agvpct + 
-  ggtitle(unique(dt$hu4vzoneid)[1]) +
-  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
-                broom::tidy(fit)$estimate[1])
+loo_compare(loo0, loo1)
 

### 2019-04-30 figures/07_model-selection.Rmd
compare against zero slopes

@@
 
+good_hu4s <- readRDS("../data/dt.rds") %>%
+  group_by(hu4_zoneid) %>% 
+  tally() %>%
+  dplyr::filter(n >= 3)
+dt <- dplyr::filter(dt, hu4vzoneid %in% good_hu4s$hu4_zoneid)
+
 # linear
@@
 
-dt %>%
-  modelr::data_grid(agvpct = seq_range(agvpct, n = 101)) %>%
-  mutate(hu4vzoneid = hu4_id[1]) %>%
+dplyr::filter(dt, hu4vzoneid %in% hu4_signif$ZoneID) %>%
+  modelr::data_grid(agvpct = seq_range(agvpct, n = 101), hu4vzoneid) %>%
   add_predicted_draws(fit) %>%
@@
   stat_lineribbon(aes(y = .prediction), .width = c(.99, .95, .8, .5), color = "#08519C") +
-  geom_point(data = dplyr::filter(dt, hu4vzoneid == hu4_id[1]), 
+  geom_point(data = dplyr::filter(dt, hu4vzoneid %in% hu4_signif$ZoneID), 
                                   size = 2) +
-  scale_fill_brewer()
+  scale_fill_brewer() +
+  facet_wrap(~ hu4vzoneid)
+
+hu4_not_signif_n <- sample(unique(
+  pull(
+    dplyr::filter(dt, !(hu4vzoneid %in% hu4_signif$ZoneID)),
+    hu4vzoneid)), 5)
+
+dplyr::filter(dt, hu4vzoneid %in% hu4_not_signif_n) %>%
+  modelr::data_grid(agvpct = seq_range(agvpct, n = 101), hu4vzoneid) %>%
+  add_predicted_draws(fit) %>%
+  ggplot(aes(x = agvpct, y = tp)) +
+  stat_lineribbon(aes(y = .prediction), .width = c(.99, .95, .8, .5), color = "#08519C") +
+  geom_point(data = dplyr::filter(dt, hu4vzoneid %in% hu4_not_signif_n), 
+                                  size = 2) +
+  scale_fill_brewer() +
+  facet_wrap(~ hu4vzoneid)
 

### 2019-04-30 figures/08_exploratory_dotplot.Rmd
show full heatmap

@@
 
-# pheatmap::pheatmap(
-#   t(dt_tp),  
-#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
-#                                             "Reds"))(100),
-#   cluster_cols = FALSE, cluster_rows = FALSE, 
-#   na.col = "grey", 
-#   cellheight = 7)
+# ----
+dt_tp <- dt_sub %>%
+  corrr::correlate() %>%
+  corrr::shave() %>%
+  janitor::remove_empty(c("rows", "cols")) %>%
+  mutate_if(is.numeric, round, 2) %>%
+  data.frame()
+
+dt_tp_rows <- dt_tp$rowname
+dt_tp <- dt_tp %>%
+  dplyr::select(-rowname) %>%
+  mutate_all(abs)
+row.names(dt_tp) <- dt_tp_rows
+
+pheatmap::pheatmap(
+  t(dt_tp),
+  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
+                                            "Reds"))(100),
+  cluster_cols = FALSE, cluster_rows = FALSE,
+  na.col = "grey",
+  cellheight = 7)
 # 

### 2019-04-30 figures/08_exploratory_dotplot.Rmd
clustered heatmap

--- 2019-04-24 figures/08_exploratory_dotplot.Rmd
@@
 
-# pheatmap::pheatmap(
-#   t(dt_tp),  
-#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
-#                                             "Reds"))(100),
-#   cluster_cols = FALSE, cluster_rows = FALSE, 
-#   na.col = "grey", 
-#   cellheight = 7)
+# ----
+dt_tp <- dt_sub %>%
+  corrr::correlate() %>%
+  # corrr::shave() %>%
+  # janitor::remove_empty(c("rows", "cols")) %>%
+  mutate_if(is.numeric, round, 2) %>%
+  data.frame()
+
+dt_tp_rows       <- dt_tp$rowname
+dt_tp            <- dt_tp %>%
+  dplyr::select(-rowname) %>%
+  mutate_all(abs)
+row.names(dt_tp) <- dt_tp_rows
+
+pheatmap::pheatmap(
+  t(dt_tp),
+  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
+                                            "Reds"))(100),
+  cluster_cols = TRUE, cluster_rows = TRUE,
+  na.col = "grey",
+  cellheight = 7)
 # 

### 2019-05-02 figures/07_model-selection.Rmd
towards crude caching of model fits

@@
 
+brm_fit <- function(destfile, formula, data){
+  fit <- brm(formula = formula, data = data, 
+           family = gaussian())
+  saveRDS(fit, destfile)
+  return(fit)
+}
+
 # linear
 model_form <- bf(tp ~ agvpct)
-fit0 <- brm(formula = model_form, data = dt, 
-           family = gaussian())
+fit0 <- get_if_not_exists(brm_fit, "fit0.rds", formula = model_form, data = dt)
 

### 2019-05-02 scripts/99_utils.R

@@ -252,3 +252,28 @@ backstitch <- function(
     )
   }
 }
+
+# jsta::get_if_not_exists
+get_if_not_exists <- function(x, destfile, overwrite = FALSE, ...){
+  
+  if(is.function(x)){
+    if(!file.exists(destfile) | overwrite){
+      res <- x(destfile, ...)
+      return(res)
+    }else{
+      message(paste0("A local evaulation of x already exists on disk"))
+      if(length(grep("*.rds", destfile)) > 0){
+        return(readRDS(destfile))
+      }
+    }
+  } 
+  
+  if(!is.function(x)){
+    if(!file.exists(destfile) | overwrite){
+      download.file(x, destfile)
+    }else{
+      message(paste0("A local copy of ", x, " already exists on disk"))
+    }
+    invisible(x)
+  }
+}

### 2019-05-02 figures/07_model-selection.Rmd
cleanup output

@@
 
-```{r ```{r 07_model_selection, fig.height=3, echo=FALSE}
+```{r 07_model_selection, fig.height=3, echo=FALSE}
 
@@
 
-```{r brms_stan}
+```{r model_fitting, echo=FALSE}
 library(brms)
@@
 
-get_variables(fit0)
-plot(fit0, pars = "agvpct")
-
 # linear re
 model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))
-fit <- brm(formula = model_form, data = dt, 
-           family = gaussian())
+fit <- get_if_not_exists(brm_fit, "fit.rds", formula = model_form, data = dt)
 
@@
                  nl = TRUE)
-fit1 <- brm(formula = model_form, data = dt, 
-           family = gaussian())
+fit1 <- get_if_not_exists(brm_fit, "fit1.rds", formula = model_form, data = dt)
 
@@
                  nl = TRUE)
-fit2 <- brm(formula = model_form2, data = dt, 
-           family = gaussian())
----
+fit2 <- get_if_not_exists(brm_fit, "fit2.rds", formula = model_form2, data = dt)
+```
+
+```{r model_diagnostics, echo=FALSE}
+# get_variables(fit0)
+plot(fit0, pars = "agvpct")
 
@@
 # hu4_signif$ZoneID
-hu4_id               <- hu4_signif$ZoneID[3]
+hu4_id               <- hu4_signif$ZoneID[2]
 conditions           <- data.frame(hu4vzoneid = hu4_id)
@@
 
-plot(me_zone, ncol = 1)$agvpct + 
-  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
-                broom::tidy(fit)$estimate[3]) + 
-  ggtitle(hu4_id)
+# plot(me_zone, ncol = 1)$agvpct # + 
+  # geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
+  #               broom::tidy(fit)$estimate[3]) + 
+  # ggtitle(hu4_id)
 
-ggplot() + 
-    geom_point(data = dplyr::filter(dt, 
-                                  hu4vzoneid == hu4_id), 
-             aes(x = agvpct, y = tp)) + 
-  geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
-                broom::tidy(fit)$estimate[3])
+# ggplot() + 
+#     geom_point(data = dplyr::filter(dt, 
+#                                   hu4vzoneid == hu4_id), 
+#              aes(x = agvpct, y = tp)) + 
+#   geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
+#                 broom::tidy(fit)$estimate[3]) +
+#   ylim(0, 450) + xlim(40, 90) + ggtitle(hu4_id)
 
@@
 
-----
 # loo significance testing
@@
 loo2 <- loo(fit2)
+loo_compare(loo0, loo1)
 loo_compare(loo1, loo2)
-loo_compare(loo0, loo1)
-
 ```

### 2019-05-02 figures/07_model-selection.Rmd
breakup plots, print formulas

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
+knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5, eval = TRUE, warning = FALSE, message = FALSE)
 # setwd("figures")
@@
                 by = "hu4_zoneid") %>%
-  dplyr::filter(n >= 5) %>%
+  dplyr::filter(n >= 3) %>%
   mutate(n = n / max(n, na.rm = TRUE))
@@
                 color = "black", linetype = "dashed") +
+    # geom_abline(slope = 1.55, intercept = -19.86, color = "red") +
     # scale_y_log10() + scale_x_log10() +
@@
 fit0 <- get_if_not_exists(brm_fit, "fit0.rds", formula = model_form, data = dt)
+print("fixed effect")
+print(fit0$formula)
 
@@
 fit <- get_if_not_exists(brm_fit, "fit.rds", formula = model_form, data = dt)
+# plot(fit)
+# print(fit$formula)
 
@@
 fit1 <- get_if_not_exists(brm_fit, "fit1.rds", formula = model_form, data = dt)
+# plot(fit1)
+print("random effects")
+print(fit1$formula)
 
@@
 fit2 <- get_if_not_exists(brm_fit, "fit2.rds", formula = model_form2, data = dt)
+print("re w/ 2nd level coeffs")
+print(fit2$formula)
+
 ```
 
-```{r model_diagnostics, echo=FALSE}
+```{r model_diagnostics_basics, echo=FALSE, fig.height=2}
 # get_variables(fit0)
 plot(fit0, pars = "agvpct")
+```
 
+```{r model_diagnostics_advanced, fig.height=4, echo=FALSE}
 # pull global distribution (lower, mean, upper)
@@
   st_cast(to = "MULTIPOLYGON")
+```
+
+```{r signif_map, echo=FALSE}
+ggplot() + 
+  geom_sf(data = hu4) +
+  geom_sf(data = hu4_signif, color = "red")
+```
+
+```{r model_summary, echo=FALSE, fig.height=3}
 
@@
   coord_flip()
+
+```
+
+```{r asdf, echo=FALSE}
 
@@
 
+```
+
+```{r not_signif, echo=FALSE}
 hu4_not_signif_n <- sample(unique(

### 2019-05-02 scripts/99_utils.R

@@ -1,7 +1,7 @@
 #' 99_utils.R
 #' =======================================================
 #+ setup, include=FALSE
-knitr::opts_chunk$set(eval = FALSE)
+# knitr::opts_chunk$set(eval = FALSE)
 #+
 
 

### 2019-05-02 figures/07_model-selection.Rmd
include dotplot in figures doc

@@
 model_form <- bf(tp ~ agvpct)
-fit0 <- get_if_not_exists(brm_fit, "fit0.rds", formula = model_form, data = dt)
+fit0 <- get_if_not_exists(brm_fit, "../data/mcmc/fit0.rds", formula = model_form, 
+                          data = dt)
 print("fixed effect")
@@
 model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))
-fit <- get_if_not_exists(brm_fit, "fit.rds", formula = model_form, data = dt)
+fit <- get_if_not_exists(brm_fit, "../data/mcmc/fit.rds", formula = model_form, 
+                         data = dt)
 # plot(fit)
@@
                  nl = TRUE)
-fit1 <- get_if_not_exists(brm_fit, "fit1.rds", formula = model_form, data = dt)
+fit1 <- get_if_not_exists(brm_fit, "../data/mcmc/fit1.rds", formula = model_form, 
+                          data = dt)
 # plot(fit1)
@@
                  nl = TRUE)
-fit2 <- get_if_not_exists(brm_fit, "fit2.rds", formula = model_form2, data = dt)
+fit2 <- get_if_not_exists(brm_fit, "../data/mcmc/fit2.rds", formula = model_form2, 
+                          data = dt)
 print("re w/ 2nd level coeffs")

### 2019-05-02 figures/08_exploratory_dotplot.Rmd
include dotplot in figures doc

--- 2019-04-24 figures/08_exploratory_dotplot.Rmd
@@
 
-# pheatmap::pheatmap(
-#   t(dt_tp),  
-#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
-#                                             "Reds"))(100),
-#   cluster_cols = FALSE, cluster_rows = FALSE, 
-#   na.col = "grey", 
-#   cellheight = 7)
+# ----
+dt_tp_hmap <- dt_sub %>%
+  corrr::correlate() %>%
+  # corrr::shave() %>%
+  # janitor::remove_empty(c("rows", "cols")) %>%
+  mutate_if(is.numeric, round, 2) %>%
+  data.frame()
+
+dt_tp_rows       <- dt_tp_hmap$rowname
+dt_tp_hmap            <- dt_tp_hmap %>%
+  dplyr::select(-rowname) %>%
+  mutate_all(abs)
+row.names(dt_tp_hmap) <- dt_tp_rows
+
+pheatmap::pheatmap(
+  t(dt_tp_hmap),
+  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
+                                            "Reds"))(100),
+  cluster_cols = TRUE, cluster_rows = TRUE,
+  na.col = "grey",
+  cellheight = 7)
 # 

### 2019-05-02 manuscript/figures.Rmd
stash completed dotplot, closes #8
include dotplot in figures doc

@@
 ```
+
+```{r exploratory_heatmap, fig.cap = "Exploratory heatmap showing absolute value correlations.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
+```
+
+```{r exploratory_dotplot, fig.cap = "Exploratory dotplots showing absolute value correlations.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/08_exploratory_dotplot-2.pdf")
+```

### 2019-05-06 figures/04_nlcd-versus-cdl.Rmd
add r2 to cdl validation plot

@@
 
+get_r2 <- function(x, y){
+  fit <- lm(y ~ x)
+  round(broom::glance(fit)$r.squared, 2)
+}
+
+r2 <- data.frame(variable = c("ag", "pasture"), 
+                 r2 = c(get_r2(dplyr::filter(res, variable == "ag")$cdl, 
+                               dplyr::filter(res, variable == "ag")$nlcd), 
+                        get_r2(dplyr::filter(res, variable == "pasture")$cdl, 
+                               dplyr::filter(res, variable == "pasture")$nlcd)
+                        ), stringsAsFactors = FALSE)
+r2$r2 <- paste0("r2 = ", r2$r2)
+
 ggplot(data = res, aes(x = nlcd, y = cdl)) + 
@@
   facet_wrap(~variable) +
+  geom_text(data = r2, aes(x = 13, y = 75, label = r2)) +
   theme_minimal()

### 2019-05-06 scripts/99_utils.R

@@ -29,6 +29,7 @@ suppressMessages(library(raster))
 library(progress)
 suppressMessages(library(smoothr))
 library(assertr)
+library(HydroData) # install_github("mikejohnson51/HydroData")
 
 theme_opts <- theme(axis.text = element_blank(),
                     axis.ticks = element_blank(),

### 2019-05-06 manuscript/figures.Rmd
specify 1 to 1 line

@@
 
-```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.", warning=FALSE, echo = FALSE}
+```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.
+Line is 1:1 not regression.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")

### 2019-05-07 scripts/03_model.R
use depth for mediation model

@@ -39,10 +39,11 @@ dt <- data.frame(dt) %>%
 #### explore mediation effects
 # https://en.wikipedia.org/wiki/Mediation_(statistics)
 fit1 <- lm(tn ~ row_crop_pct, data = dt)
-fit2 <- lm(tn ~ iwsla_ratio, data = dt)
-fit3 <- lm(tn ~ row_crop_pct + iwsla_ratio, data = dt)
+fit2 <- lm(tn ~ maxdepth, data = dt)
+fit3 <- lm(tn ~ row_crop_pct + maxdepth, data = dt)
 
 summary(fit1)
+summary(fit2)
 summary(fit3)
 
 

### 2019-05-07 figures/08_exploratory_dotplot.Rmd
add depth to heatmap and dotplot

@@
   cellheight = 7)
-# 
-# pheatmap::pheatmap(
-#   t(dt_tn),  
-#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
-#                                                       "Reds"))(100),
-#   cluster_cols = FALSE, cluster_rows = FALSE, 
-#   na.col = "grey", 
-#   cellheight = 7)
 

### 2019-05-07 figures/08_exploratory_dotplot.Rmd
explore distributions

@@
 
-# ----
+# ---- heatmap ----
 dt_tp_hmap <- dt_sub %>%
@@
 
+# ---- dotplot ----
+
 prep_dotplot <- function(x, col_name){
@@
 
+# ---- densityplots ----
+library(ggforce)
+
+ggplot(data = tidyr::gather(dt_sub)) + 
+  geom_density(aes(value)) +
+  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 1)
+ggplot(data = tidyr::gather(dt_sub)) + 
+  geom_density(aes(value)) +
+  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 2)
+ggplot(data = tidyr::gather(dt_sub)) + 
+  geom_density(aes(value)) +
+  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 3)
+ggplot(data = tidyr::gather(dt_sub)) + 
+  geom_density(aes(value)) +
+  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 4)
+
 ```

### 2019-05-08 tables/01_predictors.Rmd
add precip predictors

@@
 dt <- readRDS("../data/dt.rds") %>%
-  dplyr::select(tp:clay_pct, -hu4_zoneid) %>%
+  dplyr::select(tp:clay_pct, -matches("zoneid")) %>%
   tidyr::gather(key = "variable") %>%

### 2019-05-08 scripts/00_get_ep.R

@@ -87,9 +87,15 @@ ep <- ep %>%
 # add focal predictors
 ep <- ep %>%
   left_join(dplyr::select(lg$iws, lagoslakeid, iws_ha)) %>%
-  left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid, lake_area_ha)) %>%
+  left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid, hu12_zoneid, 
+                          lake_area_ha)) %>%
   left_join(dplyr::select(lg$lakes_limno, lagoslakeid, maxdepth)) %>%
   mutate(iwsla_ratio = iws_ha / lake_area_ha)
+
+# add huc predictors
+ep <- ep %>%
+  left_join(dplyr::select(lg$hu12.chag, hu12_zoneid,                           hu12_ppt_mean = hu12_prism_ppt_30yr_normal_800mm2_annual_mean, 
+    hu12_ppt_std = hu12_prism_ppt_30yr_normal_800mm2_annual_std))
 
 # filter focal predictors
 ep <- dplyr::filter(ep, iws_ha <= max_iws_ha & 

### 2019-05-09 figures/07_model-selection.Rmd
explore multivariate predictors

@@
 dt        <- readRDS("../data/dt.rds") %>% 
-  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", 
-                "ag_pct", "phosphorus_fertilizer_use", "soybeans")
+  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", "hu12_ppt_mean", 
+                "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
+                "soybeans", "pasture", 
+                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use")
 names(dt) <- gsub("_", "v", names(dt))
-dt        <- dplyr::filter(dt, !is.na(phosphorusvfertilizervuse), 
-                    !is.na(soybeans))
+dt        <- dplyr::filter(dt, 
+                           !is.na(phosphorusvfertilizervuse), 
+                           !is.na(soybeans), 
+                           !is.na(maxdepth), 
+                           !is.na(tp))
+dt <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid))
 
@@
 # linear
-model_form <- bf(tp ~ agvpct)
+model_form <- bf(tp ~ ag)
+# unlink("../data/mcmc/fit0.rds")
 fit0 <- get_if_not_exists(brm_fit, "../data/mcmc/fit0.rds", formula = model_form, 
@@
 # linear re
-model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))
+model_form <- bf(tp ~ (1 + ag | hu4vzoneid))
+# unlink("../data/mcmc/fit.rds")
 fit <- get_if_not_exists(brm_fit, "../data/mcmc/fit.rds", formula = model_form, 
@@
 # print(fit$formula)
+
+# linear re with focal predictor
+model_form <- bf(tp ~ maxdepth + (1 + ag | hu4vzoneid))
+# unlink("../data/mcmc/fit1.rds")
+fit1 <- get_if_not_exists(brm_fit, "../data/mcmc/fit1.rds", formula = model_form, 
+                         data = dt)
+# plot(fit1)
+# print(fit$formula)
+
+# linear re with multivariate focal predictor
+model_form <- bf(tp ~ maxdepth + iwslavratio + (1 + ag | hu4vzoneid))
+# unlink("../data/mcmc/fit2.rds")
+fit2 <- get_if_not_exists(brm_fit, "../data/mcmc/fit2.rds", formula = model_form, 
+                         data = dt)
+# plot(fit1)
+# print(fit$formula)
+
+loo_compare(loo(fit1), loo(fit2))
+
+range(dt$iwslavratio)
+
+range((dt$iwslavratio - mean(dt$iwslavratio)) / sd(dt$iwslavratio))
+hist((dt$iwslavratio - mean(dt$iwslavratio)) / sd(dt$iwslavratio))
+test <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid))
 
@@
 # get_variables(fit0)
-plot(fit0, pars = "agvpct")
+plot(fit0, pars = "ag")
 ```
@@
 # get_variables(fit0)
-global_dist <- spread_draws(fit0, b_agvpct) %>%
+global_dist <- spread_draws(fit0, b_ag) %>%
     mutate(hu4vzoneid = "global") %>%
     group_by(hu4vzoneid) %>%
-    do(tibble::as_tibble(t(quantile(.$b_agvpct, c(0.05, 0.5, 0.95)))))
+    do(tibble::as_tibble(t(quantile(.$b_ag, c(0.05, 0.5, 0.95)))))
 
@@
 hu4_dist <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
-  dplyr::filter(term == "agvpct") %>%
+  dplyr::filter(term == "ag") %>%
   group_by(hu4vzoneid) %>%
@@
 # loo significance testing
-loo0 <- loo(fit)
+loo  <- loo(fit)
+loo0 <- loo(fit0)
 loo1 <- loo(fit1)

### 2019-05-09 figures/07_model-selection.Rmd
explore multivariate focal predictors

@@
 dt        <- readRDS("../data/dt.rds") %>% 
-  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", "hu12_ppt_mean", 
+  dplyr::select("lagoslakeid", "hu4_zoneid", "hu12_zoneid", 
+                "tp", "hu12_ppt_mean", "hu12_baseflow_mean",
                 "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
@@
                            !is.na(soybeans), 
+                           !is.na(corn),
                            !is.na(maxdepth), 
                            !is.na(tp))
-dt <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid))
+dt <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid, -hu12vzoneid))
 
@@
 
-# linear re with multivariate focal predictor
-model_form <- bf(tp ~ maxdepth + iwslavratio + (1 + ag | hu4vzoneid))
+model_form <- bf(tp ~ hu12vbaseflowvmean + 
+                   (1 + ag | hu4vzoneid))
 # unlink("../data/mcmc/fit2.rds")
@@
                          data = dt)
-# plot(fit1)
-# print(fit$formula)
 
-loo_compare(loo(fit1), loo(fit2))
+# linear re with multivariate focal predictor
+model_form <- bf(tp ~ maxdepth + iwslavratio + hu12vbaseflowvmean +
+                   (1 + ag | hu4vzoneid))
+# unlink("../data/mcmc/fit3.rds")
+fit3 <- get_if_not_exists(brm_fit, "../data/mcmc/fit3.rds", formula = model_form, 
+                         data = dt)
+
+model_form <- bf(tp ~ maxdepth + iwslavratio + hu12vbaseflowvmean +
+                   (1 + soybeans | hu4vzoneid))
+# unlink("../data/mcmc/fit4.rds")
+fit4 <- get_if_not_exists(brm_fit, "../data/mcmc/fit4.rds", formula = model_form, 
+                         data = dt)
+
+loo_compare(loo(fit3), loo(fit4))
+
+model_form <- bf(tp ~ maxdepth + iwslavratio + 
+                   (1 + corn | hu4vzoneid))
+# unlink("../data/mcmc/fit3.rds")
+fit4 <- get_if_not_exists(brm_fit, "../data/mcmc/fit4.rds", formula = model_form, 
+                         data = dt)
+
+brms::bayes_R2(fit2)
+brms::bayes_R2(fit3)
+brms::bayes_R2(fit4)
 

### 2019-05-10 figures/06_lulc_buffer_demo.Rmd
explore iws with outsized stream buffer ag

@@
 ```
+
+```{r buffer-lulc_vs_iws-lulc, echo=FALSE}
+dt <- readRDS("../data/dt.rds") %>%
+  mutate(diff = stream_cultivated_crops - ag_pct) %>%
+  drop_na(diff)
+
+# ggplot(data = dt) + 
+#   geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = diff > 0)) + 
+#   geom_abline(aes(slope = 1, intercept = 0))
+# 
+# res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
+#                       dplyr::filter(dt, diff > 0)$lagoslakeid)
+res_iws  <- query_gis("IWS", "lagoslakeid", dplyr::filter(dt, diff > 3)$lagoslakeid)
+
+# ggplot() + 
+#   geom_sf(data = state_sf()) +
+#   geom_sf(data = res_pnt)
+
+library(curl)
+library(glue)
+library(slippymath)
+library(raster)
+library(rgdal)
+
+get_image <- function(outpath, iws){
+  # outpath <- outpaths[1]
+  # iws <- res_iws[1,]
+  tile_grid <- bbox_to_tile_grid(st_bbox(
+    st_transform(iws, 4326)), max_tiles = 15)
+
+  mapbox_query_string <-
+    paste0("https://api.mapbox.com/v4/mapbox.satellite/{zoom}/{x}/{y}.jpg90",
+           "?access_token=",
+           Sys.getenv("MAPBOX_API_KEY"))
+
+  images <- apply(tile_grid$tiles, 1, function(i) {
+    url     <- glue(mapbox_query_string, x = i[1], y = i[2], 
+                zoom = tile_grid$zoom)
+    outfile <- glue("../data/mapbox/{x}_{y}.jpg", x = i[1], y = i[2])
+    get_if_not_exists(url, outfile)
+    return(outfile)
+  })
+
+  raster_out <- compose_tile_grid(tile_grid, images)
+
+  writeRaster(raster_out, outpath, options="INTERLEAVE=BAND")   
+  return(raster_out)
+}
+
+# lapply iws's
+outpaths <- paste0("../data/mapbox/", res_iws$lagoslakeid, ".tif")
+images   <- lapply(seq_along(outpaths), function(i) 
+  get_if_not_exists(get_image, outpaths[i], raster::raster, iws = res_iws[i,]))
+
+iws_sized <- which(abs(res_iws$IWSAreaHa - median(res_iws$IWSAreaHa)) < 1000)
+images_sized <- images[iws_sized]
+
+plotRGB(images_sized[[1]])
+
+res_streams <- lapply(iws_sized, function(x) 
+  nhdR::nhd_plus_query(poly = res_iws[x,], dsn = "NHDFlowLine")$sp$NHDFlowLine)
+
+viewRGB(images_sized[[1]]) + mapview(res_streams$sp$NHDFlowLine)
+
+library(tmap)
+
+tm_basemap(leaflet::providers$Stamen.Watercolor) +
+
+  tmap_mode("plot")
+tm_basemap(leaflet::providers$Stamen.Terrain) + 
+  tm_shape(res_iws[8,]) + tm_fill(alpha = 0) + tm_borders() +
+    tm_basemap(server = "OpenTopoMap")
+
+  tm_tiles(paste0("http://services.arcgisonline.com/arcgis/rest/services/Canvas/",
+    "World_Light_Gray_Reference/MapServer/tile/{z}/{y}/{x}"), group = "Labels")
+
+```

### 2019-05-10 scripts/99_utils.R

@@ -256,7 +256,8 @@ backstitch <- function(
 }
 
 # jsta::get_if_not_exists
-get_if_not_exists <- function(x, destfile, overwrite = FALSE, ...){
+get_if_not_exists <- function(x, destfile, read_function = readRDS, 
+                              overwrite = FALSE, ...){
   
   if(is.function(x)){
     if(!file.exists(destfile) | overwrite){
@@ -264,9 +265,7 @@ get_if_not_exists <- function(x, destfile, overwrite = FALSE, ...){
       return(res)
     }else{
       message(paste0("A local evaulation of x already exists on disk"))
-      if(length(grep("*.rds", destfile)) > 0){
-        return(readRDS(destfile))
-      }
+      return(read_function(destfile))
     }
   } 
   

### 2019-05-10 figures/06_lulc_buffer_demo.Rmd
explore iws with undersized stream buffer ag

--- 2019-04-24 figures/06_lulc_buffer_demo.Rmd
@@
 ```
+
+```{r buffer-lulc_vs_iws-lulc, echo=FALSE}
+dt <- readRDS("../data/dt.rds") %>%
+  mutate(diff = stream_cultivated_crops - ag_pct) %>%
+  drop_na(diff)
+
+ggplot(data = dt) +
+  geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = diff > 3)) +
+  geom_abline(aes(slope = 1, intercept = 0)) +
+  theme(legend.position = 0)
+# 
+# res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
+#                       dplyr::filter(dt, diff > 0)$lagoslakeid)
+res_iws  <- query_gis("IWS", "lagoslakeid", 
+                      dplyr::filter(dt, diff > 3)$lagoslakeid)
+
+# ggplot() + 
+#   geom_sf(data = state_sf()) +
+#   geom_sf(data = res_pnt)
+
+library(curl)
+library(glue)
+library(slippymath)
+library(raster)
+library(rgdal)
+
+get_image <- function(outpath, iws){
+  tile_grid <- bbox_to_tile_grid(st_bbox(
+    st_transform(iws, 4326)), max_tiles = 15)
+
+  mapbox_query_string <-
+    paste0("https://api.mapbox.com/v4/mapbox.satellite/{zoom}/{x}/{y}.jpg90",
+           "?access_token=",
+           Sys.getenv("MAPBOX_API_KEY"))
+
+  images <- apply(tile_grid$tiles, 1, function(i) {
+    url     <- glue(mapbox_query_string, x = i[1], y = i[2], 
+                zoom = tile_grid$zoom)
+    outfile <- glue("../data/mapbox/{x}_{y}.jpg", x = i[1], y = i[2])
+    get_if_not_exists(url, outfile)
+    return(outfile)
+  })
+
+  raster_out <- compose_tile_grid(tile_grid, images)
+
+  writeRaster(raster_out, outpath, options="INTERLEAVE=BAND")   
+  return(raster_out)
+}
+
+outpaths     <- paste0("../data/mapbox/", res_iws$lagoslakeid, ".tif")
+images       <- lapply(seq_along(outpaths), function(i) 
+  get_if_not_exists(get_image, outpaths[i], raster::brick, iws = res_iws[i,]))
+
+iws_sized    <- which(abs(res_iws$IWSAreaHa - median(res_iws$IWSAreaHa)) < 1000)
+images_sized <- images[iws_sized]
+
+get_streams <- function(destfile){
+  res <- lapply(iws_sized, function(x) 
+            nhdR::nhd_plus_query(
+              poly = res_iws[x,], dsn = "NHDFlowLine")$sp$NHDFlowLine)
+  saveRDS(res, destfile)
+  return(res)
+}
+
+res_streams <- get_if_not_exists(get_streams, "../data/nhd/res_streams.rds")
+
+# m <- viewRGB(r) + 
+#   mapview(res_streams[[1]]) + 
+#   mapview(s, alpha.regions = 0, color = "red")
+# 
+# mapshot(m, file = paste0(getwd(), "/map.png"))
+# extent(r); st_bbox(s)
+
+i <- 7
+r_raw      <- images_sized[[i]]
+r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])
+
+tab        <- as.data.frame(r, xy = TRUE)
+names(tab) <- c("x", "y", "red", "green", "blue")
+tab$red   <- scales::rescale(tab$red, to = c(0, 255))
+tab$blue  <- scales::rescale(tab$blue, to = c(0, 255))
+tab$green <- scales::rescale(tab$green, to = c(0, 255))
+tab          <- tab[complete.cases(tab),]
+tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)
+
+ggplot() + 
+  geom_raster(data = tab, aes(x, y, fill = I(hex))) +
+  geom_sf(data = res_iws[iws_sized[i],], alpha = 0, color = "red") +
+  geom_sf(data = res_streams[[i]], color = "cyan") +
+  coord_sf(datum = NA) +
+  theme_void()
+
+outpaths     <- paste0("../data/mapbox/", 6201, ".tif") # good sized but low stream ag
+iws_temp     <- query_gis("IWS", "lagoslakeid", 6201)
+# unlink("../data/mapbox/6201.tif")
+images       <- lapply(seq_along(outpaths), function(i) 
+  get_if_not_exists(get_image, outpaths[i], raster::brick, iws = iws_temp))
+
+get_streams <- function(destfile){
+  res <- lapply(iws_sized, function(x) 
+            nhdR::nhd_plus_query(
+              poly = iws_temp, dsn = "NHDFlowLine")$sp$NHDFlowLine)
+  saveRDS(res, destfile)
+  return(res)
+}
+
+streams_temp <- get_if_not_exists(get_streams, "../data/nhd/temp_streams.rds")
+r_raw      <- images[[1]]
+r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])
+
+tab        <- as.data.frame(r, xy = TRUE)
+names(tab) <- c("x", "y", "red", "green", "blue")
+tab$red   <- scales::rescale(tab$red, to = c(0, 255))
+tab$blue  <- scales::rescale(tab$blue, to = c(0, 255))
+tab$green <- scales::rescale(tab$green, to = c(0, 255))
+tab          <- tab[complete.cases(tab),]
+tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)
+
+ggplot() + 
+  geom_raster(data = tab, aes(x, y, fill = I(hex))) +
+  geom_sf(data = iws_temp, alpha = 0, color = "red") +
+  geom_sf(data = streams_temp[[1]], color = "cyan") +
+  coord_sf(datum = NA) +
+  theme_void()
+
+```

### 2019-05-10 figures/06_lulc_buffer_demo.Rmd
add stream buffer satellite pics

@@
 
-```{r buffer-lulc_vs_iws-lulc, echo=FALSE}
+```{r buffer-lulc_vs_iws-lulc, echo=FALSE, fig.height=3}
 dt <- readRDS("../data/dt.rds") %>%
@@
   theme(legend.position = 0)
+```
+
+```{r satellite, echo=FALSE}
 # 
@@
 i          <- 7
+s          <- res_iws[iws_sized[i],]
 r_raw      <- images_sized[[i]]

### 2019-05-10 manuscript/figures.Rmd
add stream buffer satellite pics

@@
 
+```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/buffer-lulc_vs_iws-lulc-1.pdf")
+```
+
+```{r big_stream_ag, fig.cap = "Stream buffer Ag >> IWS", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/satellite-1.pdf")
+```
+
+```{r small_stream_ag, fig.cap = "Stream buffer Ag << IWS", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/satellite-2.pdf")
+```
+
 ```{r exploratory_heatmap, fig.cap = "Exploratory heatmap showing absolute value correlations.", warning=FALSE, echo = FALSE}

### 2019-05-10 figures/06_lulc_buffer_demo.Rmd
towards a CDL demo

@@
 ```
+
+```{r cdl_viewport}
+library(raster)
+library(dplyr)
+
+cdl_key <- read.csv("../data/cdl/cdl_key.csv", stringsAsFactors = FALSE)
+
+r  <- raster::raster("../data/cdl/2745.tif")
+
+cdl_table <- as.data.frame(table(values(r)), stringsAsFactors = FALSE) %>%
+    mutate(code = as.integer(Var1)) %>%
+    dplyr::select(-Var1) %>%
+    left_join(cdl_key, by = "code")
+
+test2 <- cdl_table %>% 
+  dplyr::filter(description != "Background") %>%
+  rename(n = Freq) %>%
+  arrange(desc(n)) %>%
+  group_by(category) %>%
+  summarize(group_n = sum(n, na.rm = TRUE), is_ag = first(is_ag)) %>%
+  ungroup() %>%
+  mutate(percent = round((group_n / sum(group_n, na.rm = TRUE)) * 100, 0)) %>%
+  dplyr::filter(percent >= 1) %>%
+  arrange(is_ag, percent) 
+%>%
+  add_row(category = "ag", group_n = 100, is_ag = "ag", percent = 200)
+
+test2 <- test2 %>%
+  add_row(category = "ag", group_n = NA, is_ag = NA, percent = 
+            sum(dplyr::filter(test2, is_ag == "ag" & 
+                                category != "pasture")$percent))
+
+ggplot() + 
+  geom_col(data = test2, aes(x = category, 
+                             y = percent, 
+                             fill = category)) +
+  theme(legend.direction = "horizontal", 
+        legend.position = 0,
+        axis.text.x = element_text(angle = 90)) +
+  guides(fill = guide_legend(ncol = 2)) +
+  ggtitle("CDL llid = 2745")
+```

### 2019-05-10 figures/07_model-selection.Rmd

@@
 
-loo_compare(loo(fit3), loo(fit4))
+model_form <- bf(tp ~ maxdepth + iwslavratio + hu12vbaseflowvmean + soybeans)
+# unlink("../data/mcmc/fit5.rds")
+fit5 <- get_if_not_exists(brm_fit, "../data/mcmc/fit5.rds", formula = model_form, 
+                         data = dt)
 
-model_form <- bf(tp ~ maxdepth + iwslavratio + 
-                   (1 + corn | hu4vzoneid))
-# unlink("../data/mcmc/fit3.rds")
-fit4 <- get_if_not_exists(brm_fit, "../data/mcmc/fit4.rds", formula = model_form, 
-                         data = dt)
+loo_compare(loo(fit4), loo(fit5))
+
+quantile(ranef(fit4)$hu4vzoneid[,,2], c(0, 0.05, 0.5, 0.95, 1))
+plot(fit4)
 

### 2019-05-10 figures/06_lulc_buffer_demo.Rmd
cdl demo works

@@
 library(dplyr)
+library(stars)
 
@@
 r  <- raster::raster("../data/cdl/2745.tif")
+
+cdl_df <- as.data.frame(r, xy = TRUE) %>%
+  dplyr::select(x, y, contains("2745"))
+names(cdl_df)[3] <- "value"
+cdl_df <- left_join(cdl_df, cdl_key, by = c("value" = "code"))
+
+ggplot() + 
+  geom_raster(data = cdl_df, aes(x = x, y = y, fill = category))
 
@@
   arrange(is_ag, percent)
-%>%
-  add_row(category = "ag", group_n = 100, is_ag = "ag", percent = 200)
 
 test2 <- test2 %>%
-  add_row(category = "ag", group_n = NA, is_ag = NA, percent = 
+  add_row(category = "crops", group_n = NA, is_ag = NA, percent = 
             sum(dplyr::filter(test2, is_ag == "ag" & 

### 2019-05-13 figures/06_lulc_buffer_demo.Rmd
separate cdl and buffer analyses

--- 2019-05-10 figures/06_lulc_buffer_demo.Rmd
@@
 
-```{r buffer-lulc_vs_iws-lulc, echo=FALSE, fig.height=3}
-dt <- readRDS("../data/dt.rds") %>%
-  mutate(diff = stream_cultivated_crops - ag_pct) %>%
-  drop_na(diff)
-
-ggplot(data = dt) +
-  geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = diff > 3)) +
-  geom_abline(aes(slope = 1, intercept = 0)) +
-  theme(legend.position = 0)
-```
-
-```{r satellite, echo=FALSE}
-# 
-# res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
-#                       dplyr::filter(dt, diff > 0)$lagoslakeid)
-res_iws  <- query_gis("IWS", "lagoslakeid", 
-                      dplyr::filter(dt, diff > 3)$lagoslakeid)
-
-# ggplot() + 
-#   geom_sf(data = state_sf()) +
-#   geom_sf(data = res_pnt)
-
-library(curl)
-library(glue)
-library(slippymath)
-library(raster)
-library(rgdal)
-
-get_image <- function(outpath, iws){
-  tile_grid <- bbox_to_tile_grid(st_bbox(
-    st_transform(iws, 4326)), max_tiles = 15)
-
-  mapbox_query_string <-
-    paste0("https://api.mapbox.com/v4/mapbox.satellite/{zoom}/{x}/{y}.jpg90",
-           "?access_token=",
-           Sys.getenv("MAPBOX_API_KEY"))
-
-  images <- apply(tile_grid$tiles, 1, function(i) {
-    url     <- glue(mapbox_query_string, x = i[1], y = i[2], 
-                zoom = tile_grid$zoom)
-    outfile <- glue("../data/mapbox/{x}_{y}.jpg", x = i[1], y = i[2])
-    get_if_not_exists(url, outfile)
-    return(outfile)
-  })
-
-  raster_out <- compose_tile_grid(tile_grid, images)
-
-  writeRaster(raster_out, outpath, options="INTERLEAVE=BAND")   
-  return(raster_out)
-}
-
-outpaths     <- paste0("../data/mapbox/", res_iws$lagoslakeid, ".tif")
-images       <- lapply(seq_along(outpaths), function(i) 
-  get_if_not_exists(get_image, outpaths[i], raster::brick, iws = res_iws[i,]))
-
-iws_sized    <- which(abs(res_iws$IWSAreaHa - median(res_iws$IWSAreaHa)) < 1000)
-images_sized <- images[iws_sized]
-
-get_streams <- function(destfile){
-  res <- lapply(iws_sized, function(x) 
-            nhdR::nhd_plus_query(
-              poly = res_iws[x,], dsn = "NHDFlowLine")$sp$NHDFlowLine)
-  saveRDS(res, destfile)
-  return(res)
-}
-
-res_streams <- get_if_not_exists(get_streams, "../data/nhd/res_streams.rds")
-
-# m <- viewRGB(r) + 
-#   mapview(res_streams[[1]]) + 
-#   mapview(s, alpha.regions = 0, color = "red")
-# 
-# mapshot(m, file = paste0(getwd(), "/map.png"))
-# extent(r); st_bbox(s)
-
-i          <- 7
-s          <- res_iws[iws_sized[i],]
-r_raw      <- images_sized[[i]]
-r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])
-
-tab        <- as.data.frame(r, xy = TRUE)
-names(tab) <- c("x", "y", "red", "green", "blue")
-tab$red   <- scales::rescale(tab$red, to = c(0, 255))
-tab$blue  <- scales::rescale(tab$blue, to = c(0, 255))
-tab$green <- scales::rescale(tab$green, to = c(0, 255))
-tab          <- tab[complete.cases(tab),]
-tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)
-
-ggplot() + 
-  geom_raster(data = tab, aes(x, y, fill = I(hex))) +
-  geom_sf(data = res_iws[iws_sized[i],], alpha = 0, color = "red") +
-  geom_sf(data = res_streams[[i]], color = "cyan") +
-  coord_sf(datum = NA) +
-  theme_void()
-
-outpaths     <- paste0("../data/mapbox/", 6201, ".tif") # good sized but low stream ag
-iws_temp     <- query_gis("IWS", "lagoslakeid", 6201)
-# unlink("../data/mapbox/6201.tif")
-images       <- lapply(seq_along(outpaths), function(i) 
-  get_if_not_exists(get_image, outpaths[i], raster::brick, iws = iws_temp))
-
-get_streams <- function(destfile){
-  res <- lapply(iws_sized, function(x) 
-            nhdR::nhd_plus_query(
-              poly = iws_temp, dsn = "NHDFlowLine")$sp$NHDFlowLine)
-  saveRDS(res, destfile)
-  return(res)
-}
-
-streams_temp <- get_if_not_exists(get_streams, "../data/nhd/temp_streams.rds")
-r_raw      <- images[[1]]
-r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])
-
-tab        <- as.data.frame(r, xy = TRUE)
-names(tab) <- c("x", "y", "red", "green", "blue")
-tab$red   <- scales::rescale(tab$red, to = c(0, 255))
-tab$blue  <- scales::rescale(tab$blue, to = c(0, 255))
-tab$green <- scales::rescale(tab$green, to = c(0, 255))
-tab          <- tab[complete.cases(tab),]
-tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)
-
-ggplot() + 
-  geom_raster(data = tab, aes(x, y, fill = I(hex))) +
-  geom_sf(data = iws_temp, alpha = 0, color = "red") +
-  geom_sf(data = streams_temp[[1]], color = "cyan") +
-  coord_sf(datum = NA) +
-  theme_void()
-
-```
-
-```{r cdl_viewport}
+```{r cdl_viewport, fig.height=5}
 library(raster)
 library(dplyr)
+library(stars)
 
@@
   arrange(is_ag, percent)
-%>%
-  add_row(category = "ag", group_n = 100, is_ag = "ag", percent = 200)
 
-test2 <- test2 %>%
-  add_row(category = "ag", group_n = NA, is_ag = NA, percent = 
-            sum(dplyr::filter(test2, is_ag == "ag" & 
-                                category != "pasture")$percent))
+# test2 <- test2 %>%
+#   add_row(category = "crops", group_n = NA, is_ag = NA, percent = 
+#             sum(dplyr::filter(test2, is_ag == "ag" & 
+#                                 category != "pasture")$percent))
 
-ggplot() + 
+g_bar <- ggplot() + 
   geom_col(data = test2, aes(x = category, 
@@
   ggtitle("CDL llid = 2745")
+
+####
+
+cdl_df <- as.data.frame(r, xy = TRUE) %>%
+  dplyr::select(x, y, contains("2745"))
+names(cdl_df)[3] <- "value"
+cdl_df <- left_join(cdl_df, cdl_key, by = c("value" = "code")) 
+cdl_df <- dplyr::filter(cdl_df, !is.na(category), 
+                        category %in% test2$category)
+
+g_raster <- ggplot() + 
+  geom_raster(data = cdl_df, aes(x = x, y = y, fill = category)) +
+  theme_void()
+
+####
+
+cowplot::plot_grid(g_raster, g_bar)
+
 ```

### 2019-05-13 figures/06_lulc_buffer_demo.Rmd
recolor cdl figs

@@
 library(dplyr)
-library(stars)
 
@@
 
-g_bar <- ggplot() + 
+color_key <- data.frame(category = test2$category, 
+                         color_cat = c("ag", "ag", "ag", "ag", "ag", "ag", 
+                                       "water", "dev", "forest"),
+                         color = c(
+                           RColorBrewer::brewer.pal(6, "YlOrBr"), 
+                           "#9ecae1", "#000000", "#2ca25f"),
+                        stringsAsFactors = FALSE)
+color_key <- arrange(color_key, color_cat)
+
+test2 <- left_join(test2, color_key)
+test2$category <- factor(test2$category, levels = color_key$category)
+
+g_bar <- 
+    ggplot() + 
   geom_col(data = test2, aes(x = category, 
-                             y = percent, 
-                             fill = category)) +
+                             y = percent, fill = category)) +
+    scale_fill_manual(values = setNames(color_key$color, color_key$category)) +
   theme(legend.direction = "horizontal", 
@@
                         category %in% test2$category)
+cdl_df$category <- factor(cdl_df$category, levels = color_key$category)
 
@@
   geom_raster(data = cdl_df, aes(x = x, y = y, fill = category)) +
+  scale_fill_manual(values = setNames(color_key$color, 
+                                      color_key$category)) +
   theme_void()

### 2019-05-13 tables/02_cdl_key.Rmd
add cdl key table, closes #11

---
output:
  pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
```

```{r summary_table, eval=TRUE}
library(kableExtra)
library(dplyr)
library(magrittr)

# setwd("tables")
# ---- cdl_key ----
cdl_key <- read.csv("../data/cdl/cdl_key.csv", stringsAsFactors = FALSE)
cdl_key %>%
  group_by(category) %>%
  sample_n(1) %>%
  knitr::kable(digits = 0, format = "markdown", caption = "Example of CDL categorizations.")

# ---- cdl summary ----
cdl_data <- read.csv("../data/cdl/cdl_summary.csv", stringsAsFactors = FALSE)

apply(cdl_data, 2, function(x) quantile(x, c(0.05, 0.5, 0.95), 
                                        na.rm = TRUE)) %>%
  data.frame() %>%
  dplyr::select(-llid) %>%
  t() %>%
  knitr::kable(format = "markdown", caption = "CDL summary statistics")
```

### 2019-05-13 figures/07_model-selection.Rmd
Setup model summary infrastructure

@@
 }
+
+# evaulate fixed effects
+# ag + {maxdepth, baseflow, iwslavratio}
+
+(model_forms <- list(
+  "ag" = bf(tp ~ ag), 
+  "depth+bf" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean),
+  "depth+iwsla" = bf(tp ~ ag + maxdepth + iwslavratio), 
+  "all" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean + iwslavratio) 
+))
+
+fe_brms <- 
+  lapply(seq_along(model_forms), function(i) 
+    get_if_not_exists(brm_fit, 
+                      paste0("../data/mcmc/fe/", names(model_forms)[i]), 
+                      formula = model_forms[[i]], 
+                      data = dt))
+
+dplyr::bind_rows(
+  lapply(fe_brms, function(x) data.frame(brms::bayes_R2(x)))) %>%
+  mutate(Model = names(model_forms), 
+         Response = "TP", 
+         Estimate = round(Estimate, 2)) %>%
+  dplyr::select(Response, Model, Estimate)
+
+# evaulate spatial random effects
+# {fixed effects} + 1/ag, 1/soybeans, 1/corn
 

### 2019-05-13 figures/07_model-selection.Rmd
More model comparisons

--- 2019-05-10 figures/07_model-selection.Rmd
@@
   dplyr::select("lagoslakeid", "hu4_zoneid", "hu12_zoneid", 
-                "tp", "hu12_ppt_mean", "hu12_baseflow_mean",
+                "tp", "tn", "hu12_ppt_mean", "hu12_baseflow_mean",
                 "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
@@
                            !is.na(maxdepth), 
-                           !is.na(tp))
+                           !is.na(tp), 
+                           !is.na(tn))
 dt <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid, -hu12vzoneid))
@@
 }
+
+# evaulate fixed effects
+# ag + {maxdepth, baseflow, iwslavratio}
+
+(model_forms <- list(
+  "tp_depth+bf" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean),
+  "tp_depth+iwsla" = bf(tp ~ ag + maxdepth + iwslavratio), 
+  "tp_fe" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean + iwslavratio), 
+  "tn_depth+bf" = bf(tn ~ ag + maxdepth + hu12vbaseflowvmean),
+  "tn_depth+iwsla" = bf(tn ~ ag + maxdepth + iwslavratio), 
+  "tn_fe" = bf(tn ~ ag + maxdepth + hu12vbaseflowvmean + iwslavratio) 
+))
+
+fe_brms <- 
+  lapply(seq_along(model_forms), function(i) 
+    get_if_not_exists(brm_fit, 
+                      paste0("../data/mcmc/fe/", names(model_forms)[i]), 
+                      formula = model_forms[[i]], 
+                      data = dt))
+
+dplyr::bind_rows(
+  lapply(fe_brms, function(x) data.frame(brms::bayes_R2(x)))) %>%
+  mutate(Model = names(model_forms), 
+         Estimate = round(Estimate, 2)) %>%
+  dplyr::select(Model, Estimate)
+
+# evaulate spatial random effects
+# {fixed effects} + 1/ag, 1/soybeans, 1/corn
+(model_forms <- list(
+  "tp_ag" = bf(tp ~  maxdepth + hu12vbaseflowvmean +
+                   (1 + ag | hu4vzoneid)),
+  "tp_soybeans" = bf(tp ~  maxdepth + hu12vbaseflowvmean +
+                   (1 + soybeans | hu4vzoneid)),
+  "tp_re" = bf(tp ~  maxdepth + hu12vbaseflowvmean +
+                   (1 + ag + soybeans | hu4vzoneid))
+))
+
+re_brms <- 
+  lapply(seq_along(model_forms), function(i) 
+    get_if_not_exists(brm_fit, 
+                      paste0("../data/mcmc/re/", names(model_forms)[i]), 
+                      formula = model_forms[[i]], 
+                      data = dt))
+
+dplyr::bind_rows(
+  lapply(re_brms, function(x) data.frame(brms::bayes_R2(x)))) %>%
+  mutate(Model = names(model_forms), 
+         Estimate = round(Estimate, 2)) %>%
+  dplyr::select(Model, Estimate)
 

### 2019-05-14 figures/07_model-selection.Rmd
create model summary table

--- 2019-05-10 figures/07_model-selection.Rmd
@@
 library(modelr)
-
-dt        <- readRDS("../data/dt.rds") %>% 
-  dplyr::select("lagoslakeid", "hu4_zoneid", "hu12_zoneid", 
-                "tp", "hu12_ppt_mean", "hu12_baseflow_mean",
-                "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
-                "soybeans", "pasture", 
-                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use")
-names(dt) <- gsub("_", "v", names(dt))
-dt        <- dplyr::filter(dt, 
-                           !is.na(phosphorusvfertilizervuse), 
-                           !is.na(soybeans), 
-                           !is.na(corn),
-                           !is.na(maxdepth), 
-                           !is.na(tp))
-dt <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid, -hu12vzoneid))
-
-good_hu4s <- readRDS("../data/dt.rds") %>%
-  group_by(hu4_zoneid) %>% 
-  tally() %>%
-  dplyr::filter(n >= 3)
-dt <- dplyr::filter(dt, hu4vzoneid %in% good_hu4s$hu4_zoneid)
-
-brm_fit <- function(destfile, formula, data){
-  fit <- brm(formula = formula, data = data, 
-           family = gaussian())
-  saveRDS(fit, destfile)
-  return(fit)
-}
 

### 2019-05-14 tables/03_model_summary.Rmd
create model summary table

--- 2019-05-13 tables/02_cdl_key.Rmd
@@
 # setwd("tables")
-# ---- cdl_key ----
-cdl_key <- read.csv("../data/cdl/cdl_key.csv", stringsAsFactors = FALSE)
-cdl_key %>%
-  group_by(category) %>%
-  sample_n(1) %>%
-  knitr::kable(digits = 0, format = "markdown", caption = "Example of CDL categorizations.")
-
-# ---- cdl summary ----
-cdl_data <- read.csv("../data/cdl/cdl_summary.csv", stringsAsFactors = FALSE)
-
-apply(cdl_data, 2, function(x) quantile(x, c(0.05, 0.5, 0.95), 
-                                        na.rm = TRUE)) %>%
-  data.frame() %>%
-  dplyr::select(-llid) %>%
-  t() %>%
-  knitr::kable(format = "markdown", caption = "CDL summary statistics")
+read.csv("../data/mcmc/model_r2.csv", 
+                     stringsAsFactors = FALSE) %>%
+  knitr::kable(digits = 2, format = "markdown", caption = "Model R2")
 ```

### 2019-05-14 scripts/03_model.R

@@ -1,106 +1,202 @@
 source("scripts/99_utils.R")
 
+library(brms)
+library(tidybayes)
+library(modelr)
+
+dt        <- readRDS("data/dt.rds") %>% 
+  dplyr::select("lagoslakeid", "hu4_zoneid", "hu12_zoneid", 
+                "tp", "tn", "hu12_ppt_mean", "hu12_baseflow_mean",
+                "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
+                "soybeans", "pasture", 
+                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use")
+names(dt) <- gsub("_", "v", names(dt))
+dt        <- dplyr::filter(dt, 
+                           !is.na(phosphorusvfertilizervuse), 
+                           !is.na(soybeans), 
+                           !is.na(corn),
+                           !is.na(maxdepth), 
+                           !is.na(tp), 
+                           !is.na(tn))
+dt <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid, -hu12vzoneid))
+
+good_hu4s <- readRDS("data/dt.rds") %>%
+  group_by(hu4_zoneid) %>% 
+  tally() %>%
+  dplyr::filter(n >= 3)
+dt <- dplyr::filter(dt, hu4vzoneid %in% good_hu4s$hu4_zoneid)
+
+brm_fit <- function(destfile, formula, data){
+  fit <- brm(formula = formula, data = data, 
+             family = gaussian())
+  saveRDS(fit, destfile)
+  return(fit)
+}
+
+
+# evaulate fixed effects
+# ag + {maxdepth, baseflow, iwslavratio}
+
+(model_forms <- list(
+  "tp_depth+bf" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean),
+  "tp_depth+iwsla" = bf(tp ~ ag + maxdepth + iwslavratio), 
+  "tp_fe" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean + iwslavratio), 
+  "tn_depth+bf" = bf(tn ~ ag + maxdepth + hu12vbaseflowvmean),
+  "tn_depth+iwsla" = bf(tn ~ ag + maxdepth + iwslavratio), 
[…]

### 2019-05-14 figures/08_exploratory_dotplot.Rmd
remove nlcd and junk predictors

@@
                         -mixed.crop) %>%
+  dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>%
+  dplyr::select(-matches("other")) %>%
   dplyr::filter(complete.cases(.)) %>%

### 2019-05-15 figures/08_exploratory_dotplot.Rmd
add buffer ag

--- 2019-05-07 figures/08_exploratory_dotplot.Rmd
@@
 dt     <- readRDS("../data/dt.rds")
-dt_sub <- dplyr::select(dt, tp, tn, lake_area_ha:wheat, -other.non.ag, 
-                        -mixed.crop) %>%
+dt_sub <- dt %>% 
+  dplyr::select(tp, tn, lake_area_ha:wheat, 
+                matches("cultivated_crops")) %>%
+  dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
+  dplyr::select(-mixed.crop, -matches("other")) %>% # rm junk
   dplyr::filter(complete.cases(.)) %>%

### 2019-05-15 figures/09_stream_buffer.Rmd
stash stream buffer exploration

---
output: pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 7, fig.height = 7)
# setwd("figures")
source("../scripts/99_utils.R")
```

```{r 09_stream_buffer, echo=FALSE, fig.height=3, fig.width=4}
dt <- readRDS("../data/dt.rds") %>%
  mutate(diff = stream_cultivated_crops - ag_pct, 
         category = cut(diff, breaks = c(Inf, 3, -65, -Inf))) %>%
  drop_na(diff)

ggplot(data = dt) +
  geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = category)) +
  geom_abline(aes(slope = 1, intercept = 3)) +
  geom_abline(aes(slope = 1, intercept = -65)) +
  theme(legend.position = 0) +
  ylab("Stream buffer Ag (%)") + xlab("IWS Ag (%)") +
  xlim(c(40, 100)) + ylim(c(0, 100))
```

```{r satellite, echo=FALSE}
# 
# res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
#                       dplyr::filter(dt, diff > 0)$lagoslakeid)
res_iws  <- query_gis("IWS", "lagoslakeid", 
                      dplyr::filter(dt, diff > 3)$lagoslakeid)

# ggplot() + 
#   geom_sf(data = state_sf()) +
#   geom_sf(data = res_pnt)

library(curl)
library(glue)
library(slippymath)
library(raster)
library(rgdal)

get_image <- function(outpath, iws){
  tile_grid <- bbox_to_tile_grid(st_bbox(
    st_transform(iws, 4326)), max_tiles = 15)

  mapbox_query_string <-
    paste0("https://api.mapbox.com/v4/mapbox.satellite/{zoom}/{x}/{y}.jpg90",
           "?access_token=",
           Sys.getenv("MAPBOX_API_KEY"))

  images <- apply(tile_grid$tiles, 1, function(i) {
    url     <- glue(mapbox_query_string, x = i[1], y = i[2], 
                zoom = tile_grid$zoom)
    outfile <- glue("../data/mapbox/{x}_{y}.jpg", x = i[1], y = i[2])
    get_if_not_exists(url, outfile)
    return(outfile)
  })

  raster_out <- compose_tile_grid(tile_grid, images)

  writeRaster(raster_out, outpath, options="INTERLEAVE=BAND")   
  return(raster_out)
}

outpaths     <- paste0("../data/mapbox/", res_iws$lagoslakeid, ".tif")
images       <- lapply(seq_along(outpaths), function(i) 
  get_if_not_exists(get_image, outpaths[i], raster::brick, iws = res_iws[i,]))

iws_sized    <- which(abs(res_iws$IWSAreaHa - median(res_iws$IWSAreaHa)) < 1000)
images_sized <- images[iws_sized]

get_streams <- function(destfile){
  res <- lapply(iws_sized, function(x) 
            nhdR::nhd_plus_query(
              poly = res_iws[x,], dsn = "NHDFlowLine")$sp$NHDFlowLine)
  saveRDS(res, destfile)
  return(res)
}

res_streams <- get_if_not_exists(get_streams, "../data/nhd/res_streams.rds")

# m <- viewRGB(r) + 
#   mapview(res_streams[[1]]) + 
#   mapview(s, alpha.regions = 0, color = "red")
# 
# mapshot(m, file = paste0(getwd(), "/map.png"))
# extent(r); st_bbox(s)

i          <- 7
s          <- res_iws[iws_sized[i],]
r_raw      <- images_sized[[i]]
r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])

tab        <- as.data.frame(r, xy = TRUE)
names(tab) <- c("x", "y", "red", "green", "blue")
tab$red   <- scales::rescale(tab$red, to = c(0, 255))
tab$blue  <- scales::rescale(tab$blue, to = c(0, 255))
tab$green <- scales::rescale(tab$green, to = c(0, 255))
tab          <- tab[complete.cases(tab),]
tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)

ggplot() + 
  geom_raster(data = tab, aes(x, y, fill = I(hex))) +
  geom_sf(data = res_iws[iws_sized[i],], alpha = 0, color = "red") +
  geom_sf(data = res_streams[[i]], color = "cyan") +
  coord_sf(datum = NA) +
  theme_void()

outpaths     <- paste0("../data/mapbox/", 6201, ".tif") # good sized but low stream ag
iws_temp     <- query_gis("IWS", "lagoslakeid", 6201)
# unlink("../data/mapbox/6201.tif")
images       <- lapply(seq_along(outpaths), function(i) 
  get_if_not_exists(get_image, outpaths[i], raster::brick, iws = iws_temp))

get_streams <- function(destfile){
  res <- lapply(iws_sized, function(x) 
            nhdR::nhd_plus_query(
              poly = iws_temp, dsn = "NHDFlowLine")$sp$NHDFlowLine)
  saveRDS(res, destfile)
  return(res)
}

streams_temp <- get_if_not_exists(get_streams, "../data/nhd/temp_streams.rds")
r_raw      <- images[[1]]
r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])

tab        <- as.data.frame(r, xy = TRUE)
names(tab) <- c("x", "y", "red", "green", "blue")
tab$red   <- scales::rescale(tab$red, to = c(0, 255))
tab$blue  <- scales::rescale(tab$blue, to = c(0, 255))
tab$green <- scales::rescale(tab$green, to = c(0, 255))
tab          <- tab[complete.cases(tab),]
tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)

ggplot() + 
  geom_raster(data = tab, aes(x, y, fill = I(hex))) +
  geom_sf(data = iws_temp, alpha = 0, color = "red") +
  geom_sf(data = streams_temp[[1]], color = "cyan") +
  coord_sf(datum = NA) +
  theme_void()
```

### 2019-05-16 manuscript/figures.Rmd
separate cdl and buffer analyses
pull from stream_buffer Rmd

@@
 
+```{r cdl_viewport, fig.cap = "CDL landuse cover in example IWS.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/cdl_viewport-1.pdf")
+```
+
 ```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/buffer-lulc_vs_iws-lulc-1.pdf")
+knitr::include_graphics("../figures/09_stream_buffer-1.pdf")
 ```

### 2019-05-16 figures/09_stream_buffer.Rmd
label focal lakes

@@
          category = cut(diff, breaks = c(Inf, 3, -65, -Inf))) %>%
-  drop_na(diff)
+  drop_na(diff) %>%
+  dplyr::select(lagoslakeid, ag_pct, stream_cultivated_crops, 
+                diff, category)
+
+# llid 6201 as a low stream ag
+# llid 7026 as a high stream ag
+llids <- c("6201", "7026")
 
@@
   geom_abline(aes(slope = 1, intercept = -65)) +
+  ggrepel::geom_text_repel(data = dplyr::filter(dt, lagoslakeid %in% llids), 
+            aes(x = ag_pct, y = stream_cultivated_crops, label = lagoslakeid)) + 
   theme(legend.position = 0) +
@@
 ```{r satellite, echo=FALSE}
-# 
 # res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
 #                       dplyr::filter(dt, diff > 0)$lagoslakeid)
-res_iws  <- query_gis("IWS", "lagoslakeid", 
-                      dplyr::filter(dt, diff > 3)$lagoslakeid)
-
 # ggplot() + 
@@
 library(slippymath)
-library(raster)
 library(rgdal)
+
+res_iws  <- query_gis("IWS", "lagoslakeid", llids)
 
@@
 
-outpaths     <- paste0("../data/mapbox/", res_iws$lagoslakeid, ".tif")
+outpaths     <- paste0("../data/mapbox/", llids, ".tif")
 images       <- lapply(seq_along(outpaths), function(i) 
@@
 
-iws_sized    <- which(abs(res_iws$IWSAreaHa - median(res_iws$IWSAreaHa)) < 1000)
-images_sized <- images[iws_sized]
-
 get_streams <- function(destfile){
-  res <- lapply(iws_sized, function(x) 
+  res <- lapply(seq_along(llids), function(x) 
             nhdR::nhd_plus_query(
@@
 
+# unlink("../data/nhd/res_streams.rds")
 res_streams <- get_if_not_exists(get_streams, "../data/nhd/res_streams.rds")
 
-# m <- viewRGB(r) + 
-#   mapview(res_streams[[1]]) + 
-#   mapview(s, alpha.regions = 0, color = "red")
-# 
-# mapshot(m, file = paste0(getwd(), "/map.png"))
-# extent(r); st_bbox(s)
-
-i          <- 7
-s          <- res_iws[iws_sized[i],]
-r_raw      <- images_sized[[i]]
-r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])
-
+prep_ggplot_raster <- function(r, iws){
+  r_raw <- r
+  r     <- projectRaster(r_raw, 
+                         crs = as.character(st_crs(iws))[2])
   tab        <- as.data.frame(r, xy = TRUE)
@@
   tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)
+  tab
+}
 
-ggplot() + 
-  geom_raster(data = tab, aes(x, y, fill = I(hex))) +
-  geom_sf(data = res_iws[iws_sized[i],], alpha = 0, color = "red") +
+i <- 1
+gg_low_ag <- ggplot() + 
+  geom_raster(data = prep_ggplot_raster(images[[i]], res_iws[i,]), 
+              aes(x, y, fill = I(hex))) +
+  geom_sf(data = res_iws[i,], alpha = 0, color = "red") +
   geom_sf(data = res_streams[[i]], color = "cyan") +
   coord_sf(datum = NA) +
-  theme_void()
+  theme_void() +
+  ggtitle(llids[i])
 
-outpaths     <- paste0("../data/mapbox/", 6201, ".tif") # good sized but low stream ag
-iws_temp     <- query_gis("IWS", "lagoslakeid", 6201)
-# unlink("../data/mapbox/6201.tif")
-images       <- lapply(seq_along(outpaths), function(i) 
-  get_if_not_exists(get_image, outpaths[i], raster::brick, iws = iws_temp))
+i <- 2
+gg_hi_ag <- ggplot() + 
+  geom_raster(data = prep_ggplot_raster(images[[i]], res_iws[i,]), 
+              aes(x, y, fill = I(hex))) +
+  geom_sf(data = res_iws[i,], alpha = 0, color = "red") +
+  geom_sf(data = res_streams[[i]], color = "cyan") +
+  coord_sf(datum = NA) +
+  theme_void() +
+  ggtitle(llids[i])
 
-get_streams <- function(destfile){
-  res <- lapply(iws_sized, function(x) 
-            nhdR::nhd_plus_query(
-              poly = iws_temp, dsn = "NHDFlowLine")$sp$NHDFlowLine)
-  saveRDS(res, destfile)
-  return(res)
-}
-
-streams_temp <- get_if_not_exists(get_streams, "../data/nhd/temp_streams.rds")
-r_raw      <- images[[1]]
-r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])
-
-tab        <- as.data.frame(r, xy = TRUE)
-names(tab) <- c("x", "y", "red", "green", "blue")
-tab$red   <- scales::rescale(tab$red, to = c(0, 255))
-tab$blue  <- scales::rescale(tab$blue, to = c(0, 255))
-tab$green <- scales::rescale(tab$green, to = c(0, 255))
-tab          <- tab[complete.cases(tab),]
-tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)
-
-ggplot() + 
-  geom_raster(data = tab, aes(x, y, fill = I(hex))) +
-  geom_sf(data = iws_temp, alpha = 0, color = "red") +
-  geom_sf(data = streams_temp[[1]], color = "cyan") +
-  coord_sf(datum = NA) +
-  theme_void()
+cowplot::plot_grid(gg_low_ag, gg_hi_ag)
 ```

### 2019-05-16 manuscript/figures.Rmd
label focal lakes

@@
 
-```{r big_stream_ag, fig.cap = "Stream buffer Ag >> IWS", warning=FALSE, echo = FALSE}
+```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/satellite-1.pdf")
-```
-
-```{r small_stream_ag, fig.cap = "Stream buffer Ag << IWS", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/satellite-2.pdf")
 ```

### 2019-05-16 figures/06_lulc_buffer_demo.Rmd
add cdl vs nlcd map

@@
 
-llid <- dt$lagoslakeid[2]
+llid <- 2745
 ll_pnt <- st_coordinates(
@@
   function(x) length(x) == 0)),]
+iws  <- query_gis("IWS", "lagoslakeid", llid)
 
 network_buffer <- st_buffer(network, 100)
-nlcd           <- get_nlcd(template = as_Spatial(st_as_sfc(st_bbox(network_buffer))), 
+nlcd           <- get_nlcd(template = as_Spatial(st_as_sfc(st_bbox(iws))), 
                  label = llid)
+# mapview(nlcd) + mapview(iws)
 network_buffer <- st_transform(network_buffer, projection(nlcd))
@@
 ```{r cdl_viewport, fig.height=5}
-library(raster)
-library(dplyr)
-
+# pull cdl lulc
 cdl_key <- read.csv("../data/cdl/cdl_key.csv", stringsAsFactors = FALSE)
-
 r  <- raster::raster("../data/cdl/2745.tif")
@@
 color_key <- data.frame(category = test2$category, 
-                         color_cat = c("ag", "ag", "ag", "ag", "ag", "ag", 
+                         color_cat = c("ag", "ag", "ag", "ag", "ag", "pasture", 
                                        "water", "dev", "forest"),
                          color = c(
-                           RColorBrewer::brewer.pal(6, "YlOrBr"), 
+                           RColorBrewer::brewer.pal(5, "YlOrBr"), "#DBD83D",
                            "#9ecae1", "#000000", "#2ca25f"),
@@
 ```
+
+```{r cdl_vs_nlcd}
+# mask nlcd lulc
+
+test <- raster::mask(nlcd, iws) %>% 
+  as.data.frame(xy = TRUE) %>%
+  dplyr::select(x, y, contains("Value"))
+test <- test[test[,3] %in% c(81, 82),]
+test[,3] <- factor(test[,3])
+names(test)[3] <- "value"
+test <- test %>%
+  drop_na("value")
+cols <- dplyr::filter(pal_nlcd(), code %in% unique(test[,3]))
+
+# codes 81 = pasture; 82 = row_crop
+
+g_nlcd <- ggplot() + 
+  geom_raster(data = test, aes(x = x, y = y, fill = value)) +
+  scale_fill_manual(values = cols$color, labels = cols$description) +
+  geom_sf(data = iws, alpha = 0) +
+  coord_sf(datum = NA) + 
+  theme_void() + 
+  theme(legend.position = 0)
+
+g_cdl <- ggplot() + 
+  geom_raster(data = dplyr::filter(cdl_df, as.character(category) %in% 
+                                     c("corn", "soybeans", "pasture")), 
+              aes(x = x, y = y, fill = category)) +
+  scale_fill_manual(values = setNames(color_key$color, 
+                                      color_key$category)) +
+  geom_sf(data = iws, alpha = 0) +
+  geom_sf(data = network) +
+  geom_sf(data = ll_lake) +
+  coord_sf(datum = NA) + 
+  theme_void()
+
+cowplot::plot_grid(g_nlcd + ggtitle("NLCD (2011)"), 
+                   g_cdl + ggtitle("CDL (2010)"), 
+                   rel_widths = c(0.75, 1))
+```

### 2019-05-16 scripts/03_model.R
add stream ag predictor

@@ -8,8 +8,9 @@ dt        <- readRDS("data/dt.rds") %>%
   dplyr::select("lagoslakeid", "hu4_zoneid", "hu12_zoneid", 
                 "tp", "tn", "hu12_ppt_mean", "hu12_baseflow_mean",
                 "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
-                "soybeans", "pasture", 
-                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use")
+                "soybeans", "pasture", "p_input", "n_input",
+                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use", 
+                "stream_cultivated_crops")
 names(dt) <- gsub("_", "v", names(dt))
 dt        <- dplyr::filter(dt, 
                            !is.na(phosphorusvfertilizervuse), 
@@ -93,10 +94,25 @@ r2_re <- dplyr::bind_rows(
          Estimate = round(Estimate, 2)) %>%
   dplyr::select(Model, Estimate)
 
-write.csv(dplyr::bind_rows(r2_fe, r2_re), "data/mcmc/model_r2.csv",
-          row.names = FALSE)
+if(!interactive()){
+  write.csv(dplyr::bind_rows(r2_fe, r2_re), 
+            "data/mcmc/model_r2.csv",
+            row.names = FALSE)
+}
 
 # ---- diagnostics ----
+
+# look for evidence of interaction effects
+# following shalizi...
+dt %>%
+  add_residual_draws(fe_brms[[1]]) %>%
+  ggplot(aes(x = log(maxdepth + abs(min(dt$maxdepth))), y = .residual, color = iwslavratio)) +
+  geom_point() +
+  # stat_pointinterval(alpha = 0.4) +
+  theme(axis.text.x = element_text(angle = 90))
+
+# ----
+
 # knitr::kable(r2_fe, "markdown")
 # knitr::kable(r2_re, "markdown")
 # 
@@ -123,29 +139,37 @@ write.csv(dplyr::bind_rows(r2_fe, r2_re), "data/mcmc/model_r2.csv",
 #   tn, tp")
 
 # ---- exploratory_models ----
-
-# library(dplyr)
+# #### Find optimal random effects structure
 # library(lme4)
-# library(merTools)
-# library(LAGOSNE)
[…]

### 2019-05-17 figures/06_lulc_buffer_demo.Rmd
add raster resolution fig

@@
 ```
+
+```{r raster_resolution}
+library(nadp)
+
+llid  <- 2745
+
+iws   <- query_gis("IWS", "lagoslakeid", llid)
+n_dep <- nadp_load("2010", "totalN")
+n_dep <- raster::crop(n_dep, as_Spatial(st_as_sfc(st_bbox(iws))))
+n_dep <- mask(n_dep, iws)
+
+# create a baseflow grid of 1000m and a ndep grid of 2338 m
+gg_dep_grid <- ggplot() + 
+  geom_sf(data = iws) +
+  geom_sf(data = st_make_grid(iws, cellsize = 2338), alpha = 0) +
+  coord_sf(datum = NA) +
+  theme_void()
+
+gg_bf_grid <- ggplot() + 
+  geom_sf(data = iws) +
+  geom_sf(data = st_make_grid(
+    st_buffer(st_as_sfc(st_bbox(st_make_grid(iws, cellsize = 2338))), 400), 
+                    cellsize = 1000), 
+    alpha = 0) +
+  coord_sf(datum = NA) +
+  theme_void()
+
+cowplot::plot_grid(gg_dep_grid, gg_bf_grid)
+```

### 2019-05-17 figures/08_exploratory_dotplot.Rmd
show n dep dotplot

--- 2019-05-07 figures/08_exploratory_dotplot.Rmd
@@
 dt     <- readRDS("../data/dt.rds")
-dt_sub <- dplyr::select(dt, tp, tn, lake_area_ha:wheat, -other.non.ag, 
-                        -mixed.crop) %>%
+dt_sub <- dt %>% 
+  dplyr::select(tp, tn, lake_area_ha:wheat, 
+                matches("cultivated_crops")) %>%
+  dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
+  dplyr::select(-mixed.crop, -matches("other"), -forage, 
+                -hu12_ppt_std, -water, -developed, -forest) %>% # rm junk
   dplyr::filter(complete.cases(.)) %>%
@@
   corrr::correlate() %>%
-  corrr::shave() %>%
+  # corrr::shave() %>%
   janitor::remove_empty(c("rows", "cols")) %>%
@@
 ```
+
+```{r n-dep_dotplot}
+
+slice_cormat <- function(var_name, dt_sub){
+  # var_name <- "nitrogen_atmospheric_deposition"
+
+  dt_corr <- dt_sub %>%
+    corrr::correlate() %>%
+    # corrr::shave() %>%
+    janitor::remove_empty(c("rows", "cols")) %>%
+    mutate_if(is.numeric, round, 2) %>%
+    arrange(desc(abs(!!rlang::sym(var_name)))) %>%
+    data.frame() %>%
+    dplyr::select(rowname, var_name)
+
+  dt_corr_rows <- dt_corr$rowname
+  dt_corr <- dt_corr %>%
+    dplyr::select(-rowname) %>%
+    mutate_all(abs)
+  row.names(dt_corr) <- dt_corr_rows
+
+  dt_corr
+}
+
+test <- slice_cormat("nitrogen_atmospheric_deposition", dt_sub)
+
+ggplot(data = prep_dotplot(test, "nitrogen_atmospheric_deposition")) +
+    geom_point(aes(x = nitrogen_atmospheric_deposition, y = var)) +
+    plot_opts
+
+```

### 2019-05-17 figures/08_exploratory_dotplot.Rmd
move ndep analysis to seprate file

@@
 ```
-
-```{r n-dep_dotplot}
-
-slice_cormat <- function(var_name, dt_sub){
-  # var_name <- "nitrogen_atmospheric_deposition"
-
-  dt_corr <- dt_sub %>%
-    corrr::correlate() %>%
-    # corrr::shave() %>%
-    janitor::remove_empty(c("rows", "cols")) %>%
-    mutate_if(is.numeric, round, 2) %>%
-    arrange(desc(abs(!!rlang::sym(var_name)))) %>%
-    data.frame() %>%
-    dplyr::select(rowname, var_name)
-
-  dt_corr_rows <- dt_corr$rowname
-  dt_corr <- dt_corr %>%
-    dplyr::select(-rowname) %>%
-    mutate_all(abs)
-  row.names(dt_corr) <- dt_corr_rows
-
-  dt_corr
-}
-
-test <- slice_cormat("nitrogen_atmospheric_deposition", dt_sub)
-
-ggplot(data = prep_dotplot(test, "nitrogen_atmospheric_deposition")) +
-    geom_point(aes(x = nitrogen_atmospheric_deposition, y = var)) +
-    plot_opts
-
-```

### 2019-05-17 figures/10_nitrogen_deposition.Rmd
move ndep analysis to seprate file

--- 2019-05-17 figures/08_exploratory_dotplot.Rmd
@@
 
-dt_tp <- dt_sub %>%
-  corrr::correlate() %>%
-  # corrr::shave() %>%
-  janitor::remove_empty(c("rows", "cols")) %>%
-  mutate_if(is.numeric, round, 2) %>%
-  arrange(desc(abs(tp))) %>%
-  data.frame() %>%
-  dplyr::select(rowname, tp, tn)
+plot(lg$hu12.chag$hu12_dep_totaln_2010_mean, 
+     lg$hu12.chag$hu12_prism_ppt_30yr_normal_800mm2_annual_mean)
 
-dt_tn <- dt_tp %>% 
-  arrange(desc(abs(tn))) %>% 
-  data.frame()
-
-dt_tp_rows <- dt_tp$rowname
-dt_tp <- dt_tp %>%
-  dplyr::select(-rowname) %>%
-  mutate_all(abs)
-row.names(dt_tp) <- dt_tp_rows
-
-dt_tn_rows <- dt_tn$rowname
-dt_tn <- dt_tn %>%
-  dplyr::select(-rowname) %>%
-  mutate_all(abs)
-row.names(dt_tn) <- dt_tn_rows
-
-# ---- heatmap ----
-dt_tp_hmap <- dt_sub %>%
-  corrr::correlate() %>%
-  # corrr::shave() %>%
-  # janitor::remove_empty(c("rows", "cols")) %>%
-  mutate_if(is.numeric, round, 2) %>%
-  data.frame()
-
-dt_tp_rows       <- dt_tp_hmap$rowname
-dt_tp_hmap            <- dt_tp_hmap %>%
-  dplyr::select(-rowname) %>%
-  mutate_all(abs)
-row.names(dt_tp_hmap) <- dt_tp_rows
-
-pheatmap::pheatmap(
-  t(dt_tp_hmap),
-  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
-                                            "Reds"))(100),
-  cluster_cols = TRUE, cluster_rows = TRUE,
-  na.col = "grey",
-  cellheight = 7)
-
-# ---- dotplot ----
-
-prep_dotplot <- function(x, col_name){
-  dplyr::select(x, UQ(rlang::sym(col_name))) %>% 
-    dplyr::mutate(var = factor(row.names(x), 
-                            levels = rev(row.names(x)))) %>%
-    dplyr::filter(!(var %in% c("tp", "tn")))
-}
-
-plot_opts <- theme(axis.title.y = element_blank(), 
-                   axis.text = element_text(size = 8))
-plot_grid(
-  ggplot(data = prep_dotplot(dt_tp, "tp")) + 
-    geom_point(aes(x = tp, y = var)) + 
-    plot_opts, 
-  ggplot(data = prep_dotplot(dt_tn, "tn")) + 
-    geom_point(aes(x = tn, y = var)) +
-    plot_opts
-)
-
-# ---- densityplots ----
-library(ggforce)
-
-ggplot(data = tidyr::gather(dt_sub)) + 
-  geom_density(aes(value)) +
-  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 1)
-ggplot(data = tidyr::gather(dt_sub)) + 
-  geom_density(aes(value)) +
-  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 2)
-ggplot(data = tidyr::gather(dt_sub)) + 
-  geom_density(aes(value)) +
-  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 3)
-ggplot(data = tidyr::gather(dt_sub)) + 
-  geom_density(aes(value)) +
-  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 4)
-
-```
-
-```{r n-dep_dotplot}
+ggplot(data = dt_sub) + 
+  geom_point(aes(x = ))
 
@@
 
-test <- slice_cormat("nitrogen_atmospheric_deposition", dt_sub)
+prep_dotplot <- function(x, col_name){
+  dplyr::select(x, UQ(rlang::sym(col_name))) %>% 
+    dplyr::mutate(var = factor(row.names(x), 
+                            levels = rev(row.names(x)))) %>%
+    dplyr::filter(!(var %in% c("tp", "tn")))
+}
 
-ggplot(data = prep_dotplot(test, "nitrogen_atmospheric_deposition")) +
+dt_ndep <- slice_cormat("nitrogen_atmospheric_deposition", dt_sub)
+
+ggplot(data = prep_dotplot(dt_ndep, "nitrogen_atmospheric_deposition")) +
     geom_point(aes(x = nitrogen_atmospheric_deposition, y = var)) +

### 2019-05-17 figures/10_nitrogen_deposition.Rmd
add some autocorellation todos

@@
 
-```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE}
+```{r 10_nitrogen_deposition, echo=FALSE, message=TRUE, eval=TRUE}
 dt     <- readRDS("../data/dt.rds")
@@
   data.frame(stringsAsFactors = FALSE)
-
-plot(lg$hu12.chag$hu12_dep_totaln_2010_mean, 
-     lg$hu12.chag$hu12_prism_ppt_30yr_normal_800mm2_annual_mean)
-
-ggplot(data = dt_sub) + 
-  geom_point(aes(x = ))
 
@@
 ggplot(data = prep_dotplot(dt_ndep, "nitrogen_atmospheric_deposition")) +
-    geom_point(aes(x = nitrogen_atmospheric_deposition, y = var)) +
-    plot_opts
+    geom_point(aes(x = nitrogen_atmospheric_deposition, y = var))
+
+# ---- scatterplots ----
+# plot n_dep vs ppt
+# plot n_dep vs baseflow
+
+# plot(lg$hu12.chag$hu12_dep_totaln_2010_mean, 
+#      lg$hu12.chag$hu12_prism_ppt_30yr_normal_800mm2_annual_mean)
+
+# ggplot(data = dt_sub) + 
+#   geom_point(aes(x = ))
+
+# ---- autocorrelation_plots ----
+# spind::acfft()
 

### 2019-05-17 scripts/03_model.R

@@ -111,6 +111,10 @@ dt %>%
   # stat_pointinterval(alpha = 0.4) +
   theme(axis.text.x = element_text(angle = 90))
 
+# choropleth of model residuals
+
+# autocorrelation plot of model residuals
+
 # ----
 
 # knitr::kable(r2_fe, "markdown")

### 2019-05-20 figures/08_exploratory_dotplot.Rmd
add color to dotplot

@@
 prep_dotplot <- function(x, col_name){
-  dplyr::select(x, UQ(rlang::sym(col_name))) %>% 
+  pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
+  res      <- dplyr::select(x, UQ(rlang::sym(col_name))) %>%
+    dplyr::mutate(var = row.names(x)) %>%
+    dplyr::left_join(pred_key, by = "var") %>%
     dplyr::mutate(var = factor(row.names(x), 
-                            levels = rev(row.names(x)))) %>%
+                            levels = rev(row.names(x))), 
+                  category = factor(category, 
+                                    levels = c("lake", "nutrient_sources",
+                                               "nutrient_proxies",
+                                               "transport_capacity"))) %>%
     dplyr::filter(!(var %in% c("tp", "tn")))
+  res
 }
@@
 plot_opts <- theme(axis.title.y = element_blank(), 
-                   axis.text = element_text(size = 8))
+                   axis.text = element_text(size = 8), 
+                   legend.position = 0)
+
+# show_col(brewer_pal("div", "Set1")(4))                   
 plot_grid(
   ggplot(data = prep_dotplot(dt_tp, "tp")) + 
-    geom_point(aes(x = tp, y = var)) + 
+    geom_point(aes(x = tp, y = var, color = category)) + 
+    scale_color_brewer(palette = "Set1") +
     plot_opts, 
   ggplot(data = prep_dotplot(dt_tn, "tn")) + 
-    geom_point(aes(x = tn, y = var)) +
+    geom_point(aes(x = tn, y = var, color = category)) +
+    scale_color_brewer(palette = "Set1") +
     plot_opts

### 2019-05-20 figures/08_exploratory_dotplot.Rmd
prettyfi dotplot labels

--- 2019-05-17 figures/08_exploratory_dotplot.Rmd
@@
 prep_dotplot <- function(x, col_name){
-  dplyr::select(x, UQ(rlang::sym(col_name))) %>% 
+  pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
+  res      <- dplyr::select(x, UQ(rlang::sym(col_name))) %>%
+
+    dplyr::mutate(var = row.names(x)) %>%
+    dplyr::left_join(pred_key, by = "var") %>%
     dplyr::mutate(var = factor(row.names(x), 
-                            levels = rev(row.names(x)))) %>%
+                            levels = rev(row.names(x))), 
+                  pretty = factor(pretty, levels = rev(pretty)),
+                  category = factor(category, 
+                                    levels = c("Lake", "Nutrient sources",
+                                               "Nutrient proxies",
+                                               "Transport capacity"))) %>%
     dplyr::filter(!(var %in% c("tp", "tn")))
+  res
 }
@@
 plot_opts <- theme(axis.title.y = element_blank(), 
-                   axis.text = element_text(size = 8))
+                   axis.text = element_text(size = 8), 
+                   legend.position = 0)
+
+# head(prep_dotplot(dt_tp, "tp"))
+# show_col(brewer_pal("div", "Set1")(4))                   
+gg_tp <-  ggplot(data = prep_dotplot(dt_tp, "tp")) + 
+    geom_point(aes(x = tp, y = pretty, color = category)) + 
+    scale_color_brewer(palette = "Set1") +
+    xlim(0, 0.5) +
+    plot_opts
+gg_tn <- ggplot(data = prep_dotplot(dt_tn, "tn")) + 
+    geom_point(aes(x = tn, y = pretty, color = category)) +
+    scale_color_brewer(palette = "Set1") +
+    xlim(0, 0.5) +
+    plot_opts
+legend_b <- get_legend(gg_tp + 
+                         theme(legend.position="bottom", 
+                               legend.justification = "center", 
+                               legend.text = element_text(size = 10), 
+                               legend.title = element_blank()))
 plot_grid(
-  ggplot(data = prep_dotplot(dt_tp, "tp")) + 
-    geom_point(aes(x = tp, y = var)) + 
-    plot_opts, 
-  ggplot(data = prep_dotplot(dt_tn, "tn")) + 
-    geom_point(aes(x = tn, y = var)) +
-    plot_opts
-)
+  plot_grid(gg_tp, gg_tn), 
+  legend_b, ncol = 1, rel_heights = c(1, 0.1))
 

### 2019-05-20 scripts/99_make_predictor_key.R

@@ -7,15 +7,24 @@ pred_key <- data.frame(var = c(
   "soil_org_carbon", "soybeans","n_input", 
   "nitrogen_fertilizer_use", "phosphorus_fertilizer_use","p_input", 
   "phosphorus_livestock_manure", "wheat","pasture"),
+                      pretty = c(
+    "N deposition", "Max depth", "Watershed-lake ratio", 
+    "Baseflow", "Precipitation", "Lake-buffer Ag", 
+    "Stream-buffer Ag", "Wetlands", "Ag",
+    "Non-ag", "Clay", "Lake area",
+    "Wetland potential", "Corn", "Manure N input", 
+    "Soil organic carbon", "Soybeans", "N input",
+    "Fertilizer N input", "Fertilizer P input", "P input", 
+    "Manure P input", "Wheat", "Pasture"),
                       category = c(
-  "nutrient_sources", "lake", "lake", 
-  "transport_capacity", "transport_capacity", "nutrient_proxies",
-  "nutrient_proxies","nutrient_proxies","nutrient_proxies",
-  "nutrient_proxies", "transport_capacity","lake",
-  "transport_capacity", "nutrient_proxies","nutrient_sources", 
-  "nutrient_proxies", "nutrient_proxies", "nutrient_sources",
-  "nutrient_sources", "nutrient_sources", "nutrient_sources", 
-  "nutrient_sources", "nutrient_proxies","nutrient_proxies"),
+  "Nutrient sources", "Lake", "Lake", 
+  "Transport capacity", "Transport capacity", "Nutrient proxies",
+  "Nutrient proxies","Nutrient proxies","Nutrient proxies",
+  "Nutrient proxies", "Transport capacity","Lake",
+  "Transport capacity", "Nutrient proxies","Nutrient sources", 
+  "Nutrient proxies", "Nutrient proxies", "Nutrient sources",
+  "Nutrient sources", "Nutrient sources", "Nutrient sources", 
+  "Nutrient sources", "Nutrient proxies","Nutrient proxies"),
                       stringsAsFactors = FALSE)
 
 # View(pred_key)

### 2019-05-21 figures/08_exploratory_dotplot.Rmd
linting

@@
   pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
-  res      <- dplyr::select(x, UQ(rlang::sym(col_name))) %>%
-
+  res      <- 
+    dplyr::select(x, UQ(rlang::sym(col_name))) %>%
     dplyr::mutate(var = row.names(x)) %>%

### 2019-05-21 figures/08_exploratory_dotplot.Rmd
prettyfi hmap labels

@@
 ```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE}
+pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
 dt       <- readRDS("../data/dt.rds")
@@
 row.names(dt_tp_hmap) <- dt_tp_rows
+
+# prettyfi variable labels
+pretty_names <- pred_key$pretty[match(names(dt_tp_hmap), pred_key$var)] 
+pretty_names <- pretty_names[!is.na(pretty_names)]
+names(dt_tp_hmap)[which(!is.na(match(names(dt_tp_hmap), pred_key$var)))] <- 
+  pretty_names
+pretty_names <- pred_key$pretty[match(row.names(dt_tp_hmap), pred_key$var)] 
+pretty_names <- pretty_names[!is.na(pretty_names)]
+row.names(dt_tp_hmap)[which(!is.na(match(row.names(dt_tp_hmap), pred_key$var)))] <- 
+  pretty_names
 

### 2019-05-22 figures/01_county_extent.Rmd
cleanup legends

@@
 knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
+# setwd("figures")
+source("../scripts/99_utils.R")
 ```
@@
 ```{r lagos_setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE}
-# setwd("_episodes_rmd")
-library(vapour)
-library(LAGOSNE)
-library(magrittr)
-library(dplyr)
-library(lme4)
-library(sf)
-library(units)
-library(merTools)
-library(ggplot2)
-library(cowplot)
-library(ggridges)
-library(tidyr)
-library(ggExtra)
+# library(LAGOSNE)
+# library(magrittr)
+# library(dplyr)
+# library(lme4)
+# library(sf)
+# library(units)
+# library(merTools)
+# library(ggplot2)
+# library(cowplot)
+# library(ggridges)
+# library(tidyr)
+# library(ggExtra)
 
@@
 ```
+
+```{r tptn_maps, echo=FALSE}
+ep         <- readRDS("../data/ep.rds")
+
+mround <- function(x, base){
+        base * round(x / base)
+}
+
+q_breaks <- function(x, var_name){
+  # x <- ep
+  # var_name <- "tn"
+  qs              <- c(mround(quantile(as.numeric(as.data.frame(x[,var_name])[,1]), na.rm = TRUE), 5))
+  labels          <- as.character(qs)
+  res             <- cut(as.numeric(as.data.frame(x[,var_name])[,1]), 
+                         breaks = c(qs, Inf), 
+                         labels = as.character(qs), 
+                         include.lowest = TRUE)
+
+  levels(res)[1]  <- paste0("> ", levels(res)[1])
+  levels(res)[length(levels(res))] <- 
+    paste0("> ", levels(res)[length(levels(res))])
+  res
+}
+
+plot_opts <- theme_void() + 
+  theme(title = element_text(size = 10), 
+        # legend.position = "bottom", 
+        panel.border = element_rect(colour = "black", fill = NA, size=1), 
+        legend.spacing.x = unit(0.000001, "cm"), 
+        legend.direction = "horizontal", 
+        legend.position = "bottom", 
+        legend.justification = "left")
+
+ep$plot_breaks <- q_breaks(ep, "tp")
+
+gg_tp <- ggplot() +
+  geom_sf(data = state_intersects) +
+  geom_sf(data = dplyr::filter(coordinatize(ep), !is.na(tp)), 
+          aes(color = plot_breaks), show.legend = "point", size = 0.7) +
+  scale_color_viridis_d() +
+  labs(color = "tp") +
+  coord_sf(datum = NA) +
+  plot_opts
+
+ep$plot_breaks <- q_breaks(ep, "tn")
+
+gg_tn <- ggplot() +
+  geom_sf(data = state_intersects) +
+  geom_sf(data = dplyr::filter(coordinatize(ep), !is.na(tn)), 
+          aes(color = plot_breaks), show.legend = "point", size = 0.7) +
+  scale_color_viridis_d() +
+  labs(color = "tn") +
+  coord_sf(datum = NA) +
+  guides(color = guide_legend(nrow = 1)) +
+  plot_opts
+
+# View(ep[,c("tn", "plot_breaks")])
+
+plot_grid(gg_tp, 
+          ggplot() + geom_blank(), gg_tn,
+          nrow = 1, rel_widths = c(1, 0.1, 1))
+```

### 2019-05-22 manuscript/figures.Rmd
add cdl vs nlcd map
cleanup legends

@@
 
+```{r maps, fig.cap = "Quanitle map of lake nutrients.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/tptn_maps-1.pdf")
+```
+
+```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.
+Line is 1:1 not regression.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
+```
+
+```{r nlcd-versus-cdl_map, fig.cap = "Comparison between NLCD (2011) ag and pasture against CDL (2010) specific crops.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
+```
+
+```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/09_stream_buffer-1.pdf")
+```
+
+```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/satellite-1.pdf")
+```
+
+```{r exploratory_dotplot, fig.cap = "Exploratory dotplots showing absolute value correlations.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/08_exploratory_dotplot-2.pdf")
+```
+
+```{r exploratory_heatmap, fig.cap = "Exploratory heatmap showing absolute value correlations.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
+```
+
 ```{r hierarchical_demo, fig.cap = "A) Global (dashed line) and regional (solid lines) fits to the relationship between lake phosphorus and IWS Ag.
@@
 knitr::include_graphics("../figures/03_wetland_potential-1.pdf")
-```
-
-```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.
-Line is 1:1 not regression.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
 ```
@@
 ```
-
-```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/09_stream_buffer-1.pdf")
-```
-
-```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/satellite-1.pdf")
-```
-
-```{r exploratory_heatmap, fig.cap = "Exploratory heatmap showing absolute value correlations.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
-```
-
-```{r exploratory_dotplot, fig.cap = "Exploratory dotplots showing absolute value correlations.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/08_exploratory_dotplot-2.pdf")
-```

### 2019-05-22 scripts/99_utils.R

@@ -31,6 +31,7 @@ suppressMessages(library(smoothr))
 library(assertr)
 library(HydroData) # install_github("mikejohnson51/HydroData")
 library(kableExtra)
+library(vapour)
 
 theme_opts <- theme(axis.text = element_blank(),
                     axis.ticks = element_blank(),

### 2019-05-22 figures/01_county_extent.Rmd
embiggen map
plot residual spatial autocorrellation range

@@
 
-```{r tptn_maps, echo=FALSE}
+```{r tptn_maps, echo=FALSE, fig.width=7}
 ep         <- readRDS("../data/ep.rds")
@@
 ```
+
+```{r }
+# residual autocorrelation range
+pnt <- LAGOSNE::coordinatize(ep[1,])
+
+ggplot() + 
+  geom_sf(data = state_intersects) +
+  geom_sf(data = st_buffer(pnt, 0.3), color = "red") +
+  geom_sf(data = pnt, size = 0.5) +
+  coord_sf(datum = NA) +
+  plot_opts
+```

### 2019-05-22 figures/08_exploratory_dotplot.Rmd
use scaled variables in heatmap plus dotplot

@@
 pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
-dt       <- readRDS("../data/dt.rds")
+
+dt       <- readRDS("../data/dt_scaled.rds")
 dt_sub   <- dt %>% 

### 2019-05-22 scripts/02_aggregate_predictors.R

@@ -63,6 +63,26 @@ saveRDS(dt, "data/dt.rds")
 write.csv(dt, "data/dt.csv", row.names = FALSE)
 # dt <- readRDS("data/dt.rds")
 
+dt_scaled <- dt %>% 
+  dplyr::select("lagoslakeid", "hu4_zoneid", "hu12_zoneid", 
+                "tp", "tn", "hu12_ppt_mean", "hu12_baseflow_mean",
+                "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
+                "soybeans", "pasture", "p_input", "n_input",
+                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use", 
+                "stream_cultivated_crops") %>% 
+  dplyr::filter(!is.na(phosphorus_fertilizer_use), 
+                !is.na(soybeans), 
+                !is.na(corn),
+                !is.na(maxdepth), 
+                !is.na(tp), 
+                !is.na(tn)) %>%
+  mutate_at(log, .vars = vars(tp, tn)) %>%
+  mutate_at(scale, .vars = vars(-lagoslakeid, -hu4_zoneid, -hu12_zoneid))
+
+saveRDS(dt, "data/dt_scaled.rds")
+write.csv(dt, "data/dt_scaled.csv", row.names = FALSE)
+# dt_scaled <- readRDS("data/dt_scaled.rds")
+
 dt_units <- data.frame(variable = names(dt), stringsAsFactors = FALSE) %>%
   mutate(units = case_when(
     variable %in% names(cdl)[-1] ~ "percent",

### 2019-05-22 scripts/03_model.R

@@ -4,24 +4,8 @@ library(brms)
 library(tidybayes)
 library(modelr)
 
-dt        <- readRDS("data/dt.rds") %>% 
-  dplyr::select("lagoslakeid", "hu4_zoneid", "hu12_zoneid", 
-                "tp", "tn", "hu12_ppt_mean", "hu12_baseflow_mean",
-                "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
-                "soybeans", "pasture", "p_input", "n_input",
-                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use", 
-                "stream_cultivated_crops")
+dt        <- readRDS("data/dt_scaled.rds") 
 names(dt) <- gsub("_", "v", names(dt))
-dt        <- dplyr::filter(dt, 
-                           !is.na(phosphorusvfertilizervuse), 
-                           !is.na(soybeans), 
-                           !is.na(corn),
-                           !is.na(maxdepth), 
-                           !is.na(tp), 
-                           !is.na(tn))
-dt <- mutate_at(dt, log, .vars = vars(tp, tn))
-dt <- mutate_at(dt, scale, 
-                .vars = vars(-lagoslakeid, -hu4vzoneid, -hu12vzoneid))
 
 good_hu4s <- readRDS("data/dt.rds") %>%
   group_by(hu4_zoneid) %>% 

### 2019-05-22 scripts/99_utils.R

@@ -280,4 +280,3 @@ get_if_not_exists <- function(x, destfile, read_function = readRDS,
   }
 }
 
-lg <- LAGOSNE::lagosne_load()

### 2019-05-22 figures/08_exploratory_dotplot.Rmd
remake dotplot with dt_scaled

@@
 dt_sub   <-  dt %>% 
-  dplyr::select(tp, tn, lake_area_ha:wheat, 
-                matches("cultivated_crops")) %>%
-  dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
-  dplyr::select(-mixed.crop, -matches("other"), -forage, 
-                -hu12_ppt_std, -water, -developed, -forest) %>% # rm junk
-  dplyr::filter(complete.cases(.)) %>%
+  dplyr::select(-lagoslakeid) %>%
+  # dplyr::select(tp, tn, lake_area_ha:wheat, 
+  #               matches("cultivated_crops")) %>%
+  # dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
+  # dplyr::select(-mixed.crop, -matches("other"), -forage, 
+  #               -hu12_ppt_std, -water, -developed, -forest) %>% # rm junk
+  # dplyr::filter(complete.cases(.)) %>%
   mutate_all(as.numeric) %>%
+  janitor::remove_empty("cols") %>%
   data.frame(stringsAsFactors = FALSE)
+
+# cor.test(dt_sub$nitrogen_atmospheric_deposition, dt_sub$tp)
 
@@
 prep_dotplot <- function(x, col_name){
+  # x <- dt_tp
+  # col_name <- "tp"
   pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
-  res      <- 
-    dplyr::select(x, UQ(rlang::sym(col_name))) %>%
+  res      <- x %>%
+    dplyr::select(UQ(rlang::sym(col_name))) %>%
+    # dplyr::filter(!is.na(UQ(rlang::sym(col_name)))) %>%
     dplyr::mutate(var = row.names(x)) %>%
@@
     scale_color_brewer(palette = "Set1") +
-    xlim(0, 0.5) +
+    xlim(0, 0.6) +
     plot_opts
@@
   facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 3)
-ggplot(data = tidyr::gather(dt_sub)) + 
-  geom_density(aes(value)) +
-  facet_wrap_paginate(~key, scales = "free", ncol = 2, nrow = 4, page = 4)
 

### 2019-05-22 scripts/02_aggregate_predictors.R

@@ -61,15 +61,17 @@ dt <- ep %>%
 
 saveRDS(dt, "data/dt.rds")
 write.csv(dt, "data/dt.csv", row.names = FALSE)
-# dt <- readRDS("data/dt.rds")
+# dt <- readRDS("../data/dt.rds")
 
 dt_scaled <- dt %>% 
   dplyr::select("lagoslakeid", "hu4_zoneid", "hu12_zoneid", 
                 "tp", "tn", "hu12_ppt_mean", "hu12_baseflow_mean",
                 "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
-                "soybeans", "pasture", "p_input", "n_input",
-                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use", 
-                "stream_cultivated_crops") %>% 
+                "soybeans", "pasture", 
+                "nitrogen_atmospheric_deposition", "clay_pct", 
+                "lake_area_ha", "wetland_potential", contains("manure"), 
+                contains("fertilizer"), contains("input"), 
+                contains("cultivated_crops")) %>% 
   dplyr::filter(!is.na(phosphorus_fertilizer_use), 
                 !is.na(soybeans), 
                 !is.na(corn),
@@ -79,8 +81,8 @@ dt_scaled <- dt %>%
   mutate_at(log, .vars = vars(tp, tn)) %>%
   mutate_at(scale, .vars = vars(-lagoslakeid, -hu4_zoneid, -hu12_zoneid))
 
-saveRDS(dt, "data/dt_scaled.rds")
-write.csv(dt, "data/dt_scaled.csv", row.names = FALSE)
+saveRDS(dt_scaled, "data/dt_scaled.rds")
+write.csv(dt_scaled, "data/dt_scaled.csv", row.names = FALSE)
 # dt_scaled <- readRDS("data/dt_scaled.rds")
 
 dt_units <- data.frame(variable = names(dt), stringsAsFactors = FALSE) %>%

### 2019-05-22 scripts/99_make_predictor_key.R

@@ -6,7 +6,7 @@ pred_key <- data.frame(var = c(
   "wetland_potential", "corn","nitrogen_livestock_manure", 
   "soil_org_carbon", "soybeans","n_input", 
   "nitrogen_fertilizer_use", "phosphorus_fertilizer_use","p_input", 
-  "phosphorus_livestock_manure", "wheat","pasture"),
+  "phosphorus_livestock_manure", "wheat","pasture", "row_crop_pct"),
                       pretty = c(
     "N deposition", "Max depth", "Watershed-lake ratio", 
     "Baseflow", "Precipitation", "Lake-buffer Ag", 
@@ -15,7 +15,7 @@ pred_key <- data.frame(var = c(
     "Wetland potential", "Corn", "Manure N input", 
     "Soil organic carbon", "Soybeans", "N input",
     "Fertilizer N input", "Fertilizer P input", "P input", 
-    "Manure P input", "Wheat", "Pasture"),
+    "Manure P input", "Wheat", "Pasture", "Row-crop Ag"),
                       category = c(
   "Nutrient sources", "Lake", "Lake", 
   "Transport capacity", "Transport capacity", "Nutrient proxies",
@@ -24,7 +24,7 @@ pred_key <- data.frame(var = c(
   "Transport capacity", "Nutrient proxies","Nutrient sources", 
   "Nutrient proxies", "Nutrient proxies", "Nutrient sources",
   "Nutrient sources", "Nutrient sources", "Nutrient sources", 
-  "Nutrient sources", "Nutrient proxies","Nutrient proxies"),
+  "Nutrient sources", "Nutrient proxies","Nutrient proxies", "Nutrient proxies"),
                       stringsAsFactors = FALSE)
 
 # View(pred_key)

### 2019-05-23 figures/01_county_extent.Rmd
supress messages for clean pngs

@@
 
-```{r setup, include=FALSE}
+```{r setup, include=FALSE, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE}
 knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
@@
 
-```{r 01_county_extent, eval=TRUE, echo=FALSE, fig.width = 5.5, fig.height = 3}
+```{r 01_county_extent, eval=TRUE, echo=FALSE, fig.width = 5.5, fig.height = 3, message=FALSE, warning=FALSE}
 # counties that overlap hi ag iws with ep data
@@
 
-```{r tptn_maps, echo=FALSE, fig.width=7}
+\pagebreak
+
+```{r tptn_maps, echo=FALSE, fig.width=7, message=FALSE, eval=TRUE, warning=FALSE}
 ep         <- readRDS("../data/ep.rds")
@@
 
-```{r }
+\pagebreak
+```{r autocor_range, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE}
 # residual autocorrelation range

### 2019-05-23 figures/06_lulc_buffer_demo.Rmd
supress messages for clean pngs

@@
 
-```{r setup, include=FALSE}
+```{r setup, include=FALSE, message=FALSE, warning=FALSE}
 knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 7, fig.height = 7)
@@
 
-```{r 06_lulc_buffer_demo, echo=FALSE, eval=TRUE}
+```{r 06_lulc_buffer_demo, echo=FALSE, eval=TRUE, message=FALSE}
 # setwd("figures")
@@
 
-```{r cdl_viewport, fig.height=5}
+```{r cdl_viewport, fig.height=5, echo=FALSE, message=FALSE}
 # pull cdl lulc
@@
 
-```{r cdl_vs_nlcd}
+```{r cdl_vs_nlcd, echo=FALSE, message=FALSE}
 # mask nlcd lulc
@@
 
-```{r raster_resolution}
+```{r raster_resolution, echo=FALSE, message=FALSE}
 library(nadp)

### 2019-05-23 figures/08_exploratory_dotplot.Rmd
supress messages for clean pngs

@@
 
-```{r setup, include=FALSE}
+```{r setup, include=FALSE, message=FALSE, echo=FALSE, warning=FALSE}
 knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 6.5, fig.height = 4.5)
@@
 
-```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE}
+```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE, warning=FALSE}
 pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
@@
   cellheight = 7)
+```
 
+```{r dotplot, message=FALSE, echo=FALSE, warning=FALSE}
 # ---- dotplot ----
@@
 
+```
+
+```{r densityplots, message=FALSE, echo=FALSE, warning=FALSE}
 # ---- densityplots ----

### 2019-05-23 figures/09_stream_buffer.Rmd
reverse panel order
supress messages for clean pngs

@@
 
-```{r satellite, echo=FALSE}
+```{r satellite, echo=FALSE, message=FALSE, warning=FALSE}
 # res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
@@
 
-cowplot::plot_grid(gg_low_ag, gg_hi_ag)
+cowplot::plot_grid(gg_hi_ag, gg_low_ag)
 ```

### 2019-05-23 scripts/03_model.R
towards results table

@@ -38,14 +38,14 @@ brm_fit <- function(destfile, formula, data){
 fe_brms <- 
   lapply(seq_along(model_forms_fe), function(i) 
     get_if_not_exists(brm_fit, 
-                      paste0("data/mcmc/fe/", names(model_forms)[i]), 
-                      formula = model_forms[[i]], 
+                      paste0("data/mcmc/fe/", names(model_forms_fe)[i]), 
+                      formula = model_forms_fe[[i]], 
                       data = dt))
 
 
 r2_fe <- dplyr::bind_rows(
   lapply(fe_brms, function(x) data.frame(brms::bayes_R2(x)))) %>%
-  mutate(Model = names(model_forms), 
+  mutate(Model = names(model_forms_fe), 
          Estimate = round(Estimate, 2)) %>%
   dplyr::select(Model, Estimate) 
 
@@ -78,14 +78,14 @@ r2_fe <- dplyr::bind_rows(
 re_brms <- 
   lapply(seq_along(model_forms_re), function(i) 
     get_if_not_exists(brm_fit, 
-                      paste0("data/mcmc/re/", names(model_forms)[i]), 
-                      formula = model_forms[[i]], 
+                      paste0("data/mcmc/re/", names(model_forms_re)[i]), 
+                      formula = model_forms_re[[i]], 
                       data = dt))
 
 
 r2_re <- dplyr::bind_rows(
   lapply(re_brms, function(x) data.frame(brms::bayes_R2(x)))) %>%
-  mutate(Model = names(model_forms), 
+  mutate(Model = names(model_forms_re), 
          Estimate = round(Estimate, 2)) %>%
   dplyr::select(Model, Estimate)
 
@@ -97,6 +97,12 @@ r2_fe$`Transport` <- c(NA, NA, "Baseflow", "Baseflow",
                        NA, NA, "Soil Org Carbon", "Soil Org Carbon")
 r2_fe$`Source`    <- c(NA, NA, NA, "N fertilizer", 
                     NA, NA, NA, "N fertilizer")
+
+r2_re$`Proxy`     <- c("Ag", "Stream Ag", "Soybeans", "Pasture", "Row Crop",
+                       "Ag", "Stream Ag", "Corn", "Pasture", "Row Crop") 
+r2_re$`Lake`      <- c(rep("maxdepth", 10))
[…]

### 2019-05-23 figures/08_exploratory_dotplot.Rmd
split mega figs

@@
 
+\pagebreak
 ```{r dotplot, message=FALSE, echo=FALSE, warning=FALSE}
@@
 
+\pagebreak
 ```{r densityplots, message=FALSE, echo=FALSE, warning=FALSE}

### 2019-05-24 tables/02_cdl_key.Rmd
format tables for presentation

@@
 
-```{r summary_table, eval=TRUE}
+```{r cdl_key, eval=TRUE}
 library(kableExtra)
@@
   sample_n(1) %>%
+  arrange(is_ag, code) %>%
+  dplyr::select(-is_forage) %>%
+  dplyr::select(category, ag = is_ag, example = description, code) %>%
   knitr::kable(digits = 0, format = "markdown", caption = "Example of CDL categorizations.") 
+```
 
+\pagebreak
+```{r cdl_summary}
 # ---- cdl summary ----
@@
   t() %>%
-  knitr::kable(format = "markdown", caption = "CDL summary statistics")
+  knitr::kable(caption = "CDL summary statistics", format = "latex", booktabs = TRUE) %>%
+  kable_styling(latex_options = c("hold_position"), full_width = FALSE) %>%
+  add_header_above(c(" ", "Quantiles" = 3))
 ```

### 2019-05-24 tables/03_model_summary.Rmd
format tables for presentation

@@
 library(magrittr)
+library(stringr)
 
 # setwd("tables")
-read.csv("../data/mcmc/model_r2.csv", 
-                     stringsAsFactors = FALSE) %>%
-  knitr::kable(digits = 2, format = "markdown", caption = "Model R2")
+dt <- read.csv("../data/mcmc/model_r2.csv", 
+                     stringsAsFactors = FALSE)
+
+options(knitr.kable.NA = "-")  
+dplyr::filter(dt, str_detect(Model, "tp")) %>%
+  dplyr::select(-Model) %>%
+  dplyr::rename("$R^2$" = Estimate) %>%
+  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2")
 ```
+
+\pagebreak
+```{r tn_results}
+dplyr::filter(dt, str_detect(Model, "tn")) %>%
+  dplyr::select(-Model) %>%
+  dplyr::rename("$R^2$" = Estimate) %>%
+  knitr::kable(digits = 2, format = "markdown", caption = "TN Model R2")
+```

### 2019-05-24 scripts/03_model.R

@@ -111,8 +111,13 @@ if(!interactive()){
             "data/mcmc/model_r2.csv",
             row.names = FALSE)
 }
+# r2 <- read.csv("../data/mcmc/model_r2.csv")
 
 # ---- diagnostics ----
+# loo comparison
+loo_compare(loo(re_brms[[6]]), loo(re_brms[[8]])) # corn model has lowest error
+loo_compare(loo(re_brms[[1]]), loo(re_brms[[5]])) # Ag model has lowest error
+ 
 # get median residuals of each model object
 # get_residuals <- function(model, threshold = 0.1){
 #   # model <- re_brms[[1]]

### 2019-05-30 figures/07_model-selection.Rmd
cleanup stream buffer scatter plot
make residual dotplot

@@
 # setwd("figures")
-ids <- test <- readRDS("../data/dt.rds") %>%
+ids <- readRDS("../data/dt.rds") %>%
   group_by(hu4_zoneid) %>% 
@@
 #                 summarize(
+
 #                   group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
@@
 
-```{r model_fitting, echo=FALSE}
+```{r residual_dotplot, echo=FALSE}
+fit <- readRDS("data/mcmc/re/tn_corn")
+
+get_residuals <- function(model, threshold = 0.1){
+  # model <- re_brms[[1]]
+  model$res_med <- dt %>%
+    add_residual_draws(model) %>%
+    group_by(lagoslakeid) %>%
+    summarize(.residual_median = median(.residual)) %>%
+    left_join(dplyr::select(lg$locus, lagoslakeid, nhd_lat, nhd_long),
+              by = "lagoslakeid")
+
+  model$res_med <- dt %>%
+    add_fitted_draws(model) %>%
+    group_by(lagoslakeid) %>%
+    summarize(.value_median = median(.value)) %>%
+    right_join(model$res_med, by = "lagoslakeid")
+
+  model$res_test <- abs(
+    median(model$res_med$.residual_median, na.rm = TRUE)) < threshold
+  model
+}
+lg <- lagosne_load()
+fit <- get_residuals(fit)
+
+states_lg <- 
+  state_sf()[unlist(lapply(st_intersects(state_sf(), LAGOSNE::coordinatize(fit$res_med)), function(x) length(x) > 0)),]
+
+ggplot() + 
+  geom_sf(data = states_lg) +
+  geom_sf(data = LAGOSNE::coordinatize(fit$res_med), 
+          aes(color = .residual_median), size = 0.8) +
+  coord_sf(datum = NA) +
+  theme_void() + 
+  scale_color_gradient2() +
+  labs(color = "tn_corn model residuals")
+
+```
+
+```{r model_fitting, echo=FALSE, eval=FALSE}
 library(brms)
@@
 
-```{r model_diagnostics_basics, echo=FALSE, fig.height=2}
+```{r model_diagnostics_basics, echo=FALSE, fig.height=2, eval=FALSE}
 # get_variables(fit0)
@@
 
-```{r model_diagnostics_advanced, fig.height=4, echo=FALSE}
+```{r model_diagnostics_advanced, fig.height=4, echo=FALSE, eval=FALSE}
 # pull global distribution (lower, mean, upper)
@@
 
-```{r signif_map, echo=FALSE}
+```{r signif_map, echo=FALSE, eval=FALSE}
 ggplot() + 

### 2019-05-30 figures/07_model-selection.Rmd
add resid dotplot to makefile

@@
 
-```{r 07_model_selection, fig.height=3, echo=FALSE}
+```{r 07_model_selection, fig.height=3, echo=FALSE,eval=FALSE}
 
@@
 ```{r residual_dotplot, echo=FALSE}
-fit <- readRDS("data/mcmc/re/tn_corn")
+library(tidybayes)
+library(brms)
+
+fit <- readRDS("../data/mcmc/re/tn_corn")
+
+dt        <- readRDS("../data/dt_scaled.rds") 
+names(dt) <- gsub("_", "v", names(dt))
+
+good_hu4s <- readRDS("../data/dt.rds") %>%
+  group_by(hu4_zoneid) %>% 
+  tally() %>%
+  dplyr::filter(n >= 3)
+dt <- dplyr::filter(dt, hu4vzoneid %in% good_hu4s$hu4_zoneid)
 
 get_residuals <- function(model, threshold = 0.1){
-  # model <- re_brms[[1]]
+  # model <- fit
   model$res_med <- dt %>%
@@
 
-states_lg <- 
-  state_sf()[unlist(lapply(st_intersects(state_sf(), LAGOSNE::coordinatize(fit$res_med)), function(x) length(x) > 0)),]
+states_lg <- state_sf()[
+  unlist(lapply(
+    st_intersects(state_sf(), LAGOSNE::coordinatize(fit$res_med)),
+    function(x) length(x) > 0)),]
 

### 2019-06-10 figures/07_model-selection.Rmd
all makefile targets run

@@
   scale_color_gradient2() +
-  labs(color = "tn_corn model residuals")
+  labs(color = "tn_corn \n model residuals")
 
@@
 
-```{r model_fitting, echo=FALSE, eval=FALSE}
+```{r model_fitting, echo=FALSE, eval=TRUE}
 library(brms)
@@
 library(modelr)
+
+brm_fit <- function(destfile, formula, data){
+  fit <- brm(formula = formula, data = data, 
+             family = gaussian())
+  saveRDS(fit, destfile)
+  return(fit)
+}
 
@@
 hist((dt$iwslavratio - mean(dt$iwslavratio)) / sd(dt$iwslavratio))
-test <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid))
+test <- dt %>% mutate_if(function(col) is.numeric(col) & 
+                    !all(col == .$lagoslakeid) &
+                    !all(col == .$hu4vzoneid), scale)
 
 # non-linear re
-model_form <- bf(tp ~ bagvpct * agvpct, 
+model_form <- bf(tp ~ bagvpct * ag, 
                  bagvpct ~ 1 + 
@@
 # non-linear re w/ 2nd level coeffs
-model_form2 <- bf(tp ~ bagvpct * agvpct, 
+model_form2 <- bf(tp ~ bagvpct * ag, 
                  bagvpct ~ 1 + phosphorusvfertilizervuse + soybeans +
@@
                  nl = TRUE)
-fit2 <- get_if_not_exists(brm_fit, "../data/mcmc/fit2.rds", formula = model_form2, 
+fit_nle <- get_if_not_exists(brm_fit, "../data/mcmc/fit_nle.rds", formula = model_form2, 
                           data = dt)
 print("re w/ 2nd level coeffs")
-print(fit2$formula)
+print(fit_nle$formula)
 
@@
 
-```{r model_diagnostics_advanced, fig.height=4, echo=FALSE, eval=FALSE}
+```{r model_diagnostics_advanced, fig.height=4, echo=FALSE, eval=TRUE}
 # pull global distribution (lower, mean, upper)
@@
 coef_signif <- bind_rows(
-  spread_draws(fit2, b_bagvpct_soybeans) %>%
+  spread_draws(fit_nle, b_bagvpct_soybeans) %>%
     do(tibble::as_tibble(t(quantile(.$b_bagvpct_soybeans, 
                                     c(0.05, 0.5, 0.95))))), 
-  spread_draws(fit2, b_bagvpct_phosphorusvfertilizervuse) %>%
+  spread_draws(fit_nle, b_bagvpct_phosphorusvfertilizervuse) %>%
     do(tibble::as_tibble(t(quantile(.$b_bagvpct_phosphorusvfertilizervuse, 
@@
 dplyr::filter(dt, hu4vzoneid %in% hu4_signif$ZoneID) %>%
-  modelr::data_grid(agvpct = seq_range(agvpct, n = 101), hu4vzoneid) %>%
+  modelr::data_grid(ag = seq_range(ag, n = 101), hu4vzoneid) %>%
   add_predicted_draws(fit) %>%
-  ggplot(aes(x = agvpct, y = tp)) +
+  ggplot(aes(x = ag, y = tp)) +
   stat_lineribbon(aes(y = .prediction), .width = c(.99, .95, .8, .5), color = "#08519C") +
@@
 
-```{r not_signif, echo=FALSE}
+```{r not_signif, echo=FALSE, eval=FALSE}
 hu4_not_signif_n <- sample(unique(
@@
 dplyr::filter(dt, hu4vzoneid %in% hu4_not_signif_n) %>%
-  modelr::data_grid(agvpct = seq_range(agvpct, n = 101), hu4vzoneid) %>%
+  modelr::data_grid(ag = seq_range(ag, n = 101), hu4vzoneid) %>%
   add_predicted_draws(fit) %>%
-  ggplot(aes(x = agvpct, y = tp)) +
+  ggplot(aes(x = ag, y = tp)) +
   stat_lineribbon(aes(y = .prediction), .width = c(.99, .95, .8, .5), color = "#08519C") +

### 2019-06-13 tables/01_predictors.Rmd
calculate new cdl categories, closes #13

--- 2018-10-03 tables/01_predictors.Rmd
@@
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
+# setwd("figures")
 ```
@@
 
+cdl_vars <- readRDS("../data/dt.rds") %>%
+  dplyr::select(ag:wheat) %>%
+  summarize_all(median, na.rm = TRUE) %>%
+  tidyr::gather() %>%
+  dplyr::filter(value >= 1.4) %>%
+  arrange(desc(value)) %>%
+  pull(key)
+
 # setwd("tables")
 dt <- readRDS("../data/dt.rds") %>%
-  dplyr::select(tp:clay_pct, -hu4_zoneid) %>%
+  dplyr::select(tp:clay_pct, -matches("zoneid"), -matches("pct"), cdl_vars) %>%
   tidyr::gather(key = "variable") %>%

### 2019-06-13 manuscript/appendix.Rmd
add exploration of lake trophic state, closes #12

---
title: "Appendix"
output:
  pdf_document:
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
```

```{r read_chunks, cache=FALSE, echo=FALSE}
knitr::read_chunk("../scripts/99_utils.R")
```

```{r source_utils, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
# setwd("scripts")
source("../scripts/99_utils.R")
```

```{r trophic_state, fig.cap="Lake trophic state", fig.width = 5.5, fig.height = 4, warning=FALSE, message=FALSE}

dt <- readRDS("../data/dt.rds") %>%
  dplyr::filter(!is.na(chla)) %>%
  mutate(trophic_state = cut(chla, 
                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
                             labels = c("oligotrophic", "mesotrophic", 
                                        "eutrophic", "hypereutrophic"))) %>%
  dplyr::select(chla, trophic_state) %>%
  group_by(trophic_state) %>%
  count()

g <- gridExtra::tableGrob(dt, rows = rep("", nrow(dt)))
grid.draw(g)
```

### 2019-06-13 figures/08_exploratory_dotplot.Rmd
add buffer composition category

@@
                                                "Nutrient proxies",
-                                               "Transport capacity"))) %>%
-    dplyr::filter(!(var %in% c("tp", "tn")))
+                                               "Transport capacity", 
+                                               "Buffer composition"))) %>%
+    dplyr::filter(!(var %in% c("tp", "tn"))) %>%
+    dplyr::filter(!is.na(category))
   res
@@
 
-plot_opts <- theme(axis.title.y = element_blank(), 
+plot_opts <- theme_cowplot() +
+  theme(axis.title.y = element_blank(), 
                    axis.text = element_text(size = 8), 

### 2019-06-13 manuscript/figures.Rmd
add buffer composition category

@@
 ```{r exploratory_dotplot, fig.cap = "Exploratory dotplots showing absolute value correlations.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/08_exploratory_dotplot-2.pdf")
+knitr::include_graphics("../figures/dotplot-1.pdf")
 ```

### 2019-06-13 scripts/99_make_predictor_key.R

@@ -2,7 +2,7 @@ pred_key <- data.frame(var = c(
   "nitrogen_atmospheric_deposition","maxdepth","iwsla_ratio",
   "hu12_baseflow_mean","hu12_ppt_mean","lake_cultivated_crops", 
   "stream_cultivated_crops","wetlands","ag", 
-  "nonag","clay_pct","lake_area_ha", 
+  "nonag", "nfixer", "clay_pct","lake_area_ha", 
   "wetland_potential", "corn","nitrogen_livestock_manure", 
   "soil_org_carbon", "soybeans","n_input", 
   "nitrogen_fertilizer_use", "phosphorus_fertilizer_use","p_input", 
@@ -11,16 +11,16 @@ pred_key <- data.frame(var = c(
     "N deposition", "Max depth", "Watershed-lake ratio", 
     "Baseflow", "Precipitation", "Lake-buffer Ag", 
     "Stream-buffer Ag", "Wetlands", "Ag",
-    "Non-ag", "Clay", "Lake area",
+    "Non-ag", "N-fixer", "Clay", "Lake area",
     "Wetland potential", "Corn", "Manure N input", 
     "Soil organic carbon", "Soybeans", "N input",
     "Fertilizer N input", "Fertilizer P input", "P input", 
     "Manure P input", "Wheat", "Pasture", "Row-crop Ag"),
                       category = c(
   "Nutrient sources", "Lake", "Lake", 
-  "Transport capacity", "Transport capacity", "Nutrient proxies",
-  "Nutrient proxies","Nutrient proxies","Nutrient proxies",
-  "Nutrient proxies", "Transport capacity","Lake",
+  "Transport capacity", "Transport capacity", "Buffer composition",
+  "Buffer composition","Nutrient proxies","Nutrient proxies",
+  "Nutrient proxies", "Nutrient proxies", "Transport capacity","Lake",
   "Transport capacity", "Nutrient proxies","Nutrient sources", 
   "Transport capacity", "Nutrient proxies", "Nutrient sources",
   "Nutrient sources", "Nutrient sources", "Nutrient sources", 

### 2019-06-17 figures/09_stream_buffer.Rmd
turn on cowplot theme

@@
             aes(x = ag_pct, y = stream_cultivated_crops, label = lagoslakeid)) + 
+  theme_cowplot() +
   theme(legend.position = 0) +

### 2019-06-17 figures/08_exploratory_dotplot.Rmd
rm p from tn plot and vice versa

@@
 
+dt_tp <- prep_dotplot(dt_tp, "tp") %>%
+  dplyr::filter(!str_detect(pretty, "^N ")) %>%
+  dplyr::filter(!str_detect(pretty, " N "))
+
+dt_tn <- prep_dotplot(dt_tn, "tn") %>%
+  dplyr::filter(!str_detect(pretty, "^P ")) %>%
+  dplyr::filter(!str_detect(pretty, " P "))
+
 # head(prep_dotplot(dt_tp, "tp"))
 # show_col(brewer_pal("div", "Set1")(4))                   
-gg_tp <-  ggplot(data = prep_dotplot(dt_tp, "tp")) + 
+gg_tp <-  ggplot(data = dt_tp) + 
     geom_point(aes(x = tp, y = pretty, color = category)) + 
@@
     plot_opts
-gg_tn <- ggplot(data = prep_dotplot(dt_tn, "tn")) + 
+gg_tn <- ggplot(data = dt_tn) + 
     geom_point(aes(x = tn, y = pretty, color = category)) +

### 2019-06-17 figures/09_stream_buffer.Rmd
use ag instead of mixed ag + row crops

--- 2019-05-23 figures/09_stream_buffer.Rmd
@@
 dt <- readRDS("../data/dt.rds") %>%
-  mutate(diff = stream_cultivated_crops - ag_pct, 
-         category = cut(diff, breaks = c(Inf, 3, -65, -Inf))) %>%
+  dplyr::filter(stream_ag > 0) %>%
+  mutate(diff = stream_ag - ag, 
+         category = cut(diff, breaks = c(Inf, 28, -28, -Inf))) %>%
   drop_na(diff) %>%
-  dplyr::select(lagoslakeid, ag_pct, stream_cultivated_crops, 
-                diff, category)
+  dplyr::select(lagoslakeid, ag, stream_ag, 
+                diff, category, iws_ha) %>%
+  arrange(diff)
 
-# llid 6201 as a low stream ag
-# llid 7026 as a high stream ag
-llids <- c("6201", "7026")
+# first llid is a low stream ag lake
+# second llids is a high stream ag lake
+llids <- c("4532", "96236")
 
 ggplot(data = dt) +
-  geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = category)) +
-  geom_abline(aes(slope = 1, intercept = 3)) +
-  geom_abline(aes(slope = 1, intercept = -65)) +
+  geom_point(aes(x = ag, y = stream_ag, color = category)) +
+  geom_abline(aes(slope = 1, intercept = 28)) +
+  # geom_abline(aes(slope = 1, intercept = 0)) +
+  geom_abline(aes(slope = 1, intercept = -28)) +
   ggrepel::geom_text_repel(data = dplyr::filter(dt, lagoslakeid %in% llids), 
-            aes(x = ag_pct, y = stream_cultivated_crops, label = lagoslakeid)) + 
+            aes(x = ag, y = stream_ag, label = lagoslakeid), nudge_y = 2) + 
+  theme_cowplot() +
   theme(legend.position = 0) +
   ylab("Stream buffer Ag (%)") + xlab("IWS Ag (%)") +
-  xlim(c(40, 100)) + ylim(c(0, 100))
+  ylim(c(1, 100)) # + xlim(c(40, 100))
+
+# dplyr::filter(dt, lagoslakeid %in% llids)
 ```

### 2019-06-17 figures/09_stream_buffer.Rmd
nudge labels

@@
   mutate(diff = stream_ag - ag, 
-         category = cut(diff, breaks = c(Inf, 28, -28, -Inf))) %>%
+         category = cut(diff, breaks = c(Inf, 25, -25, -Inf))) %>%
   drop_na(diff) %>%
@@
   geom_point(aes(x = ag, y = stream_ag, color = category)) +
-  geom_abline(aes(slope = 1, intercept = 28)) +
+  geom_abline(aes(slope = 1, intercept = 25)) +
   # geom_abline(aes(slope = 1, intercept = 0)) +
-  geom_abline(aes(slope = 1, intercept = -28)) +
+  geom_abline(aes(slope = 1, intercept = -25)) +
   ggrepel::geom_text_repel(data = dplyr::filter(dt, lagoslakeid %in% llids), 
-            aes(x = ag, y = stream_ag, label = lagoslakeid), nudge_y = 2) + 
+            aes(x = ag, y = stream_ag, label = lagoslakeid), nudge_y = 8) + 
   theme_cowplot() +

### 2019-06-17 tables/04_hu4s.Rmd
explore hu4 attributes

---
output:
  pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
# setwd("figures")
```

```{r summary_table, eval=TRUE}
library(kableExtra)
library(dplyr)
library(magrittr)

focal_hu4s <- data.frame(hu4_zoneid = paste0("HU4_", 
                                             c("56", "57", "36", "37", "38")), 
                         stringsAsFactors = FALSE)

lg <- lagosne_load("1.087.1")
dt <- lg$hu4 %>%
  left_join(lg$hu4.chag) %>%
  left_join(lg$hu4.conn) %>%
  # left_join(lg$hu4.lulc) %>%
  dplyr::filter(hu4_zoneid %in% unique(readRDS("../data/dt.rds")$hu4_zoneid)) %>%
  dplyr::select(-matches("count")) %>%
  dplyr::select(-matches("nwi")) %>%
  dplyr::select(-matches("lakes10ha")) %>%
  dplyr::select(-matches("std")) %>%
  dplyr::select(-matches("min")) %>%
  dplyr::select(-matches("max")) %>%
  dplyr::select(-matches("canalditchdensity")) %>%
  dplyr::select(-matches("wetlandsundissolved")) %>%
  dplyr::select(-matches("overlapping")) %>%
  dplyr::select(-matches("contributing")) %>%
  dplyr::select(-matches("1985|1990|1995|2000|2005")) %>%
  mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>% 
  group_by(is_focal) %>%
  summarize_all(median, na.rm = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -is_focal) %>%
  dplyr::filter(!is.na(value)) %>%
  dplyr::filter(value != 0) %>%
  tidyr::spread(key, value) %>%
  t()
dt <- dt[complete.cases(dt),] 
View(dt)

knitr::kable(dt, digits = 0, format = "markdown") 
#%>%
 # add_header_above(c(" ", " ", Ranges = 3, " ", " "))
```

### 2019-06-18 tables/04_hu4s.Rmd
cleaner comparison

@@
 # setwd("figures")
+source("../scripts/99_utils.R")
 ```
@@
 
+lg <- lagosne_load("1.087.1")
 focal_hu4s <- data.frame(hu4_zoneid = paste0("HU4_", 
@@
 
-lg <- lagosne_load("1.087.1")
-dt <- lg$hu4 %>%
+dt_raw <- lg$hu4 %>%
   left_join(lg$hu4.chag) %>%
@@
   dplyr::select(-matches("1985|1990|1995|2000|2005")) %>%
+  dplyr::select(-matches("_ha")) %>%
   mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>% 
@@
   t()
+
+row_names <- row.names(dt_raw)
+
+dt <- dt_raw %>%
+  data.frame(stringsAsFactors = FALSE) %>%
+  setNames(c("nonfocal", "focal")) %>%
+  mutate_all(~as.numeric(.)) %>%
+  mutate(var = row_names) %>%
+  mutate(diff = abs(abs(nonfocal - focal)/nonfocal)) %>%
+  mutate_if(is.numeric, ~format(., scientific = FALSE)) %>%
+  dplyr::filter(diff > 0.02) %>%
+  arrange(desc(diff))
+
 dt <- dt[complete.cases(dt),] 

### 2019-06-18 tables/04_hu4s.Rmd
clean up focal hu4 comparison

@@
 
-dt_raw <- lg$hu4 %>%
+compare_focal <- function(dt, ids){
+  dt <- dt %>%
+  mutate(is_focal = hu4_zoneid %in% ids) %>% 
+  group_by(is_focal) %>%
+  summarize_all(median, na.rm = TRUE) %>%
+  tidyr::gather(key = "key", value = "value", -is_focal) %>%
+  dplyr::filter(!is.na(value)) %>%
+  dplyr::filter(value != 0) %>%
+  tidyr::spread(key, value) %>%
+  t()
+
+  row_names <- row.names(dt)
+
+  res <- dt %>%
+    data.frame(stringsAsFactors = FALSE) %>%
+    setNames(c("nonfocal", "focal")) %>%
+    mutate_all(~as.numeric(.)) %>%
+    mutate(var = row_names) %>%
+    mutate(diff = abs(abs(nonfocal - focal)/nonfocal)) %>%
+    mutate_if(is.numeric, ~format(., scientific = FALSE)) %>%
+    # dplyr::filter(diff > 0.02) %>%
+    arrange(desc(diff))
+
+  res
+}
+
+hu4 <- lg$hu4 %>%
   left_join(lg$hu4.chag) %>%
@@
   dplyr::select(-matches("_ha")) %>%
-  mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>% 
-  group_by(is_focal) %>%
-  summarize_all(median, na.rm = TRUE) %>%
-  tidyr::gather(key = "key", value = "value", -is_focal) %>%
-  dplyr::filter(!is.na(value)) %>%
-  dplyr::filter(value != 0) %>%
-  tidyr::spread(key, value) %>%
-  t()
+  compare_focal(focal_hu4s$hu4_zoneid)
 
-row_names <- row.names(dt_raw)
-
-dt <- dt_raw %>%
-  data.frame(stringsAsFactors = FALSE) %>%
-  setNames(c("nonfocal", "focal")) %>%
-  mutate_all(~as.numeric(.)) %>%
-  mutate(var = row_names) %>%
-  mutate(diff = abs(abs(nonfocal - focal)/nonfocal)) %>%
-  mutate_if(is.numeric, ~format(., scientific = FALSE)) %>%
-  dplyr::filter(diff > 0.02) %>%
-  arrange(desc(diff))
-
-dt <- dt[complete.cases(dt),] 
+dt        <- compare_focal(readRDS("../data/dt.rds"), focal_hu4s$hu4_zoneid)
+dt_scaled <- compare_focal(readRDS("../data/dt_scaled.rds"), focal_hu4s$hu4_zoneid)                     
 View(dt)

### 2019-06-18 scripts/03_model.R

@@ -39,7 +39,10 @@ brm_fit <- function(destfile, formula, data){
   "tn_nfert" = bf(tn ~ ag + maxdepth + soilvorgvcarbon + 
                     nitrogenvfertilizervuse), # sources 
   "tn_buffer" = bf(tn ~ ag + maxdepth + soilvorgvcarbon + 
-                     nitrogenvfertilizervuse + buffervcultivatedvcrops) # buffer
+                     nitrogenvfertilizervuse + buffervcultivatedvcrops), # buffer
+  "tn_ndep" = bf(tn ~ ag + maxdepth + soilvorgvcarbon + 
+                   nitrogenvfertilizervuse + buffervcultivatedvcrops + 
+                   hu4vnitrogenvatmosphericvdeposition)
 ))
 
 fe_brms <- 
@@ -56,16 +59,16 @@ r2_fe <- dplyr::bind_rows(
          Estimate = round(Estimate, 2)) %>%
   dplyr::select(Model, Estimate) 
 
-r2_fe$`Proxy`     <- c(rep("Ag", 5), 
-                       rep("Ag", 5))
-r2_fe$`Lake`      <- c(NA, rep("maxdepth", 4), 
-                       NA, rep("maxdepth", 4))
-r2_fe$`Transport` <- c(NA, NA, "Baseflow", "Baseflow", "Baseflow",
-                       NA, NA, "Soil Org Carbon", "Soil Org Carbon", "Soil Org Carbon")
-r2_fe$`Source`    <- c(NA, NA, NA, "P fertilizer", "P fertilizer",
-                       NA, NA, NA, "N fertilizer", "N fertilizer")
-r2_fe$`Buffer`    <- c(NA, NA, NA, NA, "Row crop",
-                       NA, NA, NA, NA, "Row crop")
+# r2_fe$`Proxy`     <- c(rep("Ag", 5), 
+#                        rep("Ag", 5))
+# r2_fe$`Lake`      <- c(NA, rep("maxdepth", 4), 
+#                        NA, rep("maxdepth", 4))
+# r2_fe$`Transport` <- c(NA, NA, "Baseflow", "Baseflow", "Baseflow",
+#                        NA, NA, "Soil Org Carbon", "Soil Org Carbon", "Soil Org Carbon")
+# r2_fe$`Source`    <- c(NA, NA, NA, "P fertilizer", "P fertilizer",
+#                        NA, NA, NA, "N fertilizer", "N fertilizer")
[…]

### 2019-06-18 figures/08_exploratory_dotplot.Rmd
fix cut off figure

@@
 
-```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE, warning=FALSE}
+```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE, warning=FALSE, fig.height=5.5}
 pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)

### 2019-06-19 tables/04_hu4s.Rmd
fill out hu4 comparison tables

--- 2019-06-18 tables/04_hu4s.Rmd
@@
 
-dt_raw <- lg$hu4 %>%
+compare_focal <- function(dt, ids, threshold = 0){
+  dt <- dt %>%
+  mutate(is_focal = hu4_zoneid %in% ids) %>% 
+  group_by(is_focal) %>%
+  summarize_all(median, na.rm = TRUE) %>%
+  tidyr::gather(key = "key", value = "value", -is_focal) %>%
+  dplyr::filter(!is.na(value)) %>%
+  dplyr::filter(value != 0) %>%
+  tidyr::spread(key, value) %>%
+  t()
+
+  row_names <- row.names(dt)
+
+  res <- dt %>%
+    data.frame(stringsAsFactors = FALSE) %>%
+    setNames(c("nonfocal", "focal")) %>%
+    mutate_all(~as.numeric(.)) %>%
+    mutate(var = row_names) %>%
+    mutate(diff = abs(abs(nonfocal - focal)/nonfocal)) %>%
+    dplyr::filter(!is.na(diff)) %>%
+    dplyr::filter(diff > threshold) %>%
+    arrange(desc(diff)) %>%
+    mutate_if(is.numeric, ~format(., scientific = FALSE))
+
+  res
+}
+
+hu4 <- lg$hu4 %>%
   left_join(lg$hu4.chag) %>%
@@
   dplyr::select(-matches("_ha")) %>%
-  mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>% 
-  group_by(is_focal) %>%
-  summarize_all(median, na.rm = TRUE) %>%
-  tidyr::gather(key = "key", value = "value", -is_focal) %>%
-  dplyr::filter(!is.na(value)) %>%
-  dplyr::filter(value != 0) %>%
-  tidyr::spread(key, value) %>%
-  t()
+  compare_focal(focal_hu4s$hu4_zoneid, threshold = 0.011)
 
-row_names <- row.names(dt_raw)
+dt        <- suppressWarnings(
+  compare_focal(readRDS("../data/dt.rds"), focal_hu4s$hu4_zoneid, threshold = 0.28))
+dt_scaled <- suppressWarnings(
+  compare_focal(readRDS("../data/dt_scaled.rds"), focal_hu4s$hu4_zoneid, threshold = 0.9))
 
-dt <- dt_raw %>%
-  data.frame(stringsAsFactors = FALSE) %>%
-  setNames(c("nonfocal", "focal")) %>%
-  mutate_all(~as.numeric(.)) %>%
-  mutate(var = row_names) %>%
-  mutate(diff = abs(abs(nonfocal - focal)/nonfocal)) %>%
-  mutate_if(is.numeric, ~format(., scientific = FALSE)) %>%
-  dplyr::filter(diff > 0.02) %>%
-  arrange(desc(diff))
+jsta::pdf_table(dt, "../tables/dt.pdf")
+jsta::pdf_table(dt_scaled, "../tables/dt_scaled.pdf")
+jsta::pdf_table(hu4, "../tables/hu4.pdf")
 
-dt <- dt[complete.cases(dt),] 
 View(dt)

### 2019-06-19 figures/07_model-selection.Rmd
clean up colors on hu4 sample size map

@@
 
-```{r 07_model_selection, fig.height=3, echo=FALSE,eval=FALSE}
-
+```{r 07_model_selection, fig.height=3, echo=FALSE,eval=TRUE}
+print("07_model_selection")
 # setwd("figures")
@@
   left_join(ids, by = c("ZoneID" = "hu4_zoneid"))
-
 n_cat  <- 6
-colors <- c("#FFFFFF", viridisLite::viridis(n_cat - 1))
+colors <- c(#"#FFFFFF", 
+            viridisLite::viridis(n_cat))
 hu4    <- mutate(hu4, 
             n_cat = cut(hu4$n, breaks = 
-                          classInt::classIntervals(hu4$n, n = n_cat)$brks))
+                round(classInt::classIntervals(hu4$n, n = n_cat,
+                                               style = "kmeans")$brks, 0)
+                ))
 hu4 <- dplyr::filter(hu4, !is.na(n_cat))
+
+gg_hu4_n <- ggplot() +
+    geom_sf(data = hu4, aes(fill = n_cat)) +
+    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
+    theme_minimal() + 
+    theme(legend.position = "bottom", 
+          axis.title = element_blank(), 
+          legend.title = element_blank()) + 
+    scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
+    guides(guide_legend(nrow = 2))
 
@@
 # table(as.character(dt$hu4_zoneid))
-
-lg <- lagosne_load("1.087.1")
-
-# ep <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
-#                 summarize(
-
-#                   group_by(dplyr::select(lg$epi_nutr, lagoslakeid, tp, chla), 
-#                            lagoslakeid), 
-#                   tp = median(tp, na.rm = TRUE), 
-#                   chla = median(chla, na.rm = TRUE)), 
-#                 by = "lagoslakeid") %>%
-#   tidyr::drop_na()
 
@@
     scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
-  ggplot() +
-    geom_sf(data = hu4, aes(fill = n_cat)) +
-    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
-    theme_minimal() + 
-    theme(legend.position = "bottom", 
-          axis.title = element_blank(), 
-          legend.title = element_blank()) + 
-    scale_fill_manual(values = colors, levels(hu4$n_cat)), 
+  gg_hu4_n, 
   rel_heights = c(0.6, 1), labels = "AUTO"
@@
 ```{r residual_dotplot, echo=FALSE}
-library(tidybayes)
-library(brms)
+suppressMessages(library(tidybayes))
+suppressMessages(library(brms))
+
+lg <- lagosne_load("1.087.1")
 
@@
 
-```{r signif_map, echo=FALSE, eval=FALSE}
+```{r signif_map, echo=FALSE, eval=TRUE}
 ggplot() + 

### 2019-06-19 scripts/00_get_ep.R
explore more hu4 predictors

@@ -101,7 +101,8 @@ ep <- ep %>%
     hu12_ppt_std = hu12_prism_ppt_30yr_normal_800mm2_annual_std, 
     hu12_baseflow_mean = hu12_baseflowindex_mean)) %>%
   left_join(dplyr::select(lg$hu4.chag, hu4_zoneid, 
-                    hu4_nitrogen_atmospheric_deposition = hu4_dep_totaln_2010_mean))
+                    hu4_nitrogen_atmospheric_deposition = hu4_dep_totaln_2010_mean, 
+                    hu4_clay_pct = hu4_surficialgeology_till_clay_pct))
 
 # filter focal predictors
 ep <- dplyr::filter(ep, iws_ha <= max_iws_ha & 

### 2019-06-19 scripts/02_aggregate_predictors.R

@@ -115,7 +115,7 @@ cdl_vars <- dt %>%
 dt_scaled <- dt %>% 
   dplyr::select("lagoslakeid", "hu4_zoneid", "hu12_zoneid", 
                 "tp", "tn", "chla", "hu12_ppt_mean", "hu12_baseflow_mean", 
-                "hu4_nitrogen_atmospheric_deposition",
+                "hu4_nitrogen_atmospheric_deposition", "hu4_clay_pct",
                 "maxdepth", "iwsla_ratio", "row_crop_pct", "soil_org_carbon",
                 "nitrogen_atmospheric_deposition", "clay_pct", 
                 "lake_area_ha", "wetland_potential", contains("manure"), 

### 2019-06-19 scripts/03_model.R
towards hu4 maps

@@ -115,12 +115,12 @@ r2_re <- dplyr::bind_rows(
          Estimate = round(Estimate, 2)) %>%
   dplyr::select(Model, Estimate)
 
-r2_re$`Proxy`     <- c("Ag", "Soybeans", "Pasture",
-                       "Ag", "Corn", "Pasture") 
-r2_re$`Lake`      <- c(rep("maxdepth", 6))
-r2_re$`Transport` <- c(rep("Baseflow", 3), rep("Soil Org Carbon", 3))
-r2_re$`Source`    <- c(rep("P fertilizer", 3), rep("N fertilizer", 3))
-r2_re$`Buffer`    <- c(rep("Row Crop", 6))
+# r2_re$`Proxy`     <- c("Ag", "Soybeans", "Pasture",
+#                        "Ag", "Corn", "Pasture") 
+# r2_re$`Lake`      <- c(rep("maxdepth", 6))
+# r2_re$`Transport` <- c(rep("Baseflow", 3), rep("Soil Org Carbon", 3))
+# r2_re$`Source`    <- c(rep("P fertilizer", 3), rep("N fertilizer", 3))
+# r2_re$`Buffer`    <- c(rep("Row Crop", 6))
 
 r2    <- dplyr::bind_rows(r2_fe, r2_re)
 

### 2019-06-19 figures/07_model-selection.Rmd
make hu4 comparison maps

@@
 # setwd("figures")
+
+dt      <- readRDS("../data/dt.rds")
 ids     <- readRDS("../data/dt.rds") %>%
@@
 hu4 <- dplyr::filter(hu4, !is.na(n_cat))
+hu4 <- dplyr::left_join(hu4, 
+                        distinct(dplyr::select(dt, contains("hu4_")), 
+                                 hu4_zoneid, .keep_all = TRUE), 
+                        by = c("ZoneID" = "hu4_zoneid"))
+
+re_brms <- readRDS("../data/mcmc/re_brms.rds")
+# lapply(re_brms, function(x) x$formula) 
+signif_hu4_ids <- re_brms[[5]]$re_signif_ids # 5 is best tn model with re effects
+signif_hu4 <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)
 
@@
     geom_sf(data = hu4, aes(fill = n_cat)) +
+    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
     # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
@@
 
+(gg_hu4_ndep <- ggplot() +
+    geom_sf(data = hu4, aes(fill = hu4_nitrogen_atmospheric_deposition)) +
+    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
+    theme_minimal() + 
+    theme(legend.position = "bottom", 
+          axis.title = element_blank(), 
+          legend.title = element_blank()))
+
+# gg_hu4_clay <- ggplot() +
+#     geom_sf(data = hu4, aes(fill = hu4_clay_pct)) +
+#     theme_minimal() + 
+#     theme(legend.position = "bottom", 
+#           axis.title = element_blank(), 
+#           legend.title = element_blank())
+
 # hist(hu4$n, n = 20)
 # table(as.character(dt$hu4_zoneid))
-
-dt <- readRDS("../data/dt.rds") %>%
-  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", 
-                "ag_pct", "phosphorus_fertilizer_use", "soybeans")
 
@@
     scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
-  gg_hu4_n, 
-  rel_heights = c(0.6, 1), labels = "AUTO"
+  gplot_grid(gg_hu4_n, gg_hu4_ndep, ncol = 1),
+  rel_heights = c(0.6, 1), labels = "AUTO", ncol = 2
 )

### 2019-06-19 scripts/03_model.R

@@ -107,13 +107,39 @@ re_brms <-
                       formula = model_forms_re[[i]], 
                       data = dt))
 
+# evaluate hu4 re slope significance
+get_re_text <- function(x){
+  # x <- "maxdepth + hu12vbaseflowvmean + phosphorusvfertilizervuse + buffervcultivatedvcrops + (1 + ag | hu4vzoneid)"
+  res <- strsplit(x, "\\|")[[1]][1]
+  res <- strsplit(res, " ")[[1]]
+  res[length(res)]
+}
+
+get_re_signif <- function(x){
+  # x <- re_brms[[5]]
+  res <- x %>%
+    spread_draws(r_hu4vzoneid[hu4vzoneid,term]) %>%
+    dplyr::filter(term == get_re_text(as.character(x$formula)[1])) %>%
+    group_by(hu4vzoneid) %>%
+    do(tibble::as_tibble(t(quantile(.$r_hu4vzoneid, c(0.05, 0.5, 0.95))))) %>%
+    mutate(signif = case_when(`5%` > 0 ~ TRUE, 
+                              TRUE ~ FALSE))
+  x$re_signif <- any(res$signif)
+  x$re_signif_ids <- dplyr::filter(res, signif == TRUE)$hu4vzoneid
+  x
+}
+  
+re_brms <- lapply(re_brms, function(x) get_re_signif(x))
+
 saveRDS(re_brms, "data/mcmc/re_brms.rds")
+# re_brms <- readRDS("data/mcmc/re_brms.rds")
 
 r2_re <- dplyr::bind_rows(
   lapply(re_brms, function(x) data.frame(brms::bayes_R2(x)))) %>%
   mutate(Model = names(model_forms_re), 
          Estimate = round(Estimate, 2)) %>%
   dplyr::select(Model, Estimate)
+r2_re$re_signif <- unlist(lapply(res_brms, function(x) x$re_signif))
 
 # r2_re$`Proxy`     <- c("Ag", "Soybeans", "Pasture",
 #                        "Ag", "Corn", "Pasture") 
@@ -134,8 +160,11 @@ if(!interactive()){
 # ---- diagnostics ----
 if(interactive()){
 # loo comparison
-loo_compare(loo(re_brms[[4]]), loo(re_brms[[5]])) # Corn model has lowest error
-loo_compare(loo(re_brms[[1]]), loo(re_brms[[3]])) # Pasture model has lowest error
+# r2_re
[…]

### 2019-06-19 figures/07_model-selection.Rmd
towards post hoc plots

@@
 
-```{r 07_model_selection, fig.height=3, echo=FALSE,eval=TRUE}
+```{r 07_model_selection, fig.height=3, echo=FALSE, fig.width=6, eval=TRUE}
 print("07_model_selection")
@@
 # lapply(re_brms, function(x) x$formula) 
-signif_hu4_ids <- re_brms[[5]]$re_signif_ids # 5 is best tn model with re effects
+fit_tn <- re_brms[[5]] # 5 is best tn model with re effects
+signif_hu4_ids <- fit_tn$re_signif_ids 
 signif_hu4 <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)
 
+# plotting
 gg_hu4_n <- ggplot() +
@@
     scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
-    guides(guide_legend(nrow = 2))
+    guides(guide_legend(nrow = 2)) + 
+  ggtitle("# of lakes")
 
-(gg_hu4_ndep <- ggplot() +
+gg_hu4_ndep <- ggplot() +
     geom_sf(data = hu4, aes(fill = hu4_nitrogen_atmospheric_deposition)) +
@@
           axis.title = element_blank(), 
-          legend.title = element_blank()))
+          legend.title = element_blank()) +
+  ggtitle("N Deposition")
 
@@
 
-plot_grid(
-  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
-    # geom_point() +
+gg_smooth <- ggplot(data = dt, 
+                    aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
     geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
@@
          y = "TP")  +
-    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
-  gplot_grid(gg_hu4_n, gg_hu4_ndep, ncol = 1),
-  rel_heights = c(0.6, 1), labels = "AUTO", ncol = 2
-)
+    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300))
+
+plot_grid(gg_hu4_n, gg_hu4_ndep)
 ```
 
-```{r residual_dotplot, echo=FALSE}
+```{r prediction_lines, echo=FALSE, eval=TRUE}
+# plot prediction lines
+# corn vs tn
+
+# hu4_signif$ZoneID
+dt        <- readRDS("../data/dt_scaled.rds") 
+names(dt) <- gsub("_", "v", names(dt))
+
+hu4_id               <- signif_hu4_ids[1]
+conditions           <- data.frame(hu4vzoneid = hu4_id)
+rownames(conditions) <- hu4_id
+
+me_zone <- marginal_effects(fit_tn, conditions = conditions, 
+                            re_formula = NULL, method = "predict")
+
+ran_ef <- as.data.frame(ranef(fit_tn)$hu4vzoneid) %>%
+  mutate(zoneid = rownames(.)) %>%
+  dplyr::filter(zoneid == hu4_id)
+
+# plot(me_zone, ncol = 1)$agvpct # + 
+  # geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
+  #               broom::tidy(fit)$estimate[3]) + 
+  # ggtitle(hu4_id)
+
+# ggplot() + 
+#     geom_point(data = dplyr::filter(dt, 
+#                                   hu4vzoneid == hu4_id), 
+#              aes(x = agvpct, y = tp)) + 
+#   geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
+#                 broom::tidy(fit)$estimate[3]) +
+#   ylim(0, 450) + xlim(40, 90) + ggtitle(hu4_id)
+
+dplyr::filter(dt, hu4vzoneid %in% signif_hu4$ZoneID) %>%
+  modelr::data_grid(corn = modelr::seq_range(corn, n = 101), 
+                    maxdepth = modelr::seq_range(corn, n = 101), 
+                    soilvorgvcarbon = modelr::seq_range(soilvorgvcarbon, n = 101), 
+                    nitrogenvfertilizervuse = modelr::seq_range(nitrogenvfertilizervuse, n = 101), 
+                    buffervcultivatedvcrops = modelr::seq_range(buffervcultivatedvcrops, n = 101), 
+                    hu4vzoneid) %>%
+  tidybayes::add_predicted_draws(fit_tn) %>%
+  ggplot(aes(x = corn, y = tn)) +
+  stat_lineribbon(aes(y = .prediction), 
+                  .width = c(.99, .95, .8, .5), color = "#08519C") +
+  geom_point(data = dplyr::filter(dt, hu4vzoneid %in% hu4_signif$ZoneID), 
+                                  size = 2) +
+  scale_fill_brewer() +
+  facet_wrap(~ hu4vzoneid)
+
+```
+
+```{r residual_dotplot, echo=FALSE, eval=FALSE}
 suppressMessages(library(tidybayes))
@@
 
-```{r model_fitting, echo=FALSE, eval=TRUE}
+```{r model_fitting, echo=FALSE, eval=FALSE}
 library(brms)
@@
 
-```{r model_diagnostics_advanced, fig.height=4, echo=FALSE, eval=TRUE}
+```{r model_diagnostics_advanced, fig.height=4, echo=FALSE, eval=FALSE}
 # pull global distribution (lower, mean, upper)
@@
 
-```{r signif_map, echo=FALSE, eval=TRUE}
+```{r signif_map, echo=FALSE, eval=FALSE}
 ggplot() + 
@@
 
-```{r model_summary, echo=FALSE, fig.height=3}
+```{r model_summary, echo=FALSE, fig.height=3, eval=FALSE}
 
@@
 
-```{r asdf, echo=FALSE}
+```{r asdf, echo=FALSE, eval=FALSE}
 

### 2019-06-19 scripts/99_utils.R

@@ -35,6 +35,8 @@ library(vapour)
 library(cdlTools)
 suppressMessages(library(unpivotr))
 library(snakecase)
+suppressMessages(library(brms))
+suppressMessages(library(tidybayes))
 
 theme_opts <- theme(axis.text = element_blank(),
                     axis.ticks = element_blank(),

### 2019-06-20 figures/07_model-selection.Rmd
more hu4 exploration

@@
 
-```{r prediction_lines, echo=FALSE, eval=TRUE}
+```{r signif_hu4_lakes}
+# compare lakes in signif hu4s
+dt        <- readRDS("../data/dt_scaled.rds") %>%
+  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
+  tidyr::gather(key = "key", value = "value", 
+                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4)
+
+ggplot(data = dt) + 
+  geom_histogram(aes(x = value, fill = signif_hu4)) +
+  geom_vline(aes(xintercept = median(value, na.rm = TRUE), color = signif_hu4)) +
+  facet_wrap(~key)
+
+```
+
+```{r prediction_lines, echo=FALSE, eval=FALSE}
 # plot prediction lines
@@
 
-hu4_id               <- signif_hu4_ids[1]
+hu4_id               <- unique(dt$hu4vzoneid)
 conditions           <- data.frame(hu4vzoneid = hu4_id)
@@
                             re_formula = NULL, method = "predict")
+plot(me_zone, points = TRUE)
+
+n_predict <- 3
+reps      <- length(unique(dt$hu4vzoneid)) / 3
+reps      <- 2
+new_data <- data.frame(
+      maxdepth = rep(modelr::seq_range(dt$maxdepth, n = n_predict), reps), 
+      soilvorgvcarbon = rep(modelr::seq_range(dt$maxdepth, n = n_predict), reps), 
+      nitrogenvfertilizervuse = rep(modelr::seq_range(dt$nitrogenvfertilizervuse, 
+                                                  n = n_predict), reps), 
+      buffervcultivatedvcrops = rep(modelr::seq_range(dt$buffervcultivatedvcrops, 
+                                                  n = n_predict), reps), 
+      corn = rep(modelr::seq_range(dt$corn, n = n_predict), reps), 
+      hu4vzoneid = unique(dt$hu4vzoneid)[1:2],
+      stringsAsFactors = FALSE)
+new_data <- expand.grid(new_data)
+
+test <- add_predicted_draws()
+
+test <- predict(fit_tn, newdata = new_data, allow_new_levels = TRUE)
+test2 <- cbind(new_data, test)
+plot(test2$corn, test2$Estimate)
 
@@
   mutate(zoneid = rownames(.)) %>%
+  arrange(desc(Estimate.corn))
+%>%
   dplyr::filter(zoneid == hu4_id)

### 2019-06-20 scripts/99_utils.R
require ggforce

@@ -37,6 +37,7 @@ suppressMessages(library(unpivotr))
 library(snakecase)
 suppressMessages(library(brms))
 suppressMessages(library(tidybayes))
+library(ggforce)
 
 theme_opts <- theme(axis.text = element_blank(),
                     axis.ticks = element_blank(),

### 2019-06-20 scripts/ComparingSpatialExtents.R
rm collins script

@@ -1,93 +1,0 @@
-###SMC, 17 Aug 2017
-# will be using county level data for extended ag data, so interested in seeing whether LAGOS NCLD ag data at the county scale are correlated to other more relevant spatial scales for watersheds, e.g. IWS, HU12, HU4
-
-# ---- setup -----
-library(LAGOSNE)
-lg <- lagosne_load(version="1.087.1")
-
-# ---- pull_data ----
-
-geo.relevantzones <- lagosne_select(table = "lakes.geo",
-            vars = c("lagoslakeid", "hu4_zoneid", "hu12_zoneid", "county_zoneid"))
-
-county.ag                  <- lagosne_select(table = "county.lulc",
-      vars = c("county_zoneid", "county_nlcd2006_pct_81", "county_nlcd2006_pct_82"))
-names(county.ag)           <- c("county_zoneid", "county_pasturehay06", "county_rowcrop06")
-county.ag$county_totalag06 <- county.ag$county_pasturehay06 + county.ag$county_rowcrop06
-
-#
-
-iws.ag <- lagosne_select(table = "iws.lulc", vars = c("lagoslakeid", "iws_nlcd2006_pct_81",
-                                                    "iws_nlcd2006_pct_82"))
-names(iws.ag) <- c("lagoslakeid", "iws_pasturehay06", "iws_rowcrop06")
-iws.ag$iws_totalag06 <- iws.ag$iws_pasturehay06 + iws.ag$iws_rowcrop06
-
-#
-
-ag.county <- merge(geo.relevantzones, county.ag, by = "county_zoneid", all.x = T,
-                   all.y = T)
-ag.county.iws <- merge(ag.county, iws.ag, by = "lagoslakeid", all.x = T, all.y = T)
-ag.county.iws <- na.omit(ag.county.iws)
-
-# doesn't look so great, but maybe ok?  add in hu12 and hu4 to see how everything
-# looks against each other and whether it's just county that sucks
-hu12.ag                <- lagosne_select(table = "hu12.lulc",
[…]

### 2019-06-20 figures/07_model-selection.Rmd
hu4 histograms

@@
   tidyr::gather(key = "key", value = "value", 
-                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4)
+                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4) %>%
+  group_by(key, signif_hu4) %>%
+  mutate(median = median(value, na.rm = TRUE))
 
-ggplot(data = dt) + 
-  geom_histogram(aes(x = value, fill = signif_hu4)) +
-  geom_vline(aes(xintercept = median(value, na.rm = TRUE), color = signif_hu4)) +
+dt_predictors <- dplyr::filter(dt, key %in% 
+                                 c("wetland_potential", "tp",
+                                   "nitrogen_atmospheric_deposition",
+                                   "hu12_baseflow_mean", "clay_pct"))
+dt_modelled <- dplyr::filter(dt, key %in% 
+                               c("maxdepth", "tn", "soil_org_carbon",
+                                 "buffer_cultivated_crops", "corn",
+                                 "nitrogen_fertilizer_use"))
+
+ggplot(data = dt_predictors) + 
+  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
+  geom_vline(aes(xintercept = median, color = signif_hu4), 
+             linetype = "dashed") +
   facet_wrap(~key)
+
+ggplot(data = dt_modelled) + 
+  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
+  geom_vline(aes(xintercept = median, color = signif_hu4), 
+             linetype = "dashed") +
+  facet_wrap(~key)
+
+fit_tn$formula
 

### 2019-06-20 figures/07_model-selection.Rmd
hu4 lines

@@
 fit_tn$formula
+
+dt        <- readRDS("../data/dt_scaled.rds") %>%
+  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
+  tidyr::gather(key = "key", value = "value", 
+                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4, -tn) %>%
+  dplyr::filter(key %in% c("maxdepth", "tn", "soil_org_carbon",
+                                 "buffer_cultivated_crops", "corn",
+                                 "nitrogen_fertilizer_use"))
+
+ggplot(data = dt) + 
+  geom_point(aes(x = tn, y = value, color = signif_hu4)) +
+  geom_line(stat = "smooth", method = lm, se = FALSE, 
+            aes(x = tn, y = value, color = signif_hu4)) +
+  facet_wrap(~key)
+
+dt        <- readRDS("../data/dt_scaled.rds") %>%
+  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
+  tidyr::gather(key = "key", value = "value", 
+                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4, -tn) %>%
+  dplyr::filter(key %in% c("wetland_potential", "tp",
+                                   "nitrogen_atmospheric_deposition",
+                                   "hu12_baseflow_mean", "clay_pct"))
+
+ggplot(data = dt) + 
+  geom_point(aes(x = tn, y = value, color = signif_hu4)) +
+  geom_line(stat = "smooth", method = lm, se = FALSE, 
+            aes(x = tn, y = value, color = signif_hu4)) +
+  facet_wrap(~key)
 

### 2019-06-20 scripts/03_model.R
save re draws

@@ -124,7 +124,8 @@ get_re_signif <- function(x){
     do(tibble::as_tibble(t(quantile(.$r_hu4vzoneid, c(0.05, 0.5, 0.95))))) %>%
     mutate(signif = case_when(`5%` > 0 ~ TRUE, 
                               TRUE ~ FALSE))
-  x$re_signif <- any(res$signif)
+  x$re            <- res
+  x$re_signif     <- any(res$signif)
   x$re_signif_ids <- dplyr::filter(res, signif == TRUE)$hu4vzoneid
   x
 }

### 2019-06-20 figures/07_model-selection.Rmd
cleanup hu4 summary plots

--- 2019-06-20 figures/07_model-selection.Rmd
@@
 # plotting
-gg_hu4_n <- ggplot() +
-    geom_sf(data = hu4, aes(fill = n_cat)) +
+gg_hu4 <- ggplot() +
+    geom_sf(data = hu4) +
     geom_sf(data = signif_hu4, color = "red", alpha = 0) +
@@
     scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
-    guides(guide_legend(nrow = 2)) + 
-  ggtitle("# of lakes")
+    guides(guide_legend(nrow = 2))
 
-gg_hu4_ndep <- ggplot() +
-    geom_sf(data = hu4, aes(fill = hu4_nitrogen_atmospheric_deposition)) +
-    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
-    theme_minimal() + 
-    theme(legend.position = "bottom", 
-          axis.title = element_blank(), 
-          legend.title = element_blank()) +
-  ggtitle("N Deposition")
+gg_corn_re <- ggplot(data = fit_tn$re) +
+  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
+                      ymin = `5%`, ymax = `95%`, color = signif)) +
+  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  geom_hline(yintercept = 0) +
+  coord_flip() +
+  ylab("TN model, corn RE slope") + theme(legend.position = 0)
+
+plot_grid(gg_corn_re, gg_hu4)
+
+# gg_hu4_ndep <- ggplot() +
+#     geom_sf(data = hu4, aes(fill = hu4_nitrogen_atmospheric_deposition)) +
+#     geom_sf(data = signif_hu4, color = "red", alpha = 0) +
+#     theme_minimal() + 
+#     theme(legend.position = "bottom", 
+#           axis.title = element_blank(), 
+#           legend.title = element_blank()) +
+#   ggtitle("N Deposition")
 
@@
 # create alpha sample size weightings
-dt <- left_join(dt, ungroup(count(group_by(dt, hu4_zoneid))), 
-                by = "hu4_zoneid") %>%
-  dplyr::filter(n >= 3) %>%
-  mutate(n = n / max(n, na.rm = TRUE))
+# dt <- left_join(dt, ungroup(count(group_by(dt, hu4_zoneid))), 
+#                 by = "hu4_zoneid") %>%
+#   dplyr::filter(n >= 3) %>%
+#   mutate(n = n / max(n, na.rm = TRUE))
 
@@
 # create hu4 labels
-centroid_xy <- sf::st_as_text(sf::st_geometry(sf::st_centroid(hu4[,"ZoneID"])))
-extract_coords <- function(messy_centroid){
-  res <- stringr::str_split(messy_centroid, "\\(", simplify = TRUE)[2]
-  res <- stringr::str_split(res, "\\)", simplify = TRUE)[1]
-  stringr::str_split(res, " ", simplify = TRUE)
-}
-coords <- data.frame(matrix(
-            as.numeric(unlist(lapply(centroid_xy, extract_coords))),
-            ncol = 2, byrow = TRUE), stringsAsFactors = FALSE)
-names(coords) <- c("x", "y")
-coords$ZoneID <- gsub("HU4_", "", hu4[,"ZoneID"]$ZoneID)
-
-gg_smooth <- ggplot(data = dt, 
-                    aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
-    geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
-    geom_smooth(aes(group = 1), method = lm, se = FALSE, 
-                color = "black", linetype = "dashed") +
-    # geom_abline(slope = 1.55, intercept = -19.86, color = "red") +
-    # scale_y_log10() + scale_x_log10() +
-    theme(legend.position = "") +
-    labs(x = "Ag. LULC (pct, NLCD 2011)", 
-         y = "TP")  +
-    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300))
-
-plot_grid(gg_hu4_n, gg_hu4_ndep)
+# centroid_xy <- sf::st_as_text(sf::st_geometry(sf::st_centroid(hu4[,"ZoneID"])))
+# extract_coords <- function(messy_centroid){
+#   res <- stringr::str_split(messy_centroid, "\\(", simplify = TRUE)[2]
+#   res <- stringr::str_split(res, "\\)", simplify = TRUE)[1]
+#   stringr::str_split(res, " ", simplify = TRUE)
+# }
+# coords <- data.frame(matrix(
+#             as.numeric(unlist(lapply(centroid_xy, extract_coords))),
+#             ncol = 2, byrow = TRUE), stringsAsFactors = FALSE)
+# names(coords) <- c("x", "y")
+# coords$ZoneID <- gsub("HU4_", "", hu4[,"ZoneID"]$ZoneID)
+# 
+# gg_smooth <- ggplot(data = dt, 
+#                     aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
+#     geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
+#     geom_smooth(aes(group = 1), method = lm, se = FALSE, 
+#                 color = "black", linetype = "dashed") +
+#     # geom_abline(slope = 1.55, intercept = -19.86, color = "red") +
+#     # scale_y_log10() + scale_x_log10() +
+#     theme(legend.position = "") +
+#     labs(x = "Ag. LULC (pct, NLCD 2011)", 
+#          y = "TP")  +
+#     scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300))
+#     
+# plot_grid(gg_hu4_n, gg_hu4_ndep)
 ```
 
-```{r signif_hu4_lakes}
+```{r signif_hu4_lakes, echo=FALSE}
 # compare lakes in signif hu4s
@@
   tidyr::gather(key = "key", value = "value", 
-                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4)
+                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4) %>%
+  group_by(key, signif_hu4) %>%
+  mutate(median = median(value, na.rm = TRUE))
 
-ggplot(data = dt) + 
-  geom_histogram(aes(x = value, fill = signif_hu4)) +
-  geom_vline(aes(xintercept = median(value, na.rm = TRUE), color = signif_hu4)) +
+dt_predictors <- dplyr::filter(dt, key %in% 
+                                 c("tp",
+                                   "nitrogen_atmospheric_deposition",
+                                   "clay_pct"))
+dt_modelled <- dplyr::filter(dt, key %in% 
+                               c("maxdepth", "tn", "soil_org_carbon",
+                                 "buffer_cultivated_crops", "corn",
+                                 "nitrogen_fertilizer_use"))
+
+gg_hist <- ggplot(data = dt_predictors) + 
+  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
+  geom_vline(aes(xintercept = median, color = signif_hu4), 
+             linetype = "dashed") +
+  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  theme(legend.position = 0) +
   facet_wrap(~key)
+
+# ggplot(data = dt_modelled) + 
+#   geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
+#   geom_vline(aes(xintercept = median, color = signif_hu4), 
+#              linetype = "dashed") +
+#   facet_wrap(~key)
+
+dt        <- readRDS("../data/dt_scaled.rds") %>%
+  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
+  tidyr::gather(key = "key", value = "value", 
+                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4, -tn) %>%
+  dplyr::filter(key %in% c(c("tp"))) %>%
+  tidyr::spread(key, value)
+
+gg_tp <- ggplot(data = dt) + 
+  geom_point(aes(x = tn, y = tp, color = signif_hu4)) +
+  geom_line(stat = "smooth", method = lm, se = FALSE, 
+            aes(x = tn, y = tp, color = signif_hu4)) +
+  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  # facet_wrap(~key) +
+  theme(legend.position = 0)
+
+plot_grid(gg_hist, gg_tp, nrow = 2)
 

### 2019-06-21 manuscript/figures.Rmd
specify correlation coefficients

@@
 
-```{r exploratory_dotplot, fig.cap = "Exploratory dotplots showing absolute value correlations.", warning=FALSE, echo = FALSE}
+```{r exploratory_dotplot, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/dotplot-1.pdf")
@@
 
-```{r exploratory_heatmap, fig.cap = "Exploratory heatmap showing absolute value correlations.", warning=FALSE, echo = FALSE}
+```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")

### 2019-06-21 figures/07_model-selection.Rmd
towards coefficient summary fig

@@
 plot_grid(gg_hist, gg_tp, nrow = 2)
+
+```
+
+```{r model_summary, echo=FALSE}
+fit_tp <- re_brms[[3]] # 3 is best tp model with re effects
+
+# plot(fit_tp)
+
+gg_tp <- spread_draws(fit_tp, 
+                     b_maxdepth, 
+                     b_hu12vbaseflowvmean, 
+                     b_phosphorusvfertilizervuse, 
+                     b_buffervcultivatedvcrops) %>%
+  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
+  ggplot(aes(x = value)) +
+  geom_histogram(alpha = 0.8) +
+  theme_cowplot() +
+  xlab("") + ylab("") +
+  facet_wrap(~key, nrow = 1, scales = "free")
+
+# summary(fit_tn)
+
+spread_draws(fit_tn, 
+                     b_maxdepth, 
+                     b_soilvorgvcarbon, 
+                     b_nitrogenvfertilizervuse, 
+                     b_buffervcultivatedvcrops) %>%
+  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
+  mutate(key = factor(key, levels = c("b_maxdepth", 
+                     "b_soilvorgvcarbon", 
+                     "b_nitrogenvfertilizervuse", 
+                     "b_buffervcultivatedvcrops"))) %>%
+  ggplot(aes(x = value)) +
+  geom_histogram(alpha = 0.8) +
+  theme_cowplot() +
+  theme(axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank()) +
+  xlab("") + ylab("") +
+  facet_wrap(~key, nrow = 1, scales = "free")
+
+plot_grid(gg_tp, gg_tn, nrow = 2)
 

### 2019-06-21 figures/07_model-selection.Rmd
plot fixed effects summary

--- 2019-06-20 figures/07_model-selection.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 5, eval = TRUE, warning = FALSE, message = FALSE)
+knitr::opts_chunk$set(echo = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 5, eval = TRUE, warning = FALSE, message = FALSE)
 # setwd("figures")
@@
 
-```{r 07_model_selection, fig.height=3, echo=FALSE, fig.width=6, eval=TRUE}
-print("07_model_selection")
-# setwd("figures")
-
+```{r gis_setup}
 dt      <- readRDS("../data/dt.rds")
@@
 re_brms        <- readRDS("../data/mcmc/re_brms.rds")
+pred_key       <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
+```
+
+```{r tp_summary, fig.height=4}
 # lapply(re_brms, function(x) x$formula) 
-fit_tn         <- re_brms[[5]] # 5 is best tn model with re effects
+fit_tp   <- re_brms[[3]] # 3 is best tp model with random effects
+signif_hu4_ids <- fit_tp$re_signif_ids 
+signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)
+
+# plot tp model fixed effects summary
+# summary(fit_tp)
+gg_tp <- spread_draws(fit_tp, 
+                     b_maxdepth, 
+                     b_hu12vbaseflowvmean, 
+                     b_phosphorusvfertilizervuse, 
+                     b_buffervcultivatedvcrops) %>%
+  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
+  mutate(key = stringr::str_replace(key, "b_", "")) %>%
+  left_join(pred_key, by = c("key" = "varv")) %>%
+  mutate(key = factor(pretty, levels = c("Max depth", 
+                     "Baseflow", 
+                     "Fertilizer P input", 
+                     "Buffer Ag"))) %>%
+  group_by(key) %>%
+  summarize(value = list(tibble::enframe(quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
+  unnest() %>%
+  tidyr::spread(name, value) %>%
+  rowwise() %>%
+  mutate(signif = `5%` & `95%` > 0 | `5%` & `95%` < 0)
+
+gg_tp_fe <- ggplot(data = gg_tp) + 
+  geom_pointrange(aes(x = key, y = `50%`, 
+                      ymin = `5%`, ymax = `95%`, color = signif)) +
+  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  geom_hline(yintercept = 0) +
+  coord_flip() +
+  theme_cowplot() +
+  ylim(-0.6, 0.4) +
+  ylab("Standardized FE slope") + theme(legend.position = 0) +
+  xlab("")
+
+gg_tp_fe
+
+```
+
+```{r tn_summary, fig.height=4}
+# lapply(re_brms, function(x) x$formula) 
+fit_tn         <- re_brms[[5]] # 5 is best tn model with random effects
 signif_hu4_ids <- fit_tn$re_signif_ids 
@@
 
-# plotting
+# plot tn model fixed effects summary
+# summary(fit_tn)
+gg_tn <- spread_draws(fit_tn, 
+                     b_maxdepth, 
+                     b_soilvorgvcarbon, 
+                     b_nitrogenvfertilizervuse, 
+                     b_buffervcultivatedvcrops) %>%
+  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
+  mutate(key = stringr::str_replace(key, "b_", "")) %>%
+  left_join(pred_key, by = c("key" = "varv")) %>%
+  mutate(key = factor(pretty, levels = c("Max depth", 
+                     "Soil organic carbon", 
+                     "Fertilizer N input", 
+                     "Buffer Ag"))) %>%
+  group_by(key) %>%
+  summarize(value = list(tibble::enframe(quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
+  unnest() %>%
+  tidyr::spread(name, value) %>%
+  rowwise() %>%
+  mutate(signif = `5%` & `95%` > 0 | `5%` & `95%` < 0)
+
+gg_tn_fe <- ggplot(data = gg_tn) + 
+  geom_pointrange(aes(x = key, y = `50%`, 
+                      ymin = `5%`, ymax = `95%`, color = signif)) +
+  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  geom_hline(yintercept = 0) +
+  coord_flip() +
+  theme_cowplot() +
+  ylim(-0.6, 0.4) +
+  ylab("Standardized FE slope") + theme(legend.position = 0) +
+  xlab("")
+
+gg_tn_fe
+```
+
+```{r tn_re}
+# map significant random effects hu4s
 gg_hu4 <- ggplot() +
@@
 
-gg_corn_re <- ggplot(data = fit_tn$re) +
+# dotplot tn hu4 randome effects
+gg_tn_re <- ggplot(data = fit_tn$re) +
   geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
@@
 
-plot_grid(gg_corn_re, gg_hu4)
+plot_grid(gg_hu4, gg_tn_re)
+```
 
+```{r tn_re_compare}
+# compare lakes in signif hu4s
+dt        <- readRDS("../data/dt_scaled.rds") %>%
+  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
+  tidyr::gather(key = "key", value = "value", 
+                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4) %>%
+  group_by(key, signif_hu4) %>%
+  mutate(median = median(value, na.rm = TRUE))
+
+dt_predictors <- dplyr::filter(dt, key %in% 
+                                 c("tp",
+                                   "nitrogen_atmospheric_deposition",
+                                   "clay_pct"))
+dt_modelled <- dplyr::filter(dt, key %in% 
+                               c("maxdepth", "tn", "soil_org_carbon",
+                                 "buffer_cultivated_crops", "corn",
+                                 "nitrogen_fertilizer_use"))
+
+gg_hist <- ggplot(data = dt_predictors) + 
+  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
+  geom_vline(aes(xintercept = median, color = signif_hu4), 
+             linetype = "dashed") +
+  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  theme(legend.position = 0) +
+  facet_wrap(~key)
+
+# line graph tn vs tp
+dt        <- readRDS("../data/dt_scaled.rds") %>%
+  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
+  tidyr::gather(key = "key", value = "value", 
+                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4, -tn) %>%
+  dplyr::filter(key %in% c(c("tp"))) %>%
+  tidyr::spread(key, value)
+
+gg_tp <- ggplot(data = dt) + 
+  geom_point(aes(x = tn, y = tp, color = signif_hu4)) +
+  geom_line(stat = "smooth", method = lm, se = FALSE, 
+            aes(x = tn, y = tp, color = signif_hu4)) +
+  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  theme(legend.position = 0)
+
+plot_grid(gg_hist, gg_tp, nrow = 2)
+```
+
+```{r 07_model_selection, fig.height=3, echo=FALSE, fig.width=6, eval=FALSE}
 # gg_hu4_ndep <- ggplot() +
@@
 ``` 
-
-```{r signif_hu4_lakes, echo=FALSE}
-# compare lakes in signif hu4s
-dt        <- readRDS("../data/dt_scaled.rds") %>%
-  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
-  tidyr::gather(key = "key", value = "value", 
-                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4) %>%
-  group_by(key, signif_hu4) %>%
-  mutate(median = median(value, na.rm = TRUE))
-
-dt_predictors <- dplyr::filter(dt, key %in% 
-                                 c("tp",
-                                   "nitrogen_atmospheric_deposition",
-                                   "clay_pct"))
-dt_modelled <- dplyr::filter(dt, key %in% 
-                               c("maxdepth", "tn", "soil_org_carbon",
-                                 "buffer_cultivated_crops", "corn",
-                                 "nitrogen_fertilizer_use"))
-
-gg_hist <- ggplot(data = dt_predictors) + 
-  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
-  geom_vline(aes(xintercept = median, color = signif_hu4), 
-             linetype = "dashed") +
-  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  theme(legend.position = 0) +
-  facet_wrap(~key)
-
-# ggplot(data = dt_modelled) + 
-#   geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
-#   geom_vline(aes(xintercept = median, color = signif_hu4), 
-#              linetype = "dashed") +
-#   facet_wrap(~key)
-
-dt        <- readRDS("../data/dt_scaled.rds") %>%
-  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
-  tidyr::gather(key = "key", value = "value", 
-                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4, -tn) %>%
-  dplyr::filter(key %in% c(c("tp"))) %>%
-  tidyr::spread(key, value)
-
-gg_tp <- ggplot(data = dt) + 
-  geom_point(aes(x = tn, y = tp, color = signif_hu4)) +
-  geom_line(stat = "smooth", method = lm, se = FALSE, 
-            aes(x = tn, y = tp, color = signif_hu4)) +
-  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  # facet_wrap(~key) +
-  theme(legend.position = 0)
-
-plot_grid(gg_hist, gg_tp, nrow = 2)
-
-```
-
 ```{r prediction_lines, echo=FALSE, eval=FALSE}

### 2019-06-21 scripts/99_make_predictor_key.R

@@ -29,6 +29,8 @@ pred_key <- data.frame(var = c(
   "Nutrient sources", "Nutrient sources", "Nutrient sources", 
   "Nutrient sources", "Nutrient proxies","Nutrient proxies", "Nutrient proxies"),
                       stringsAsFactors = FALSE)
+  
+pred_key$varv <- gsub("_", "v", pred_key$var)
 
 # View(pred_key)
 write.csv(pred_key, "data/predictor_key.csv", row.names = FALSE)

### 2019-06-21 figures/07_model-selection.Rmd
add a tp re plot

@@
 
+```{r tp_re}
+fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
+gg_tp_re <- ggplot(data = fit_tp$re) +
+  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
+                      ymin = `5%`, ymax = `95%`, color = signif)) +
+  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  geom_hline(yintercept = 0) +
+  coord_flip() +
+  ylab("TP model, pasture RE slope") + theme(legend.position = 0)
+
+gg_tp_re
+```
+
 ```{r tn_summary, fig.height=4}
@@
 # dotplot tn hu4 randome effects
+fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
 gg_tn_re <- ggplot(data = fit_tn$re) +

### 2019-06-21 figures/07_model-selection.Rmd
separate plots

@@
 
-```{r tn_re}
+```{r tn_re_hu4}
+
 # map significant random effects hu4s
@@
 
-# dotplot tn hu4 randome effects
+gg_hu4
+```
+
+```{r tn_re}
+# dotplot tn hu4 random effects
 fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
@@
 
-plot_grid(gg_hu4, gg_tn_re)
+gg_tn_re
 ```

### 2019-06-23 figures/09_stream_buffer.Rmd
suppress pkg msgs
explore different buffer contrasts

@@
 
-```{r 09_stream_buffer, echo=FALSE, fig.height=3, fig.width=4}
+```{r 09_stream_buffer, echo=FALSE, fig.height=3, fig.width=4, warning=FALSE}
 dt <- readRDS("../data/dt.rds") %>%
@@
 # first llid is a low stream ag lake
-# second llids is a high stream ag lake
-llids <- c("4532", "96236")
+# second llid is a high stream ag lake
+
+llids <- c("6992", "7026")
 
@@
 library(curl)
-library(glue)
+suppressMessages(library(glue))
 library(slippymath)
-library(rgdal)
+suppressMessages(library(rgdal))
 

### 2019-06-24 figures/07_model-selection.Rmd
plot ndep vs re slope

@@
 plot_grid(gg_hist, gg_tp, nrow = 2)
+
+lg <- lagosne_load("1.087.1")
+gg_line <- fit_tn$re %>%
+  ungroup() %>%
+  mutate(hu4vzoneid = paste0("HU4_", hu4vzoneid)) %>%
+  left_join(dplyr::select(lg$hu4.chag, 
+                          hu4_zoneid, hu4_dep_totaln_2010_mean), 
+            by = c("hu4vzoneid" = "hu4_zoneid")) %>%
+ggplot() +
+  geom_point(aes(x = hu4_dep_totaln_2010_mean, y = `50%`, color = signif)) +
+  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  theme_cowplot() +
+  ylab("TN model, corn RE slope") + xlab("N deposition") +
+  theme(legend.position = 0)
+
+gg_tn_re
+
 ```

### 2019-06-24 manuscript/appendix.Rmd
add buffer composition category
explore trophic state breakdown by hu4

@@
 
+focal_hu4s <- data.frame(hu4_zoneid = paste0("HU4_", 
+                                             c("56", "57", "36", "37", "38")), 
+                         stringsAsFactors = FALSE)
+
 dt <- readRDS("../data/dt.rds") %>%
@@
 grid.draw(g)
+
+test <- readRDS("../data/dt.rds") %>%
+  mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>%
+  dplyr::filter(!is.na(chla)) %>%
+  mutate(trophic_state = cut(chla, 
+                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
+                             labels = c("oligotrophic", "mesotrophic", 
+                                        "eutrophic", "hypereutrophic"))) %>%
+  dplyr::select(lagoslakeid, is_focal, chla, hu4_zoneid, trophic_state) %>%
+  group_by(is_focal, trophic_state) %>%
+  count() %>%
+  tidyr::spread(trophic_state, n)
 ```
+
+```{r predictor_maps}
+# 
+```

### 2019-06-24 figures/07_model-selection.Rmd
test for interaction effects

--- 2019-06-21 figures/07_model-selection.Rmd
@@
 plot_grid(gg_hist, gg_tp, nrow = 2)
+
+lg <- lagosne_load("1.087.1")
+gg_line <- fit_tn$re %>%
+  ungroup() %>%
+  mutate(hu4vzoneid = paste0("HU4_", hu4vzoneid)) %>%
+  left_join(dplyr::select(lg$hu4.chag, 
+                          hu4_zoneid, hu4_dep_totaln_2010_mean), 
+            by = c("hu4vzoneid" = "hu4_zoneid")) %>%
+ggplot() +
+  geom_pointrange(aes(x = hu4_dep_totaln_2010_mean, y = `50%`,
+                      ymin = `5%`, ymax = `95%`, color = signif)) +
+  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  theme_cowplot() +
+  ylab("TN model, corn RE slope") + xlab("N deposition") +
+  theme(legend.position = 0)
+
+gg_tn_re
+
+gg_line
+
+```
+
+```{r tn_interaction, eval=FALSE}
+# lapply(re_brms, function(x) x$formula) 
+fit <- re_brms[[6]]
+fit$formula
+head(fit$res_med)
+test <- readRDS("../data/dt_scaled.rds") %>%
+  dplyr::select(lagoslakeid, hu4_nitrogen_atmospheric_deposition, corn, 
+                maxdepth, soil_org_carbon, 
+                nitrogen_fertilizer_use, buffer_cultivated_crops) %>%
+  left_join(fit$res_med)
+
+cor.test(test$.residual_median, test$hu4_nitrogen_atmospheric_deposition * test$soil_org_carbon)
+abline(0, 1)
 ```

### 2019-06-24 figures/08_exploratory_dotplot.Rmd
figure resize

--- 2019-06-17 figures/08_exploratory_dotplot.Rmd
@@
 
-```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE, warning=FALSE}
+```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE, warning=FALSE, fig.height=5.5, fig.width=6.9}
 pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)

### 2019-06-30 figures/02_hierarchical_demo.Rmd
toward a colorless hierarchical demo

@@
     # scale_y_log10() + scale_x_log10() +
+    theme_cowplot() +
     theme(legend.position = "") +
     labs(x = "Ag. LULC (pct, NLCD 2011)", 
-         y = "TP")  +
-    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
+         y = "TP (ug/L)")  +
+    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 150)) + 
+    scale_color_manual(values = rep("black", 26)),
   ggplot() +
-    geom_sf(data = hu4, aes(fill = n_cat)) +
+    geom_sf(data = hu4, aes(fill = n_cat, alpha = n)) +
     # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
@@
           legend.title = element_blank()) +
-    scale_fill_manual(values = colors, levels(hu4$n_cat)),
+    scale_fill_manual(values = rep("black", 5)),
   rel_heights = c(0.6, 1), labels = "AUTO"

### 2019-07-02 figures/06_lulc_buffer_demo.Rmd
towards total ag panel

@@
 cols     <- dplyr::filter(pal_nlcd(), code %in% unique(test[,3]))
+cols_agg <- mutate(cols, color = "#AA7028")
 
 # codes 81 = pasture; 82 = row_crop
+
+g_nlcd_agg <- ggplot() + 
+  geom_raster(data = test, aes(x = x, y = y, fill = value)) +
+  scale_fill_manual(values = cols_agg$color, labels = cols_agg$description) +
+  geom_sf(data = iws, alpha = 0) +
+  geom_sf(data = network) +
+  geom_sf(data = ll_lake) +
+  coord_sf(datum = NA) + 
+  theme_void() # + 
+  # theme(legend.position = 0)
 
@@
   geom_sf(data = iws, alpha = 0) +
+  geom_sf(data = network) +
+  geom_sf(data = ll_lake) +
   coord_sf(datum = NA) + 
@@
 
-cowplot::plot_grid(g_nlcd + ggtitle("NLCD (2011)"), 
-                   g_cdl + ggtitle("CDL (2010)"), 
+cowplot::plot_grid(
+  g_nlcd_agg + ggtitle("Total Ag"), 
+  g_nlcd + ggtitle("Row Crop / Pasture"), 
+  g_cdl + ggtitle("Individual Crops / Pasture"), 
                    rel_widths = c(0.75, 1))

### 2019-07-03 figures/06_lulc_buffer_demo.Rmd
add total ag panel, closes #15

--- 2019-05-23 figures/06_lulc_buffer_demo.Rmd
@@
   drop_na("value")
-cols <- dplyr::filter(pal_nlcd(), code %in% unique(test[,3]))
+cols     <- dplyr::filter(pal_nlcd(), code %in% unique(test[,3])) %>%
+  mutate(description = c("Pasture", "Row Crops"))
+cols_agg <- mutate(cols, color = "#AA7028", description = "Total Ag")[2,]
 
 # codes 81 = pasture; 82 = row_crop
+
+g_nlcd_agg <- ggplot() + 
+  geom_raster(data = mutate(test, value = 82), aes(x = x, y = y, fill = as.factor(value))) +
+  scale_fill_manual(values = cols_agg$color, labels = cols_agg$description) +
+  geom_sf(data = iws, alpha = 0) +
+  geom_sf(data = network) +
+  geom_sf(data = ll_lake) +
+  coord_sf(datum = NA) + 
+  labs(fill = "") +
+  theme_void() # + 
+  # theme(legend.position = 0)
 
@@
   geom_sf(data = iws, alpha = 0) +
+  geom_sf(data = network) +
+  geom_sf(data = ll_lake) +
   coord_sf(datum = NA) + 
-  theme_void() + 
-  theme(legend.position = 0)
+  labs(fill = "") +
+  theme_void() # + 
+  # theme(legend.position = 0)
 
+cdl_df <- mutate(cdl_df, category = forcats::fct_collapse(cdl_df$category, 
+                                                        `Corn` = "corn", 
+                                                        `Soybeans` = "soybeans", 
+                                                        `Pasture` = "pasture"))
 g_cdl <- ggplot() + 
   geom_raster(data = dplyr::filter(cdl_df, as.character(category) %in% 
-                                     c("corn", "soybeans", "pasture")), 
+                                     c("Corn", "Soybeans", "Pasture")), 
               aes(x = x, y = y, fill = category)) +
-  scale_fill_manual(values = setNames(color_key$color, 
-                                      color_key$category)) +
+  scale_fill_manual(values = 
+                      setNames(
+                        color_key$color, 
+                        snakecase::to_any_case(color_key$category, "sentence"))
+    ) +
   geom_sf(data = iws, alpha = 0) +
@@
   coord_sf(datum = NA) + 
+  labs(fill = "") +
   theme_void()
 
-cowplot::plot_grid(g_nlcd + ggtitle("NLCD (2011)"), 
-                   g_cdl + ggtitle("CDL (2010)"), 
-                   rel_widths = c(0.75, 1))
+cowplot::plot_grid(
+  g_nlcd_agg + ggtitle("Total Ag"), 
+  g_nlcd + ggtitle("Row Crops"), 
+  g_cdl + ggtitle("Individual Crops"), 
+                   rel_widths = c(0.95, 1, 0.95), nrow = 1)
 ```

### 2019-07-03 figures/02_hierarchical_demo.Rmd
cleanup hiearchical demo fig

--- 2019-04-24 figures/02_hierarchical_demo.Rmd
@@
 
-cowplot::plot_grid(
-  ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
+gg_lines <- ggplot(data = dt, aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
     # geom_point() +
@@
     # scale_y_log10() + scale_x_log10() +
+    theme_cowplot() +
     theme(legend.position = "") +
-    labs(x = "Ag. LULC (pct, NLCD 2011)", 
-         y = "TP")  +
-    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300)),
-  ggplot() +
-    geom_sf(data = hu4, aes(fill = n_cat)) +
+    labs(x = "Ag. LULC (pct)", # , NLCD 2011
+         y = "TP (ug/L)")  +
+    scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 150)) + 
+    scale_color_manual(values = rep("black", 26))
+gg_hu4 <- ggplot() +
+    geom_sf(data = hu4, aes(fill = n_cat, alpha = n)) +
     # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
     theme_minimal() +
-    theme(legend.position = "bottom",
+    theme(legend.position = 0,
           axis.title = element_blank(),
           legend.title = element_blank()) +
-    scale_fill_manual(values = colors, levels(hu4$n_cat)),
-  rel_heights = c(0.6, 1), labels = "AUTO"
-)
+    scale_fill_manual(values = rep("black", 5))
+
+cowplot::plot_grid(
+  plot_grid(nullGrob(), gg_lines, nullGrob(), 
+            ncol = 1, rel_heights = c(0.33, 1, 0.33)), 
+  gg_hu4)
 ```

### 2019-07-03 figures/07_model-selection.Rmd
use transparent backgrounds

@@
   coord_flip() +
+  cowplot::theme_cowplot() +
+  theme(rect = element_rect(fill = "transparent")) +
   ylab("TP model, pasture RE slope") + theme(legend.position = 0)
@@
   coord_flip() +
+  cowplot::theme_cowplot() +
+  theme(rect = element_rect(fill = "transparent")) +
   ylab("TN model, corn RE slope") + theme(legend.position = 0)
@@
                                    "nitrogen_atmospheric_deposition",
-                                   "clay_pct"))
+                                   "clay_pct")) %>%
+  dplyr::left_join(pred_key, by = c("key" = "var"))
+dt_predictors[is.na(dt_predictors$pretty), "pretty"] <- 
+  sapply(dt_predictors[is.na(dt_predictors$pretty), "key"], toupper)
+
 dt_modelled <- dplyr::filter(dt, key %in% 
@@
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  cowplot::theme_cowplot() +
   theme(legend.position = 0) +
-  facet_wrap(~key)
+  theme(rect = element_rect(fill = "transparent"), 
+        strip.background = element_rect(fill = "white"), 
+        strip.text = element_text(face = "bold")) +
+  facet_wrap(~pretty)
 
@@
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  theme(legend.position = 0)
+  cowplot::theme_cowplot() +
+  theme(legend.position = 0) + 
+  theme(rect = element_rect(fill = "transparent"))
 
@@
   ylab("TN model, corn RE slope") + xlab("N deposition") +
-  theme(legend.position = 0)
+  cowplot::theme_cowplot() +
+  theme(legend.position = 0) + 
+  theme(rect = element_rect(fill = "transparent"))
 

### 2019-07-03 figures/07_model-selection.Rmd
figure resize

@@
 
-```{r tp_summary, fig.height=4}
+```{r tp_summary, fig.width=3.25, fig.height=4}
 # lapply(re_brms, function(x) x$formula) 
@@
 
-```{r tp_re}
+```{r tp_re, fig.width=3.25, fig.height=4.5}
 fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
@@
 
-```{r tn_summary, fig.height=4}
+```{r tn_summary, fig.height=4, fig.width=3.25}
 # lapply(re_brms, function(x) x$formula) 
@@
 
-```{r tn_re}
+```{r tn_re, fig.width=3.25, fig.height=4.5}
 # dotplot tn hu4 random effects
@@
   theme(rect = element_rect(fill = "transparent"), 
-        strip.background = element_rect(fill = "white"), 
+        strip.background = element_rect(fill = "transparent"), 
         strip.text = element_text(face = "bold")) +

### 2019-07-08 figures/07_model-selection.Rmd
fix labels, significance coloring

@@
   rowwise() %>%
-  mutate(signif = `5%` & `95%` > 0 | `5%` & `95%` < 0)
+  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))
 
@@
   theme(rect = element_rect(fill = "transparent")) +
-  ylab("TP model, pasture RE slope") + theme(legend.position = 0)
+  ylab("TP model, pasture RE slope") + xlab("Zone ID") +
+  theme(legend.position = 0)
 
@@
   theme(rect = element_rect(fill = "transparent")) +
-  ylab("TN model, corn RE slope") + theme(legend.position = 0)
+  ylab("TN model, corn RE slope") + xlab("Zone ID") + 
+  theme(legend.position = 0)
 

### 2019-07-08 figures/07_model-selection.Rmd
figure resize

@@
 
-```{r tp_summary, fig.width=3.25, fig.height=4}
+```{r tp_summary, fig.width=4, fig.height=4.25}
 # lapply(re_brms, function(x) x$formula) 
@@
 
-```{r tn_summary, fig.height=4, fig.width=3.25}
+```{r tn_summary, fig.height=4, fig.width=4.25}
 # lapply(re_brms, function(x) x$formula) 

### 2019-07-09 figures/07_model-selection.Rmd
add map to makefile

@@
 gg_tp <- ggplot(data = dt) + 
-  geom_point(aes(x = tn, y = tp, color = signif_hu4)) +
+  geom_point(aes(x = tp, y = tn, color = signif_hu4)) +
   geom_line(stat = "smooth", method = lm, se = FALSE, 
-            aes(x = tn, y = tp, color = signif_hu4)) +
+            aes(x = tp, y = tn, color = signif_hu4)) +
   scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +

### 2019-07-09 manuscript/figures.Rmd
add map to makefile

@@
 
-```{r maps, fig.cap = "Quanitle map of lake nutrients.", warning=FALSE, echo = FALSE}
+```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/tptn_maps-1.pdf")
+```
+
+```{r maps2, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/11_map-1.pdf")
 ```

### 2019-07-09 figures/07_model-selection.Rmd
make fig single panel
Reize

@@
 
-```{r tn_re_compare}
+```{r tn_re_compare, fig.height=3}
 # compare lakes in signif hu4s
@@
 
-plot_grid(gg_hist, gg_tp, nrow = 2)
+plot_grid(gg_hist, nrow = 1)
+# plot_grid(gg_hist, gg_tp, nrow = 2)
 

### 2019-07-10 figures/08_exploratory_dotplot.Rmd
towards stacked legend

@@
   theme(axis.title.y = element_blank(), 
-                   axis.text = element_text(size = 8), 
-                   legend.position = 0)
+                   axis.text = element_text(size = 8))
 
@@
     xlim(0, 0.6) +
-    plot_opts
+    plot_opts +
+  theme(legend.text = element_text(size = 8), 
+        legend.position = c(0.53, 0.23), 
+        legend.box.background = element_rect(color = "black"), 
+        legend.title = element_blank())
 gg_tn <- ggplot(data = dt_tn) + 
@@
     xlim(0, 0.6) +
-    plot_opts
-legend_b <- get_legend(gg_tp + 
-                         theme(legend.position="bottom", 
-                               legend.justification = "center", 
-                               legend.text = element_text(size = 10), 
-                               legend.title = element_blank()))
-plot_grid(
-  plot_grid(gg_tp, gg_tn), 
-  legend_b, ncol = 1, rel_heights = c(1, 0.1))
+    plot_opts +
+  theme(legend.position = 0)
+
+plot_grid(gg_tp, ggplot() + geom_blank(),
+          gg_tn, rel_widths = c(1, 0.2, 1), nrow = 1)
 

### 2019-07-12 figures/08_exploratory_dotplot.Rmd
make dotplot legend vertical

--- 2019-06-24 figures/08_exploratory_dotplot.Rmd
@@
 
-plot_opts <- theme_cowplot() +
-  theme(axis.title.y = element_blank(), 
-                   axis.text = element_text(size = 8), 
-                   legend.position = 0)
-
 dt_tp <- prep_dotplot(dt_tp, "tp") %>%
@@
 # show_col(brewer_pal("div", "Set1")(4))                   
+plot_opts <- theme_cowplot() +
+  theme(axis.title.y = element_blank(), 
+        axis.text = element_text(size = 8), 
+        axis.title.x = element_blank())
+
 gg_tp <-  ggplot(data = dt_tp) + 
@@
     xlim(0, 0.6) +
-    plot_opts
-legend_b <- get_legend(gg_tp + 
-                         theme(legend.position="bottom", 
-                               legend.justification = "center", 
-                               legend.text = element_text(size = 10), 
-                               legend.title = element_blank()))
-plot_grid(
-  plot_grid(gg_tp, gg_tn), 
-  legend_b, ncol = 1, rel_heights = c(1, 0.1))
+    plot_opts +
+  theme(legend.position = 0)
+
+plot_grid(NULL, 
+plot_grid(gg_tp, NULL,
+          gg_tn, rel_widths = c(1, 0.2, 1), nrow = 1, 
+          labels = c("TP", "", "TN"), 
+          label_x = c(0.6, 0.5, 0.6), 
+          label_y = c(1.05, 1.1, 1.05)), 
+ncol = 1, rel_heights = c(0.07, 1))
 

### 2019-07-12 figures/09_stream_buffer.Rmd
label with name + state

@@
 llids         <- c("6992", "7026")
+llid_metadata <- lake_info(llids)
+llid_callouts <- paste(llid_metadata$gnis_name, "-", llid_metadata$state)
 
@@
   theme_void() +
-  ggtitle(llids[i])
+  ggtitle(llid_callouts[i])
 

### 2019-07-12 figures/09_stream_buffer.Rmd
add lake and buffer outlines

@@
 res_iws    <- query_gis("IWS", "lagoslakeid", llids)
+res_lakes  <- query_gis("LAGOS_NE_All_Lakes_4ha", "lagoslakeid", llids)
 
@@
 
+### draw forest outlines
+# i <- 2
+# forest_outline <- mapedit::editMap(
+#   mapview(images[[i]])
+#   )
+# forest_outline <- smoothr::smooth(forest_outline$drawn)
+# forest_outline <- st_intersection(
+#   st_transform(forest_outline, st_crs(res_iws[i,])),
+#   res_iws[i,])
+# mapview(forest_outline)
+# saveRDS(forest_outline, "../data/res_forest_outline_2.rds")
+forest_outline_1 <- readRDS("../data/res_forest_outline_1.rds")
+forest_outline_2 <- readRDS("../data/res_forest_outline_2.rds")
+
 i <- 1
@@
   geom_sf(data = res_iws[i,], alpha = 0, color = "red") +
-  geom_sf(data = res_streams[[i]], color = "cyan") +
+  geom_sf(data = res_lakes[i,], alpha = 0, color = "cyan") +
+  geom_sf(data = forest_outline_1, color = "green3") +
+  geom_sf(data = st_difference(
+      st_transform(res_streams[[i]], st_crs(res_lakes[i,])), 
+      res_lakes[i,]), 
+    color = "cyan") +
   coord_sf(datum = NA) +
@@
   geom_sf(data = res_iws[i,], alpha = 0, color = "red") +
-  geom_sf(data = res_streams[[i]], color = "cyan") +
+  geom_sf(data = res_lakes[i,], alpha = 0, color = "cyan") +
+  geom_sf(data = forest_outline_2, color = "green3") +
+  geom_sf(data = st_difference(
+      st_transform(res_streams[[i]], st_crs(res_lakes[i,])), 
+      res_lakes[i,]), 
+    color = "cyan") +
   coord_sf(datum = NA) +

### 2019-07-12 figures/06_lulc_buffer_demo.Rmd
rename panel title

@@
   g_nlcd_agg + ggtitle("Total Ag"), 
-  g_nlcd + ggtitle("Row Crops"), 
+  g_nlcd + ggtitle("Ag Cover Type"), 
   g_cdl + ggtitle("Individual Crops"), 

### 2019-07-15 manuscript/appendix.Rmd
show trophic state with waffle charts

--- 2019-06-13 manuscript/appendix.Rmd
@@
 ```{r trophic_state, fig.cap="Lake trophic state", fig.width = 5.5, fig.height = 4, warning=FALSE, message=FALSE}
+lg <- lagosne_load("1.087.1")
+focal_hu4s <- data.frame(hu4_zoneid = paste0("HU4_", 
+                                             c("56", "57", "36", "37", "38")), 
+                         stringsAsFactors = FALSE)
 
@@
   group_by(trophic_state) %>%
-  count()
+  count() %>%
+  ungroup() %>% # rowwise() %>%
+  mutate(frac = (n / sum(n)) * 100)
 
-g <- gridExtra::tableGrob(dt, rows = rep("", nrow(dt)))
-grid.draw(g)
+lg_trophic_state <- dplyr::filter(lg$epi_nutr, 
+                                  !(lagoslakeid %in%
+                                      readRDS("../data/dt.rds")$lagoslakeid)) %>%
+  dplyr::filter(!is.na(chla)) %>%
+  dplyr::select(chla, lagoslakeid, sampledate) %>%
+  group_by(lagoslakeid) %>%
+  summarise(chla = median(chla)) %>%
+  mutate(trophic_state = cut(chla, 
+                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
+                             labels = c("oligotrophic", "mesotrophic", 
+                                        "eutrophic", "hypereutrophic"))) %>%
+  dplyr::select(chla, trophic_state) %>%
+  group_by(trophic_state) %>%
+  count() %>%
+  ungroup() %>% # rowwise() %>%
+  mutate(frac = (n / sum(n)) * 100)
+
+dt <- data.frame(`Trophic State` = dt$trophic_state, 
+           `Study` = round(dt$frac, 1), 
+           `All` = round(lg_trophic_state$frac, 1), 
+           stringsAsFactors = FALSE)
+dt <- setNames(dt, c("Trophic State", "This Study", "All Lakes"))
+
+# g <- gridExtra::tableGrob(dt, rows = rep("", nrow(dt)))
+# grid.draw(g)
+
+# waffle
+library(waffle)
+library(hrbrthemes)
+
+ggplot(tidyr::gather(dt, key = "key", value = "value", -`Trophic State`),
+       aes(fill=`Trophic State`, values = `value`)) +
+  geom_waffle(color = "white", size=1.125, n_rows = 7) +
+  facet_wrap(~key, ncol=1) +
+  scale_x_discrete(expand=c(0,0)) +
+  scale_y_discrete(expand=c(0,0)) +
+  ggthemes::scale_fill_tableau(name=NULL) +
+  coord_equal() +
+  labs(title = "Trophic State")  +
+#   theme_ipsum_rc(grid="") +
+   theme_enhance_waffle() + 
+  theme(strip.background = element_blank())
+
+# highlighted regions
+test <- readRDS("../data/dt.rds") %>%
+  mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>%
+  dplyr::filter(!is.na(chla)) %>%
+  mutate(trophic_state = cut(chla, 
+                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
+                             labels = c("oligotrophic", "mesotrophic", 
+                                        "eutrophic", "hypereutrophic"))) %>%
+  dplyr::select(lagoslakeid, is_focal, chla, hu4_zoneid, trophic_state) %>%
+  group_by(is_focal, trophic_state) %>%
+  count() %>%
+  tidyr::spread(trophic_state, n)
 ```
+
+```{r predictor_maps}
+# 
+```

### 2019-07-15 manuscript/appendix.Rmd
transparent waffle background

@@
    theme_enhance_waffle() + 
-  theme(strip.background = element_blank())
+  theme(strip.background = element_blank(), 
+        rect = element_rect(fill = "transparent"))
 

### 2019-07-15 manuscript/appendix.Rmd
size adjustments

--- 2019-07-15 manuscript/appendix.Rmd
@@
 
-```{r trophic_state, fig.cap="Lake trophic state", fig.width = 5.5, fig.height = 4, warning=FALSE, message=FALSE}
+```{r trophic_state, fig.cap="Lake trophic state", fig.width = 6, fig.height = 3.2, warning=FALSE, message=FALSE}
 lg <- lagosne_load("1.087.1")
@@
 
-ggplot(tidyr::gather(dt, key = "key", value = "value", -`Trophic State`),
+dt_waffle <- tidyr::gather(dt, key = "key", value = "value", -`Trophic State`) %>%
+  add_row(`Trophic State` = "oligotrophic", `key` = "All Lakes", `value` = 2) %>%
+  add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%
+  arrange(`Trophic State`)
+
+ggplot(dt_waffle,
        aes(fill=`Trophic State`, values = `value`)) +
-  geom_waffle(color = "white", size=1.125, n_rows = 7) +
+  geom_waffle(color = "white", size=0.7, n_rows = 5) +
   facet_wrap(~key, ncol=1) +
@@
    theme_enhance_waffle() + 
-  theme(strip.background = element_blank())
+  theme(strip.background = element_blank(), 
+        rect = element_rect(fill = "transparent"), 
+        legend.position = "bottom", 
+        title = element_text(size = 18), 
+        strip.text = element_text(size = 16), 
+        legend.text = element_text(size = 10), 
+        legend.key.size = unit(0.5, "line")) + 
+  guides(fill = guide_legend(nrow = 2))
 

### 2019-07-16 figures/08_exploratory_dotplot.Rmd
rename variable categories

@@
                   category = factor(category, 
-                                    levels = c("Lake", "Nutrient sources",
-                                               "Nutrient proxies",
-                                               "Transport capacity", 
-                                               "Buffer composition"))) %>%
+                                    levels = c("Nutrient inputs",
+                                               "Nutrient transport", 
+                                               "Land-use cover",
+                                               "Buffer composition", 
+                                               "Lake"))) %>%
     dplyr::filter(!(var %in% c("tp", "tn"))) %>%

### 2019-07-16 scripts/99_make_predictor_key.R

@@ -19,15 +19,15 @@ pred_key <- data.frame(var = c(
     "Fertilizer N input", "Fertilizer P input", "P input", 
     "Manure P input", "Wheat", "Pasture", "Row-crop Ag"),
                       category = c(
-  "Nutrient sources", "Lake", "Lake", 
-  "Transport capacity", "Transport capacity", "Buffer composition",
-  "Buffer composition","Nutrient proxies","Nutrient proxies", "Nutrient proxies",
+  "Nutrient inputs", "Lake", "Lake", 
+  "Nutrient transport", "Nutrient transport", "Buffer composition",
+  "Buffer composition","Land-use cover","Land-use cover", "Land-use cover",
   "Buffer composition", "Buffer composition", "Buffer composition",
-  "Nutrient proxies", "Nutrient proxies", "Transport capacity","Lake",
-  "Transport capacity", "Nutrient proxies","Nutrient sources", 
-  "Transport capacity", "Nutrient proxies", "Nutrient sources",
-  "Nutrient sources", "Nutrient sources", "Nutrient sources", 
-  "Nutrient sources", "Nutrient proxies","Nutrient proxies", "Nutrient proxies"),
+  "Land-use cover", "Land-use cover", "Nutrient transport","Lake",
+  "Nutrient transport", "Land-use cover","Nutrient inputs", 
+  "Nutrient transport", "Land-use cover", "Nutrient inputs",
+  "Nutrient inputs", "Nutrient inputs", "Nutrient inputs", 
+  "Nutrient inputs", "Land-use cover","Land-use cover", "Land-use cover"),
                       stringsAsFactors = FALSE)
   
 pred_key$varv <- gsub("_", "v", pred_key$var)

### 2019-07-16 manuscript/appendix.Rmd
recolor

@@
 
-```{r trophic_state, fig.cap="Lake trophic state", fig.width = 6, fig.height = 3.2, warning=FALSE, message=FALSE}
+```{r data_prep, fig.cap="Lake trophic state", fig.width = 6, fig.height = 3.2, warning=FALSE, message=FALSE}
 lg <- lagosne_load("1.087.1")
@@
 # grid.draw(g)
+```
 
+```{r trophic_state, fig.cap="Lake trophic state", fig.width = 6, fig.height = 3.2, warning=FALSE, message=FALSE}
 # waffle
@@
   geom_waffle(color = "white", size=0.7, n_rows = 5) +
-  facet_wrap(~key, ncol=1) +
-  scale_x_discrete(expand=c(0,0)) +
-  scale_y_discrete(expand=c(0,0)) +
-  ggthemes::scale_fill_tableau(name=NULL) +
+  facet_wrap(~key, ncol = 1) +
+  scale_x_discrete(expand = c(0,0)) +
+  scale_y_discrete(expand = c(0,0)) +
+  shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
+                    shades::delta(-10)) +
   coord_equal() +
-  labs(title = "Trophic State")  +
-#   theme_ipsum_rc(grid="") +
   theme_enhance_waffle() + 
@@
         legend.position = "bottom", 
-        title = element_text(size = 18), 
+        title = element_blank(), 
         strip.text = element_text(size = 16), 

### 2019-07-16 figures/07_model-selection.Rmd
add re_global to huc slope estimates

@@
 fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
+fit_tp$re <- fit_tp$re %>%
+  mutate_at(vars(matches("%")), function(x) x + 
+              as.numeric(fit_tp$re_global["50%"]))
+
 gg_tp_re <- ggplot(data = fit_tp$re) +
@@
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  geom_hline(yintercept = 0) +
+  geom_hline(yintercept = as.numeric(fit_tp$re_global["50%"])) +
   coord_flip() +
@@
 fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
+fit_tn$re <- fit_tn$re %>%
+  mutate_at(vars(matches("%")), function(x) x + 
+              as.numeric(fit_tn$re_global["50%"]))
+
 gg_tn_re <- ggplot(data = fit_tn$re) +
@@
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  geom_hline(yintercept = 0) +
+  geom_hline(yintercept = as.numeric(fit_tn$re_global["50%"])) +
   coord_flip() +

### 2019-07-16 scripts/03_model.R

@@ -1,6 +1,7 @@
 # setwd("../")
 source("scripts/99_utils.R")
 
+lg <- lagosne_load("1.087.1")
 dt        <- readRDS("data/dt_scaled.rds") 
 names(dt) <- gsub("_", "v", names(dt))
 
@@ -112,7 +113,17 @@ get_re_text <- function(x){
 }
 
 get_re_signif <- function(x){
-  # x <- re_brms[[5]]
+  # x <- re_brms[[1]]
+  # tidybayes::get_variables(x)
+  print(as.character(x$formula)[1])
+  
+  re_global <- x %>%
+    spread_draws(!!rlang::parse_expr(
+      paste0("sd_hu4vzoneid__", get_re_text(as.character(x$formula)[1])))) %>%
+    dplyr::select(tail(names(.), 1)) %>%
+    pull(names(.)[1]) %>%
+    quantile(c(0.05, 0.5, 0.95))
+  
   res <- x %>%
     spread_draws(r_hu4vzoneid[hu4vzoneid,term]) %>%
     dplyr::filter(term == get_re_text(as.character(x$formula)[1])) %>%
@@ -121,6 +132,7 @@ get_re_signif <- function(x){
     mutate(signif = case_when(`5%` > 0 ~ TRUE, 
                               TRUE ~ FALSE))
   x$re            <- res
+  x$re_global     <- re_global
   x$re_signif     <- any(res$signif)
   x$re_signif_ids <- dplyr::filter(res, signif == TRUE)$hu4vzoneid
   x
@@ -130,6 +142,7 @@ re_brms <- lapply(re_brms, function(x) get_re_signif(x))
 
 # save model residuals
 get_residuals <- function(model, threshold = 0.1){
+  lg <- parent.env(environment())$lg
   # model <- re_brms[[1]]
   model$res_med <- dt %>%
     add_residual_draws(model) %>%
@@ -151,6 +164,7 @@ get_residuals <- function(model, threshold = 0.1){
 re_brms <- lapply(re_brms, function(x) get_residuals(x))
 
 saveRDS(re_brms, "data/mcmc/re_brms.rds")
+# unlink("data/mcmc/re_brms.rds")
 # re_brms <- readRDS("data/mcmc/re_brms.rds")
 
 r2_re <- dplyr::bind_rows(
@@ -221,10 +235,9 @@ hu4_signif <-  LAGOSNEgis::query_gis(
 # mapview::mapview(hu4_signif, color = "red")
 
 
-
-
[…]

### 2019-07-18 figures/07_model-selection.Rmd
run and start evaluation of horseshoe results

@@
 # lapply(re_brms, function(x) x$formula) 
-fit_tp   <- re_brms[[3]] # 3 is best tp model with random effects
+fit_tp   <- re_brms[[1]] # 1 is best tp model with random effects
 signif_hu4_ids <- fit_tp$re_signif_ids 

### 2019-07-18 scripts/03_model.R

@@ -120,19 +120,19 @@ r2_fe <- dplyr::bind_rows(
                       (1 + pasture | hu4vzoneid))
 ))
 
-re_brms <- list()
-for(i in seq_along(model_forms_re)){
-  # i <- 2
-  print(paste0("Fitting ", paste0("data/mcmc/re/", names(model_forms_re)[i])))
-  if(!file.exists(paste0("data/mcmc/re/", names(model_forms_re)[i]))){
-    re_brms[[i]] <- brm(formula = model_forms_re[[i]], data = dt, 
-                        prior = set_prior("horseshoe(1)"), family = gaussian(), 
-                        control = list(adapt_delta = 0.99))
-    saveRDS(re_brms[[i]], paste0("data/mcmc/re/", names(model_forms_re)[i]))
-  }else{
-    re_brms[[i]] <- readRDS(paste0("data/mcmc/re/", names(model_forms_re)[i]))
-  }
-}
+# re_brms <- list()
+# for(i in seq_along(model_forms_re)){
+#   # i <- 6
+#   print(paste0("Fitting ", paste0("data/mcmc/re/", names(model_forms_re)[i])))
+#   if(!file.exists(paste0("data/mcmc/re/", names(model_forms_re)[i]))){
+#     re_brms[[i]] <- brm(formula = model_forms_re[[i]], data = dt, 
+#                         prior = set_prior("horseshoe(1)"), family = gaussian(), 
+#                         control = list(adapt_delta = 0.99))
+#     saveRDS(re_brms[[i]], paste0("data/mcmc/re/", names(model_forms_re)[i]))
+#   }else{
+#     re_brms[[i]] <- readRDS(paste0("data/mcmc/re/", names(model_forms_re)[i]))
+#   }
+# }
 
 re_brms <- 
   lapply(seq_along(model_forms_re), function(i) 
@@ -140,29 +140,6 @@ re_brms <-
                       paste0("data/mcmc/re/", names(model_forms_re)[i]), 
                       formula = model_forms_re[[i]], 
                       data = dt))
-
-if(!interactive()){
-  # investigate horseshoe prior
-  # fit_tn <- re_brms[[5]] # 5 is best tn model with random effects
-  # tidybayes::get_variables(fit_tn)
-  # model_forms_re[[5]]
-  tn_horse_form_all <- bf(tn ~ 
-                            maxdepth + iwslavratio +
[…]

### 2019-07-18 figures/07_model-selection.Rmd
show all horseshoe results

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 5, eval = TRUE, warning = FALSE, message = FALSE)
+knitr::opts_chunk$set(echo = FALSE, fig.path = "../figures/", eval = TRUE, warning = FALSE, message = FALSE)
 # setwd("figures")
@@
 
-```{r tp_summary, fig.width=4, fig.height=4.25}
+```{r tp_summary, out.width="3.25in", out.height="4in"}
 # lapply(re_brms, function(x) x$formula) 
@@
 # summary(fit_tp)
-gg_tp <- spread_draws(fit_tp, 
-                     b_maxdepth, 
-                     b_hu12vbaseflowvmean, 
-                     b_phosphorusvfertilizervuse, 
-                     b_buffervcultivatedvcrops) %>%
+
+b_vars <- stringr::str_subset(
+  tidybayes::get_variables(fit_tp), 
+  c("^(b_)(?!.*Intercept).*$"))
+
+gg_tp <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
   tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
+  dplyr::filter(key != "b_Intercept") %>%
   mutate(key = stringr::str_replace(key, "b_", "")) %>%
   left_join(pred_key, by = c("key" = "varv")) %>%
-  mutate(key = factor(pretty, levels = c("Max depth", 
-                     "Baseflow", 
-                     "Fertilizer P input", 
-                     "Buffer Ag"))) %>%
-  group_by(key) %>%
+  group_by(pretty) %>%
   summarize(value = list(tibble::enframe(quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
@@
 gg_tp_fe <- ggplot(data = gg_tp) + 
-  geom_pointrange(aes(x = key, y = `50%`, 
+  geom_pointrange(aes(x = pretty, y = `50%`, 
                       ymin = `5%`, ymax = `95%`, color = signif)) +
@@
 gg_tp_fe
-
 ```
@@
 
-```{r tn_summary, fig.height=4, fig.width=4.25}
+```{r tn_summary, out.width="3.25in", out.height="4in"}
 # lapply(re_brms, function(x) x$formula) 
@@
 # summary(fit_tn)
-gg_tn <- spread_draws(fit_tn, 
-                     b_maxdepth, 
-                     b_soilvorgvcarbon, 
-                     b_nitrogenvfertilizervuse, 
-                     b_buffervcultivatedvcrops) %>%
+gg_tn <- spread_draws(fit_tn, `b_.*`, regex = TRUE) %>%
   tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
+  dplyr::filter(key != "b_Intercept") %>%
   mutate(key = stringr::str_replace(key, "b_", "")) %>%
   left_join(pred_key, by = c("key" = "varv")) %>%
-  mutate(key = factor(pretty, levels = c("Max depth", 
-                     "Soil organic carbon", 
-                     "Fertilizer N input", 
-                     "Buffer Ag"))) %>%
-  group_by(key) %>%
-  summarize(value = list(tibble::enframe(quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
+  group_by(pretty) %>%
+  summarize(value = list(tibble::enframe(
+    quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
   unnest() %>%
@@
 gg_tn_fe <- ggplot(data = gg_tn) + 
-  geom_pointrange(aes(x = key, y = `50%`, 
+  geom_pointrange(aes(x = pretty, y = `50%`, 
                       ymin = `5%`, ymax = `95%`, color = signif)) +

### 2019-07-18 scripts/99_make_predictor_key.R
add ndep to key

@@ -7,6 +7,7 @@ pred_key <- data.frame(var = c(
   "wetland_potential", "corn","nitrogen_livestock_manure", 
   "soil_org_carbon", "soybeans","n_input", 
   "nitrogen_fertilizer_use", "phosphorus_fertilizer_use","p_input", 
+  "hu4vnitrogenvatmosphericvdeposition",
   "phosphorus_livestock_manure", "wheat","pasture", "row_crop_pct"),
                       pretty = c(
     "N deposition", "Max depth", "Watershed-lake ratio", 
@@ -17,6 +18,7 @@ pred_key <- data.frame(var = c(
     "Wetland potential", "Corn", "Manure N input", 
     "Soil organic carbon", "Soybeans", "N input",
     "Fertilizer N input", "Fertilizer P input", "P input", 
+    "N Deposition",
     "Manure P input", "Wheat", "Pasture", "Row-crop Ag"),
                       category = c(
   "Nutrient inputs", "Lake", "Lake", 
@@ -27,6 +29,7 @@ pred_key <- data.frame(var = c(
   "Nutrient transport", "Land-use cover","Nutrient inputs", 
   "Nutrient transport", "Land-use cover", "Nutrient inputs",
   "Nutrient inputs", "Nutrient inputs", "Nutrient inputs", 
+  "Nutrient inputs",
   "Nutrient inputs", "Land-use cover","Land-use cover", "Land-use cover"),
                       stringsAsFactors = FALSE)
   

### 2019-07-18 figures/07_model-selection.Rmd
fix label

@@
   theme(rect = element_rect(fill = "transparent")) +
-  ylab("TP model, pasture RE slope") + xlab("Zone ID") +
+  ylab("TP model, Ag RE slope") + xlab("Zone ID") +
   theme(legend.position = 0)

### 2019-07-18 scripts/03_model.R

@@ -125,18 +125,18 @@ r2_fe <- dplyr::bind_rows(
                       (1 + pasture | hu4vzoneid))
 ))
 
-re_brms <- list()
+# re_brms <- list()
 # for(i in seq_along(model_forms_re)){
   # i <- 1
-  print(paste0("Fitting ", paste0("data/mcmc/re/", names(model_forms_re)[i])))
-  if(!file.exists(paste0("data/mcmc/re/", names(model_forms_re)[i]))){
-    re_brms[[i]] <- brm(formula = model_forms_re[[i]], data = dt,
-                        prior = set_prior("horseshoe(1)"), family = gaussian(),
-                        control = list(adapt_delta = 0.99))
-    saveRDS(re_brms[[i]], paste0("data/mcmc/re/", names(model_forms_re)[i]))
-  }else{
-    re_brms[[i]] <- readRDS(paste0("data/mcmc/re/", names(model_forms_re)[i]))
-  }
+  # print(paste0("Fitting ", paste0("data/mcmc/re/", names(model_forms_re)[i])))
+  # if(!file.exists(paste0("data/mcmc/re/", names(model_forms_re)[i]))){
+  #   re_brms[[i]] <- brm(formula = model_forms_re[[i]], data = dt,
+  #                       prior = set_prior("horseshoe(1)"), family = gaussian(),
+  #                       control = list(adapt_delta = 0.99))
+  #   saveRDS(re_brms[[i]], paste0("data/mcmc/re/", names(model_forms_re)[i]))
+  # }else{
+  #   re_brms[[i]] <- readRDS(paste0("data/mcmc/re/", names(model_forms_re)[i]))
+  # }
 # }
 
 re_brms <- 

### 2019-07-19 figures/07_model-selection.Rmd
figure combine + cleanup

@@
 
-```{r tp_summary, out.width="3.25in", out.height="4in"}
+```{r tp_fe, out.width="3.25in", out.height="4in"}
 # lapply(re_brms, function(x) x$formula) 
@@
   xlab("") 
-
-gg_tp_fe
 ```
@@
 
-```{r tn_summary, out.width="3.25in", out.height="4in"}
+```{r tn_fe, out.width="3.25in", out.height="4in"}
 # lapply(re_brms, function(x) x$formula) 
@@
   xlab("") 
-
-gg_tn_fe
 ```
@@
 
+```
+
+```{r fe}
+cowplot::plot_grid(gg_tp_fe + theme(axis.title.x = element_blank()), 
+                   gg_tn_fe + theme(axis.text.y = element_blank(), 
+                                    axis.title.x = element_blank()), 
+                   rel_widths = c(1, 0.6))
+```
+
+```{r re}
+cowplot::plot_grid(gg_tp_re, 
+                   gg_tn_re + theme(axis.text.y = element_blank(), 
+                                    axis.title.y = element_blank()), 
+                   rel_widths = c(1, 0.9))
 ```

### 2019-07-19 manuscript/appendix.Rmd
figure combine + cleanup

@@
   add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%
-  arrange(`Trophic State`)
+  arrange(`Trophic State`) %>%
+  dplyr::filter(key == "This Study")
 
@@
        aes(fill=`Trophic State`, values = `value`)) +
-  geom_waffle(color = "white", size=0.7, n_rows = 5) +
-  facet_wrap(~key, ncol = 1) +
+  geom_waffle(color = "white", size=0.7, n_rows = 5, flip = TRUE) +
+  # facet_wrap(~key, ncol = 1) +
   scale_x_discrete(expand = c(0,0)) +

### 2019-07-19 scripts/99_make_predictor_key.R

@@ -1,3 +1,5 @@
+suppressMessages(library(dplyr))
+
 pred_key <- data.frame(var = c(
   "nitrogen_atmospheric_deposition","maxdepth","iwsla_ratio",
   "hu12_baseflow_mean","hu12_ppt_mean",
@@ -34,6 +36,11 @@ pred_key <- data.frame(var = c(
                       stringsAsFactors = FALSE)
   
 pred_key$varv <- gsub("_", "v", pred_key$var)
+
+pred_key <- dplyr::filter(pred_key, 
+                          !(tolower(pretty) %in% c("lake depth", "n-fixer", 
+                                                   "non-ag")))
+
 
 # View(pred_key)
 write.csv(pred_key, "data/predictor_key.csv", row.names = FALSE)

### 2019-07-19 figures/07_model-selection.Rmd
presentation edits

@@
 
-```{r tn_re_compare, fig.height=3}
+```{r tn_re_compare, fig.height=3, fig.width=4}
 # compare lakes in signif hu4s
@@
 dt_predictors <- dplyr::filter(dt, key %in% 
-                                 c("tp",
+                                 c(#"tp",
                                    "nitrogen_atmospheric_deposition",

### 2019-07-19 manuscript/appendix.Rmd
presentation edits

@@
        aes(fill=`Trophic State`, values = `value`)) +
-  geom_waffle(color = "white", size=0.7, n_rows = 5, flip = TRUE) +
+  geom_waffle(color = "white", size=0.7, n_rows = 10, flip = TRUE) +
   # facet_wrap(~key, ncol = 1) +

### 2019-07-19 scripts/99_make_predictor_key.R

@@ -38,8 +38,8 @@ pred_key <- data.frame(var = c(
 pred_key$varv <- gsub("_", "v", pred_key$var)
 
 pred_key <- dplyr::filter(pred_key, 
-                          !(tolower(pretty) %in% c("lake depth", "n-fixer", 
-                                                   "non-ag")))
+                          !(pretty %in% c("Lake area", "N-fixer", 
+                                                   "Non-ag")))
 
 
 # View(pred_key)

### 2019-07-22 figures/07_model-selection.Rmd
move labels

@@
   theme(rect = element_rect(fill = "transparent")) +
-  ylab("TP model, Ag RE slope") + xlab("Zone ID") +
+  ggtitle("TP ~ Ag slope") + xlab("Zone ID") + ylab("") +
   theme(legend.position = 0)
@@
   theme(rect = element_rect(fill = "transparent")) +
-  ylab("TN model, corn RE slope") + xlab("Zone ID") + 
+  ggtitle("TN ~ corn slope") + xlab("Zone ID") + ylab("") +
   theme(legend.position = 0)
 
-gg_tn_re
 ```

### 2019-07-22 figures/02_hierarchical_demo.Rmd
towards sorting fixed effect plots

@@
     geom_sf(data = hu4, aes(fill = n_cat, alpha = n)) +
+    coord_sf(datum = NA) +
     # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
@@
   plot_grid(nullGrob(), gg_lines, nullGrob(), 
-            ncol = 1, rel_heights = c(0.33, 1, 0.33)), 
-  gg_hu4)
+            ncol = 1, rel_heights = c(0.53, 1, 0.53)), 
+  gg_hu4, rel_widths = c(0.7, 1))
 ```

### 2019-07-22 figures/07_model-selection.Rmd
towards sorting fixed effect plots

@@
   group_by(pretty) %>%
-  summarize(value = list(tibble::enframe(quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
-  unnest() %>%
+  summarize(value = list(tibble::enframe(
+    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
   tidyr::spread(name, value) %>%
   rowwise() %>%
-  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))
+  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
+  left_join(dplyr::select(pred_key, pretty, category)) %>%
+  arrange(category) %>%
+  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty))
 
-gg_tp_fe <- ggplot(data = gg_tp) + 
+text_colors <- ifelse(gg_tp$signif == 0, "black", "red")
+(gg_tp_fe <- ggplot(data = gg_tp) + 
   geom_pointrange(aes(x = pretty, y = `50%`, 
@@
   theme_cowplot() +
+  theme(axis.text.y = element_text(size = 12, color = text_colors)) +
   ylim(-0.6, 0.4) +
   ylab("Standardized FE slope") + theme(legend.position = 0) + 
-  xlab("") 
+  ggtitle("TP ~ Slope") +
+  xlab(""))
 ```
@@
   ylim(-0.6, 0.4) +
-  ylab("Standardized FE slope") + theme(legend.position = 0) +
+  ylab("Standardized FE slope") + theme(legend.position = 0) + ggtitle("TN ~ Slope") +
   xlab("") 

### 2019-07-22 figures/07_model-selection.Rmd
order rows

@@
   left_join(dplyr::select(pred_key, pretty, category)) %>%
+  mutate(category = factor(category, 
+                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
+                                      "Land-use cover", "Buffer composition", 
+                                      "Lake")))) %>%
   arrange(category) %>%

### 2019-07-23 figures/07_model-selection.Rmd
towards labeling and coloring

--- 2019-07-22 figures/07_model-selection.Rmd
@@
   left_join(dplyr::select(pred_key, pretty, category)) %>%
+  mutate(category = factor(category, 
+                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
+                                      "Land-use cover", "Buffer composition", 
+                                      "Lake")))) %>%
   arrange(category) %>%
-  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty))
+  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
+  arrange(category, pretty)
 
-text_colors <- ifelse(gg_tp$signif == 0, "black", "red")
-(gg_tp_fe <- ggplot(data = gg_tp) + 
+text_colors <- rev(ifelse(gg_tp$signif == 0, "black", "red"))
+# cbind(text_colors, as.character(gg_tp$pretty))
+
+gg_tp_fe <- ggplot(data = gg_tp) + 
   geom_pointrange(aes(x = pretty, y = `50%`, 
                       ymin = `5%`, ymax = `95%`, color = signif)) + 
+  expand_limits(y = -1.2) +
+  geom_rect(ymin = -0.6, ymax = -1.5, xmin = 0, xmax = nrow(gg_tp) + 1, 
+              fill = "white") +
+  geom_text(aes(x = pretty, label = pretty, color = signif), 
+            y = -0.65, vjust = 1.1, hjust = "right") + 
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
     geom_hline(yintercept = 0) +
+  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
+                     labels = scales::format_format(scientific = FALSE)) +
   coord_flip() +
-  theme_cowplot() +
-  theme(axis.text.y = element_text(size = 12, color = text_colors)) +
-  ylim(-0.6, 0.4) +
+  theme(axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        axis.title.y = element_blank()) + 
+    facet_wrap(~category, strip.position = "left", ncol = 1, scales = "free_y",
+               as.table = FALSE) +
+    theme(panel.spacing = unit(0, "lines"), 
+          strip.placement = "outside", 
+          strip.background = element_blank(), 
+          axis.title.y = element_blank()) + 
         ylab("Standardized FE slope") + theme(legend.position = 0) + 
-  ggtitle("TP ~ Slope") +
-  xlab(""))
+        ggtitle("TP ~ Slope") + xlab("")
+
+gp <- ggplotGrob(gg_tp_fe)
+facet.columns <- gp$layout$t[grepl("panel", gp$layout$name)]
+x.var         <- sapply(ggplot_build(gg_tp_fe)$layout$panel_scales_x,
+                function(l) length(l$range$range))
+gp$heights[facet.columns] <- gp$heights[facet.columns] * rev(x.var)
+gg_tp_fe <- ggplotify::as.ggplot(gp)
+gg_tp_fe
 ```

### 2019-07-23 manuscript/appendix.Rmd
horizontal trophic plot

--- 2019-07-19 manuscript/appendix.Rmd
@@
        aes(fill=`Trophic State`, values = `value`)) +
-  geom_waffle(color = "white", size=0.7, n_rows = 5, flip = TRUE) +
+  geom_waffle(color = "white", size=0.7, n_rows = 5, flip = FALSE) +
   # facet_wrap(~key, ncol = 1) +
@@
         legend.key.size = unit(0.5, "line")) + 
-  guides(fill = guide_legend(nrow = 2))
+  guides(fill = guide_legend(nrow = 1))
 

### 2019-07-25 figures/02_hierarchical_demo.Rmd
cleanup

--- 2019-07-03 figures/02_hierarchical_demo.Rmd
@@
     scale_color_manual(values = rep("black", 26))
+
 gg_hu4 <- ggplot() +
     geom_sf(data = hu4, aes(fill = n_cat, alpha = n)) +
+    coord_sf(datum = NA) +
     # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +
@@
           legend.title = element_blank()) +
-    scale_fill_manual(values = rep("black", 5))
+    scale_fill_manual(values = rep("black", 5)) +
+  ggtitle("# of lakes per region")
 
@@
   plot_grid(nullGrob(), gg_lines, nullGrob(), 
-            ncol = 1, rel_heights = c(0.33, 1, 0.33)), 
-  gg_hu4)
+            ncol = 1, rel_heights = c(0.52, 1, 0.51)), 
+  gg_hu4, rel_widths = c(0.7, 1))
 ```

### 2019-07-25 figures/07_model-selection.Rmd
cleanup

--- 2019-07-22 figures/07_model-selection.Rmd
@@
   left_join(dplyr::select(pred_key, pretty, category)) %>%
+  mutate(category = factor(category, 
+                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
+                                      "Land-use cover", "Buffer composition", 
+                                      "Lake")))) %>%
+  mutate(category = forcats::fct_recode(category, 
+                                        Buffer = "Buffer composition")) %>%
   arrange(category) %>%
-  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty))
+  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
+  arrange(category, pretty)
 
-text_colors <- ifelse(gg_tp$signif == 0, "black", "red")
-(gg_tp_fe <- ggplot(data = gg_tp) + 
+gg_tp_fe <- ggplot(data = gg_tp) + 
   geom_pointrange(aes(x = pretty, y = `50%`, 
                       ymin = `5%`, ymax = `95%`, color = signif)) + 
+  expand_limits(y = -1.8) +
+  geom_rect(ymin = -0.6, ymax = -0.6 - 2, xmin = 0, xmax = nrow(gg_tp) + 1, 
+              fill = "transparent") +
+  geom_text(aes(x = pretty, label = pretty, color = signif), 
+            y = -0.65, vjust = 0.5, hjust = "right") + 
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
     geom_hline(yintercept = 0) +
+  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
+                     labels = scales::number_format(accuracy = 0.1)) +
   coord_flip() +
-  theme_cowplot() +
-  theme(axis.text.y = element_text(size = 12, color = text_colors)) +
-  ylim(-0.6, 0.4) +
-  ylab("Standardized FE slope") + theme(legend.position = 0) + 
-  ggtitle("TP ~ Slope") +
-  xlab(""))
+  theme(axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        axis.title.y = element_blank()) + 
+    facet_wrap(~category, strip.position = "left", ncol = 1, scales = "free_y",
+               as.table = FALSE) +
+    theme(panel.spacing = unit(0, "lines"), 
+          strip.placement = "outside", 
+          strip.background = element_blank(), 
+          axis.title.y = element_blank()) + 
+        ylab("Standardized slope") + theme(legend.position = 0) + 
+        ggtitle("TP") + xlab("") +
+  theme(panel.background = element_rect(fill = "transparent", color = NA),
+        plot.background = element_rect(fill = "transparent", color = NA), 
+        panel.grid = element_blank(),
+        rect = element_rect(fill = "transparent")) + 
+    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
+             colour="black", lwd=0.9, geom="segment")
+
+gp <- ggplotGrob(gg_tp_fe)
+facet.columns <- gp$layout$t[grepl("panel", gp$layout$name)]
+x.var         <- sapply(ggplot_build(gg_tp_fe)$layout$panel_scales_x,
+                function(l) length(l$range$range))
+gp$heights[facet.columns] <- gp$heights[facet.columns] * rev(x.var)
+gg_tp_fe <- ggplotify::as.ggplot(gp)
+gg_tp_fe
 ```
@@
   summarize(value = list(tibble::enframe(
-    quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
-  unnest() %>%
+    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
   tidyr::spread(name, value) %>%
   rowwise() %>%
-  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))
+  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
+  left_join(dplyr::select(pred_key, pretty, category)) %>%
+  mutate(category = factor(category, 
+                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
+                                      "Land-use cover", "Buffer composition", 
+                                      "Lake")))) %>%
+  mutate(category = forcats::fct_recode(category, 
+                                        Buffer = "Buffer composition")) %>%
+  arrange(category) %>%
+  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
+  arrange(category, pretty)
 
-gg_tn_fe <- ggplot(data = gg_tn) + 
+gg_tn_fe <- 
+  ggplot(data = gg_tn) + 
   geom_pointrange(aes(x = pretty, y = `50%`, 
                       ymin = `5%`, ymax = `95%`, color = signif)) + 
+  expand_limits(y = c(-0.6, 1.6)) +
+  geom_rect(ymin = 0.44, ymax = 0.44 + 2, xmin = 0, xmax = nrow(gg_tn) + 1, 
+              fill = "transparent") +
+  geom_text(aes(x = pretty, label = pretty, color = signif), 
+            y = 0.44, vjust = 0.5, hjust = "left") + 
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
     geom_hline(yintercept = 0) +
+  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
+                     labels = scales::number_format(accuracy = 0.1)) +
   coord_flip() +
-  theme_cowplot() +
-  ylim(-0.6, 0.4) +
-  ylab("Standardized FE slope") + theme(legend.position = 0) + ggtitle("TN ~ Slope") +
-  xlab("") 
+  theme(axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        axis.title.y = element_blank()) + 
+    facet_wrap(~category, strip.position = "right", ncol = 1, scales = "free_y",
+               as.table = FALSE) +
+    theme(panel.spacing = unit(0, "lines"), 
+          strip.placement = "outside", 
+          strip.background = element_blank(), 
+          axis.title.y = element_blank()) + 
+        ylab("Standardized slope") + theme(legend.position = 0) + 
+        ggtitle("TN") + xlab("") +
+  theme(panel.background = element_rect(fill = "transparent"), 
+        panel.grid = element_blank(),
+        rect = element_rect(fill = "transparent")) + 
+    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
+             colour="black", lwd=0.9, geom="segment")
+
+gp <- ggplotGrob(gg_tn_fe)
+facet.columns <- gp$layout$t[grepl("panel", gp$layout$name)]
+x.var         <- sapply(ggplot_build(gg_tn_fe)$layout$panel_scales_x,
+                function(l) length(l$range$range))
+gp$heights[facet.columns] <- gp$heights[facet.columns] * rev(x.var)
+gg_tn_fe <- ggplotify::as.ggplot(gp)
+gg_tn_fe
 ```
 
-```{r tn_re_hu4}
+```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
 
@@
     # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
+    coord_sf(datum = NA) +
     theme_minimal() + 
@@
                                     axis.title.x = element_blank()), 
-                   rel_widths = c(1, 0.6))
+                   rel_widths = c(1, 1))
 ```

### 2019-07-25 manuscript/appendix.Rmd
cleanup

--- 2019-07-19 manuscript/appendix.Rmd
@@
 
-```{r trophic_state, fig.cap="Lake trophic state", fig.width = 6, fig.height = 3.2, warning=FALSE, message=FALSE}
+```{r trophic_state, fig.cap="Lake trophic state", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
 # waffle
 library(waffle)
-library(hrbrthemes)
 
-dt_waffle <- tidyr::gather(dt, key = "key", value = "value", -`Trophic State`) %>%
-  add_row(`Trophic State` = "oligotrophic", `key` = "All Lakes", `value` = 2) %>%
-  add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%
-  arrange(`Trophic State`) %>%
-  dplyr::filter(key == "This Study")
+total_cells <- 41.5
+dt_waffle <- dt %>% 
+  dplyr::rename(trophic_state = `Trophic State`) %>%
+  tidyr::gather(key = "key", value = "value", -trophic_state) %>%
+  dplyr::filter(key == "This Study") %>%
+  mutate(value = floor((value / 100) * total_cells)) %>%
+  arrange(trophic_state)
+# sum(dt_waffle$value)
+# add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%
 
 ggplot(dt_waffle,
-       aes(fill=`Trophic State`, values = `value`)) +
-  geom_waffle(color = "white", size=0.7, n_rows = 5, flip = TRUE) +
+       aes(fill = trophic_state, values = value)) +
+  geom_waffle(color = "white", size = 3, n_rows = 4, flip = FALSE) +
   # facet_wrap(~key, ncol = 1) +

### 2019-07-26 figures/09_stream_buffer.Rmd
figure cleanup

--- 2019-06-23 figures/09_stream_buffer.Rmd
@@
 llids         <- c("6992", "7026")
+lg            <- lagosne_load("1.087.1")
+llid_metadata <- lake_info(llids, dt = lg)
+llid_callouts <- paste(llid_metadata$gnis_name, "-", llid_metadata$state)
 
@@
 
+### draw forest outlines
+# i <- 2
+# forest_outline <- mapedit::editMap(
+#   mapview(images[[i]])
+#   )
+# forest_outline <- smoothr::smooth(forest_outline$drawn)
+# forest_outline <- st_intersection(
+#   st_transform(forest_outline, st_crs(res_iws[i,])),
+#   res_iws[i,])
+# mapview(forest_outline)
+# saveRDS(forest_outline, "../data/res_forest_outline_2.rds")
+# forest_outline_1 <- readRDS("../data/res_forest_outline_1.rds")
+# forest_outline_2 <- readRDS("../data/res_forest_outline_2.rds")
+
 i <- 1
+rs <- prep_ggplot_raster(images[[i]], res_iws[i,])
 gg_low_ag <- ggplot() + 
-  geom_raster(data = prep_ggplot_raster(images[[i]], res_iws[i,]), 
+  geom_raster(data = rs, 
               aes(x, y, fill = I(hex))) +
   geom_sf(data = res_iws[i,], alpha = 0, color = "red") +
-  geom_sf(data = res_streams[[i]], color = "cyan") +
+  geom_sf(data = res_lakes[i,], alpha = 0, color = "cyan") +
+  # geom_sf(data = forest_outline_1, color = "green3") +
+  geom_sf(data = st_difference(
+      st_transform(res_streams[[i]], st_crs(res_lakes[i,])), 
+      res_lakes[i,]), 
+    color = "cyan") +
   coord_sf(datum = NA) +
   theme_void() +
-  ggtitle(llids[i])
+  annotate("text", label = llid_callouts[i], x = median(rs$x), 
+           y = min(rs$y))
 
 i <- 2
+rs <- prep_ggplot_raster(images[[i]], res_iws[i,])
 gg_hi_ag <- ggplot() + 
-  geom_raster(data = prep_ggplot_raster(images[[i]], res_iws[i,]), 
+  geom_raster(data = rs, 
               aes(x, y, fill = I(hex))) +
   geom_sf(data = res_iws[i,], alpha = 0, color = "red") +
-  geom_sf(data = res_streams[[i]], color = "cyan") +
+  geom_sf(data = res_lakes[i,], alpha = 0, color = "cyan") +
+  # geom_sf(data = forest_outline_2, color = "green3") +
+  geom_sf(data = st_difference(
+      st_transform(res_streams[[i]], st_crs(res_lakes[i,])), 
+      res_lakes[i,]), 
+    color = "cyan") +
   coord_sf(datum = NA) +
   theme_void() +
-  ggtitle(llids[i])
+  annotate("text", label = llid_callouts[i], x = median(rs$x), 
+           y = min(rs$y))
 

### 2019-07-29 figures/02_hierarchical_demo.Rmd
towards consistent cartography

@@
 # setwd("figures")
-ids <- readRDS("../data/dt.rds") %>%
+cl            <- cart_layers()
+ep            <- cl$ep
+states        <- cl$states
+study_bbox    <- cl$study_bbox
+
+dt            <- readRDS("../data/dt.rds")
+
+ids <- dt %>%
   group_by(hu4_zoneid) %>% 
@@
 lg <- lagosne_load("1.087.1")
-
 ep <- left_join(dplyr::select(lg$locus, lagoslakeid, hu4_zoneid), 
@@
     scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 150)) + 
-    scale_color_manual(values = rep("black", 26))
+    scale_color_manual(values = rep("#a50f15", 26))
 
-gg_hu4 <- ggplot() +
-    geom_sf(data = hu4, aes(fill = n_cat, alpha = n)) +
+gg_hu4 <- 
+  ggplot() +
+    geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
+              color = "black", fill = "#1D9DCF") +
+    geom_sf(data = states, fill = "gray", color = "black", size = 0.3) +
+    geom_sf(data = hu4, aes(fill = n_cat), color = "black", size = 0.4) +
+  scale_fill_manual(values = c("#fee5d9", "#fcae91", "#fb6a4a", "#de2d26", "#a50f15")) +
     coord_sf(datum = NA) +
@@
           legend.title = element_blank()) +
-    scale_fill_manual(values = rep("black", 5)) +
   ggtitle("# of lakes per region")

### 2019-07-29 figures/07_model-selection.Rmd
figure cleanup
towards consistent cartography

@@
 ```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
+cl            <- cart_layers()
+states        <- cl$states
+study_bbox    <- cl$study_bbox
 
 # map significant random effects hu4s
-gg_hu4 <- ggplot() +
-    geom_sf(data = hu4) +
+gg_hu4 <- 
+  ggplot() +
+    geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
+              color = "black", fill = "#1D9DCF") +
+    geom_sf(data = states, fill = "gray", color = "black", size = 0.3) +
+    geom_sf(data = hu4, fill = "white", color = "black", size = 0.4) +
     geom_sf(data = signif_hu4, color = "red", alpha = 0) +
@@
 }
-lg <- lagosne_load()
+lg <- lagosne_load("1.087.1")
 fit <- get_residuals(fit)

### 2019-07-29 scripts/99_utils.R

@@ -38,6 +38,7 @@ library(snakecase)
 suppressMessages(library(brms))
 suppressMessages(library(tidybayes))
 library(ggforce)
+library(rnaturalearth)
 
 theme_opts <- theme(axis.text = element_blank(),
                     axis.ticks = element_blank(),
@@ -286,3 +287,20 @@ get_if_not_exists <- function(x, destfile, read_function = readRDS,
   }
 }
 
+cart_layers <- function(){
+  lg            <- lagosne_load("1.087.1")
+  ep            <- LAGOSNE::coordinatize(readRDS("../data/ep.rds")) %>%
+    left_join(dplyr::select(lg$locus, "lagoslakeid", "state_zoneid")) %>%
+    left_join(lg$state)
+  
+  states        <- ne_states(country = c("united states of america", "canada", "mexico"), 
+                             returnclass = "sf")
+  states_shaded <- states[states$name %in% unique(ep$state_name),]
+  study_bbox    <- st_as_sfc(st_bbox(states_shaded))
+  states        <- st_crop(states, study_bbox)
+  
+  list(ep = ep, 
+       states = states, 
+       states_shaded = states_shaded,
+       study_bbox = study_bbox)
+}

### 2019-07-29 figures/02_hierarchical_demo.Rmd
cartography and panel arragement

@@
 # setwd("figures")
-cl            <- cart_layers()
-ep            <- cl$ep
-states        <- cl$states
-study_bbox    <- cl$study_bbox
+# cl            <- cart_layers()
+# ep            <- cl$ep
+# states        <- cl$states
+# study_bbox    <- cl$study_bbox
+
+study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
+ep            <- st_read("../data/gis.gpkg", "ep", quiet = TRUE)
+states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
+hu4           <- st_read("../data/gis.gpkg", "hu4s", quiet = TRUE)
 
 dt            <- readRDS("../data/dt.rds")
-
 ids           <- dt %>%
@@
 
-hu4 <-  LAGOSNEgis::query_gis("HU4", "ZoneID", ids$hu4_zoneid) %>%
-  st_cast(to = "MULTIPOLYGON") %>%
+hu4    <-  hu4 %>%
+  # st_cast(to = "MULTIPOLYGON") %>%
   left_join(ids, by = c("ZoneID" = "hu4_zoneid"))
-
 n_cat  <- 6
@@
               color = "black", fill = "#1D9DCF") +
-    geom_sf(data = states, fill = "gray", color = "black", size = 0.3) +
+    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
     geom_sf(data = hu4, aes(fill = n_cat), color = "black", size = 0.4) +
@@
 
-cowplot::plot_grid(
+cowplot::plot_grid(gg_hu4,
   plot_grid(nullGrob(), gg_lines, nullGrob(), 
             ncol = 1, rel_heights = c(0.52, 1, 0.51)), 
-  gg_hu4, rel_widths = c(0.7, 1))
+  rel_widths = c(1, 0.7))
 ```

### 2019-07-29 figures/07_model-selection.Rmd
cartography and panel arragement

@@
 ```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
-cl            <- cart_layers()
-states        <- cl$states
-study_bbox    <- cl$study_bbox
+study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
+states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
 
@@
               color = "black", fill = "#1D9DCF") +
-    geom_sf(data = states, fill = "gray", color = "black", size = 0.3) +
+    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
     geom_sf(data = hu4, fill = "white", color = "black", size = 0.4) +
@@
     scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
-    guides(guide_legend(nrow = 2))
+    guides(guide_legend(nrow = 2))  +
+  ggtitle("Ag sensitive regions")
 

### 2019-07-29 scripts/00_get_gis.R

@@ -9,19 +9,24 @@ knitr::opts_chunk$set(eval = FALSE)
 source("scripts/99_utils.R")
 
 # ---- size_comparison ----
-lg   <- lagosne_load()
-gpkg_path <- "data/gis.gpkg"
+lg         <- lagosne_load("1.087.1")
+gpkg_path  <- "data/gis.gpkg"
 
-ep  <- readRDS("data/ep.rds") %>%
+ep         <- readRDS("data/ep.rds") %>%
   st_as_sf(coords = c("nhd_long", "nhd_lat"), crs = 4326)
 
-iws  <- LAGOSNEgis::query_gis("IWS", "lagoslakeid", ep$lagoslakeid)
+iws        <- LAGOSNEgis::query_gis("IWS", "lagoslakeid", ep$lagoslakeid)
 
+states_all <- ne_states(country = c("united states of america", "canada", "mexico"),
+                        returnclass = "sf")
 state_codes <- c("IL", "IN", "IA",
                  "MI", "MN", "MO",
                  "NY", "OH", "PA", "WI")
-states <- state_sf() %>%
-  dplyr::filter(., ABB %in% state_codes)
+states_focal <- states_all %>%
+  dplyr::filter(., postal %in% state_codes & iso_a2 == "US")
+study_bbox   <- st_as_sfc(st_bbox(states_focal))
+states_all   <- states_all %>%
+  st_crop(study_bbox)
 
 counties <- dplyr::filter(county_sf(), state_abb %in% state_codes)
 cnty_lg <- lg$county %>%
@@ -30,11 +35,11 @@ cnty_lg <- lg$county %>%
   mutate(county_name = gsub("\\.", "", gsub(" ", "", county_name))) %>%
   mutate(county_name = gsub("'", "", gsub("saint", "st", county_name))) %>%
   mutate(state_name = tolower(state_name)) %>%
-  select(state_zoneid, state_name, county_name, county_state, county_zoneid) %>%
+  dplyr::select(state_zoneid, state_name, county_name, county_state, county_zoneid) %>%
   # dplyr::filter(cnty_lg, str_detect(county_name, "brien"))
   left_join(st_drop_geometry(counties), .,
             by = c("state" = "state_name", "county" = "county_name")) %>%
-  select(state_abb, county, county_zoneid)
+  dplyr::select(state_abb, county, county_zoneid)
[…]

### 2019-07-29 scripts/99_utils.R

@@ -286,21 +286,3 @@ get_if_not_exists <- function(x, destfile, read_function = readRDS,
     invisible(x)
   }
 }
-
-cart_layers <- function(){
-  lg            <- lagosne_load("1.087.1")
-  ep            <- LAGOSNE::coordinatize(readRDS("../data/ep.rds")) %>%
-    left_join(dplyr::select(lg$locus, "lagoslakeid", "state_zoneid")) %>%
-    left_join(lg$state)
-  
-  states        <- ne_states(country = c("united states of america", "canada", "mexico"), 
-                             returnclass = "sf")
-  states_shaded <- states[states$name %in% unique(ep$state_name),]
-  study_bbox    <- st_as_sfc(st_bbox(states_shaded))
-  states        <- st_crop(states, study_bbox)
-  
-  list(ep = ep, 
-       states = states, 
-       states_shaded = states_shaded,
-       study_bbox = study_bbox)
-}

### 2019-07-29 figures/07_model-selection.Rmd
highlight re

@@
 
-gg_tp_fe <- ggplot(data = gg_tp) + 
+gg_tp_fe <- 
+  ggplot(data = gg_tp) + 
   geom_pointrange(aes(x = pretty, y = `50%`, 
@@
              colour="black", lwd=0.9, geom="segment") 
-
-gp <- ggplotGrob(gg_tp_fe)
-facet.columns <- gp$layout$t[grepl("panel", gp$layout$name)]
-x.var         <- sapply(ggplot_build(gg_tp_fe)$layout$panel_scales_x,
-                function(l) length(l$range$range))
-gp$heights[facet.columns] <- gp$heights[facet.columns] * rev(x.var)
-gg_tp_fe <- ggplotify::as.ggplot(gp)
-gg_tp_fe
 ```
@@
 
-gp <- ggplotGrob(gg_tn_fe)
+equalize_panels <- function(x){
+  gp <- ggplotGrob(x)
   facet.columns <- gp$layout$t[grepl("panel", gp$layout$name)]
-x.var         <- sapply(ggplot_build(gg_tn_fe)$layout$panel_scales_x,
+  x.var         <- sapply(ggplot_build(x)$layout$panel_scales_x,
                   function(l) length(l$range$range))
   gp$heights[facet.columns] <- gp$heights[facet.columns] * rev(x.var)
-gg_tn_fe <- ggplotify::as.ggplot(gp)
-gg_tn_fe
+  x <- ggplotify::as.ggplot(gp)
+  x
+}
 ```
@@
 gg_tn_re <- ggplot(data = fit_tn$re) +
+  geom_hline(yintercept = as.numeric(fit_tn$re_global["50%"])) +
   geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
@@
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  geom_hline(yintercept = as.numeric(fit_tn$re_global["50%"])) +
   coord_flip() +
@@
 
+```
+
+```{r fe}
+cowplot::plot_grid(
+  equalize_panels(
+    gg_tp_fe + theme(axis.title.x = element_blank())
+  ), 
+  equalize_panels(
+    gg_tn_fe + 
+      theme(axis.text.y = element_blank(), 
+            axis.title.x = element_blank())), 
+  rel_widths = c(1, 1))
 ```
@@
 
-```{r fe}
-cowplot::plot_grid(gg_tp_fe + theme(axis.title.x = element_blank()), 
-                   gg_tn_fe + theme(axis.text.y = element_blank(), 
-                                    axis.title.x = element_blank()), 
-                   rel_widths = c(1, 1))
-```
-
 ```{r re}
@@
                                     axis.title.y = element_blank()), 
+                   rel_widths = c(1, 0.9))
+
+cowplot::plot_grid(gg_tp_re, 
+                   gg_tn_re + 
+                     theme(axis.text.y = element_blank(), 
+                           axis.title.y = element_blank()) + 
+                     gghighlight(max(`50%`), n = 1), 
                    rel_widths = c(1, 0.9))

### 2019-07-29 scripts/99_utils.R

@@ -39,6 +39,7 @@ suppressMessages(library(brms))
 suppressMessages(library(tidybayes))
 library(ggforce)
 library(rnaturalearth)
+library(gghighlight)
 
 theme_opts <- theme(axis.text = element_blank(),
                     axis.ticks = element_blank(),

### 2019-08-05 figures/07_model-selection.Rmd
composition to configuration

@@
                            levels = rev(c("Nutrient inputs", "Nutrient transport", 
-                                      "Land-use cover", "Buffer composition", 
+                                      "Land-use cover", "Buffer configuration", 
                                       "Lake")))) %>%
   mutate(category = forcats::fct_recode(category, 
-                                        Buffer = "Buffer composition")) %>%
+                                        Buffer = "Buffer configuration")) %>%
   arrange(category) %>%

### 2019-08-05 figures/08_exploratory_dotplot.Rmd
composition to configuration

@@
                                                "Land-use cover",
-                                               "Buffer composition", 
+                                               "Buffer configuration", 
                                                "Lake"))) %>%

### 2019-08-05 scripts/99_make_predictor_key.R

@@ -25,8 +25,8 @@ pred_key <- data.frame(var = c(
                       category = c(
   "Nutrient inputs", "Lake", "Lake", 
   "Nutrient transport", "Nutrient transport", 
-  "Buffer composition","Land-use cover","Land-use cover", "Land-use cover",
-  "Buffer composition", "Buffer composition",
+  "Buffer configuration","Land-use cover","Land-use cover", "Land-use cover",
+  "Buffer configuration", "Buffer configuration",
   "Land-use cover", "Land-use cover", "Nutrient transport","Lake",
   "Nutrient transport", "Land-use cover","Nutrient inputs", 
   "Nutrient transport", "Land-use cover", "Nutrient inputs",

### 2019-08-05 figures/07_model-selection.Rmd
towards viz of global re

@@
                    rel_widths = c(1, 0.9))
+```
+
+```{r re-comparison}
+
+# tp, tn
+# ag, row_crop, pasture, corn, soybeans
+re_global <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
+re_global$term <- unlist(lapply(re_brms, 
+                                function(x) get_re_text(as.character(x$formula)[1])))
+re_global$response <- c(rep("tp", 5), rep("tn", 5))
+re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
+
+loo_compare(
+  loo(re_brms[[1]]), 
+  loo(re_brms[[2]]), 
+  loo(re_brms[[3]]), 
+  loo(re_brms[[4]]), 
+  loo(re_brms[[5]]) 
+)
+
+loo_compare(
+  loo(re_brms[[6]]), 
+  loo(re_brms[[7]]), 
+  loo(re_brms[[8]]), 
+  loo(re_brms[[9]]), 
+  loo(re_brms[[10]]) 
+)
+
+group_by(re_global, response) %>%
+  arrange(desc(`50%`))
+
+ggplot(data = re_global) +
+  geom_pointrange()
+
 ```

### 2019-08-05 scripts/99_utils.R

@@ -287,3 +287,10 @@ get_if_not_exists <- function(x, destfile, read_function = readRDS,
     invisible(x)
   }
 }
+
+get_re_text <- function(x){
+  # x <- "maxdepth + hu12vbaseflowvmean + phosphorusvfertilizervuse + buffervcultivatedvcrops + (1 + ag | hu4vzoneid)"
+  res <- strsplit(x, "\\|")[[1]][1]
+  res <- strsplit(res, " ")[[1]]
+  res[length(res)]
+}

### 2019-08-05 figures/07_model-selection.Rmd
viz global re coefs

--- 2019-08-05 figures/07_model-selection.Rmd
@@
                    rel_widths = c(1, 0.9))
+```
+
+```{r re-comparison}
+# tp, tn
+# ag, row_crop, pasture, corn, soybeans
+re_global <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
+re_global$term <- unlist(lapply(re_brms, 
+                                function(x) get_re_text(as.character(x$formula)[1])))
+re_global$response <- c(rep("tp", 5), rep("tn", 5))
+re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
+
+# loo_compare(loo(re_brms[[1]]), loo(re_brms[[2]]), loo(re_brms[[3]]),
+#             loo(re_brms[[4]]), loo(re_brms[[5]]))
+# loo_compare(loo(re_brms[[6]]), loo(re_brms[[7]]), loo(re_brms[[8]]), 
+#             loo(re_brms[[9]]), loo(re_brms[[10]]))
+
+group_by(re_global, response) %>%
+  arrange(desc(`50%`))
+
+gg_tn <- ggplot(data = dplyr::filter(re_global, response == "tn")) +
+    geom_pointrange(aes(x = term, y = `50%`, 
+                      ymin = `5%`, ymax = `95%`), color = "red") +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  expand_limits(y = -0.2) +
+  coord_flip() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        strip.placement = "outside", 
+        strip.background = element_blank(), 
+        panel.background = element_rect(fill = "transparent", color = NA),
+        plot.background = element_rect(fill = "transparent", color = NA), 
+        panel.grid = element_blank(),
+        rect = element_rect(fill = "transparent"), 
+        axis.line = element_line(), 
+        axis.text.y = element_blank()) +
+  ggtitle("TN")
+
+gg_tp <- ggplot(data = dplyr::filter(re_global, response == "tp")) +
+    geom_pointrange(aes(x = term, y = `50%`, 
+                      ymin = `5%`, ymax = `95%`), color = "red") +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  expand_limits(y = -0.2) +
+  coord_flip() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        strip.placement = "outside", 
+        strip.background = element_blank(), 
+        panel.background = element_rect(fill = "transparent", color = NA),
+        plot.background = element_rect(fill = "transparent", color = NA), 
+        panel.grid = element_blank(),
+        rect = element_rect(fill = "transparent"), 
+        axis.line = element_line()) +
+  ggtitle("TP")
+
+cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.8))
 ```

### 2019-08-05 tables/03_model_summary.Rmd
towards a re results table

@@
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
+# setwd("../")
+source("scripts/99_utils.R")
 ```
@@
 # setwd("tables")
-dt <- read.csv("../data/mcmc/model_r2.csv", 
-                     stringsAsFactors = FALSE)
+re_brms <- readRDS("data/mcmc/re_brms.rds")
+
+r2_re <- dplyr::bind_rows(
+  lapply(re_brms, function(x) data.frame(brms::bayes_R2(x))))
+r2_re$term <- unlist(lapply(re_brms, 
+                                function(x) get_re_text(as.character(x$formula)[1])))
+r2_re$response <- c(rep("tp", 5), rep("tn", 5))
+r2_re <- dplyr::filter(r2_re, term != "rowvcropvpct")
+
+sort_loo <- function(x){
+  x_df       <- as.data.frame(x)
+  x_df$index <- row.names(x_df)
+  x_df$index <- stringr::str_extract(x_df$index, "\\d+")
+  arrange(x_df, index)
+}
+
+loo_re <- rbind(
+  sort_loo(loo_compare(loo(re_brms[[1]]),
+                       loo(re_brms[[3]]), loo(re_brms[[4]]),
+                       loo(re_brms[[5]]))),
+  sort_loo(loo_compare(loo(re_brms[[6]]),
+                       loo(re_brms[[8]]), loo(re_brms[[9]]),
+                       loo(re_brms[[10]])))
+  ) %>%
+  arrange(index)
+
+dt           <- r2_re
+dt$elpd_diff <- loo_re$elpd_diff
+dt <- dplyr::select(dt, 
+                    response, term, r2 = Estimate, elpd_diff)
+test <- dt[order(dt$response, dt$elpd_diff, decreasing = TRUE),]
 

### 2019-08-05 tables/03_model_summary.Rmd
build global re results table

@@
                     response, term, r2 = Estimate, elpd_diff)
-test <- dt[order(dt$response, dt$elpd_diff, decreasing = TRUE),]
+dt <- dt[order(dt$response, dt$elpd_diff, decreasing = FALSE),]
 
 options(knitr.kable.NA = "-")  
-dplyr::filter(dt, str_detect(Model, "tp")) %>%
-  dplyr::select(-Model) %>%
-  dplyr::rename("$R^2$" = Estimate) %>%
+dplyr::filter(dt, str_detect(response, "tp")) %>%
+  dplyr::select(-response) %>%
+  dplyr::rename("$R^2$" = r2) %>%
   knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2")
@@
 ```{r tn_results}
-dplyr::filter(dt, str_detect(Model, "tn")) %>%
-  dplyr::select(-Model) %>%
-  dplyr::rename("$R^2$" = Estimate) %>%
+dplyr::filter(dt, str_detect(response, "tn")) %>%
+  dplyr::select(-response) %>%
+  dplyr::rename("$R^2$" = r2) %>%
   knitr::kable(digits = 2, format = "markdown", caption = "TN Model R2")

### 2019-08-06 figures/07_model-selection.Rmd
towards a re results table
organize figs for ms

@@
 # lapply(re_brms, function(x) x$formula) 
-fit_tn         <- re_brms[[5]] # 5 is best tn model with random effects
+fit_tn         <- re_brms[[9]] # 5 is best tn model with random effects
 signif_hu4_ids <- fit_tn$re_signif_ids 
@@
 
-```{r re-comparison}
+```{r re-comparison, fig.width=4}
 # tp, tn
@@
 re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
-
-# loo_compare(loo(re_brms[[1]]), loo(re_brms[[2]]), loo(re_brms[[3]]),
-#             loo(re_brms[[4]]), loo(re_brms[[5]]))
-# loo_compare(loo(re_brms[[6]]), loo(re_brms[[7]]), loo(re_brms[[8]]), 
-#             loo(re_brms[[9]]), loo(re_brms[[10]]))
 

### 2019-08-06 manuscript/appendix.Rmd
organize figs for ms

@@
 ```
+
+```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE, eval=FALSE}
+knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
+```
+
+```{r hierarchical_demo, fig.cap = "A) Global (dashed line) and regional (solid lines) fits to the relationship between lake phosphorus and IWS Ag.
+land use cover from the 2011 NLCD.
+A hierarchical model would weight these relationships by sample size (darker lines = higher sample size).
+B) Number of lakes per region.", warning=FALSE, echo = FALSE, eval=FALSE}
+knitr::include_graphics("../figures/02_hierarchical_demo-1.pdf")
+```
+
+```{r wetland_potential, fig.cap = "A) gSSURGO wetland potential versus National Wetlands Inventory cover.
+B) Locations of lakes where these number differ by more than 30 percent.", warning=FALSE, echo = FALSE, eval=FALSE}
+knitr::include_graphics("../figures/03_wetland_potential-1.pdf")
+```
+
+```{r cafos, fig.cap = "Livestock data from the 2007 USDA Census of Agriculture.", warning=FALSE, echo = FALSE, eval=FALSE, eval=FALSE}
+knitr::include_graphics("../figures/05_cafos-1.pdf")
+```
+
+```{r lulc_buffers, fig.cap = "Landuse cover in stream buffers.", warning=FALSE, echo = FALSE, eval=FALSE}
+knitr::include_graphics("../figures/06_lulc_buffer_demo-1.pdf")
+```
+
+```{r cdl_viewport, fig.cap = "CDL landuse cover in example IWS.", warning=FALSE, echo = FALSE, eval=TRUE}
+knitr::include_graphics("../figures/cdl_viewport-1.pdf")
+```
+
+```{r county_extent, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (greater than 40 percent) and water quality data in LAGOS from at least 3 sampling events between 2000 and 2010.", warning=FALSE, echo = FALSE, eval = FALSE}
+knitr::include_graphics("../figures/01_county_extent-1.pdf")
+```
+
+```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE, eval=FALSE}
+knitr::include_graphics("../figures/tptn_maps-1.pdf")
+```
+
+```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.
+Line is 1:1 not regression.", warning=FALSE, echo = FALSE, eval=FALSE}
+knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
+```
+
+```{r nlcd-versus-cdl_map, fig.cap = "Comparison between NLCD (2011) ag and pasture against CDL (2010) specific crops.", warning=FALSE, echo = FALSE, eval = FALSE}
+knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
+```
+
+```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE, eval=FALSE}
+knitr::include_graphics("../figures/09_stream_buffer-1.pdf")
+```
+
+```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE, eval=FALSE}
+knitr::include_graphics("../figures/satellite-1.pdf")
+```

### 2019-08-06 manuscript/figures.Rmd
organize figs for ms

@@
 
-```{r county_extent, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (greater than 40 percent) and water quality data in LAGOS from at least 3 sampling events between 2000 and 2010.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/01_county_extent-1.pdf")
-```
-
-```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/tptn_maps-1.pdf")
-```
+\pagebreak
 
@@
 knitr::include_graphics("../figures/11_map-1.pdf")
-```
-
-```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.
-Line is 1:1 not regression.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
-```
-
-```{r nlcd-versus-cdl_map, fig.cap = "Comparison between NLCD (2011) ag and pasture against CDL (2010) specific crops.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
-```
-
-```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/09_stream_buffer-1.pdf")
-```
-
-```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/satellite-1.pdf")
 ```
@@
 
-```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
+```{r fe-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/fe-1.pdf")
 ```
 
-```{r hierarchical_demo, fig.cap = "A) Global (dashed line) and regional (solid lines) fits to the relationship between lake phosphorus and IWS Ag.
-land use cover from the 2011 NLCD.
-A hierarchical model would weight these relationships by sample size (darker lines = higher sample size).
-B) Number of lakes per region.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/02_hierarchical_demo-1.pdf")
+```{r re-comparison-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/re-comparison-1.pdf")
 ```
 
-```{r wetland_potential, fig.cap = "A) gSSURGO wetland potential versus National Wetlands Inventory cover.
-B) Locations of lakes where these number differ by more than 30 percent.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/03_wetland_potential-1.pdf")
+```{r re-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/re-1.pdf")
 ```
 
-```{r cafos, fig.cap = "Livestock data from the 2007 USDA Census of Agriculture.", warning=FALSE, echo = FALSE, eval=FALSE}
-knitr::include_graphics("../figures/05_cafos-1.pdf")
+```{r tn_re_hu4-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/tn_re_hu4-1.pdf")
 ```
 
-```{r lulc_buffers, fig.cap = "Landuse cover in stream buffers.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/06_lulc_buffer_demo-1.pdf")
+```{r tn_re_compare-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/tn_re_compare-1.pdf")
 ```
-
-```{r cdl_viewport, fig.cap = "CDL landuse cover in example IWS.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/cdl_viewport-1.pdf")
-```

### 2019-08-06 figures/07_model-selection.Rmd
align panel titles

@@
         panel.grid = element_blank(),
-        rect = element_rect(fill = "transparent")) + 
+        rect = element_rect(fill = "transparent"), 
+        plot.title = element_text(hjust = 0.5, face = "bold")) + 
     annotate(x=0, xend=0, y=-0.6, yend=0.4, 
@@
   ggtitle("TP ~ Ag slope") + xlab("Zone ID") + ylab("") +
+  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
   theme(legend.position = 0)
@@
   ggtitle("TN ~ corn slope") + xlab("Zone ID") + ylab("") +
+  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
   theme(legend.position = 0)
@@
 
-group_by(re_global, response) %>%
-  arrange(desc(`50%`))
+# group_by(re_global, response) %>%
+#   arrange(desc(`50%`))
 
@@
         axis.text.y = element_blank()) +
-  ggtitle("TN")
+  ggtitle("TN") + 
+  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
 
@@
         axis.line = element_line()) +
-  ggtitle("TP")
+  ggtitle("TP") + 
+  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
 
-cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.8))
+cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.75))
 ```

### 2019-08-07 manuscript/figures.Rmd
add real captions

@@
 
-```{r maps2, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE}
+```{r maps2, fig.cap = "Map of lake locations and hydrologic (HUC) regions.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/11_map-1.pdf")
@@
 
-```{r exploratory_dotplot, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
+```{r exploratory_dotplot, fig.cap = "Dotplots showing absolute value Pearson's correlation coefficients. Dots are colored according to predictor categories.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/dotplot-1.pdf")
@@
 
-```{r fe-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
+```{r fe-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals.
+Values that do not overlap zero are shaded in red.
+Horizontal bars separate coefficients in distinct predictor categories.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/fe-1.pdf")
@@
 
-```{r re-comparison-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
+```{r re-comparison-1, fig.cap = "Population level effect of watershed land use on lake TP and TN.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/re-comparison-1.pdf")
@@
 
-```{r re-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
+```{r re-1, fig.cap = "Hydrologic region level effect of watershed land use for the best performing model for TP and TN respectively.
+Values that do not overlap the population level median are shaded in red.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/re-1.pdf")
@@
 
-```{r tn_re_hu4-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
+```{r tn_re_hu4-1, fig.cap = "Map highlighting corn sensitive regions from the previous figure.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/tn_re_hu4-1.pdf")
@@
 
-```{r tn_re_compare-1, fig.cap = "Exploratory dotplots showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE}
+```{r tn_re_compare-1, fig.cap = "Histograms showing the distribution of Clay and N deposition for the corn sensitive regions compared to all other regions.
+Medians for each group are shown as vertical dashed lines.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/tn_re_compare-1.pdf")

### 2019-08-07 manuscript/appendix.Rmd
turn on specific figs for appendix

@@
 source("../scripts/99_utils.R")
+```
+
+\pagebreak
+
+```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE, eval=TRUE}
+knitr::include_graphics("../figures/tptn_maps-1.pdf")
 ```
@@
 
-```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE, eval=FALSE}
+```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE, eval=TRUE}
 knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
+```
+
+```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.
+Line is 1:1 not regression.", warning=FALSE, echo = FALSE, eval=TRUE}
+knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
+```
+
+```{r nlcd-versus-cdl_map, fig.cap = "Comparison between NLCD (2011) ag and pasture against CDL (2010) specific crops.", warning=FALSE, echo = FALSE, eval = TRUE}
+knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
+```
+
+```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE, eval=FALSE}
+knitr::include_graphics("../figures/09_stream_buffer-1.pdf")
+```
+
+```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE, eval=TRUE}
+knitr::include_graphics("../figures/satellite-1.pdf")
+```
+
+```{r cdl_viewport, fig.cap = "CDL landuse cover in example IWS.", warning=FALSE, echo = FALSE, eval=FALSE}
+knitr::include_graphics("../figures/cdl_viewport-1.pdf")
 ```
@@
 
-```{r cdl_viewport, fig.cap = "CDL landuse cover in example IWS.", warning=FALSE, echo = FALSE, eval=TRUE}
-knitr::include_graphics("../figures/cdl_viewport-1.pdf")
-```
-
 ```{r county_extent, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (greater than 40 percent) and water quality data in LAGOS from at least 3 sampling events between 2000 and 2010.", warning=FALSE, echo = FALSE, eval = FALSE}
@@
 ```
-
-```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE, eval=FALSE}
-knitr::include_graphics("../figures/tptn_maps-1.pdf")
-```
-
-```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.
-Line is 1:1 not regression.", warning=FALSE, echo = FALSE, eval=FALSE}
-knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
-```
-
-```{r nlcd-versus-cdl_map, fig.cap = "Comparison between NLCD (2011) ag and pasture against CDL (2010) specific crops.", warning=FALSE, echo = FALSE, eval = FALSE}
-knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
-```
-
-```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE, eval=FALSE}
-knitr::include_graphics("../figures/09_stream_buffer-1.pdf")
-```
-
-```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE, eval=FALSE}
-knitr::include_graphics("../figures/satellite-1.pdf")
-```

### 2019-08-07 figures/08_exploratory_dotplot.Rmd
addd highlight panels for dotplot

@@
   dplyr::filter(!str_detect(pretty, "^N ")) %>%
-  dplyr::filter(!str_detect(pretty, " N "))
+  dplyr::filter(!str_detect(pretty, " N ")) %>%
+  dplyr::filter(!(pretty %in% c("Stream-buffer Ag", 
+                                          "N input", "P input")))
 
@@
   dplyr::filter(!str_detect(pretty, "^P ")) %>%
-  dplyr::filter(!str_detect(pretty, " P "))
+  dplyr::filter(!str_detect(pretty, " P ")) %>%
+  dplyr::filter(!(pretty %in% c("Stream-buffer Ag", 
+                                          "N input", "P input")))
 
@@
 
+row_highlight <- function(x, gg){
+  # x <- "Fertilizer"
+  if(!(x %in% gg$data$pretty)){
+    x <- as.character(gg$data$pretty[grep(x, gg$data$pretty)])
+  }
+
+  gg + 
+    scale_color_manual(values = rep("black", 5)) +
+    gghighlight(pretty == x, use_direct_label = FALSE)  
+}
+
+dotplot_panel <- function(x){
+  plot_grid(NULL, 
+plot_grid(row_highlight(x, gg_tp) + theme(legend.position = 0), NULL,
+          row_highlight(x, gg_tn), 
+          rel_widths = c(1, 0.2, 1), nrow = 1, 
+          labels = c("TP", "", "TN"), 
+          label_x = c(0.6, 0.5, 0.6), 
+          label_y = c(1.05, 1.1, 1.05)), 
+ncol = 1, rel_heights = c(0.07, 1))
+}
+
+dotplot_panel("Max depth")
+dotplot_panel("Baseflow")
+dotplot_panel("Corn")
+dotplot_panel("Fertilizer")
+dotplot_panel("Buffer Ag")
 ```

### 2019-08-07 scripts/99_make_predictor_key.R

@@ -39,8 +39,7 @@ pred_key$varv <- gsub("_", "v", pred_key$var)
 
 pred_key <- dplyr::filter(pred_key, 
                           !(pretty %in% c("Lake area", "N-fixer", 
-                                                   "Non-ag")))
-
+                                          "Non-ag")))
 
 # View(pred_key)
 write.csv(pred_key, "data/predictor_key.csv", row.names = FALSE)

### 2019-08-07 figures/07_model-selection.Rmd
add forest models

@@
 # lapply(re_brms, function(x) x$formula) 
-fit_tn         <- re_brms[[9]] # 5 is best tn model with random effects
+fit_tn         <- re_brms[[11]] # 11 is best tn model with random effects
 signif_hu4_ids <- fit_tn$re_signif_ids 
@@
                                 function(x) get_re_text(as.character(x$formula)[1])))
-re_global$response <- c(rep("tp", 5), rep("tn", 5))
+re_global$response <- c(rep("tp", 6), rep("tn", 6))
 re_global <- dplyr::filter(re_global, term != "rowvcropvpct")

### 2019-08-07 scripts/03_model.R

@@ -79,6 +79,14 @@ r2_fe <- dplyr::bind_rows(
                        phosphorusvfertilizervuse + pvinput + phosphorusvlivestockvmanure +
                        buffervcultivatedvcrops + buffervnatural +
                       (1 + ag | hu4vzoneid)),
+  "tp_forest"       = bf(tp ~  
+                       maxdepth + iwslavratio +
+                       soilvorgvcarbon + wetlandvpotential + hu12vpptvmean + 
+                       clayvpct + hu12vbaseflowvmean +
+                       nitrogenvfertilizervuse + nvinput + nitrogenvlivestockvmanure + hu4vnitrogenvatmosphericvdeposition +
+                       phosphorusvfertilizervuse + pvinput + phosphorusvlivestockvmanure +
+                       buffervcultivatedvcrops + buffervnatural +
+                       (1 + forest | hu4vzoneid)),
   "tp_rowcrop"       = bf(tp ~  
                        maxdepth + iwslavratio +
                        soilvorgvcarbon + wetlandvpotential + hu12vpptvmean + 
@@ -122,6 +130,14 @@ r2_fe <- dplyr::bind_rows(
                       phosphorusvfertilizervuse + pvinput + phosphorusvlivestockvmanure +
                       buffervcultivatedvcrops + buffervnatural +
                       (1 + ag | hu4vzoneid)),
+  "tn_forest"      = bf(tn ~  maxdepth + iwslavratio +
+                      soilvorgvcarbon + wetlandvpotential + hu12vpptvmean + 
+                      clayvpct + hu12vbaseflowvmean +
+                      nitrogenvfertilizervuse + nvinput + nitrogenvlivestockvmanure +
+                      hu4vnitrogenvatmosphericvdeposition +
+                      phosphorusvfertilizervuse + pvinput + phosphorusvlivestockvmanure +
+                      buffervcultivatedvcrops + buffervnatural +
+                      (1 + forest | hu4vzoneid)),
   "tn_rowcrop"      = bf(tn ~  maxdepth + iwslavratio +
                       soilvorgvcarbon + wetlandvpotential + hu12vpptvmean + 
                       clayvpct + hu12vbaseflowvmean +

### 2019-08-07 manuscript/figures.Rmd
more caption detail

@@
 Values that do not overlap zero are shaded in red.
-Horizontal bars separate coefficients in distinct predictor categories.", warning=FALSE, echo = FALSE}
+Horizontal bars separate coefficients in distinct predictor categories.
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/fe-1.pdf")

### 2019-08-07 figures/07_model-selection.Rmd
align x-axis ranges

@@
   geom_hline(yintercept = 0, linetype = "dashed") +
-  expand_limits(y = -0.2) +
+  expand_limits(y = c(-0.2, 0.5)) +
   coord_flip() +

### 2019-08-08 tables/03_model_summary.Rmd
output model summary table

--- 2019-05-24 tables/03_model_summary.Rmd
@@
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
+# setwd("tables")
+source("../scripts/99_utils.R")
 ```
@@
 ```{r summary_table, eval=TRUE}
-library(kableExtra)
-library(dplyr)
-library(magrittr)
-library(stringr)
+# setwd("tables")
+re_brms <- readRDS("../data/mcmc/re_brms.rds")
 
-# setwd("tables")
-dt <- read.csv("../data/mcmc/model_r2.csv", 
-                     stringsAsFactors = FALSE)
+r2_re <- dplyr::bind_rows(
+  lapply(re_brms, function(x) data.frame(brms::bayes_R2(x))))
+r2_re$term <- unlist(lapply(re_brms, 
+                                function(x) get_re_text(as.character(x$formula)[1])))
+r2_re$response <- c(rep("tp", nrow(r2_re) / 2), rep("tn", nrow(r2_re) / 2))
+r2_re <- dplyr::filter(r2_re, term != "rowvcropvpct")
+
+sort_loo <- function(x){
+  x_df       <- as.data.frame(x)
+  x_df$index <- row.names(x_df)
+  x_df$index <- as.numeric(stringr::str_extract(x_df$index, "\\d+"))
+  arrange(x_df, index)
+}
+
+loo_re <- rbind(
+  sort_loo(loo_compare(loo(re_brms[[1]]),
+                       loo(re_brms[[3]]), loo(re_brms[[4]]),
+                       loo(re_brms[[5]]), 
+                       loo(re_brms[[6]]))),
+  sort_loo(loo_compare(loo(re_brms[[7]]),
+                       loo(re_brms[[9]]), loo(re_brms[[10]]),
+                       loo(re_brms[[11]]), 
+                       loo(re_brms[[12]])))
+  ) %>%
+  arrange(index)
+
+dt           <- r2_re
+dt$elpd_diff <- loo_re$elpd_diff
+dt <- dplyr::select(dt, 
+                    response, term, r2 = Estimate, elpd_diff)
+dt <- dt[order(dt$response, dt$elpd_diff, decreasing = c(TRUE, FALSE)),]
 
 options(knitr.kable.NA = "-")  
-dplyr::filter(dt, str_detect(Model, "tp")) %>%
-  dplyr::select(-Model) %>%
-  dplyr::rename("$R^2$" = Estimate) %>%
+dt %>%
+  # dplyr::filter(str_detect(response, "tp")) %>%
+  # dplyr::select(-response) %>%
+  dplyr::rename("$R^2$" = r2) %>%
   knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2")
@@
 \pagebreak
-```{r tn_results}
-dplyr::filter(dt, str_detect(Model, "tn")) %>%
-  dplyr::select(-Model) %>%
-  dplyr::rename("$R^2$" = Estimate) %>%
+```{r tn_results, eval=FALSE}
+dplyr::filter(dt, str_detect(response, "tn")) %>%
+  dplyr::select(-response) %>%
+  dplyr::rename("$R^2$" = r2) %>%
   knitr::kable(digits = 2, format = "markdown", caption = "TN Model R2")

### 2019-09-02 figures/07_model-selection.Rmd
dont print junk fig
show global lulc effect

@@
 
+```{r re_global}
+# tp, tn
+# ag, row_crop, pasture, corn, soybeans
+re_global          <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
+re_global$term     <- unlist(lapply(re_brms, 
+                                function(x) get_re_text(as.character(x$formula)[1])))
+re_global$response <- c(rep("tp", 6), rep("tn", 6))
+re_global          <- left_join(re_global, pred_key, by = c("term" = "var")) %>%
+  dplyr::select(pretty, `5%`:`95%`, term, response)
+# re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
+# group_by(re_global, response) %>%
+#   arrange(desc(`50%`))
+```
+
 ```{r tp_fe, out.width="3.25in", out.height="4in"}
-# lapply(re_brms, function(x) x$formula) 
-fit_tp   <- re_brms[[1]] # 1 is best tp model with random effects
+# lapply(re_brms, function(x) x $formula) 
+# re_brms[[6]]$formula
+best_tp        <- 6 # 6 is best tp model with random effects
+fit_tp         <- re_brms[[best_tp]] 
 signif_hu4_ids <- fit_tp$re_signif_ids 
@@
   tidyr::spread(name, value) %>%
+  dplyr::bind_rows(
+    dplyr::select(re_global[best_tp,], -term, -response)) %>%
   rowwise() %>%
@@
                            levels = rev(c("Nutrient inputs", "Nutrient transport", 
-                                      "Land-use cover", "Buffer configuration", 
-                                      "Lake")))) %>%
+                                      "Buffer configuration", "Lake", 
+                                      "Land-use cover")))) %>%
   mutate(category = forcats::fct_recode(category, 
@@
 # lapply(re_brms, function(x) x$formula) 
-fit_tn         <- re_brms[[11]] # 11 is best tn model with random effects
+# re_brms[[11]]$formula
+best_tn        <- 11 # 11 is best tn model with random effects
+fit_tn         <- re_brms[[best_tn]] 
 signif_hu4_ids <- fit_tn$re_signif_ids 
@@
   tidyr::spread(name, value) %>%
+  dplyr::bind_rows(
+    dplyr::select(re_global[best_tn,], -term, -response)) %>%
   rowwise() %>%
@@
 
-gg_line
+# gg_line
 
@@
 ```{r re-comparison, fig.width=4}
-# tp, tn
-# ag, row_crop, pasture, corn, soybeans
-re_global <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
-re_global$term <- unlist(lapply(re_brms, 
-                                function(x) get_re_text(as.character(x$formula)[1])))
-re_global$response <- c(rep("tp", 6), rep("tn", 6))
 re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
-
-# group_by(re_global, response) %>%
-#   arrange(desc(`50%`))
-
 gg_tn <- ggplot(data = dplyr::filter(re_global, response == "tn")) +

### 2019-09-03 figures/07_model-selection.Rmd
cleanup labels

@@
 
-```{r tp_fe, out.width="3.25in", out.height="4in"}
+```{r tp_fe, out.width="3.45in", out.height="4in"}
 # lapply(re_brms, function(x) x $formula) 
@@
   dplyr::bind_rows(
-    dplyr::select(re_global[best_tp,], -term, -response)) %>%
+    dplyr::select(re_global[best_tp,], -term, -response), 
+    data.frame(pretty = "", `5%` = "", `50%` = "", `95%` = "", 
+               stringsAsFactors = FALSE)
+    ) %>%
   rowwise() %>%
@@
   left_join(dplyr::select(pred_key, pretty, category)) %>%
+  mutate(category = tidyr::replace_na(category, "Land-use cover")) %>%
   mutate(category = factor(category, 
@@
   mutate(category = forcats::fct_recode(category, 
-                                        Buffer = "Buffer configuration")) %>%
+                                        Buffer = "Buffer configuration", 
+                                        LULC = "Land-use cover")) %>%
   arrange(category) %>%
@@
               fill = "transparent") +
+  # y-axis labels
   geom_text(aes(x = pretty, label = pretty, color = signif), 
@@
   geom_hline(yintercept = 0) +
-  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
+  # x-axis labels
+  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.6, by = 0.2), 
                      labels = scales::number_format(accuracy = 0.1)) +
@@
         plot.title = element_text(hjust = 0.5, face = "bold")) + 
-    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
+    # x-axis line length; controls dot-plot extent
+    annotate(x=0, xend=0, y=-0.6, yend=0.6, 
              colour="black", lwd=0.9, geom="segment") 
@@
 
-```{r tn_fe, out.width="3.25in", out.height="4in"}
+```{r tn_fe, out.width="3.45in", out.height="4in"}
 # lapply(re_brms, function(x) x$formula) 
@@
   dplyr::bind_rows(
-    dplyr::select(re_global[best_tn,], -term, -response)) %>%
+    dplyr::select(re_global[best_tn,], -term, -response), 
+    data.frame(pretty = "", `5%` = "", `50%` = "", `95%` = "", 
+               stringsAsFactors = FALSE)
+    ) %>%
   rowwise() %>%
@@
   geom_text(aes(x = pretty, label = pretty, color = signif), 
-            y = 0.44, vjust = 0.5, hjust = "left") + 
+            y = 0.65, vjust = 0.5, hjust = "left") + 
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
     geom_hline(yintercept = 0) +
-  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
+  scale_y_continuous(breaks = seq(from = -0.6, to = 0.6, by = 0.2), 
                      labels = scales::number_format(accuracy = 0.1)) +
@@
         plot.title = element_text(hjust = 0.5, face = "bold")) + 
-    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
+    annotate(x=0, xend=0, y=-0.6, yend=0.6, 
              colour="black", lwd=0.9, geom="segment")

### 2019-09-03 manuscript/appendix.Rmd
move dotplot to appendix
add subheadings and figure descriptions

@@
     fig_caption: yes
+header-includes: 
+- \usepackage{float}
+- \floatplacement{figure}{H}
 ---
@@
 
+## Response variable maps
+
+Some obvious data availability differences in New York and Wisconsin. Wisconsin has quite a bit fewer TN measurements.
+
 ```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE, eval=TRUE}
@@
 ```
+
+## Trophic state
+
+Over 50 percent of our study lakes were eutrophic to hypereutrophic.
 
@@
 
+\pagebreak
+
+## Bivariate relationships among predictors and lake nutrients
+
+We examined bivariate relationships between lake nutrient concentrations and predictors to determine, at least to first-approximation, the likely drivers of lake nutrients (Figure 2). 
+We found large differences between the drivers of lake phosphorus and lake nitrogen concentrations. 
+For example, max depth and baseflow had a much larger effect on P than N. Pearson’s correlation coefficients for these relationships were XX and YY respectively. 
+In contrast, watershed land-use corn cover, fertilizer inputs, and riparian buffer configuration appear to have a larger effect on N than P Pearson’s correlation coefficients for these relationships were XX, YY, and ZZ respectively.
+
+```{r exploratory_dotplot, fig.cap = "Dotplots showing absolute value Pearson's correlation coefficients. Dots are colored according to predictor categories.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/dotplot-1.pdf")
+```
+
+\pagebreak
+
+## Correlations among predictor variables
+
+There is clearly a cluster of related predictor variables that includes most nutrient input, Ag land-use, and buffer configuration measures.
+
 ```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE, eval=TRUE}
@@
 
+\pagebreak
+
+## The Cropland Data Layer
+
+The National land cover database (NLCD) is more typically used in macroecology studies.
+In our paper, we wanted to go beyond the coarse categories in the NLCD and test relationships with individual crops.
+The Cropland Data Layer (CDL) is a product that allowed us to do this.
+Because the CDL is more granular that the NLCD we could not directly compare them.
+Instead, we aggregated all the CDL categories associated with agriculture (also pasture) and compared these values for each watershed with the corresponding NLCD estimates.
+
 ```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.
-Line is 1:1 not regression.", warning=FALSE, echo = FALSE, eval=TRUE}
+Line is 1:1 not a  regression best fit.", warning=FALSE, echo = FALSE, eval=TRUE}
 knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
@@
 
-```{r nlcd-versus-cdl_map, fig.cap = "Comparison between NLCD (2011) ag and pasture against CDL (2010) specific crops.", warning=FALSE, echo = FALSE, eval = TRUE}
+```{r nlcd-versus-cdl_map, fig.cap = "Example of increasing granularity for total Ag to Ag versus pasture, to pasture versus specific crops.", warning=FALSE, echo = FALSE, eval = TRUE}
 knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
@@
 
+\pagebreak
+
+## Demo of watersheds and buffer configuration
+
+Here are two lakes each with the same percent Ag in their watersheds (red outlines).
+However, the lake on the left (Lake Carleton) has a riparian buffer (teal outlines) with a much higher percentage of Ag relative to the lake on the right (Argyle Lake).
+
+```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE, eval = TRUE}
+knitr::include_graphics("../figures/satellite-1.pdf")
+```
+
+\pagebreak
+
 ```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE, eval=FALSE}
 knitr::include_graphics("../figures/09_stream_buffer-1.pdf")
-```
-
-```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE, eval=TRUE}
-knitr::include_graphics("../figures/satellite-1.pdf")
 ```

### 2019-09-03 figures/07_model-selection.Rmd
cleanup labels

@@
   theme(rect = element_rect(fill = "transparent")) +
-  ggtitle("TP ~ Ag slope") + xlab("Zone ID") + ylab("") +
+  ggtitle("TP") + xlab("Zone ID") + ylab("") +
   theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
@@
     scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
-    guides(guide_legend(nrow = 2))  +
-  ggtitle("Ag sensitive regions")
+    guides(guide_legend(nrow = 2))  # +
+  # ggtitle("Ag sensitive regions")
 
@@
   theme(rect = element_rect(fill = "transparent")) +
-  ggtitle("TN ~ corn slope") + xlab("Zone ID") + ylab("") +
+  ggtitle("TN") + xlab("Zone ID") + ylab("") +
   theme(plot.title = element_text(hjust = 0.5, face = "bold")) +

### 2019-09-03 manuscript/figures.Rmd
move dotplot to appendix
t
include table 1 in figures doc

@@
     keep_tex: yes
+header-includes: 
+- \usepackage{colortbl}
 ---
 
+\arrayrulecolor{white}
 ```{r setup, include=FALSE}
@@
 
-```{r exploratory_dotplot, fig.cap = "Dotplots showing absolute value Pearson's correlation coefficients. Dots are colored according to predictor categories.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/dotplot-1.pdf")
+```{r re-comparison-1, fig.cap = "Population level effect of watershed land use on lake TP and TN.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/re-comparison-1.pdf")
+```
+
+```{r 03_model_summary, results='asis', warning=FALSE, echo = FALSE}
+knitr::kable('\\includegraphics{"../tables/03_model_summary"}', col.names = NULL, caption = "Model selection diagnostics")
 ```
@@
 knitr::include_graphics("../figures/fe-1.pdf")
-```
-
-```{r re-comparison-1, fig.cap = "Population level effect of watershed land use on lake TP and TN.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/re-comparison-1.pdf")
 ```

### 2019-09-05 tables/03_model_summary.Rmd
rm row names

@@
   dplyr::rename("$R^2$" = r2) %>%
-  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2")
+  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2", 
+               row.names = FALSE)
 ```

### 2019-09-06 manuscript/figures.Rmd
fix diagnositic table labeling

@@
 ```{r 03_model_summary, results='asis', warning=FALSE, echo = FALSE}
-knitr::kable('\\includegraphics{"../tables/03_model_summary"}', col.names = NULL, caption = "Model selection diagnostics")
+knitr::kable('\\includegraphics[width=5in]{"../tables/03_model_summary"}', col.names = NULL, caption = "Model selection diagnostics")
 ```

### 2019-09-06 tables/03_model_summary.Rmd
fix diagnositic table labeling

--- 2019-08-08 tables/03_model_summary.Rmd
@@
   # dplyr::select(-response) %>%
-  dplyr::rename("$R^2$" = r2) %>%
-  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2")
+  dplyr::rename("$R^2$" = r2, 
+                "LOO-ELPD" = elpd_diff) %>%
+  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2", 
+               row.names = FALSE)
 ```

### 2019-09-06 manuscript/figures.Rmd
update fig captions

--- 2019-09-03 manuscript/figures.Rmd
@@
 
-```{r re-comparison-1, fig.cap = "Population level effect of watershed land use on lake TP and TN.", warning=FALSE, echo = FALSE}
+```{r re-comparison-1, fig.cap = "Population level effect of watershed land use on lake TP and TN.
+Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
+Also shown is a comparison to a zero effect (dashed line).", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/re-comparison-1.pdf")
@@
 ```{r 03_model_summary, results='asis', warning=FALSE, echo = FALSE}
-knitr::kable('\\includegraphics{"../tables/03_model_summary"}', col.names = NULL, caption = "Model selection diagnostics")
+knitr::kable('\\includegraphics[width=5in]{"../tables/03_model_summary"}', col.names = NULL, caption = "Diagnostics for each model listed by regionally varying coefficient.
+Table is sorted by decreasing R2 and expected log predictive density.")
 ```
@@
 
-```{r re-1, fig.cap = "Hydrologic region level effect of watershed land use for the best performing model for TP and TN respectively.
-Values that do not overlap the population level median are shaded in red.", warning=FALSE, echo = FALSE}
+```{r re-1, fig.cap = "Regionally varying effect of watershed land-use cover on A) TP and B) TN.
+Lines shown are 95% credible intervals with median marked by a filled circle.
+Values that do not overlap the population level estimate are shaded in red.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/re-1.pdf")
@@
 
-```{r tn_re_hu4-1, fig.cap = "Map highlighting corn sensitive regions from the previous figure.", warning=FALSE, echo = FALSE}
+```{r tn_re_hu4-1, fig.cap = "Location of hydrologic regions sensitive to watershed land-use cover corresponds to highlighted credible intervals in Figure 4.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/tn_re_hu4-1.pdf")

### 2019-09-06 README.Rmd
cleanup

--- 2018-12-14 README.Rmd
@@
 
-## The effect of crop type, fertilizer, and manure applications on lake nutrients in agriculture watersheds at regional scales
+## Beyond land-use cover: relationships between agriculture and lake nutrient concentrations at macroscales
 
@@
 
+Appendix: [manuscript/appendix.pdf](manuscript/figures.pdf)
+
 Tables: [manuscript/tables.pdf](manuscript/tables.pdf)
-
-## Potential predictor variables
-
-<details><summary><b>Lake Characteristics</b> (`LAGOSNE`) </summary><p>
-
-* [x] Lake depth
-* [x] IWS area
-* [x] IWS/Lake area
-</p></details>
-
-* Cropland Data Layer
-    * IWS pasture types (forage or not)
-    * IWS specific crops (corn, wheat, etc.)
-    * IWS crop frequency/rotation
-* gSSURGO
-    * IWS wetland potential (as a proxy for tile drainage)
-    * IWS soil organic carbon
-    * IWS root zone depth
-    * IWS lithology (sand %, clay %, etc.)
-* USGS
-    * IWS from county - manure, fertilizer, and deposition of N,P
-
-## Research questions
-
-## Timeline
-
-## Issues
-
-* Availability of data products through time is highly variable. How to align or decide to treat properties as constant?
-
-```{r echo=FALSE}
-cdl_key <- read.csv("data/cdl/cdl_key.csv", stringsAsFactors = FALSE)
-```
-
-```{r lagos_v_cdl_v_usgs, echo=FALSE, eval=FALSE}
-# tp vs lagos ag, cdl ag, usgs P inputs
-
-# ---- setup ----
-
-library(dplyr)
-library(ggplot2)
-library(magrittr)
-library(LAGOSNE)
-library(cowplot)
-library(sf)
-
-lg          <- lagosne_load("1.087.1")
-ep          <- readRDS("data/ep.rds")
-cdl_summary <- read.csv("data/cdl/cdl_summary.csv", stringsAsFactors = FALSE)
-usgs        <- readRDS("data/usgs/usgs.rds")
-
-lg_ep <- mutate(lg$iws.lulc, 
-                lg_ag = rowSums(cbind(iws_nlcd2006_pct_81, 
-                                      iws_nlcd2006_pct_82), na.rm = TRUE)) %>%
-  select(lagoslakeid, lg_ag) %>%
-  left_join(ep, by = "lagoslakeid") %>%
-  filter(!is.na(tp))
-
-cdl_ep <- filter(cdl_summary, variable == "ag") %>%
-  left_join(
-    filter(ep, !is.na(tp)), by = c("llid" = "lagoslakeid")) %>%
-  mutate(cdl_ag = value)
-
-usgs_ep <- filter(usgs, !is.na(tp))
-
-# ---- plotting ----
-
-plot_grid(
-ggplot() +
-  geom_point(data = lg_ep, aes(x = lg_ag, y = tp)) +
-  xlab("LAGOS (NLCD 2006) Ag (%)"),
-ggplot() +
-  geom_point(data = cdl_ep, aes(x = cdl_ag, y = tp)) +
-  xlab("CDL Ag (%)"),
-ggplot() + 
-  geom_point(data = usgs_ep, aes(x = phosphorus_input, y = tp)) + 
-  scale_x_log10() + 
-  xlab("log(P Input)"))
-
-```

### 2019-09-12 figures/07_model-selection.Rmd
match hucs among figs, closes #18

@@
                 ))
+
 hu4 <- dplyr::filter(hu4, !is.na(n_cat))
@@
 states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
+hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)
 
@@
     geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
-    geom_sf(data = hu4, fill = "white", color = "black", size = 0.4) +
+    geom_sf(data = hu4_all, fill = "white", color = "black", size = 0.4) +
     geom_sf(data = signif_hu4, color = "red", alpha = 0) +
@@
 cowplot::plot_grid(
+cowplot::plot_grid(
   equalize_panels(
@@
             axis.title.x = element_blank())), 
-  rel_widths = c(1, 1))
+  rel_widths = c(1, 0.95)), 
+ggplot(data.frame(x = 1, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
+  geom_text(aes(x = x, y = y, label = label)) +
+  theme_void(),
+ncol = 1, rel_heights = c(1, 0.05))
+
 ```
@@
 
+# STOP
 hu4_signif <-  LAGOSNEgis::query_gis(

### 2019-09-13 figures/07_model-selection.Rmd
cleanup figures and legends

@@
   theme(rect = element_rect(fill = "transparent")) +
-  ggtitle("TP") + xlab("Zone ID") + ylab("") +
+  ggtitle("TP") + xlab("Zone ID") +
   theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
@@
   theme(rect = element_rect(fill = "transparent")) +
-  ggtitle("TN") + xlab("Zone ID") + ylab("") +
+  ggtitle("TN") + xlab("Zone ID") +
   theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
@@
   rel_widths = c(1, 0.95)), 
-ggplot(data.frame(x = 1, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
+ggplot(data.frame(x = 1, y = 1, label = "Standardized slopes", stringsAsFactors = FALSE)) + 
   geom_text(aes(x = x, y = y, label = label)) +
@@
         strip.text = element_text(face = "bold")) +
-  facet_wrap(~pretty)
+  facet_wrap(~pretty) +
+  xlab("Standardized value")
 
@@
 ```{r re}
-cowplot::plot_grid(gg_tp_re, 
+cowplot::plot_grid(
+cowplot::plot_grid(gg_tp_re + theme(axis.title.x = element_blank(), 
+                                     plot.margin = unit(c(0,0,0,0), "cm")),
                    gg_tn_re + theme(axis.text.y = element_blank(), 
-                                    axis.title.y = element_blank()), 
-                   rel_widths = c(1, 0.9))
+                                    axis.title.y = element_blank(), 
+                                    axis.title.x = element_blank(),
+                                    plot.margin = unit(c(0,0,0,0), "cm")), 
+                   rel_widths = c(1, 0.9)), 
+ggplot(data.frame(x = 0, y = 0, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
+  geom_text(aes(x = x, y = y, label = label), size = 5) +
+  theme_void() + 
+  theme(plot.margin = unit(c(0,0,0,0), "cm")),
+ncol = 1, rel_heights = c(1, 0.03))
 

### 2019-09-13 manuscript/figures.Rmd
cleanup figures and legends

@@
 
-```{r maps2, fig.cap = "Map of lake locations and hydrologic (HUC) regions.", warning=FALSE, echo = FALSE}
+```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC) regions.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/11_map-1.pdf")
@@
 
-```{r re-comparison-1, fig.cap = "Population level effect of watershed land use on lake TP and TN.
+```{r re-comparison-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN.
 Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
@@
 
-```{r fe-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals.
+```{r fe-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models.
 Values that do not overlap zero are shaded in red.
@@
 
-```{r re-1, fig.cap = "Regionally varying effect of watershed land-use cover on A) TP and B) TN.
+```{r re-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models.
 Lines shown are 95% credible intervals with median marked by a filled circle.
@@
 
-```{r tn_re_hu4-1, fig.cap = "Location of hydrologic regions sensitive to watershed land-use cover corresponds to highlighted credible intervals in Figure 4.", warning=FALSE, echo = FALSE}
+```{r tn_re_hu4-1, fig.cap = "Location of hydrologic regions sensitive to watershed land-use cover corresponding to highlighted credible intervals in Figure 4.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/tn_re_hu4-1.pdf")

### 2019-09-13 figures/07_model-selection.Rmd
more fig standardization

@@
   rel_widths = c(1, 0.95)), 
-ggplot(data.frame(x = 1, y = 1, label = "Standardized slopes", stringsAsFactors = FALSE)) + 
+ggplot(data.frame(x = 1, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
   geom_text(aes(x = x, y = y, label = label)) +
@@
   theme(plot.margin = unit(c(0,0,0,0), "cm")),
-ncol = 1, rel_heights = c(1, 0.03))
+ncol = 1, rel_heights = c(1, 0.05))
 
@@
 
-cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.75))
+cowplot::plot_grid(
+cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.75)),
+ggplot(data.frame(x = 1, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
+  geom_text(aes(x = x, y = y, label = label)) +
+  theme_void(),
+ncol = 1, rel_heights = c(1, 0.05))
 ```

### 2019-10-02 figures/07_model-selection.Rmd
adjust response labels

@@
                                 function(x) get_re_text(as.character(x$formula)[1])))
-re_global$response <- c(rep("tp", 6), rep("tn", 6))
+re_global$response <- c(rep("tp", 7), rep("tn", 7))
 re_global          <- left_join(re_global, pred_key, by = c("term" = "var")) %>%
@@
 ```{r tp_fe, out.width="3.45in", out.height="4in"}
+# lapply(re_brms, function(x) x$R2)
 # lapply(re_brms, function(x) x $formula) 

### 2019-10-16 figures/07_model-selection.Rmd
rerun lower ag cutoff models

--- 2019-09-13 figures/07_model-selection.Rmd
@@
                                 function(x) get_re_text(as.character(x$formula)[1])))
-re_global$response <- c(rep("tp", 6), rep("tn", 6))
+re_global$response <- c(rep("tp", nrow(re_global) / 2), rep("tn", nrow(re_global) / 2))
 re_global          <- left_join(re_global, pred_key, by = c("term" = "var")) %>%
@@
 ```{r tp_fe, out.width="3.45in", out.height="4in"}
+# lapply(re_brms, function(x) x$R2)
 # lapply(re_brms, function(x) x $formula) 
-# re_brms[[6]]$formula
-best_tp        <- 6 # 6 is best tp model with random effects
+# re_brms[[2]]$formula
+best_tp        <- 2 # 2 is best tp model with random effects
 fit_tp         <- re_brms[[best_tp]] 
@@
 # lapply(re_brms, function(x) x$formula) 
-# re_brms[[11]]$formula
-best_tn        <- 11 # 11 is best tn model with random effects
+# re_brms[[8]]$formula
+# brms::bayes_R2(re_brms[[8]])
+
+best_tn        <- 8 # 11 is best tn model with random effects
 fit_tn         <- re_brms[[best_tn]] 

### 2019-10-16 tables/03_model_summary.Rmd
rerun lower ag cutoff models

@@
 
+# lapply(re_brms, function(x) x$formula)
+
 loo_re <- rbind(
-  sort_loo(loo_compare(loo(re_brms[[1]]),
+  sort_loo(loo_compare(loo(re_brms[[1]]), loo(re_brms[[2]]),
                        loo(re_brms[[3]]), loo(re_brms[[4]]),
@@
                        loo(re_brms[[6]]))),
-  sort_loo(loo_compare(loo(re_brms[[7]]),
+  sort_loo(loo_compare(loo(re_brms[[7]]), loo(re_brms[[8]]),
                        loo(re_brms[[9]]), loo(re_brms[[10]]),

### 2019-10-17 figures/11_map.Rmd
stash map fig code

---
output: pdf_document
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 6.5, fig.height = 4.5)
# setwd("figures")
source("../scripts/99_utils.R")
```

```{r 11_map, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# cl            <- cart_layers()
# ep            <- cl$ep
# states        <- cl$states
# states_shaded <- cl$states_shaded
# study_bbox    <- cl$study_bbox
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
ep            <- st_read("../data/gis.gpkg", "ep", quiet = TRUE)
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
states_focal  <- st_read("../data/gis.gpkg", "states_focal", quiet = TRUE)
hu4_focal     <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)

# outline <- ne_countries(country = c("canada", "mexico", "united states of america"), 
#                      returnclass = "sf")
# inset_bbox <- mapedit::drawFeatures()
# sf::st_write(inset_bbox, "../data/inset_bbox.gpkg", 
#              layer_options = "OVERWRITE=YES")
# inset_bbox <- st_read("../data/inset_bbox.gpkg")
# outline <- st_crop(outline, inset_bbox)
# outline <- outline %>%
#   st_transform(LAGOSNEgis:::albers_conic()) %>%
#   st_snap(x = ., y = ., tolerance = 0.000001) %>%
#   st_union()

gg_states <- 
  ggplot() + 
    geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
    # geom_sf(data = outline, color = "black", alpha = 0, size = 0.8) +
    # geom_sf(data = hu4, fill = "grey") +
    geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = ep, size = 0.9) +
    coord_sf(datum = NA) +
    theme_void()

gg_hu4 <- 
  ggplot() + 
      geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
              color = "black", fill = "#1D9DCF") +
      geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
      geom_sf(data = hu4_focal, fill = "white", color = "black", size = 0.4) +
      # geom_sf(data = ep, size = 1) +
      coord_sf(datum = NA) +
      theme_void() + 
      theme(legend.position = 0)

cowplot::plot_grid(gg_states, gg_hu4, ncol = 2, labels = "AUTO", vjust = 8, hjust = -1)
```

### 2019-10-17 figures/11_map.Rmd
add states to map

@@
 # study_bbox    <- cl$study_bbox
-study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
+study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
 ep            <- st_read("../data/gis.gpkg", "ep", quiet = TRUE)
@@
 hu4_focal     <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)
+hu4_focal     <- st_crop(st_transform(hu4_focal, st_crs(study_bbox)), study_bbox)
 

### 2019-10-17 scripts/00_get_gis.R

@@ -21,7 +21,8 @@ states_all <- ne_states(country = c("united states of america", "canada", "mexic
                         returnclass = "sf")
 state_codes <- c("IL", "IN", "IA",
                  "MI", "MN", "MO",
-                 "NY", "OH", "PA", "WI")
+                 "NY", "OH", "PA", "WI", 
+                 "CT", "RI", "NH", "VT")
 states_focal <- states_all %>%
   dplyr::filter(., postal %in% state_codes & iso_a2 == "US")
 study_bbox   <- st_as_sfc(st_bbox(states_focal))
@@ -61,6 +62,9 @@ hu4s_focal <- LAGOSNEgis::query_gis("HU4", "ZoneID", unique(ep$hu4_zoneid))
 hu8s <- LAGOSNEgis::query_gis_(
   query = paste0("SELECT * FROM HU8 WHERE ",
                  paste0("HUC8 LIKE '", hu4s$HUC4, "%'", collapse = " OR ")))
+
+study_bbox   <- st_transform(st_as_sfc(st_bbox(hu4s_focal)), st_crs(study_bbox))
+# study_bbox   <- concaveman::concaveman(st_cast(hu4s_focal, "POINT"))
 
 # unlink("data/gis.gpkg")
 # st_layers("data/gis.gpkg")

### 2019-10-17 figures/07_model-selection.Rmd
cleanup fe dotplot

@@
 
-```{r tp_fe, out.width="3.45in", out.height="4in"}
+```{r pre_tp_fe, out.width="3.45in", out.height="4in"}
 # lapply(re_brms, function(x) x$R2)
@@
   arrange(category, pretty)
-
-gg_tp_fe <- 
-  ggplot(data = gg_tp) + 
-  geom_pointrange(aes(x = pretty, y = `50%`, 
-                      ymin = `5%`, ymax = `95%`, color = signif)) + 
-  expand_limits(y = -1.8) +
-  geom_rect(ymin = -0.6, ymax = -0.6 - 2, xmin = 0, xmax = nrow(gg_tp) + 1, 
-              fill = "transparent") +
-  # y-axis labels
-  geom_text(aes(x = pretty, label = pretty, color = signif), 
-            y = -0.65, vjust = 0.5, hjust = "right") + 
-  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  geom_hline(yintercept = 0) +
-  # x-axis labels
-  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.6, by = 0.2), 
-                     labels = scales::number_format(accuracy = 0.1)) +
-  coord_flip() +
-  theme(axis.text.y = element_blank(), 
-        axis.ticks.y = element_blank(), 
-        axis.title.y = element_blank()) + 
-    facet_wrap(~category, strip.position = "left", ncol = 1, scales = "free_y",
-               as.table = FALSE) +
-    theme(panel.spacing = unit(0, "lines"), 
-          strip.placement = "outside", 
-          strip.background = element_blank(), 
-          axis.title.y = element_blank()) + 
-        ylab("Standardized slope") + theme(legend.position = 0) + 
-        ggtitle("TP") + xlab("") +
-  theme(panel.background = element_rect(fill = "transparent", color = NA),
-        plot.background = element_rect(fill = "transparent", color = NA), 
-        panel.grid = element_blank(),
-        rect = element_rect(fill = "transparent"), 
-        plot.title = element_text(hjust = 0.5, face = "bold")) + 
-    # x-axis line length; controls dot-plot extent
-    annotate(x=0, xend=0, y=-0.6, yend=0.6, 
-             colour="black", lwd=0.9, geom="segment") 
 ```
 
-```{r tp_re, fig.width=3.25, fig.height=4.5}
-fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
-fit_tp$re <- fit_tp$re %>%
-  mutate_at(vars(matches("%")), function(x) x + 
-              as.numeric(fit_tp$re_global["50%"]))
-
-gg_tp_re <- ggplot(data = fit_tp$re) +
-  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
-                      ymin = `5%`, ymax = `95%`, color = signif)) +
-  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  geom_hline(yintercept = as.numeric(fit_tp$re_global["50%"])) +
-  coord_flip() +
-  cowplot::theme_cowplot() +
-  theme(rect = element_rect(fill = "transparent")) +
-  ggtitle("TP") + xlab("Zone ID") +
-  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
-  theme(legend.position = 0)
-
-gg_tp_re
-```
-
-```{r tn_fe, out.width="3.45in", out.height="4in"}
+```{r pre_tn_fe, out.width="3.45in", out.height="4in"}
 # lapply(re_brms, function(x) x$formula) 
@@
   arrange(category, pretty)
+```
 
-gg_tn_fe <- 
-  ggplot(data = gg_tn) + 
-  geom_pointrange(aes(x = pretty, y = `50%`, 
+```{r fe_axis}
+# specify shared x-axis range
+x_max <- c(gg_tp$`95%`, gg_tn$`95%`)[which.max(c(gg_tp$`95%`, gg_tn$`95%`))]
+x_min <- c(gg_tp$`5%`, gg_tn$`5%`)[which.min(c(gg_tp$`5%`, gg_tn$`5%`))]
+```
+
+```{r tp_fe, out.width="3.45in", out.height="4in"}
+(gg_tp_fe <- fe_dotplot(gg_tp, "left", cat_labels = TRUE,
+                        x_min, x_max, "TP"))
+```
+
+```{r tn_fe, out.width="3.45in", out.height="4in"}
+(gg_tn_fe <- fe_dotplot(gg_tn, "right", cat_labels = FALSE, 
+                        x_min, x_max, "TN"))
+```
+
+```{r fe}
+cowplot::plot_grid(
+cowplot::plot_grid(
+  equalize_panels(
+    gg_tp_fe + theme(axis.title.x = element_blank())
+  ), 
+  equalize_panels(
+    gg_tn_fe + 
+      theme(axis.text.y = element_blank(), 
+            axis.title.x = element_blank())), 
+  rel_widths = c(1, 0.95)),
+
+ggplot(data.frame(x = 1, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
+  geom_text(aes(x = x, y = y, label = label)) +
+  theme_void(),
+ncol = 1, rel_heights = c(1, 0.05))
+```
+
+```{r tp_re, fig.width=3.25, fig.height=4.5}
+fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
+fit_tp$re <- fit_tp$re %>%
+  mutate_at(vars(matches("%")), function(x) x + 
+              as.numeric(fit_tp$re_global["50%"]))
+
+gg_tp_re <- ggplot(data = fit_tp$re) +
+  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                       ymin = `5%`, ymax = `95%`, color = signif)) +
-  expand_limits(y = c(-0.6, 1.6)) +
-  geom_rect(ymin = 0.44, ymax = 0.44 + 2, xmin = 0, xmax = nrow(gg_tn) + 1, 
-              fill = "transparent") +
-  geom_text(aes(x = pretty, label = pretty, color = signif), 
-            y = 0.65, vjust = 0.5, hjust = "left") + 
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-    geom_hline(yintercept = 0) +
-  scale_y_continuous(breaks = seq(from = -0.6, to = 0.6, by = 0.2), 
-                     labels = scales::number_format(accuracy = 0.1)) +
+  geom_hline(yintercept = as.numeric(fit_tp$re_global["50%"])) +
   coord_flip() +
-  theme(axis.text.y = element_blank(), 
-        axis.ticks.y = element_blank(), 
-        axis.title.y = element_blank()) + 
-    facet_wrap(~category, strip.position = "right", ncol = 1, scales = "free_y",
-               as.table = FALSE) +
-    theme(panel.spacing = unit(0, "lines"), 
-          strip.placement = "outside", 
-          strip.background = element_blank(), 
-          axis.title.y = element_blank()) + 
-        ylab("Standardized slope") + theme(legend.position = 0) + 
-        ggtitle("TN") + xlab("") +
-  theme(panel.background = element_rect(fill = "transparent"), 
-        panel.grid = element_blank(),
-        rect = element_rect(fill = "transparent"), 
-        plot.title = element_text(hjust = 0.5, face = "bold")) + 
-    annotate(x=0, xend=0, y=-0.6, yend=0.6, 
-             colour="black", lwd=0.9, geom="segment")
+  cowplot::theme_cowplot() +
+  theme(rect = element_rect(fill = "transparent")) +
+  ggtitle("TP") + xlab("Zone ID") +
+  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
+  theme(legend.position = 0)
 
-equalize_panels <- function(x){
-  gp <- ggplotGrob(x)
-  facet.columns <- gp$layout$t[grepl("panel", gp$layout$name)]
-  x.var         <- sapply(ggplot_build(x)$layout$panel_scales_x,
-                  function(l) length(l$range$range))
-  gp$heights[facet.columns] <- gp$heights[facet.columns] * rev(x.var)
-  x <- ggplotify::as.ggplot(gp)
-  x
-}
+gg_tp_re
 ```
@@
   theme(legend.position = 0)
-
-```
-
-```{r fe}
-cowplot::plot_grid(
-cowplot::plot_grid(
-  equalize_panels(
-    gg_tp_fe + theme(axis.title.x = element_blank())
-  ), 
-  equalize_panels(
-    gg_tn_fe + 
-      theme(axis.text.y = element_blank(), 
-            axis.title.x = element_blank())), 
-  rel_widths = c(1, 0.95)), 
-ggplot(data.frame(x = 1, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
-  geom_text(aes(x = x, y = y, label = label)) +
-  theme_void(),
-ncol = 1, rel_heights = c(1, 0.05))
 

### 2019-10-17 scripts/99_utils.R

@@ -304,3 +304,82 @@ key_state <- function(x){
   dplyr::left_join(x, key, 
                    by = c("state.name"))
 }
+
+fe_dotplot <- function(x, y_label_side = "left", cat_labels = TRUE, 
+                       x_min, x_max, plot_title){
+  # x <- gg_tn
+  # plot_title <- "Asdf"
+  # x_range   <- (x$`5%` - x$`95%`)[which.min(x$`5%` - x$`95%`)] 
+  x_range <- x_min - x_max
+  
+  if(y_label_side == "left"){
+    # tp
+    y_label_x <- x_min - 0.05
+    y_label_padding_min <- x_min - 2
+    y_label_padding_max <- x_max
+    y_label_just <- "right"
+    expand_min <- x_min - 0.6
+    expand_max <- x_max
+  }else{
+    # tn
+    y_label_x <- x_max + 0.05
+    y_label_padding_min <- x_min
+    y_label_padding_max <- x_max + 2
+    y_label_just <- "left"
+    expand_min <- x_min
+    expand_max <- x_max + 0.6
+  }
+  
+  res <- ggplot(data = x) + 
+    geom_pointrange(aes(x = pretty, y = `50%`, 
+                        ymin = `5%`, ymax = `95%`, color = signif)) + 
+    expand_limits(y = c(expand_min, expand_max)) +
+    geom_rect(ymin = y_label_padding_min, ymax = y_label_padding_max, 
+              xmin = 0, xmax = nrow(x) + 1, 
+              fill = "transparent") +
+    # y-axis labels
+    geom_text(aes(x = pretty, label = pretty, color = signif), 
+                     y = y_label_x, vjust = 0.5, hjust = y_label_just) + 
+    scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+    geom_hline(yintercept = 0) +
+    # x-axis labels
+    scale_y_continuous(breaks = seq(from = x_min, 
+                                    to  = x_max, 
+                                    by = 0.2), 
+                       labels = scales::number_format(accuracy = 0.1)) +
+    coord_flip() +
+    theme(axis.text.y = element_blank(), 
+          axis.ticks.y = element_blank(), 
+          axis.title.y = element_blank()) + 
+    facet_wrap(~category, strip.position = "left", ncol = 1, scales = "free_y",
+                 as.table = FALSE) +
+    theme(panel.spacing = unit(0, "lines"), 
+          strip.placement = "outside", 
[…]

### 2019-10-18 scripts/99_utils.R
better planel spacing

@@ -317,7 +317,7 @@ fe_dotplot <- function(x, y_label_side = "left", cat_labels = TRUE,
     y_label_padding_min <- x_min - 2
     y_label_padding_max <- x_max
     y_label_just <- "right"
-    expand_min <- x_min - 1.1
+    expand_min <- x_min - 2.2
     expand_max <- x_max
   }else{
     # tn
@@ -326,7 +326,7 @@ fe_dotplot <- function(x, y_label_side = "left", cat_labels = TRUE,
     y_label_padding_max <- x_max + 2
     y_label_just <- "left"
     expand_min <- x_min
-    expand_max <- x_max + 1.1
+    expand_max <- x_max + 2.2
   }
   
   res <- ggplot(data = x) + 

### 2019-10-18 manuscript/appendix.Rmd
more detail on land-use fig

@@
 
-```{r nlcd-versus-cdl_map, fig.cap = "Example of increasing granularity for total Ag to Ag versus pasture, to pasture versus specific crops.", warning=FALSE, echo = FALSE, eval = TRUE}
+```{r nlcd-versus-cdl_map, fig.cap = "Example of increasing granularity for total Ag to Ag versus pasture, to pasture versus specific crops.
+For illustration in this example, only corn, soybeans, and pasture are shown.
+Rather than all CDL land-use categories.", warning=FALSE, echo = FALSE, eval = TRUE}
 knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")

### 2019-10-21 tables/01_predictors.Rmd
suppress pkg loading msgs
towards predictor table cleanup

@@
 library(kableExtra)
-library(dplyr)
+suppressMessages(library(dplyr))
 library(magrittr)
+
+pred_key <- read.csv("../data/predictor_key.csv", 
+                     stringsAsFactors = FALSE)
 
@@
   mutate(q10 = quantile(value, probs = c(0.1), na.rm = TRUE),
+         q25 = quantile(value, probs = c(0.25), na.rm = TRUE),
          q50 = quantile(value, probs = c(0.5), na.rm = TRUE),
+         q75 = quantile(value, probs = c(0.75), na.rm = TRUE),
          q90 = quantile(value, probs = c(0.9), na.rm = TRUE), 
@@
          n = sum(!is.na(value), na.rm = TRUE)) %>%
-  dplyr::distinct(signif(q10, 2), signif(q50, 2), signif(q90, 2), ratio, n) %>%
+  dplyr::distinct(signif(q10, 2), signif(q25, 2), signif(q50, 2), signif(q75, 2), signif(q90, 2), ratio, n) %>%
   dplyr::select(variable, 
          q10 = `signif(q10, 2)`,
+         q25 = `signif(q25, 2)`,
          q50 = `signif(q50, 2)`,
+         q75 = `signif(q75, 2)`,
          q90 = `signif(q90, 2)`,
@@
 
+dt <- ungroup(dt)
+dt <- left_join(dt, pred_key, by = c("variable" = "var"))
+dt <- dplyr::filter(dt, !is.na(pretty))
+dt <- mutate(dt, pretty = paste0(pretty, " (", units, ")"), 
+             IQR = paste0(q25, " - ", q75))
+dt <- dplyr::select(dt, Variable = pretty, 
+                    Median = q50, IQR)
+
 knitr::kable(dt, digits = 0, format = "markdown") 

### 2019-10-22 tables/01_predictors.Rmd
pull iqr

--- 2019-06-13 tables/01_predictors.Rmd
@@
 dt <- readRDS("../data/dt.rds") %>%
-  dplyr::select(tp:clay_pct, -matches("zoneid"), -matches("pct"), cdl_vars) %>%
+  dplyr::select(tp:clay_pct, -matches("zoneid"), -matches("pct"), -matches("input"), cdl_vars) %>%
   tidyr::gather(key = "variable") %>%
@@
 
+dt <- ungroup(dt)
+dt <- left_join(dt, pred_key, by = c("variable" = "var"))
+dt <- dplyr::filter(dt, !is.na(pretty))
+
+dt <- mutate(dt, pretty = case_when(
+  nchar(units) > 0 ~ paste0(pretty, " (", units, ")"),
+  TRUE ~ pretty), 
+  IQR = paste0(q25, " - ", q75))
+dt <- dplyr::select(dt, Variable = pretty, 
+                    Median = q50, Q25 = q25, Q75 = q75)
+
 knitr::kable(dt, digits = 0, format = "markdown") 

### 2019-10-22 manuscript/appendix.Rmd
add predictor table to appendix

@@
     fig_caption: yes
+    keep_tex: yes
 header-includes: 
@@
 - \floatplacement{figure}{H}
+- \usepackage{colortbl}
 ---
 
+\arrayrulecolor{white}
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
+knitr::opts_chunk$set(echo = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 5, dev = c("pdf"))
 ```
@@
 ```
+
+\pagebreak
+
+## Predictor summary table
+
+\includegraphics[width=5in]{"../tables/01_predictors"}
 

### 2019-10-22 tables/01_predictors.Rmd
add predictor table to appendix

@@
 
+# scripts/02_aggregate_predictors.R
+dt_units <- readRDS("../data/dt_units.rds")
+
 cdl_vars <- readRDS("../data/dt.rds") %>%
@@
 dt <- readRDS("../data/dt.rds") %>%
-  dplyr::select(tp:clay_pct, -matches("zoneid"), -matches("pct"), -matches("input"), cdl_vars) %>%
+  dplyr::select(tp:clay_pct, buffer_cultivated_crops, buffer_natural,
+                -matches("zoneid"), -matches("pct"), -matches("input"), cdl_vars) %>%
   tidyr::gather(key = "variable") %>%
@@
          n) %>%
-  left_join(readRDS("../data/dt_units.rds"), by = "variable") %>%
+  left_join(dt_units, by = "variable") %>%
   dplyr::select(variable, units, everything())

### 2019-10-22 scripts/01_process_cdl.R

@@ -11,8 +11,9 @@ r_list <- list.files(cdl_path, pattern = "^\\d*.tif$",
                      include.dirs = TRUE, full.names = TRUE)
 
 cdl_summary <- function(llid){
-  # llid <- 4393
-  r <- raster(r_list[grep(paste0(llid, ".tif"), r_list)[1]])
+  # llid <- 5543
+  r <- suppressMessages(
+    raster(r_list[grep(paste0(llid, ".tif"), r_list)[1]]))
   
   cdl_table <- as.data.frame(table(values(r)), stringsAsFactors = FALSE) %>%
     mutate(code = as.integer(Var1)) %>%
@@ -100,6 +101,7 @@ for(i in seq_len(length(r_list))){
 
 res <- bind_rows(res)
 res <- dplyr::filter(res, value >=0)
+res <- dplyr::filter(res, !is.na(variable))
 res <- tidyr::spread(res, variable, value, -llid, fill = NA)
 
 write.csv(res, "data/cdl/cdl_summary.csv", row.names = FALSE)

### 2019-10-22 scripts/02_aggregate_predictors.R

@@ -104,6 +104,32 @@ saveRDS(dt, "data/dt.rds")
 write.csv(dt, "data/dt.csv", row.names = FALSE)
 # dt <- readRDS("../data/dt.rds")
 
+dt_units <- data.frame(variable = names(dt), stringsAsFactors = FALSE) %>%
+  mutate(units = case_when(
+    variable %in% names(cdl)[-1] ~ "percent",
+    variable %in% names(usgs)[-1] ~ "kg/ha",
+    grepl("_ha$", tolower(variable)) ~ "hectares",
+    grepl("_ratio$", tolower(variable)) ~ "",
+    grepl("deposition", tolower(variable)) ~ "kg/ha",
+    grepl("baseflow", tolower(variable)) ~ "",
+    grepl("_ppt_", tolower(variable)) ~ "mm/yr",
+    grepl("pct$", tolower(variable)) ~ "percent",
+    grepl("buffer", tolower(variable)) ~ "percent",
+    variable %in% "maxdepth" ~ "m",
+    # keep below line as last
+    variable %in% names(ep)[c(-1, -2, -3, -9, -10, -12)] ~ "ug/l"
+  ))
+
+dt_units <- left_join(dt_units, 
+                      dplyr::select(gssurgo_key, metric, units = agg_type), 
+                      by = c("variable" = "metric")) %>%
+  mutate(units = coalesce(units.x, units.y)) %>%
+  dplyr::select(variable, units)
+
+saveRDS(dt_units, "data/dt_units.rds")
+
+# ---- create scaled version of predictors for modelling ----
+
 cdl_vars <- dt %>%
   dplyr::select(ag:wheat, -natural, -nonnatural) %>%
   summarize_all(median, na.rm = TRUE) %>%
@@ -135,21 +161,3 @@ dt_scaled <- dt %>%
 saveRDS(dt_scaled, "data/dt_scaled.rds")
 write.csv(dt_scaled, "data/dt_scaled.csv", row.names = FALSE)
 # dt_scaled <- readRDS("data/dt_scaled.rds")
-
-dt_units <- data.frame(variable = names(dt), stringsAsFactors = FALSE) %>%
-  mutate(units = case_when(
-    variable %in% names(cdl)[-1] ~ "percent",
-    variable %in% names(usgs)[-1] ~ "kg/ha",
-    grepl("_ha$", tolower(variable)) ~ "hectares",
-    grepl("_ratio$", tolower(variable)) ~ "",
[…]

### 2019-10-22 scripts/99_make_predictor_key.R

@@ -15,7 +15,7 @@ pred_key <- data.frame(var = c(
     "N deposition", "Max depth", "Watershed-lake ratio", 
     "Baseflow", "Precipitation", 
     "Stream-buffer Ag", "Wetlands", "Ag", "Forest", "Row-crop",
-    "Buffer Ag", "Buffer natural",
+    "Buffer Ag", "Buffer Natural",
     "Non-ag", "N-fixer", "Clay", "Lake area",
     "Wetland potential", "Corn", "Manure N", 
     "Soil organic carbon", "Soybeans", "N input",

### 2019-10-22 scripts/99_utils.R

@@ -317,7 +317,7 @@ fe_dotplot <- function(x, y_label_side = "left", cat_labels = TRUE,
     y_label_padding_min <- x_min - 2
     y_label_padding_max <- x_max
     y_label_just <- "right"
-    expand_min <- x_min - 2.2
+    expand_min <- x_min - 2.4
     expand_max <- x_max
   }else{
     # tn
@@ -326,7 +326,7 @@ fe_dotplot <- function(x, y_label_side = "left", cat_labels = TRUE,
     y_label_padding_max <- x_max + 2
     y_label_just <- "left"
     expand_min <- x_min
-    expand_max <- x_max + 2.2
+    expand_max <- x_max + 2.4
   }
   
   res <- ggplot(data = x) + 

### 2019-10-23 tables/01_predictors.Rmd
add clay and fix unit labels

@@
 dt <- readRDS("../data/dt.rds") %>%
-  dplyr::select(tp:clay_pct, buffer_cultivated_crops, buffer_natural,
-                -matches("zoneid"), -matches("pct"), -matches("input"), cdl_vars) %>%
+  dplyr::select(lagoslakeid, 
+                tp:clay_pct, buffer_cultivated_crops, buffer_natural,
+                -matches("zoneid"), -matches("pct"), -matches("input"), -matches("std"), 
+                cdl_vars) %>%
+  left_join(dplyr::select(readRDS("../data/dt.rds"), 
+                          lagoslakeid, clay_pct)) %>%
+  dplyr::select(-lagoslakeid) %>%
   tidyr::gather(key = "variable") %>%

### 2019-10-23 scripts/02_aggregate_predictors.R

@@ -102,6 +102,7 @@ dt <- ep %>%
 
 saveRDS(dt, "data/dt.rds")
 write.csv(dt, "data/dt.csv", row.names = FALSE)
+# setwd("tables")
 # dt <- readRDS("../data/dt.rds")
 
 dt_units <- data.frame(variable = names(dt), stringsAsFactors = FALSE) %>%
@@ -116,6 +117,7 @@ dt_units <- data.frame(variable = names(dt), stringsAsFactors = FALSE) %>%
     grepl("pct$", tolower(variable)) ~ "percent",
     grepl("buffer", tolower(variable)) ~ "percent",
     variable %in% "maxdepth" ~ "m",
+    variable %in% "soil_org_carbon" ~ "g C/m2",
     # keep below line as last
     variable %in% names(ep)[c(-1, -2, -3, -9, -10, -12)] ~ "ug/l"
   ))

### 2019-10-23 figures/07_model-selection.Rmd
better planel spacing

@@
 ```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
-study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
+study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
 states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)

### 2019-10-23 tables/02_cdl_key.Rmd

@@
 ```{r cdl_summary}
+# setwd("tables")
 # ---- cdl summary ----
@@
 
-apply(cdl_data, 2, function(x) quantile(x, c(0.05, 0.5, 0.95), 
+dt <- apply(cdl_data, 2, function(x) quantile(x, c(0.05, 0.5, 0.95), 
                                         na.rm = TRUE)) %>%
   data.frame() %>%
-  dplyr::select(-llid) %>%
+  dplyr::select(-llid)
+
+dt %>%
   t() %>%
-  knitr::kable(caption = "CDL summary statistics", format = "latex", booktabs = TRUE) %>%
+  knitr::kable(caption = "CDL summary statistics", digits = 2,
+               format = "latex", booktabs = TRUE) %>%
   kable_styling(latex_options = c("hold_position"), full_width = FALSE) %>%

### 2019-10-25 figures/07_model-selection_10.Rmd
prep for appendix model fits

--- 2019-10-17 figures/07_model-selection.Rmd
@@
 ```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
-study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)
+# setwd("figures")
+study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
 states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
 hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)
+hu4_all       <- st_crop(hu4_all, st_transform(study_bbox, st_crs(hu4_all)))
 

### 2019-10-31 figures/07_model-selection.Rmd
autoselect best model, cleaner model diagnostics

--- 2019-10-17 figures/07_model-selection.Rmd
@@
 ```{r pre_tp_fe, out.width="3.45in", out.height="4in"}
-# lapply(re_brms, function(x) x$R2)
-# lapply(re_brms, function(x) x $formula) 
-# re_brms[[2]]$formula
-best_tp        <- 2 # 2 is best tp model with random effects
+# autoselect best model
+re_names <- unlist(lapply(re_brms, function(x) 
+  get_re_text(as.character(x$formula)[[1]])))[1:(length(re_brms)/2)]
+best_tp <- loo_compare(
+  lapply(seq_len(length(re_brms)/2), function(x) re_brms[[x]]$loo))
+best_tp <- which(re_names == row.names(best_tp)[1])
+
 fit_tp         <- re_brms[[best_tp]] 
@@
 ```{r pre_tn_fe, out.width="3.45in", out.height="4in"}
-# lapply(re_brms, function(x) x$formula) 
-# re_brms[[8]]$formula
-# brms::bayes_R2(re_brms[[8]])
+# autoselect best tn model
+re_names <- unlist(lapply(re_brms, function(x) 
+  get_re_text(as.character(x$formula)[[1]])))[seq((length(re_brms)/2) + 1,
+                                                  length(re_brms))]
+best_tn <- loo_compare(
+  lapply(seq((length(re_brms)/2) + 1, length(re_brms)), 
+         function(x) re_brms[[x]]$loo))
+best_tn <- which(re_names == row.names(best_tn)[1])
 
-best_tn        <- 8 # 11 is best tn model with random effects
 fit_tn         <- re_brms[[best_tn]] 

### 2019-10-31 tables/03_model_summary.Rmd
autoselect best model, cleaner model diagnostics

--- 2019-09-06 tables/03_model_summary.Rmd
@@
 
-r2_re <- dplyr::bind_rows(
-  lapply(re_brms, function(x) data.frame(brms::bayes_R2(x))))
-r2_re$term <- unlist(lapply(re_brms, 
-                                function(x) get_re_text(as.character(x$formula)[1])))
-r2_re$response <- c(rep("tp", nrow(r2_re) / 2), rep("tn", nrow(r2_re) / 2))
-r2_re <- dplyr::filter(r2_re, term != "rowvcropvpct")
+# filter out row crop from r2_brms
+predictors <- unlist(lapply(re_brms, function(x) get_re_text(
+  as.character(x$formula)[[1]])))
+re_brms    <- re_brms[-1 * which(predictors == "rowvcropvpct")]
+predictors <- unlist(lapply(re_brms, function(x) get_re_text(
+  as.character(x$formula)[[1]])))
 
-sort_loo <- function(x){
-  x_df       <- as.data.frame(x)
-  x_df$index <- row.names(x_df)
-  x_df$index <- as.numeric(stringr::str_extract(x_df$index, "\\d+"))
-  arrange(x_df, index)
-}
+# get responses
+response <- unlist(lapply(re_brms, function(x) get_re_response(
+  as.character(x$formula)[[1]])))
 
 loo_re <- rbind(
-  sort_loo(loo_compare(loo(re_brms[[1]]),
-                       loo(re_brms[[3]]), loo(re_brms[[4]]),
-                       loo(re_brms[[5]]), 
-                       loo(re_brms[[6]]))),
-  sort_loo(loo_compare(loo(re_brms[[7]]),
-                       loo(re_brms[[9]]), loo(re_brms[[10]]),
-                       loo(re_brms[[11]]), 
-                       loo(re_brms[[12]])))
-  ) %>%
-  arrange(index)
+  loo_compare(lapply(which(response == "tp"), function(x) re_brms[[x]]$loo)), 
+  loo_compare(lapply(which(response == "tn"), function(x) re_brms[[x]]$loo))) 
+loo_re_df            <- data.frame(loo_re)
+row.names(loo_re_df) <- NULL
+loo_re_df$term       <- row.names(loo_re)
+loo_re_df$response   <- response
 
-dt           <- r2_re
-dt$elpd_diff <- loo_re$elpd_diff
+dt <- dplyr::bind_rows(lapply(re_brms, function(x) x$R2))
+dt <- left_join(loo_re_df, dt, by = c("term", "response"))
 dt <- dplyr::select(dt, 

### 2019-10-31 scripts/03_model.R

@@ -12,52 +12,52 @@ good_hu4s <- readRDS("data/dt.rds") %>%
 dt <- dplyr::filter(dt, hu4vzoneid %in% good_hu4s$hu4_zoneid)
 
 # evaulate fixed effects
-(model_forms_fe <- list(
-  "tp" = bf(tp ~ ag),
-  "tp_nolulc" = bf(tp ~ maxdepth + iwslavratio +
-                     soilvorgvcarbon + wetlandvpotential + hu12vpptvmean + 
-                     clayvpct + hu12vbaseflowvmean +
-                     nitrogenvfertilizervuse + nitrogenvlivestockvmanure +
-                     hu4vnitrogenvatmosphericvdeposition +
-                     phosphorusvfertilizervuse +
-                     phosphorusvlivestockvmanure),
-  "tp_nuts" = bf(tp ~ nitrogenvfertilizervuse + nvinput + 
-                     nitrogenvlivestockvmanure +
-                     hu4vnitrogenvatmosphericvdeposition +
-                     phosphorusvfertilizervuse + pvinput + 
-                     phosphorusvlivestockvmanure),
-  "tp_depth" = bf(tp ~ ag + maxdepth), # lake
-  "tp_bf" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean), # transport
-  "tp_nfert" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean + 
-                    phosphorusvfertilizervuse), # sources
-  "tp_buffer" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean +
-                     phosphorusvfertilizervuse + buffervcultivatedvcrops), # buffer
-  "tn" = bf(tn ~ ag), # proxy
-  "tn_nolulc" = bf(tn ~ maxdepth + iwslavratio +
-                     soilvorgvcarbon + wetlandvpotential + hu12vpptvmean + 
-                     clayvpct + hu12vbaseflowvmean +
-                     nitrogenvfertilizervuse + nvinput + nitrogenvlivestockvmanure +
-                     hu4vnitrogenvatmosphericvdeposition +
-                     phosphorusvfertilizervuse + pvinput + 
-                     phosphorusvlivestockvmanure),
-  "tn_depth" = bf(tn ~ ag + maxdepth), # lake
[…]

### 2019-10-31 scripts/99_utils.R

@@ -444,3 +444,23 @@ get_residuals <- function(model, threshold = 0.1){
     median(model$res_med$.residual_median, na.rm = TRUE)) < threshold
   model
 }
+
+sort_loo <- function(x){
+  x_df       <- as.data.frame(x)
+  x_df$index <- row.names(x_df)
+  x_df$index <- as.numeric(stringr::str_extract(x_df$index, "\\d+"))
+  arrange(x_df, index)
+}
+
+get_re_response <- function(x){
+  trimws(strsplit(x, "\\~")[[1]][1])
+}
+
+get_r2 <- function(x){
+  # x <- re_brms[[1]]
+  res          <- data.frame(brms::bayes_R2(x))
+  res$term     <- get_re_text(as.character(x$formula)[1])
+  res$response <- get_re_response(as.character(x$formula)[1])
+  x$R2 <- res
+  x
+}

### 2019-11-01 figures/07_model-selection_40.Rmd
more file name typo fixes

--- 2019-10-31 figures/07_model-selection.Rmd
@@
 
-re_brms        <- readRDS("../data/mcmc/re_brms.rds")
+re_brms        <- readRDS("../data/mcmc/re_brms_40.rds")
 pred_key       <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
@@
 ```{r pre_tn_fe, out.width="3.45in", out.height="4in"}
-# autoselect best tn model
-re_names <- unlist(lapply(re_brms, function(x) 
-  get_re_text(as.character(x$formula)[[1]])))[seq((length(re_brms)/2) + 1,
-                                                  length(re_brms))]
-best_tn <- loo_compare(
-  lapply(seq((length(re_brms)/2) + 1, length(re_brms)), 
-         function(x) re_brms[[x]]$loo))
-best_tn <- which(re_names == row.names(best_tn)[1])
+# lapply(re_brms, function(x) x$formula) 
+# re_brms[[8]]$formula
+# brms::bayes_R2(re_brms[[8]])
 
+best_tn        <- 8 # 11 is best tn model with random effects
 fit_tn         <- re_brms[[best_tn]] 

### 2019-11-01 scripts/03_model_40.R

@@ -15,8 +15,6 @@ high_ag_llids <- dplyr::filter(dt_raw, ag > 40) %>%
   pull(lagoslakeid)
 dt <- dplyr::filter(dt, lagoslakeid %in% high_ag_llids)
 
-# evaulate spatial random effects
-# {fixed effects} + 1/ag, 1/soybeans, 1/corn
 (model_forms_re <- list(
   "tp_ag"       = bf(tp ~  
                        maxdepth + iwslavratio +
@@ -141,7 +139,7 @@ dt <- dplyr::filter(dt, lagoslakeid %in% high_ag_llids)
 re_brms <- 
   lapply(seq_along(model_forms_re), function(i) 
     get_if_not_exists(brm_fit, 
-                      paste0("data/mcmc/re_10/", names(model_forms_re)[i]), 
+                      paste0("data/mcmc/re/", names(model_forms_re)[i]), 
                       formula = model_forms_re[[i]], 
                       data = dt))
 
@@ -151,6 +149,11 @@ re_brms <- lapply(re_brms, function(x) get_re_signif(x))
 # save model residuals
 re_brms <- lapply(re_brms, function(x) get_residuals(x))
 
-saveRDS(re_brms, "data/mcmc/re_brms_10.rds")
-# unlink("data/mcmc/re_brms_10.rds")
-# re_brms <- readRDS("data/mcmc/re_brms_10.rds")
+# get r2
+re_brms <- lapply(re_brms, function(x) get_r2(x))
+
+# get loo
+re_brms <- lapply(re_brms, function(x){
+  x$loo <- loo(x, model_names = get_re_text(as.character(x$formula)[[1]])); x})
+
+saveRDS(re_brms, "data/mcmc/re_brms.rds")

### 2019-11-01 figures/07_model-selection.Rmd
indexing typo fix

@@
          function(x) re_brms[[x]]$loo))
-best_tn <- which(re_names == row.names(best_tn)[1])
+best_tn <- which(re_names == row.names(best_tn)[1]) + (length(re_brms)/2)
 

### 2019-11-04 figures/07_model-selection_40.Rmd
update model fig code for appendix dotplots

@@
 
-```{r fe}
+```{r fe_40}
 cowplot::plot_grid(
@@
 
-```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
+```{r tn_re_hu4_40, fig.width = 3.77, fig.height = 4.5}
 # setwd("figures")
@@
 
-```{r tn_re_compare, fig.height=3, fig.width=4}
+```{r tn_re_compare_40, fig.height=3, fig.width=4}
 # compare lakes in signif hu4s
@@
 
-```{r re}
+```{r re_40}
 cowplot::plot_grid(
@@
 
-```{r re-comparison, fig.width=4}
+```{r re-comparison_40, fig.width=4}
 re_global <- dplyr::filter(re_global, term != "rowvcropvpct")

### 2019-11-04 figures/07_model-selection_nolulc.Rmd
update model fig code for appendix dotplots

--- 2019-11-01 figures/07_model-selection_40.Rmd
@@
 
-re_brms        <- readRDS("../data/mcmc/re_brms_40.rds")
+re_brms        <- readRDS("../data/mcmc/fe_brms_nolulc.rds")
 pred_key       <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
@@
 
-```{r re_global}
-# tp, tn
-# ag, row_crop, pasture, corn, soybeans
-re_global          <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
-re_global$term     <- unlist(lapply(re_brms, 
-                                function(x) get_re_text(as.character(x$formula)[1])))
-re_global$response <- c(rep("tp", nrow(re_global) / 2), rep("tn", nrow(re_global) / 2))
-re_global          <- left_join(re_global, pred_key, by = c("term" = "var")) %>%
-  dplyr::select(pretty, `5%`:`95%`, term, response)
-# re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
-# group_by(re_global, response) %>%
-#   arrange(desc(`50%`))
-```
+```{r pre_tp_fe, out.width="3.45in", out.height="4in"}
+responses <- unlist(lapply(re_brms, function(x){
+  get_re_response(as.character(x$formula)[1])}))
 
-```{r pre_tp_fe, out.width="3.45in", out.height="4in"}
-# autoselect best model
-re_names <- unlist(lapply(re_brms, function(x) 
-  get_re_text(as.character(x$formula)[[1]])))[1:(length(re_brms)/2)]
-best_tp <- loo_compare(
-  lapply(seq_len(length(re_brms)/2), function(x) re_brms[[x]]$loo))
-best_tp <- which(re_names == row.names(best_tp)[1])
-
+best_tp        <- which(responses == "tp")
 fit_tp         <- re_brms[[best_tp]]
-signif_hu4_ids <- fit_tp$re_signif_ids 
-signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)
 
@@
   tidyr::spread(name, value) %>%
-  dplyr::bind_rows(
-    dplyr::select(re_global[best_tp,], -term, -response), 
-    data.frame(pretty = "", `5%` = "", `50%` = "", `95%` = "", 
-               stringsAsFactors = FALSE)
-    ) %>%
   rowwise() %>%
@@
 
-best_tn        <- 8 # 11 is best tn model with random effects
+best_tn        <- which(responses == "tn")
 fit_tn         <- re_brms[[best_tn]]
-signif_hu4_ids <- fit_tn$re_signif_ids 
-signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)
 
@@
   tidyr::spread(name, value) %>%
-  dplyr::bind_rows(
-    dplyr::select(re_global[best_tn,], -term, -response), 
-    data.frame(pretty = "", `5%` = "", `50%` = "", `95%` = "", 
-               stringsAsFactors = FALSE)
-    ) %>%
   rowwise() %>%
@@
 
-```{r fe}
+```{r fe_nolulc}
 cowplot::plot_grid(
@@
 ```
-
-```{r tp_re, fig.width=3.25, fig.height=4.5}
-fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
-fit_tp$re <- fit_tp$re %>%
-  mutate_at(vars(matches("%")), function(x) x + 
-              as.numeric(fit_tp$re_global["50%"]))
-
-gg_tp_re <- ggplot(data = fit_tp$re) +
-  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
-                      ymin = `5%`, ymax = `95%`, color = signif)) +
-  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  geom_hline(yintercept = as.numeric(fit_tp$re_global["50%"])) +
-  coord_flip() +
-  cowplot::theme_cowplot() +
-  theme(rect = element_rect(fill = "transparent")) +
-  ggtitle("TP") + xlab("Zone ID") +
-  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
-  theme(legend.position = 0)
-
-gg_tp_re
-```
-
-```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
-# setwd("figures")
-study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
-states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
-hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)
-hu4_all       <- st_crop(hu4_all, st_transform(study_bbox, st_crs(hu4_all)))
-
-# map significant random effects hu4s
-gg_hu4 <- 
-  ggplot() +
-    geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
-              color = "black", fill = "#1D9DCF") +
-    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
-    geom_sf(data = hu4_all, fill = "white", color = "black", size = 0.4) +
-    geom_sf(data = signif_hu4, color = "red", alpha = 0) +
-    # geom_text(data = coords, aes(x = x, y = y, label = ZoneID)) +   
-    coord_sf(datum = NA) +
-    theme_minimal() + 
-    theme(legend.position = "bottom", 
-          axis.title = element_blank(), 
-          legend.title = element_blank()) + 
-    scale_fill_manual(values = colors, levels(hu4$n_cat)) + 
-    guides(guide_legend(nrow = 2))  # +
-  # ggtitle("Ag sensitive regions")
-
-gg_hu4
-```
-
-```{r tn_re, fig.width=3.25, fig.height=4.5}
-# dotplot tn hu4 random effects
-fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
-fit_tn$re <- fit_tn$re %>%
-  mutate_at(vars(matches("%")), function(x) x + 
-              as.numeric(fit_tn$re_global["50%"]))
-
-gg_tn_re <- ggplot(data = fit_tn$re) +
-  geom_hline(yintercept = as.numeric(fit_tn$re_global["50%"])) +
-  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
-                      ymin = `5%`, ymax = `95%`, color = signif)) +
-  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  coord_flip() +
-  cowplot::theme_cowplot() +
-  theme(rect = element_rect(fill = "transparent")) +
-  ggtitle("TN") + xlab("Zone ID") +
-  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
-  theme(legend.position = 0)
-
-```
-
-```{r tn_re_compare, fig.height=3, fig.width=4}
-# compare lakes in signif hu4s
-dt        <- readRDS("../data/dt_scaled.rds") %>%
-  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
-  tidyr::gather(key = "key", value = "value", 
-                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4) %>%
-  group_by(key, signif_hu4) %>%
-  mutate(median = median(value, na.rm = TRUE))
-
-dt_predictors <- dplyr::filter(dt, key %in% 
-                                 c(#"tp",
-                                   "nitrogen_atmospheric_deposition",
-                                   "clay_pct")) %>%
-  dplyr::left_join(pred_key, by = c("key" = "var"))
-dt_predictors[is.na(dt_predictors$pretty), "pretty"] <- 
-  sapply(dt_predictors[is.na(dt_predictors$pretty), "key"], toupper)
-
-dt_modelled <- dplyr::filter(dt, key %in% 
-                               c("maxdepth", "tn", "soil_org_carbon",
-                                 "buffer_cultivated_crops", "corn",
-                                 "nitrogen_fertilizer_use"))
-
-gg_hist <- ggplot(data = dt_predictors) + 
-  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
-  geom_vline(aes(xintercept = median, color = signif_hu4), 
-             linetype = "dashed") +
-  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  cowplot::theme_cowplot() +
-  theme(legend.position = 0) +
-  theme(rect = element_rect(fill = "transparent"), 
-        strip.background = element_rect(fill = "transparent"), 
-        strip.text = element_text(face = "bold")) +
-  facet_wrap(~pretty) +
-  xlab("Standardized value")
-
-# line graph tn vs tp
-dt        <- readRDS("../data/dt_scaled.rds") %>%
-  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
-  tidyr::gather(key = "key", value = "value", 
-                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4, -tn) %>%
-  dplyr::filter(key %in% c(c("tp"))) %>%
-  tidyr::spread(key, value)
-
-gg_tp <- ggplot(data = dt) + 
-  geom_point(aes(x = tp, y = tn, color = signif_hu4)) +
-  geom_line(stat = "smooth", method = lm, se = FALSE, 
-            aes(x = tp, y = tn, color = signif_hu4)) +
-  scale_fill_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  cowplot::theme_cowplot() +
-  theme(legend.position = 0) + 
-  theme(rect = element_rect(fill = "transparent"))
-
-plot_grid(gg_hist, nrow = 1)
-# plot_grid(gg_hist, gg_tp, nrow = 2)
-
-lg <- lagosne_load("1.087.1")
-gg_line <- fit_tn$re %>%
-  ungroup() %>%
-  mutate(hu4vzoneid = paste0("HU4_", hu4vzoneid)) %>%
-  left_join(dplyr::select(lg$hu4.chag, 
-                          hu4_zoneid, hu4_dep_totaln_2010_mean), 
-            by = c("hu4vzoneid" = "hu4_zoneid")) %>%
-ggplot() +
-  geom_pointrange(aes(x = hu4_dep_totaln_2010_mean, y = `50%`,
-                      ymin = `5%`, ymax = `95%`, color = signif)) +
-  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  theme_cowplot() +
-  ylab("TN model, corn RE slope") + xlab("N deposition") +
-  cowplot::theme_cowplot() +
-  theme(legend.position = 0) + 
-  theme(rect = element_rect(fill = "transparent"))
-
-gg_tn_re
-
-# gg_line
-
-```
-
-```{r re}
-cowplot::plot_grid(
-cowplot::plot_grid(gg_tp_re + theme(axis.title.x = element_blank(), 
-                                     plot.margin = unit(c(0,0,0,0), "cm")),
-                   gg_tn_re + theme(axis.text.y = element_blank(), 
-                                    axis.title.y = element_blank(), 
-                                    axis.title.x = element_blank(),
-                                    plot.margin = unit(c(0,0,0,0), "cm")), 
-                   rel_widths = c(1, 0.9)), 
-ggplot(data.frame(x = 0, y = 0, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
-  geom_text(aes(x = x, y = y, label = label), size = 5) +
-  theme_void() + 
-  theme(plot.margin = unit(c(0,0,0,0), "cm")),
-ncol = 1, rel_heights = c(1, 0.05))
-
-cowplot::plot_grid(gg_tp_re, 
-                   gg_tn_re + 
-                     theme(axis.text.y = element_blank(), 
-                           axis.title.y = element_blank()) + 
-                     gghighlight(max(`50%`), n = 1), 
-                   rel_widths = c(1, 0.9))
-```
-
-```{r re-comparison, fig.width=4}
-re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
-gg_tn <- ggplot(data = dplyr::filter(re_global, response == "tn")) +
-    geom_pointrange(aes(x = term, y = `50%`, 
-                      ymin = `5%`, ymax = `95%`), color = "red") +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  expand_limits(y = c(-0.2, 0.5)) +
-  coord_flip() +
-  theme(axis.title.y = element_blank(),
-        axis.title.x = element_blank(),
-        strip.placement = "outside", 
-        strip.background = element_blank(), 
-        panel.background = element_rect(fill = "transparent", color = NA),
-        plot.background = element_rect(fill = "transparent", color = NA), 
-        panel.grid = element_blank(),
-        rect = element_rect(fill = "transparent"), 
-        axis.line = element_line(), 
-        axis.text.y = element_blank()) +
-  ggtitle("TN") + 
-  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
-
-gg_tp <- ggplot(data = dplyr::filter(re_global, response == "tp")) +
-    geom_pointrange(aes(x = term, y = `50%`, 
-                      ymin = `5%`, ymax = `95%`), color = "red") +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  expand_limits(y = c(-0.2, 0.5)) +
-  coord_flip() +
-  theme(axis.title.y = element_blank(),
-        axis.title.x = element_blank(),
-        strip.placement = "outside", 
-        strip.background = element_blank(), 
-        panel.background = element_rect(fill = "transparent", color = NA),
-        plot.background = element_rect(fill = "transparent", color = NA), 
-        panel.grid = element_blank(),
-        rect = element_rect(fill = "transparent"), 
-        axis.line = element_line()) +
-  ggtitle("TP") + 
-  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
-
-cowplot::plot_grid(
-cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.75)),
-ggplot(data.frame(x = 1, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
-  geom_text(aes(x = x, y = y, label = label)) +
-  theme_void(),
-ncol = 1, rel_heights = c(1, 0.05))
-```
-
-```{r tn_interaction, eval=FALSE}
-# lapply(re_brms, function(x) x$formula) 
-fit <- re_brms[[6]]
-fit$formula
-head(fit$res_med)
-test <- readRDS("../data/dt_scaled.rds") %>%
-  dplyr::select(lagoslakeid, hu4_nitrogen_atmospheric_deposition, corn, 
-                maxdepth, soil_org_carbon, 
-                nitrogen_fertilizer_use, buffer_cultivated_crops) %>%
-  left_join(fit$res_med)
-
-cor.test(test$.residual_median, test$hu4_nitrogen_atmospheric_deposition * test$soil_org_carbon)
-abline(0, 1)
-```
-
-```{r 07_model_selection, fig.height=3, echo=FALSE, fig.width=6, eval=FALSE}
-# gg_hu4_ndep <- ggplot() +
-#     geom_sf(data = hu4, aes(fill = hu4_nitrogen_atmospheric_deposition)) +
-#     geom_sf(data = signif_hu4, color = "red", alpha = 0) +
-#     theme_minimal() + 
-#     theme(legend.position = "bottom", 
-#           axis.title = element_blank(), 
-#           legend.title = element_blank()) +
-#   ggtitle("N Deposition")
-
-# gg_hu4_clay <- ggplot() +
-#     geom_sf(data = hu4, aes(fill = hu4_clay_pct)) +
-#     theme_minimal() + 
-#     theme(legend.position = "bottom", 
-#           axis.title = element_blank(), 
-#           legend.title = element_blank())
-
-# hist(hu4$n, n = 20)
-# table(as.character(dt$hu4_zoneid))
-
-# hist(as.vector(table(dt$hu4_zoneid)))  
-# good_hu4s <- group_by(dt, hu4_zoneid) %>% 
-#   tally() %>%
-#   dplyr::filter(n > 220)  
-# dt <- dplyr::filter(dt, hu4_zoneid %in% good_hu4s$hu4_zoneid)
-# dt <- dplyr::filter(dt, tp < 500 & chla < 150)
-
-# create alpha sample size weightings
-# dt <- left_join(dt, ungroup(count(group_by(dt, hu4_zoneid))), 
-#                 by = "hu4_zoneid") %>%
-#   dplyr::filter(n >= 3) %>%
-#   mutate(n = n / max(n, na.rm = TRUE))
-
-# join iws ag
-# dt <- left_join(dt, ungroup(dplyr::select(mutate(
-#   group_by(lg$iws.lulc, lagoslakeid), 
-#   ag_pct = sum(iws_nlcd2011_pct_81,
-#                            iws_nlcd2011_pct_82, na.rm = TRUE)), 
-#   lagoslakeid, ag_pct))
-#   )
-
-# create hu4 labels
-# centroid_xy <- sf::st_as_text(sf::st_geometry(sf::st_centroid(hu4[,"ZoneID"])))
-# extract_coords <- function(messy_centroid){
-#   res <- stringr::str_split(messy_centroid, "\\(", simplify = TRUE)[2]
-#   res <- stringr::str_split(res, "\\)", simplify = TRUE)[1]
-#   stringr::str_split(res, " ", simplify = TRUE)
-# }
-# coords <- data.frame(matrix(
-#             as.numeric(unlist(lapply(centroid_xy, extract_coords))),
-#             ncol = 2, byrow = TRUE), stringsAsFactors = FALSE)
-# names(coords) <- c("x", "y")
-# coords$ZoneID <- gsub("HU4_", "", hu4[,"ZoneID"]$ZoneID)
-# 
-# gg_smooth <- ggplot(data = dt, 
-#                     aes(x = ag_pct, y = tp, color = hu4_zoneid, alpha = n)) + 
-#     geom_line(stat = "smooth", method = lm, se = FALSE, aes(alpha = n))  +
-#     geom_smooth(aes(group = 1), method = lm, se = FALSE, 
-#                 color = "black", linetype = "dashed") +
-#     # geom_abline(slope = 1.55, intercept = -19.86, color = "red") +
-#     # scale_y_log10() + scale_x_log10() +
-#     theme(legend.position = "") +
-#     labs(x = "Ag. LULC (pct, NLCD 2011)", 
-#          y = "TP")  +
-#     scale_y_continuous(breaks = seq(0, 250, by = 50), limits = c(0, 300))
-#     
-# plot_grid(gg_hu4_n, gg_hu4_ndep)
-``` 
-```{r prediction_lines, echo=FALSE, eval=FALSE}
-# plot prediction lines
-# corn vs tn
-
-# hu4_signif$ZoneID
-dt        <- readRDS("../data/dt_scaled.rds") 
-names(dt) <- gsub("_", "v", names(dt))
-
-hu4_id               <- unique(dt$hu4vzoneid)
-conditions           <- data.frame(hu4vzoneid = hu4_id)
-rownames(conditions) <- hu4_id
-
-me_zone <- marginal_effects(fit_tn, conditions = conditions, 
-                            re_formula = NULL, method = "predict")
-plot(me_zone, points = TRUE)
-
-n_predict <- 3
-reps      <- length(unique(dt$hu4vzoneid)) / 3
-reps      <- 2
-new_data <- data.frame(
-      maxdepth = rep(modelr::seq_range(dt$maxdepth, n = n_predict), reps), 
-      soilvorgvcarbon = rep(modelr::seq_range(dt$maxdepth, n = n_predict), reps), 
-      nitrogenvfertilizervuse = rep(modelr::seq_range(dt$nitrogenvfertilizervuse, 
-                                                  n = n_predict), reps), 
-      buffervcultivatedvcrops = rep(modelr::seq_range(dt$buffervcultivatedvcrops, 
-                                                  n = n_predict), reps), 
-      corn = rep(modelr::seq_range(dt$corn, n = n_predict), reps), 
-      hu4vzoneid = unique(dt$hu4vzoneid)[1:2],
-      stringsAsFactors = FALSE)
-new_data <- expand.grid(new_data)
-
-test <- add_predicted_draws()
-
-test <- predict(fit_tn, newdata = new_data, allow_new_levels = TRUE)
-test2 <- cbind(new_data, test)
-plot(test2$corn, test2$Estimate)
-
-ran_ef <- as.data.frame(ranef(fit_tn)$hu4vzoneid) %>%
-  mutate(zoneid = rownames(.)) %>%
-  arrange(desc(Estimate.corn))
-%>%
-  dplyr::filter(zoneid == hu4_id)
-
-# plot(me_zone, ncol = 1)$agvpct # + 
-  # geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
-  #               broom::tidy(fit)$estimate[3]) + 
-  # ggtitle(hu4_id)
-
-# ggplot() + 
-#     geom_point(data = dplyr::filter(dt, 
-#                                   hu4vzoneid == hu4_id), 
-#              aes(x = agvpct, y = tp)) + 
-#   geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
-#                 broom::tidy(fit)$estimate[3]) +
-#   ylim(0, 450) + xlim(40, 90) + ggtitle(hu4_id)
-
-dplyr::filter(dt, hu4vzoneid %in% signif_hu4$ZoneID) %>%
-  modelr::data_grid(corn = modelr::seq_range(corn, n = 101), 
-                    maxdepth = modelr::seq_range(corn, n = 101), 
-                    soilvorgvcarbon = modelr::seq_range(soilvorgvcarbon, n = 101), 
-                    nitrogenvfertilizervuse = modelr::seq_range(nitrogenvfertilizervuse, n = 101), 
-                    buffervcultivatedvcrops = modelr::seq_range(buffervcultivatedvcrops, n = 101), 
-                    hu4vzoneid) %>%
-  tidybayes::add_predicted_draws(fit_tn) %>%
-  ggplot(aes(x = corn, y = tn)) +
-  stat_lineribbon(aes(y = .prediction), 
-                  .width = c(.99, .95, .8, .5), color = "#08519C") +
-  geom_point(data = dplyr::filter(dt, hu4vzoneid %in% hu4_signif$ZoneID), 
-                                  size = 2) +
-  scale_fill_brewer() +
-  facet_wrap(~ hu4vzoneid)
-
-```
-
-```{r residual_dotplot, echo=FALSE, eval=FALSE}
-suppressMessages(library(tidybayes))
-suppressMessages(library(brms))
-
-lg <- lagosne_load("1.087.1")
-
-fit <- readRDS("../data/mcmc/re/tn_corn")
-
-dt        <- readRDS("../data/dt_scaled.rds") 
-names(dt) <- gsub("_", "v", names(dt))
-
-good_hu4s <- readRDS("../data/dt.rds") %>%
-  group_by(hu4_zoneid) %>% 
-  tally() %>%
-  dplyr::filter(n >= 3)
-dt <- dplyr::filter(dt, hu4vzoneid %in% good_hu4s$hu4_zoneid)
-
-get_residuals <- function(model, threshold = 0.1){
-  # model <- fit
-  model$res_med <- dt %>%
-    add_residual_draws(model) %>%
-    group_by(lagoslakeid) %>%
-    summarize(.residual_median = median(.residual)) %>%
-    left_join(dplyr::select(lg$locus, lagoslakeid, nhd_lat, nhd_long),
-              by = "lagoslakeid")
-
-  model$res_med <- dt %>%
-    add_fitted_draws(model) %>%
-    group_by(lagoslakeid) %>%
-    summarize(.value_median = median(.value)) %>%
-    right_join(model$res_med, by = "lagoslakeid")
-
-  model$res_test <- abs(
-    median(model$res_med$.residual_median, na.rm = TRUE)) < threshold
-  model
-}
-lg <- lagosne_load("1.087.1")
-fit <- get_residuals(fit)
-
-states_lg <- state_sf()[
-  unlist(lapply(
-    st_intersects(state_sf(), LAGOSNE::coordinatize(fit$res_med)),
-    function(x) length(x) > 0)),]
-
-ggplot() + 
-  geom_sf(data = states_lg) +
-  geom_sf(data = LAGOSNE::coordinatize(fit$res_med), 
-          aes(color = .residual_median), size = 0.8) +
-  coord_sf(datum = NA) +
-  theme_void() + 
-  scale_color_gradient2() +
-  labs(color = "tn_corn \n model residuals")
-
-```
-
-```{r model_fitting, echo=FALSE, eval=FALSE}
-library(brms)
-library(tidybayes)
-library(modelr)
-
-brm_fit <- function(destfile, formula, data){
-  fit <- brm(formula = formula, data = data, 
-             family = gaussian())
-  saveRDS(fit, destfile)
-  return(fit)
-}
-
-# linear
-model_form <- bf(tp ~ ag)
-# unlink("../data/mcmc/fit0.rds")
-fit0 <- get_if_not_exists(brm_fit, "../data/mcmc/fit0.rds", formula = model_form, 
-                            data = dt)
-print("fixed effect")
-print(fit0$formula)
-
-# linear re
-model_form <- bf(tp ~ (1 + ag | hu4vzoneid))
-# unlink("../data/mcmc/fit.rds")
-fit <- get_if_not_exists(brm_fit, "../data/mcmc/fit.rds", formula = model_form, 
-                         data = dt)
-# plot(fit)
-# print(fit$formula)
-
-# linear re with focal predictor
-model_form <- bf(tp ~ maxdepth + (1 + ag | hu4vzoneid))
-# unlink("../data/mcmc/fit1.rds")
-fit1 <- get_if_not_exists(brm_fit, "../data/mcmc/fit1.rds", formula = model_form, 
-                         data = dt)
-# plot(fit1)
-# print(fit$formula)
-
-model_form <- bf(tp ~ hu12vbaseflowvmean +
-                   (1 + ag | hu4vzoneid))
-# unlink("../data/mcmc/fit2.rds")
-fit2 <- get_if_not_exists(brm_fit, "../data/mcmc/fit2.rds", formula = model_form,
-                         data = dt)
-
-# linear re with multivariate focal predictor
-model_form <- bf(tp ~ maxdepth + iwslavratio + hu12vbaseflowvmean +
-                   (1 + ag | hu4vzoneid))
-# unlink("../data/mcmc/fit3.rds")
-fit3 <- get_if_not_exists(brm_fit, "../data/mcmc/fit3.rds", formula = model_form, 
-                         data = dt)
-
-model_form <- bf(tp ~ maxdepth + iwslavratio + hu12vbaseflowvmean +
-                   (1 + soybeans | hu4vzoneid))
-# unlink("../data/mcmc/fit4.rds")
-fit4 <- get_if_not_exists(brm_fit, "../data/mcmc/fit4.rds", formula = model_form, 
-                         data = dt)
-
-model_form <- bf(tp ~ maxdepth + iwslavratio + hu12vbaseflowvmean + soybeans)
-# unlink("../data/mcmc/fit5.rds")
-fit5 <- get_if_not_exists(brm_fit, "../data/mcmc/fit5.rds", formula = model_form, 
-                         data = dt)
-
-loo_compare(loo(fit4), loo(fit5))
-
-quantile(ranef(fit4)$hu4vzoneid[,,2], c(0, 0.05, 0.5, 0.95, 1))
-plot(fit4)
-
-brms::bayes_R2(fit2)
-brms::bayes_R2(fit3)
-brms::bayes_R2(fit4)
-
-range(dt$iwslavratio)
-
-range((dt$iwslavratio - mean(dt$iwslavratio)) / sd(dt$iwslavratio))
-hist((dt$iwslavratio - mean(dt$iwslavratio)) / sd(dt$iwslavratio))
-test <- dt %>% mutate_if(function(col) is.numeric(col) & 
-                    !all(col == .$lagoslakeid) &
-                    !all(col == .$hu4vzoneid), scale)
-
-# non-linear re
-model_form <- bf(tp ~ bagvpct * ag, 
-                 bagvpct ~ 1 + 
-                   (1|hu4vzoneid), 
-                 nl = TRUE)
-fit1 <- get_if_not_exists(brm_fit, "../data/mcmc/fit1.rds", formula = model_form, 
-                          data = dt)
-# plot(fit1)
-print("random effects")
-print(fit1$formula)
-
-# non-linear re w/ 2nd level coeffs
-model_form2 <- bf(tp ~ bagvpct * ag, 
-                 bagvpct ~ 1 + phosphorusvfertilizervuse + soybeans +
-                   (1|hu4vzoneid), 
-                 nl = TRUE)
-fit_nle <- get_if_not_exists(brm_fit, "../data/mcmc/fit_nle.rds", formula = model_form2, 
-                          data = dt)
-print("re w/ 2nd level coeffs")
-print(fit_nle$formula)
-
-```
-
-```{r model_diagnostics_basics, echo=FALSE, fig.height=2, eval=FALSE}
-# get_variables(fit0)
-plot(fit0, pars = "ag")
-```
-
-```{r model_diagnostics_advanced, fig.height=4, echo=FALSE, eval=FALSE}
-# pull global distribution (lower, mean, upper)
-# get_variables(fit0)
-global_dist <- spread_draws(fit0, b_ag) %>%
-    mutate(hu4vzoneid = "global") %>%
-    group_by(hu4vzoneid) %>%
-    do(tibble::as_tibble(t(quantile(.$b_ag, c(0.05, 0.5, 0.95)))))
-
-# pull hu4 distribution (lower, mean, upper)
-hu4_dist <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
-  dplyr::filter(term == "ag") %>%
-  group_by(hu4vzoneid) %>%
-  do(tibble::as_tibble(t(quantile(.$r_hu4vzoneid, c(0.05, 0.5, 0.95))))) %>%
-  mutate(signif = case_when(`5%` > 0 ~ TRUE))
-
-all_dist <- bind_rows(global_dist, hu4_dist)
-
-ggplot(data = all_dist) +
-  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
-                      ymin = `5%`, ymax = `95%`, color = signif)) +
-  geom_hline(yintercept = 0) +
-  coord_flip()
-
-# STOP
-hu4_signif <-  LAGOSNEgis::query_gis(
-  "HU4", "ZoneID", dplyr::filter(hu4_dist, signif)$hu4vzoneid) %>% 
-  st_cast(to = "MULTIPOLYGON")
-```
-
-```{r signif_map, echo=FALSE, eval=FALSE}
-ggplot() + 
-  geom_sf(data = hu4) +
-  geom_sf(data = hu4_signif, color = "red")
-```
-
-```{r model_summary, echo=FALSE, fig.height=3, eval=FALSE}
-
-# pull 2nd level covariate distributions
-coef_signif <- bind_rows(
-  spread_draws(fit_nle, b_bagvpct_soybeans) %>%
-    do(tibble::as_tibble(t(quantile(.$b_bagvpct_soybeans, 
-                                    c(0.05, 0.5, 0.95))))), 
-  spread_draws(fit_nle, b_bagvpct_phosphorusvfertilizervuse) %>%
-    do(tibble::as_tibble(t(quantile(.$b_bagvpct_phosphorusvfertilizervuse, 
-                                    c(0.05, 0.5, 0.95)))))
-  )
-coef_signif$var <- c("soybeans", "pfertilizer")
-
-ggplot(data = coef_signif) +
-  geom_pointrange(aes(x = var, y = `50%`, ymin = `5%`, ymax = `95%`)) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  coord_flip()
-
-```
-
-```{r asdf, echo=FALSE, eval=FALSE}
-
-# plot prediction lines
-# hu4_signif$ZoneID
-hu4_id               <- hu4_signif$ZoneID[2]
-conditions           <- data.frame(hu4vzoneid = hu4_id)
-rownames(conditions) <- hu4_id
-
-me_zone <- marginal_effects(fit1, conditions = conditions, 
-                            re_formula = NULL, method = "predict")
-
-ran_ef <- as.data.frame(ranef(fit1)$hu4vzoneid) %>%
-  mutate(zoneid = rownames(.)) %>%
-  dplyr::filter(zoneid == hu4_id)
-
-# plot(me_zone, ncol = 1)$agvpct # + 
-  # geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
-  #               broom::tidy(fit)$estimate[3]) + 
-  # ggtitle(hu4_id)
-
-# ggplot() + 
-#     geom_point(data = dplyr::filter(dt, 
-#                                   hu4vzoneid == hu4_id), 
-#              aes(x = agvpct, y = tp)) + 
-#   geom_abline(intercept = 0, slope = ran_ef$Estimate.bagvpct_Intercept + 
-#                 broom::tidy(fit)$estimate[3]) +
-#   ylim(0, 450) + xlim(40, 90) + ggtitle(hu4_id)
-
-dplyr::filter(dt, hu4vzoneid %in% hu4_signif$ZoneID) %>%
-  modelr::data_grid(ag = seq_range(ag, n = 101), hu4vzoneid) %>%
-  add_predicted_draws(fit) %>%
-  ggplot(aes(x = ag, y = tp)) +
-  stat_lineribbon(aes(y = .prediction), .width = c(.99, .95, .8, .5), color = "#08519C") +
-  geom_point(data = dplyr::filter(dt, hu4vzoneid %in% hu4_signif$ZoneID), 
-                                  size = 2) +
-  scale_fill_brewer() +
-  facet_wrap(~ hu4vzoneid)
-
-```
-
-```{r not_signif, echo=FALSE, eval=FALSE}
-hu4_not_signif_n <- sample(unique(
-  pull(
-    dplyr::filter(dt, !(hu4vzoneid %in% hu4_signif$ZoneID)),
-    hu4vzoneid)), 5)
-
-dplyr::filter(dt, hu4vzoneid %in% hu4_not_signif_n) %>%
-  modelr::data_grid(ag = seq_range(ag, n = 101), hu4vzoneid) %>%
-  add_predicted_draws(fit) %>%
-  ggplot(aes(x = ag, y = tp)) +
-  stat_lineribbon(aes(y = .prediction), .width = c(.99, .95, .8, .5), color = "#08519C") +
-  geom_point(data = dplyr::filter(dt, hu4vzoneid %in% hu4_not_signif_n), 
-                                  size = 2) +
-  scale_fill_brewer() +
-  facet_wrap(~ hu4vzoneid)
-
-# loo significance testing
-loo  <- loo(fit)
-loo0 <- loo(fit0)
-loo1 <- loo(fit1)
-loo2 <- loo(fit2)
-loo_compare(loo0, loo1)
-loo_compare(loo1, loo2)
-```

### 2019-11-04 manuscript/appendix.Rmd
update model fig code for appendix dotplots

@@
 
+## Fixed effects dotplots of non lulc models and nutrient only models
+
+```{r re-comparison-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN.
+Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
+Also shown is a comparison to a zero effect (dashed line).", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/re-comparison_40-1.pdf")
+```
+
+```{r fe-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models.
+Values that do not overlap zero are shaded in red.
+Horizontal bars separate coefficients in distinct predictor categories.
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/fe_40-1.pdf")
+```
+
+```{r re-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models.
+Lines shown are 95% credible intervals with median marked by a filled circle.
+Values that do not overlap the population level estimate are shaded in red.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/re_40-1.pdf")
+```
+\pagebreak
+
+```{r fe-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models.
+Values that do not overlap zero are shaded in red.
+Horizontal bars separate coefficients in distinct predictor categories.
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance.", warning=FALSE, echo = FALSE}
+knitr::include_graphics("../figures/fe_nolulc-1.pdf")
+```
+
+\pagebreak
+
 ## Bivariate relationships among predictors and lake nutrients

### 2019-11-06 figures/07_model-selection_nolulc.Rmd
make plotting more flexible for fe appendix

@@
 (gg_tp_fe <- fe_dotplot(gg_tp, "left", cat_labels = TRUE,
-                        x_min, x_max, "TP"))
+                        x_min, x_max, "TP", tick_width = 2, tick_accuracy = 1, plot_padding = 13))
 ```
@@
 (gg_tn_fe <- fe_dotplot(gg_tn, "right", cat_labels = FALSE, 
-                        x_min, x_max, "TN"))
+                        x_min, x_max, "TN", tick_width = 2, tick_accuracy = 1, plot_padding = 13))
 ```

### 2019-11-06 scripts/99_utils.R

@@ -308,7 +308,9 @@ key_state <- function(x){
 }
 
 fe_dotplot <- function(x, y_label_side = "left", cat_labels = TRUE, 
-                       x_min, x_max, plot_title){
+                       x_min, x_max, plot_title, tick_width = 0.4, 
+                       tick_accuracy = 0.1, y_label_padding = 2,
+                       plot_padding = 2.4){
   # x <- gg_tn
   # plot_title <- "Asdf"
   x_range <- x_min - x_max
@@ -316,19 +318,19 @@ fe_dotplot <- function(x, y_label_side = "left", cat_labels = TRUE,
   if(y_label_side == "left"){
     # tp
     y_label_x <- x_min - 0.05
-    y_label_padding_min <- x_min - 2
+    y_label_padding_min <- x_min - y_label_padding
     y_label_padding_max <- x_max
     y_label_just <- "right"
-    expand_min <- x_min - 2.4
+    expand_min <- x_min - plot_padding
     expand_max <- x_max
   }else{
     # tn
     y_label_x <- x_max + 0.05
     y_label_padding_min <- x_min
-    y_label_padding_max <- x_max + 2
+    y_label_padding_max <- x_max + y_label_padding
     y_label_just <- "left"
     expand_min <- x_min
-    expand_max <- x_max + 2.4
+    expand_max <- x_max + plot_padding
   }
   
   res <- ggplot(data = x) + 
@@ -346,8 +348,8 @@ fe_dotplot <- function(x, y_label_side = "left", cat_labels = TRUE,
     # x-axis labels
     scale_y_continuous(breaks = seq(from = x_min, 
                                     to  = x_max, 
-                                    by = 0.4), 
-                       labels = scales::number_format(accuracy = 0.1)) +
+                                    by = tick_width), 
+                       labels = scales::number_format(accuracy = tick_accuracy)) +
     coord_flip() +
     theme(axis.text.y = element_blank(), 
           axis.ticks.y = element_blank(), 

### 2019-11-06 manuscript/appendix.Rmd
update appendix captions

@@
 
-```{r re-comparison-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN.
+```{r re-comparison_40-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN for lakes with greater than 40% watershed agricultural land-use.
 Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
@@
 
-```{r fe-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models.
+```{r fe_40-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models for lakes with greater than 40% watershed agricultural land-use.
 Values that do not overlap zero are shaded in red.
@@
 
-```{r re-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models.
+```{r re_40-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models for lakes with greater than 40% watershed agricultural land-use.
 Lines shown are 95% credible intervals with median marked by a filled circle.
@@
 
-```{r fe-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models.
+```{r fe_nolulc-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models without a land-use predictor.
 Values that do not overlap zero are shaded in red.

### 2019-11-06 figures/07_model-selection.Rmd
simplify hu4 layer to reduce file size, closes #23

@@
 hu4_all       <- st_crop(hu4_all, st_transform(study_bbox, st_crs(hu4_all)))
+hu4_all       <- rmapshaper::ms_simplify(hu4_all)
 

### 2019-11-06 figures/11_map.Rmd
simplify hu4 layer to reduce file size, closes #23

--- 2019-10-17 figures/11_map.Rmd
@@
 hu4_focal     <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)
+hu4_focal     <- st_crop(st_transform(hu4_focal, st_crs(study_bbox)), study_bbox) 
+hu4_focal     <- rmapshaper::ms_simplify(hu4_focal)
 

### 2019-11-12 manuscript/appendix.Rmd
better appendix subheadings
add simple scatter, replace waffle chart with bar chart

@@
 
+## Percent agriculture versus lake TP and TN
+
+```{r ag-scatter, fig.cap="Lake nutrient concentrations versus percent watershed agriculture.", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
+dt <- readRDS("../data/dt.rds")
+
+cowplot::plot_grid(
+ggplot(data = dt) + 
+  geom_point(aes(x = ag, y = tn)) + 
+  ylab("TN (ug/L)") +
+  xlab("Percent Agriculture"), 
+ggplot(data = dt) + 
+  geom_point(aes(x = ag, y = tp)) +
+  ylab("TP (ug/L)") +
+  xlab("Percent Agriculture")
+)
+
+```
+
+\pagebreak
+
 ## Response variable maps
@@
 
-Over 50 percent of our study lakes were eutrophic to hypereutrophic.
+Over 35 percent of our study lakes were eutrophic to hypereutrophic.
 
@@
 lg         <- lagosne_load("1.087.1")
-focal_hu4s <- data.frame(hu4_zoneid = paste0("HU4_", 
-                                             c("56", "57", "36", "37", "38")), 
+dt         <- readRDS("../data/dt.rds")
+focal_hu4s <- data.frame(hu4_zoneid = unique(dt$hu4_zoneid), 
                          stringsAsFactors = FALSE)
 
-dt <- readRDS("../data/dt.rds") %>%
+dt <- dt %>%
   dplyr::filter(!is.na(chla)) %>%
@@
 
-```{r trophic_state, fig.cap="Lake trophic state", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
-# waffle
-library(waffle)
+```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes in the study extent.", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
 
-total_cells <- 41.5
-dt_waffle <- dt %>% 
-  dplyr::rename(trophic_state = `Trophic State`) %>%
-  tidyr::gather(key = "key", value = "value", -trophic_state) %>%
-  dplyr::filter(key == "This Study") %>%
-  mutate(value = floor((value / 100) * total_cells)) %>%
-  arrange(trophic_state)
-# sum(dt_waffle$value)
-# add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%
+dt_bar <- tidyr::pivot_longer(dt, -`Trophic State`) %>%
+  group_by(name) %>%
+  mutate(ymax = cumsum(value),           
+         ymin = c(0, head(ymax, n = -1)))
 
-ggplot(dt_waffle,
-       aes(fill = trophic_state, values = value)) +
-  geom_waffle(color = "white", size = 3, n_rows = 4, flip = FALSE) +
-  # facet_wrap(~key, ncol = 1) +
-  scale_x_discrete(expand = c(0,0)) +
-  scale_y_discrete(expand = c(0,0)) +
-  shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
-                    shades::delta(-10)) +
-  coord_equal() +
-  theme_enhance_waffle() + 
-  theme(strip.background = element_blank(), 
-        rect = element_rect(fill = "transparent"), 
-        legend.position = "bottom", 
-        title = element_blank(), 
-        strip.text = element_text(size = 16), 
-        legend.text = element_text(size = 10), 
-        legend.key.size = unit(0.5, "line")) + 
-  guides(fill = guide_legend(nrow = 1))
+ggplot(data = dt_bar) +
+  geom_rect(aes(fill = `Trophic State`, ymax = ymax, ymin = ymin, xmin = 3, xmax = 4)) +
+  theme(axis.text.x = element_blank(), 
+        axis.ticks.x = element_blank()) +
+  ylab("Percent of Lakes") +
+  facet_wrap(~name)
 
-# highlighted regions
-test <- readRDS("../data/dt.rds") %>%
-  mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>%
-  dplyr::filter(!is.na(chla)) %>%
-  mutate(trophic_state = cut(chla, 
-                             breaks = c(-Inf, 2.6, 20, 56, Inf), 
-                             labels = c("oligotrophic", "mesotrophic", 
-                                        "eutrophic", "hypereutrophic"))) %>%
-  dplyr::select(lagoslakeid, is_focal, chla, hu4_zoneid, trophic_state) %>%
-  group_by(is_focal, trophic_state) %>%
-  count() %>%
-  tidyr::spread(trophic_state, n)
+# # waffle
+# library(waffle)
+# 
+# total_cells <- 41.5
+# dt_waffle <- dt %>% 
+#   dplyr::rename(trophic_state = `Trophic State`) %>%
+#   tidyr::gather(key = "key", value = "value", -trophic_state) %>%
+#   dplyr::filter(key == "This Study") %>%
+#   mutate(value = floor((value / 100) * total_cells)) %>%
+#   arrange(trophic_state)
+# # sum(dt_waffle$value)
+# # add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%
+# 
+# ggplot(dt_waffle,
+#        aes(fill = trophic_state, values = value)) +
+#   geom_waffle(color = "white", size = 3, n_rows = 4, flip = FALSE) +
+#   # facet_wrap(~key, ncol = 1) +
+#   scale_x_discrete(expand = c(0,0)) +
+#   scale_y_discrete(expand = c(0,0)) +
+#   shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
+#                     shades::delta(-10)) +
+#   coord_equal() +
+#   theme_enhance_waffle() + 
+#   theme(strip.background = element_blank(), 
+#         rect = element_rect(fill = "transparent"), 
+#         legend.position = "bottom", 
+#         title = element_blank(), 
+#         strip.text = element_text(size = 16), 
+#         legend.text = element_text(size = 10), 
+#         legend.key.size = unit(0.5, "line")) + 
+#   guides(fill = guide_legend(nrow = 1))
+# 
+# # highlighted regions
+# test <- readRDS("../data/dt.rds") %>%
+#   mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>%
+#   dplyr::filter(!is.na(chla)) %>%
+#   mutate(trophic_state = cut(chla, 
+#                              breaks = c(-Inf, 2.6, 20, 56, Inf), 
+#                              labels = c("oligotrophic", "mesotrophic", 
+#                                         "eutrophic", "hypereutrophic"))) %>%
+#   dplyr::select(lagoslakeid, is_focal, chla, hu4_zoneid, trophic_state) %>%
+#   group_by(is_focal, trophic_state) %>%
+#   count() %>%
+#   tidyr::spread(trophic_state, n)
 ```
@@
 
-## Fixed effects dotplots of non lulc models and nutrient only models
+## Model results when lake are restricted to > 40% watershed agriculture
 
-```{r re-comparison_40-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN for lakes with greater than 40% watershed agricultural land-use.
+```{r re-comparison_40-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN from six candidate models for lakes with greater than 40% watershed agricultural land-use.
 Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
@@
 \pagebreak
+
+## Model results when land-use predictors are excluded
 

### 2019-11-15 manuscript/appendix.Rmd
cleanup extra figures and notes

@@
 
-## Predictor summary table
+```{r nlcd-versus-cdl_map, fig.cap = "Example of increasing granularity for total Ag to Ag versus pasture, to pasture versus specific crops.
+For illustration in this example, only corn, soybeans, and pasture are shown.
+Rather than all CDL land-use categories.", warning=FALSE, echo = FALSE, eval = TRUE}
+knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
+```
 
-\includegraphics[width=5in]{"../tables/01_predictors"}
+<!-- ## Predictor summary table -->
 
-\pagebreak
+<!-- \includegraphics[width=5in]{"../tables/01_predictors"} -->
 
-## Percent agriculture versus lake TP and TN
+<!-- ```{r 03_model_summary, results='asis', warning=FALSE, echo = FALSE} -->
+<!-- knitr::kable('', col.names = NULL, caption = "Diagnostics for each model listed by regionally varying coefficient. Table is sorted by decreasing R2 and expected log predictive density.") -->
+<!-- ``` -->
 
-```{r ag-scatter, fig.cap="Lake nutrient concentrations versus percent watershed agriculture.", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
+<!-- \pagebreak -->
+
+<!-- ## Percent agriculture versus lake TP and TN -->
+
+```{r ag-scatter, fig.cap="Lake nutrient concentrations versus percent watershed agriculture.", fig.width = 5, fig.height = 3.2, warning=FALSE, message=FALSE}
 dt <- readRDS("../data/dt.rds")
@@
 
-## Response variable maps
+<!-- ## Response variable maps -->
 
-Some obvious data availability differences in New York and Wisconsin. Wisconsin has quite a bit fewer TN measurements.
+<!-- Some obvious data availability differences in New York and Wisconsin. Wisconsin has quite a bit fewer TN measurements. -->
 
-```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE, eval=TRUE}
-knitr::include_graphics("../figures/tptn_maps-1.pdf")
-```
+<!-- ```{r maps, fig.cap = "Quantile map of lake nutrients.", warning=FALSE, echo = FALSE, eval=TRUE} -->
+<!-- knitr::include_graphics("../figures/tptn_maps-1.pdf") -->
+<!-- ``` -->
 
-## Trophic state
+<!-- ## Trophic state -->
 
-Over 35 percent of our study lakes were eutrophic to hypereutrophic.
+<!-- Over 35 percent of our study lakes were eutrophic to hypereutrophic. -->
 
@@
 
+<!-- \pagebreak -->
+
+<!-- ## Model results when lake are restricted to > 40% watershed agriculture -->
+
+<!-- ```{r re-comparison_40-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN from six candidate models for lakes with greater than 40% watershed agricultural land-use.
+Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
+Also shown is a comparison to a zero effect (dashed line).", warning=FALSE, echo = FALSE} -->
+<!-- knitr::include_graphics("../figures/re-comparison_40-1.pdf") -->
+<!-- ``` -->
+
+<!-- ```{r fe_40-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models for lakes with greater than 40% watershed agricultural land-use.
+Values that do not overlap zero are shaded in red.
+Horizontal bars separate coefficients in distinct predictor categories.
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance.", warning=FALSE, echo = FALSE} -->
+<!-- knitr::include_graphics("../figures/fe_40-1.pdf") -->
+<!-- ``` -->
+
+<!-- ```{r re_40-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models for lakes with greater than 40% watershed agricultural land-use.
+Lines shown are 95% credible intervals with median marked by a filled circle.
+Values that do not overlap the population level estimate are shaded in red.", warning=FALSE, echo = FALSE} -->
+<!-- knitr::include_graphics("../figures/re_40-1.pdf") -->
+<!-- ``` -->
 \pagebreak
 
-## Model results when lake are restricted to > 40% watershed agriculture
+<!-- ## Model results when land-use predictors are excluded -->
 
-```{r re-comparison_40-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN from six candidate models for lakes with greater than 40% watershed agricultural land-use.
-Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
-Also shown is a comparison to a zero effect (dashed line).", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/re-comparison_40-1.pdf")
-```
-
-```{r fe_40-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models for lakes with greater than 40% watershed agricultural land-use.
-Values that do not overlap zero are shaded in red.
-Horizontal bars separate coefficients in distinct predictor categories.
-Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/fe_40-1.pdf")
-```
-
-```{r re_40-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models for lakes with greater than 40% watershed agricultural land-use.
-Lines shown are 95% credible intervals with median marked by a filled circle.
-Values that do not overlap the population level estimate are shaded in red.", warning=FALSE, echo = FALSE}
-knitr::include_graphics("../figures/re_40-1.pdf")
-```
-\pagebreak
-
-## Model results when land-use predictors are excluded
-
-```{r fe_nolulc-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models without a land-use predictor.
+```{r fe_nolulc-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models when land-use predictors are excluded.
 Values that do not overlap zero are shaded in red.
@@
 
-## Bivariate relationships among predictors and lake nutrients
+<!-- ## Bivariate relationships among predictors and lake nutrients -->
 
-We examined bivariate relationships between lake nutrient concentrations and predictors to determine, at least to first-approximation, the likely drivers of lake nutrients (Figure 2). 
-We found large differences between the drivers of lake phosphorus and lake nitrogen concentrations. 
-For example, max depth and baseflow had a much larger effect on P than N. Pearson’s correlation coefficients for these relationships were XX and YY respectively. 
-In contrast, watershed land-use corn cover, fertilizer inputs, and riparian buffer configuration appear to have a larger effect on N than P Pearson’s correlation coefficients for these relationships were XX, YY, and ZZ respectively.
+<!-- We examined bivariate relationships between lake nutrient concentrations and predictors to determine, at least to first-approximation, the likely drivers of lake nutrients (Figure 2).  -->
+<!-- We found large differences between the drivers of lake phosphorus and lake nitrogen concentrations.  -->
+<!-- For example, max depth and baseflow had a much larger effect on P than N. Pearson’s correlation coefficients for these relationships were XX and YY respectively.  -->
+<!-- In contrast, watershed land-use corn cover, fertilizer inputs, and riparian buffer configuration appear to have a larger effect on N than P Pearson’s correlation coefficients for these relationships were XX, YY, and ZZ respectively.
+-->
 
-```{r exploratory_dotplot, fig.cap = "Dotplots showing absolute value Pearson's correlation coefficients. Dots are colored according to predictor categories.", warning=FALSE, echo = FALSE}
+```{r exploratory_dotplot, fig.cap = "Dotplots showing absolute value Pearson's correlation coefficients. Dots are colored according to predictor categories.", warning=FALSE, echo = FALSE, eval=FALSE}
 knitr::include_graphics("../figures/dotplot-1.pdf")
@@
 
-\pagebreak
+<!-- \pagebreak -->
 
-## Correlations among predictor variables
+<!-- ## Correlations among predictor variables -->
 
-There is clearly a cluster of related predictor variables that includes most nutrient input, Ag land-use, and buffer configuration measures.
+<!-- There is clearly a cluster of related predictor variables that includes most nutrient input, Ag land-use, and buffer configuration measures. -->
 
-```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients.", warning=FALSE, echo = FALSE, eval=TRUE}
+```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients among predictor variables.", warning=FALSE, echo = FALSE, eval=TRUE}
 knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
@@
 
-\pagebreak
+<!-- \pagebreak -->
 
-## The Cropland Data Layer
+<!-- ## The Cropland Data Layer -->
 
-The National land cover database (NLCD) is more typically used in macroecology studies.
+<!-- The National land cover database (NLCD) is more typically used in macroecology studies.
 In our paper, we wanted to go beyond the coarse categories in the NLCD and test relationships with individual crops.
@@
 Instead, we aggregated all the CDL categories associated with agriculture (also pasture) and compared these values for each watershed with the corresponding NLCD estimates.
+-->
 
 ```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.
-Line is 1:1 not a  regression best fit.", warning=FALSE, echo = FALSE, eval=TRUE}
+Line is 1:1 not a  regression best fit.", warning=FALSE, echo = FALSE, eval=FALSE}
 knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
@@
 
-```{r nlcd-versus-cdl_map, fig.cap = "Example of increasing granularity for total Ag to Ag versus pasture, to pasture versus specific crops.
-For illustration in this example, only corn, soybeans, and pasture are shown.
-Rather than all CDL land-use categories.", warning=FALSE, echo = FALSE, eval = TRUE}
-knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
-```
+<!-- ## Demo of watersheds and buffer configuration -->
 
-\pagebreak
+<!-- Here are two lakes each with the same percent Ag in their watersheds (red outlines).
+However, the lake on the left (Lake Carleton) has a riparian buffer (teal outlines) with a much higher percentage of Ag relative to the lake on the right (Argyle Lake).
+-->
 
-## Demo of watersheds and buffer configuration
-
-Here are two lakes each with the same percent Ag in their watersheds (red outlines).
-However, the lake on the left (Lake Carleton) has a riparian buffer (teal outlines) with a much higher percentage of Ag relative to the lake on the right (Argyle Lake).
-
-```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE, eval = TRUE}
+```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE, eval = FALSE}
 knitr::include_graphics("../figures/satellite-1.pdf")
 ```
-
-\pagebreak
 

### 2019-11-15 manuscript/figures.Rmd
more specific fig caption
cleanup extra figures and notes

@@
 
-```{r re-comparison-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN.
+```{r 01_predictors, results='asis', warning=FALSE, echo = FALSE}
+knitr::kable('\\includegraphics[width=5in]{"../tables/01_predictors"}', col.names = NULL, caption = "Medians followed by first and third quantiles of predictor variables for 928 lakes.")
+```
+
+\pagebreak
+
+```{r re-comparison-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN from six candidate models.
 Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).

### 2019-11-18 manuscript/appendix.Rmd
add cdl key to appendix, closes #24

@@
 ```{r nlcd-versus-cdl_map, fig.cap = "Example of increasing granularity for total Ag to Ag versus pasture, to pasture versus specific crops.
-For illustration in this example, only corn, soybeans, and pasture are shown.
-Rather than all CDL land-use categories.", warning=FALSE, echo = FALSE, eval = TRUE}
+For illustration in this example, only corn, soybeans, and pasture are shown rather than all CDL land-use categories.", warning=FALSE, echo = FALSE, eval = TRUE}
 knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
 ```
+
+\pagebreak
+
+\begin{center}
+\includegraphics[width=5in]{"../tables/02_cdl_key"}
+\end{center}
+
+```{r 02_cdl_key, results='asis', warning=FALSE, echo = FALSE}
+knitr::kable('', col.names = NULL, caption = "CDL category definitions. See code supplement for listing of variables classified as 'ag'")
+```
+
+\pagebreak
 

### 2019-11-18 tables/02_cdl_key.Rmd
add cdl key to appendix, closes #24

@@
 library(dplyr)
-library(magrittr)
 
@@
 cdl_key <- read.csv("../data/cdl/cdl_key.csv", stringsAsFactors = FALSE)
+# (example_full <- cdl_key %>%
+#   group_by(category) %>%
+#   sample_n(1) %>%
+#   arrange(is_ag, code) %>%
+#   dplyr::select(-is_forage) %>%
+#   dplyr::select(category, ag = is_ag, example = description, code) %>%
+#   knitr::kable(digits = 0, format = "markdown", caption = "Example of all CDL categorizations."))
+
+(example_filtered <- 
   cdl_key %>%
-  group_by(category) %>%
-  sample_n(1) %>%
-  arrange(is_ag, code) %>%
-  dplyr::select(-is_forage) %>%
-  dplyr::select(category, ag = is_ag, example = description, code) %>%
-  knitr::kable(digits = 0, format = "markdown", caption = "Example of CDL categorizations.") 
+  dplyr::filter(category %in% c("corn", "soybeans", "forest", "wetlands", "pasture")) %>%
+  arrange(category) %>%
+  select(category, description) %>%
+  mutate_all(snakecase::to_sentence_case) %>%
+  setNames(snakecase::to_sentence_case(names(.))) %>%
+  knitr::kable(digits = 0, format = "markdown", caption = "CDL categorizations. See code supplement for listing of variables classified as 'ag'"))
+
 ```
@@
 \pagebreak
-```{r cdl_summary}
+```{r cdl_summary, eval=FALSE}
 # setwd("tables")

### 2019-11-27 figures/07_model-selection.Rmd
precompute simplified hu4s

--- 2019-11-01 figures/07_model-selection.Rmd
@@
 states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
-hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)
-hu4_all       <- st_crop(hu4_all, st_transform(study_bbox, st_crs(hu4_all)))
+hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
 

### 2019-11-27 scripts/00_get_gis.R

@@ -64,6 +64,10 @@ hu8s <- LAGOSNEgis::query_gis_(
                  paste0("HUC8 LIKE '", hu4s$HUC4, "%'", collapse = " OR ")))
 
 study_bbox   <- st_transform(st_as_sfc(st_bbox(hu4s_focal)), st_crs(study_bbox))
+hu4s_focal_simple <- rmapshaper::ms_simplify(
+  st_crop(hu4s_focal, st_transform(study_bbox, st_crs(hu4s_focal)))
+)
+
 # study_bbox   <- concaveman::concaveman(st_cast(hu4s_focal, "POINT"))
 
 # unlink("data/gis.gpkg")
@@ -75,6 +79,8 @@ st_write(states_all, gpkg_path, layer = "states_all",
 st_write(hu4s, gpkg_path, layer = "hu4s", update = TRUE,
          layer_options = c("OVERWRITE=yes"))
 st_write(hu4s_focal, gpkg_path, layer = "hu4s_focal", update = TRUE,
+         layer_options = c("OVERWRITE=yes"))
+st_write(hu4s_focal_simple, gpkg_path, layer = "hu4s_focal_simple", update = TRUE,
          layer_options = c("OVERWRITE=yes"))
 st_write(hu8s, gpkg_path, layer = "hu8s", update = TRUE,
          layer_options = c("OVERWRITE=yes"))

### 2019-11-27 manuscript/figures.Rmd
specify map printing

@@
 
-```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC) regions.", warning=FALSE, echo = FALSE}
+```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC) regions.", warning=FALSE, echo = FALSE, eval=TRUE}
 knitr::include_graphics("../figures/11_map-1.pdf")

### 2019-11-27 manuscript/appendix.Rmd
brute force explore hu variation

@@
 
-<!-- \pagebreak -->
+\pagebreak
+
+```{r eval = FALSE}
+# brute force check random slopes
+# dt <- readRDS("data/dt.rds")
+dt <- readRDS("data/dt_scaled.rds")
+
+ggplot(data = dt) +
+  geom_point(aes(x = forest, y = tp, color = hu4_zoneid))
+
+res <- list()
+for(i in unique(dt$hu4_zoneid)){
+  dt_sub <- dplyr::filter(dt, hu4_zoneid == i)
+  print(i)
+  print(nrow(dt_sub))
+  if(nrow(dt_sub) > 4){
+  res[[i]] <- data.frame(
+    n = nrow(dt_sub), 
+  estimate = broom::tidy(cor.test(
+    dt_sub$forest, dt_sub$tp
+    ))$estimate, 
+  stringsAsFactors = FALSE)
+  }else{
+    res[[i]] <- data.frame(n = NA, 
+                           estimate = NA,
+                           stringsAsFactors = FALSE)
+  }
+}
+
+res <- dplyr::bind_rows(res)
+res <- dplyr::filter(res, !is.na(n))
+
+ggplot(data = res, aes(x = estimate, y = 1, color = n)) +
+  geom_point()
+```
+
+\pagebreak
 

### 2019-11-27 figures/11_map.Rmd
red cached simple hu4s

--- 2019-10-17 figures/11_map.Rmd
@@
 states_focal  <- st_read("../data/gis.gpkg", "states_focal", quiet = TRUE)
-hu4_focal     <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)
+hu4_focal     <- st_read("../data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
 

### 2019-11-27 figures/07_model-selection.Rmd
exclude rowcrop models

@@
   dplyr::select(pretty, `5%`:`95%`, term, response)
-# re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
+re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
 # group_by(re_global, response) %>%
 #   arrange(desc(`50%`))
+re_names <- unlist(lapply(re_brms, function(x) 
+  get_re_text(as.character(x$formula)[[1]])))[1:length(re_brms)]
+re_brms <- re_brms[re_names != "rowvcropvpct"]
 ```

### 2019-12-01 figures/07_model-selection.Rmd
dont add sd to re_global

@@
 fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
-fit_tp$re <- fit_tp$re %>%
-  mutate_at(vars(matches("%")), function(x) x + 
-              as.numeric(fit_tp$re_global["50%"]))
+# fit_tp$re <- fit_tp$re %>%
+#   mutate_at(vars(matches("%")), function(x) x + 
+#               as.numeric(fit_tp$re_global["50%"]))
 

### 2019-12-01 scripts/99_utils.R

@@ -407,12 +407,12 @@ get_re_signif <- function(x){
   # tidybayes::get_variables(x)
   print(as.character(x$formula)[1])
   
-  re_global <- x %>%
-    spread_draws(!!rlang::parse_expr(
-      paste0("sd_hu4vzoneid__", get_re_text(as.character(x$formula)[1])))) %>%
-    dplyr::select(tail(names(.), 1)) %>%
-    pull(names(.)[1]) %>%
-    quantile(c(0.05, 0.5, 0.95))
+  # re_global <- x %>%
+  #   spread_draws(!!rlang::parse_expr(
+  #     paste0("sd_hu4vzoneid__", get_re_text(as.character(x$formula)[1])))) %>%
+  #   dplyr::select(tail(names(.), 1)) %>%
+  #   pull(names(.)[1]) %>%
+  #   quantile(c(0.05, 0.5, 0.95))
   
   res <- x %>%
     spread_draws(r_hu4vzoneid[hu4vzoneid,term]) %>%
@@ -421,6 +421,9 @@ get_re_signif <- function(x){
     do(tibble::as_tibble(t(quantile(.$r_hu4vzoneid, c(0.05, 0.5, 0.95))))) %>%
     mutate(signif = case_when(`5%` > 0 ~ TRUE, 
                               TRUE ~ FALSE))
+  
+  re_global <- quantile(res$`50%`, c(0.05, 0.5, 0.95))
+  
   x$re            <- res
   x$re_global     <- re_global
   x$re_signif     <- any(res$signif)

### 2019-12-02 figures/07_model-selection.Rmd
fix global effect handling

--- 2019-11-27 figures/07_model-selection.Rmd
@@
 # ag, row_crop, pasture, corn, soybeans
+
 re_global          <- dplyr::rbind_all(lapply(re_brms, function(x) x$re_global))
@@
 re_global$response <- c(rep("tp", nrow(re_global) / 2), rep("tn", nrow(re_global) / 2))
+re_vars         <- paste0("b_", re_global$term)
+re_global_l     <- lapply(seq_len(length(re_brms)), function(i){
+  spread_draws(re_brms[[i]], (!!sym(re_vars[i]))) %>% 
+    summarize(value = list(tibble::enframe(
+    quantile((!!sym(re_vars[i])), probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
+      tidyr::spread(name, value)
+})
+re_global[,1:3] <- dplyr::bind_rows(re_global_l)
+
 re_global          <- left_join(re_global, pred_key, by = c("term" = "var")) %>%
   dplyr::select(pretty, `5%`:`95%`, term, response)
-# re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
+re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
 # group_by(re_global, response) %>%
 #   arrange(desc(`50%`))
+re_names <- unlist(lapply(re_brms, function(x) 
+  get_re_text(as.character(x$formula)[[1]])))[1:length(re_brms)]
+re_brms <- re_brms[re_names != "rowvcropvpct"]
 ```
@@
   arrange(category) %>%
-  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
+  ungroup() %>% distinct(pretty, .keep_all = TRUE) %>%
+  mutate(pretty = factor(pretty, levels = pretty)) %>%
   arrange(category, pretty)
@@
 
+gg_tn_re
 ```

### 2019-12-02 figures/07_model-selection.Rmd
color and legend fixes

@@
 
-# gg_line
-
 ```
@@
 ```{r re-comparison, fig.width=4}
-re_global <- dplyr::filter(re_global, term != "rowvcropvpct")
+re_global <- dplyr::filter(re_global, term != "rowvcropvpct") %>%
+mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))
+
 gg_tn <- ggplot(data = dplyr::filter(re_global, response == "tn")) +
     geom_pointrange(aes(x = term, y = `50%`, 
-                      ymin = `5%`, ymax = `95%`), color = "red") +
+                      ymin = `5%`, ymax = `95%`, color = signif)) +
+  scale_color_manual(values = c("black", "red")) +
   geom_hline(yintercept = 0, linetype = "dashed") +
@@
         axis.line = element_line(), 
-        axis.text.y = element_blank()) +
+        axis.text.y = element_blank(), 
+        legend.position = "none") +
   ggtitle("TN") + 
@@
     geom_pointrange(aes(x = term, y = `50%`, 
-                      ymin = `5%`, ymax = `95%`), color = "red") +
+                      ymin = `5%`, ymax = `95%`, color = signif)) +
+  scale_color_manual(values = c("black", "red")) +
   geom_hline(yintercept = 0, linetype = "dashed") +
@@
         rect = element_rect(fill = "transparent"), 
-        axis.line = element_line()) +
+        axis.line = element_line(), 
+        legend.position = "none") +
   ggtitle("TP") + 

### 2019-12-03 figures/07_model-selection.Rmd
show reffects relative to global

@@
 fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
+global_offset <- dplyr::filter(re_global, 
+                               response == "tp", 
+                               term == get_re_text(
+                                 as.character(fit_tp$formula)))["50%"]
 fit_tp$re <- fit_tp$re %>%
-  mutate_at(vars(matches("%")), function(x) x +
-              as.numeric(fit_tp$re_global["50%"]))
+  mutate_at(vars(matches("%")), function(x) x + as.numeric(global_offset))
 
@@
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  geom_hline(yintercept = as.numeric(fit_tp$re_global["50%"])) +
+  geom_hline(yintercept = as.numeric(global_offset)) +
   coord_flip() +
@@
 fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
+global_offset <- dplyr::filter(re_global, 
+                               response == "tn", 
+                               term == get_re_text(
+                                 as.character(fit_tn$formula)))["50%"]
 fit_tn$re <- fit_tn$re %>%
-  mutate_at(vars(matches("%")), function(x) x + 
-              as.numeric(fit_tn$re_global["50%"]))
+  mutate_at(vars(matches("%")), function(x) x + as.numeric(global_offset))
 
 gg_tn_re <- ggplot(data = fit_tn$re) +
-  geom_hline(yintercept = as.numeric(fit_tn$re_global["50%"])) +
+  geom_hline(yintercept = as.numeric(global_offset)) +
   geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
@@
                                  c(#"tp",
-                                   "nitrogen_atmospheric_deposition",
+                                   #"nitrogen_atmospheric_deposition",
                                    "clay_pct")) %>%

### 2019-12-03 manuscript/figures.Rmd
caption fix

@@
 
-```{r tn_re_compare-1, fig.cap = "Histograms showing the distribution of Clay and N deposition for the corn sensitive regions compared to all other regions.
+```{r tn_re_compare-1, fig.cap = "Histograms showing the distribution of Clay for regions sensitive to watershed land-use (see highlighted credible intervals in Figure 4) relative to all other regions.
 Medians for each group are shown as vertical dashed lines.", warning=FALSE, echo = FALSE}

### 2019-12-03 manuscript/appendix.Rmd
explore data vs predicted plots

@@
 
+# fit_tn      <- lm(log(tn) ~ log(ag), data = dt)
+# fit_tn_pred <- data.frame(tn = fit_tn$model$`log(tn)`, 
+#                           tn_pred = fit_tn$fitted.values, 
+#                           stringsAsFactors = FALSE)
+# ggplot(data = fit_tn_pred) + 
+#   geom_point(aes(x = tn, y = tn_pred)) +
+#   geom_abline(slope = 1)
+# 
+# fit_tp      <- lm(log(tp) ~ log(ag), data = dt)
+# fit_tp_pred <- data.frame(tp = fit_tp$model$`log(tp)`, 
+#                           tp_pred = fit_tp$fitted.values, 
+#                           stringsAsFactors = FALSE)
+# ggplot(data = fit_tp_pred) + 
+#   geom_point(aes(x = tp, y = tp_pred)) +
+#   geom_abline(slope = 1)
+
 cowplot::plot_grid(
 ggplot(data = dt) + 
-  geom_point(aes(x = ag, y = tn)) + 
+  geom_point(aes(x = log(ag), y = log(tn))) + 
   ylab("TN (ug/L)") +

### 2019-12-03 figures/07_model-selection.Rmd
crop hu4s to bbox

@@
 hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
+hu4_all     <- st_crop(st_transform(hu4_all, st_crs(study_bbox)), study_bbox)
 

### 2019-12-03 figures/11_map.Rmd
crop hu4s to bbox

@@
 hu4_focal     <- st_read("../data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
+hu4_focal     <- st_crop(st_transform(hu4_focal, st_crs(study_bbox)), study_bbox)
 

### 2019-12-03 figures/07_model-selection.Rmd
add coefficient summary tables, closes #25

@@
   arrange(category, pretty)
+
+# compute posterior standard deviations
+gg_tp_sd <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
+  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
+  dplyr::filter(key != "b_Intercept") %>%
+  mutate(key = stringr::str_replace(key, "b_", "")) %>%
+  left_join(pred_key, by = c("key" = "varv")) %>%
+  group_by(pretty) %>%
+  summarize(value = list(tibble::enframe(
+    round(sd(value), 2)))) %>% unnest() %>%
+  tidyr::spread(name, value) %>%
+  setNames(c("pretty", "sd"))
+
+write.csv(
+  left_join(
+    dplyr::select(gg_tp, -matches("X")), 
+    gg_tp_sd), 
+          "../data/gg_tp.csv", row.names = FALSE)
 ```
@@
   arrange(category, pretty)
+
+# compute posterior standard deviations
+gg_tn_sd <- spread_draws(fit_tn, `b_.*`, regex = TRUE) %>%
+  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
+  dplyr::filter(key != "b_Intercept") %>%
+  mutate(key = stringr::str_replace(key, "b_", "")) %>%
+  left_join(pred_key, by = c("key" = "varv")) %>%
+  group_by(pretty) %>%
+  summarize(value = list(tibble::enframe(
+    round(sd(value), 2)))) %>% unnest() %>%
+  tidyr::spread(name, value) %>%
+  setNames(c("pretty", "sd"))
+
+write.csv(
+  left_join(
+    dplyr::select(gg_tn, -matches("X")), 
+    gg_tn_sd), 
+          "../data/gg_tn.csv", row.names = FALSE)
 ```

### 2019-12-03 manuscript/appendix.Rmd
add coefficient summary tables, closes #25

@@
   geom_point(aes(x = log(ag), y = log(tn))) + 
-  ylab("TN (ug/L)") +
-  xlab("Percent Agriculture"), 
+  ylab("log(TN) (ug/L)") +
+  xlab("log(Percent Agriculture)"), 
 ggplot(data = dt) + 
-  geom_point(aes(x = ag, y = tp)) +
-  ylab("TP (ug/L)") +
-  xlab("Percent Agriculture")
+  geom_point(aes(x = log(ag), y = log(tp))) +
+  ylab("log(TP) (ug/L)") +
+  xlab("log(Percent Agriculture)")
 )
@@
 
+```{r coef-summary-table}
+gg_tp <- read.csv("../data/gg_tp.csv", stringsAsFactors = FALSE) %>%
+  dplyr::filter(nchar(pretty) > 0) %>%
+  dplyr::select(-signif, -category) %>%
+  setNames(c("variable", "5%", "50%", "95%", "SD")) %>%
+  mutate_if(is.numeric, function(x) round(x, 2))
+gg_tn <- read.csv("../data/gg_tn.csv", stringsAsFactors = FALSE) %>%
+  dplyr::filter(nchar(pretty) > 0) %>%
+  dplyr::select(-signif, -category) %>%
+  setNames(c("variable", "5%", "50%", "95%", "SD")) %>%
+  mutate_if(is.numeric, function(x) round(x, 2))
+
+knitr::kable(gg_tp, caption = "Coefficient summaries for top-ranked TP model.")
+
+knitr::kable(gg_tn, caption = "Coefficient summaries for top-ranked TN model.")
+
+```
+
 <!-- \pagebreak -->

### 2019-12-04 manuscript/appendix.Rmd
cleanup junk files and comments

@@
 \pagebreak
-
-<!-- ## Predictor summary table -->
-
-<!-- \includegraphics[width=5in]{"../tables/01_predictors"} -->
-
-<!-- ```{r 03_model_summary, results='asis', warning=FALSE, echo = FALSE} -->
-<!-- knitr::kable('', col.names = NULL, caption = "Diagnostics for each model listed by regionally varying coefficient. Table is sorted by decreasing R2 and expected log predictive density.") -->
-<!-- ``` -->
-
-<!-- \pagebreak -->
 
@@
 
-# # waffle
-# library(waffle)
-# 
-# total_cells <- 41.5
-# dt_waffle <- dt %>% 
-#   dplyr::rename(trophic_state = `Trophic State`) %>%
-#   tidyr::gather(key = "key", value = "value", -trophic_state) %>%
-#   dplyr::filter(key == "This Study") %>%
-#   mutate(value = floor((value / 100) * total_cells)) %>%
-#   arrange(trophic_state)
-# # sum(dt_waffle$value)
-# # add_row(`Trophic State` = "oligotrophic", `key` = "This Study", `value` = 2) %>%
-# 
-# ggplot(dt_waffle,
-#        aes(fill = trophic_state, values = value)) +
-#   geom_waffle(color = "white", size = 3, n_rows = 4, flip = FALSE) +
-#   # facet_wrap(~key, ncol = 1) +
-#   scale_x_discrete(expand = c(0,0)) +
-#   scale_y_discrete(expand = c(0,0)) +
-#   shades::lightness(scale_fill_brewer(palette = "Greens", type = "seq"), 
-#                     shades::delta(-10)) +
-#   coord_equal() +
-#   theme_enhance_waffle() + 
-#   theme(strip.background = element_blank(), 
-#         rect = element_rect(fill = "transparent"), 
-#         legend.position = "bottom", 
-#         title = element_blank(), 
-#         strip.text = element_text(size = 16), 
-#         legend.text = element_text(size = 10), 
-#         legend.key.size = unit(0.5, "line")) + 
-#   guides(fill = guide_legend(nrow = 1))
-# 
-# # highlighted regions
-# test <- readRDS("../data/dt.rds") %>%
-#   mutate(is_focal = hu4_zoneid %in% focal_hu4s$hu4_zoneid) %>%
-#   dplyr::filter(!is.na(chla)) %>%
-#   mutate(trophic_state = cut(chla, 
-#                              breaks = c(-Inf, 2.6, 20, 56, Inf), 
-#                              labels = c("oligotrophic", "mesotrophic", 
-#                                         "eutrophic", "hypereutrophic"))) %>%
-#   dplyr::select(lagoslakeid, is_focal, chla, hu4_zoneid, trophic_state) %>%
-#   group_by(is_focal, trophic_state) %>%
-#   count() %>%
-#   tidyr::spread(trophic_state, n)
-```
-
-```{r predictor_maps}
-# 
 ```
@@
 
-<!-- ## Model results when lake are restricted to > 40% watershed agriculture -->
-
-<!-- ```{r re-comparison_40-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN from six candidate models for lakes with greater than 40% watershed agricultural land-use.
-Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
-Also shown is a comparison to a zero effect (dashed line).", warning=FALSE, echo = FALSE} -->
-<!-- knitr::include_graphics("../figures/re-comparison_40-1.pdf") -->
-<!-- ``` -->
-
-<!-- ```{r fe_40-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models for lakes with greater than 40% watershed agricultural land-use.
-Values that do not overlap zero are shaded in red.
-Horizontal bars separate coefficients in distinct predictor categories.
-Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance.", warning=FALSE, echo = FALSE} -->
-<!-- knitr::include_graphics("../figures/fe_40-1.pdf") -->
-<!-- ``` -->
-
-<!-- ```{r re_40-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models for lakes with greater than 40% watershed agricultural land-use.
-Lines shown are 95% credible intervals with median marked by a filled circle.
-Values that do not overlap the population level estimate are shaded in red.", warning=FALSE, echo = FALSE} -->
-<!-- knitr::include_graphics("../figures/re_40-1.pdf") -->
-<!-- ``` -->
 \pagebreak
@@
 
-```{r coef-summary-table}
+```{r coef-summary-table, eval = FALSE}
 gg_tp <- read.csv("../data/gg_tp.csv", stringsAsFactors = FALSE) %>%
@@
 
-```{r cdl_viewport, fig.cap = "CDL landuse cover in example IWS.", warning=FALSE, echo = FALSE, eval=FALSE}
-knitr::include_graphics("../figures/cdl_viewport-1.pdf")
-```
-
 ```{r hierarchical_demo, fig.cap = "A) Global (dashed line) and regional (solid lines) fits to the relationship between lake phosphorus and IWS Ag.
@@
 
-```{r cafos, fig.cap = "Livestock data from the 2007 USDA Census of Agriculture.", warning=FALSE, echo = FALSE, eval=FALSE, eval=FALSE}
-knitr::include_graphics("../figures/05_cafos-1.pdf")
-```
-
-```{r lulc_buffers, fig.cap = "Landuse cover in stream buffers.", warning=FALSE, echo = FALSE, eval=FALSE}
-knitr::include_graphics("../figures/06_lulc_buffer_demo-1.pdf")
-```
-
 ```{r county_extent, fig.cap = "Number of lake watersheds per county where lakes are limited to those with high agricultural land-use cover (greater than 40 percent) and water quality data in LAGOS from at least 3 sampling events between 2000 and 2010.", warning=FALSE, echo = FALSE, eval = FALSE}

### 2019-12-04 scripts/03_model_40.R

@@ -1,159 +1,0 @@
-# setwd("../")
-source("scripts/99_utils.R")
-
-lg        <- lagosne_load("1.087.1")
-dt_raw    <- readRDS("data/dt.rds")
-dt        <- readRDS("data/dt_scaled.rds") 
-names(dt) <- gsub("_", "v", names(dt))
-
-good_hu4s <- readRDS("data/dt.rds") %>%
-  group_by(hu4_zoneid) %>% 
-  tally() %>%
-  dplyr::filter(n >= 3)
-dt <- dplyr::filter(dt, hu4vzoneid %in% good_hu4s$hu4_zoneid)
-high_ag_llids <- dplyr::filter(dt_raw, ag > 40) %>%
-  pull(lagoslakeid)
-dt <- dplyr::filter(dt, lagoslakeid %in% high_ag_llids)
-
-(model_forms_re <- list(
-  "tp_ag"       = bf(tp ~  
-                       maxdepth + iwslavratio +
-                       soilvorgvcarbon + wetlandvpotential + hu12vpptvmean + 
-                       clayvpct + hu12vbaseflowvmean +
-                       nitrogenvfertilizervuse + nitrogenvlivestockvmanure + hu4vnitrogenvatmosphericvdeposition +
-                       phosphorusvfertilizervuse + phosphorusvlivestockvmanure +
-                       buffervcultivatedvcrops + buffervnatural + ag +
-                       (1 + ag | hu4vzoneid)),
-  "tp_forest"       = bf(tp ~  
-                           maxdepth + iwslavratio +
-                           soilvorgvcarbon + wetlandvpotential + hu12vpptvmean + 
-                           clayvpct + hu12vbaseflowvmean +
-                           nitrogenvfertilizervuse + nitrogenvlivestockvmanure + hu4vnitrogenvatmosphericvdeposition +
-                           phosphorusvfertilizervuse + phosphorusvlivestockvmanure +
-                           buffervcultivatedvcrops + buffervnatural + forest +
-                           (1 + forest | hu4vzoneid)),
-  "tp_wetlands"       = bf(tp ~  
-                             maxdepth + iwslavratio +
-                             soilvorgvcarbon + wetlandvpotential + hu12vpptvmean + 
-                             clayvpct + hu12vbaseflowvmean +
-                             nitrogenvfertilizervuse + nitrogenvlivestockvmanure + hu4vnitrogenvatmosphericvdeposition +
[…]

### 2019-12-04 scripts/99_make_modelgrid.R

@@ -1,26 +1,0 @@
-
-pred_key <- read.csv("data/predictor_key.csv", stringsAsFactors = FALSE)
-pred_key <- dplyr::filter(pred_key, !(var %in% c("lake_cultivated_crops", "wetlands", 
-                                                 "wheat", "nonag", "nitrogen_livestock_manure", 
-                                                 "lake_area_ha", "iwsla_ratio", 
-                                                 "hu12_ppt_mean",
-                                                 "nitrogen_atmospheric_deposition", 
-                                                 "phosphorus_livestock_manure", 
-                                                 "p_input")))
-
-# pick one of baseflow or precip maybe the finest resolution?
-# pick just maxdepth
-# pick _one_ of the "best" t_capacity for n/p
-# pick _one_ of the "best" nut_source for n/p
-
-n_l <- list(lake = "maxdepth", 
-            t_capacity = "soil_org_carbon", 
-            nut_source = "nitrogen_fertilizer_use", 
-            nut_prox = unique(dplyr::filter(pred_key, category == "Nutrient proxies")$var))
-p_l <- list(lake = "maxdepth", 
-            t_capacity = "hu12_baseflow_mean", 
-            nut_source = "nitrogen_fertilizer_use",  
-            nut_prox = unique(dplyr::filter(pred_key, category == "Nutrient proxies")$var))
-
-expand.grid(p_l)
-expand.grid(n_l)

### 2019-12-04 scripts/gSSURGO.R

@@ -1,1 +1,0 @@
-# ---- gsuurgo_setup ----

### 2019-12-07 figures/07_model-selection.Rmd
coordinate vertical line styles, expanded caption detail

@@
   scale_color_manual(values = c("black", "red")) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
+  geom_hline(yintercept = 0) +
   expand_limits(y = c(-0.2, 0.5)) +

### 2019-12-07 manuscript/appendix.Rmd
appendix label prefix
coordinate vertical line styles, expanded caption detail

@@
 ---
+
+\def\figurename{Figure A}
+\def\tablename{Table A}
 
@@
 ```{r nlcd-versus-cdl_map, fig.cap = "Example of increasing granularity for total Ag to Ag versus pasture, to pasture versus specific crops.
-For illustration in this example, only corn, soybeans, and pasture are shown rather than all CDL land-use categories.", warning=FALSE, echo = FALSE, eval = TRUE}
+For illustration, only corn, soybeans, and pasture are shown rather than all CDL land-use categories.", warning=FALSE, echo = FALSE, eval = TRUE}
 knitr::include_graphics("../figures/cdl_vs_nlcd-1.pdf")
@@
 
-```{r ag-scatter, fig.cap="Lake nutrient concentrations versus percent watershed agriculture.", fig.width = 5, fig.height = 3.2, warning=FALSE, message=FALSE}
+```{r ag-scatter, fig.cap="Lake nutrient concentrations plotted against percent watershed agriculture.", fig.width = 5, fig.height = 3.2, warning=FALSE, message=FALSE}
 dt <- readRDS("../data/dt.rds")
@@
 
-```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes in the study extent.", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
+```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes in the study extent.
+Trophic state based on the chlorophyll critera from Carlson (1996)", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
 
@@
 ```{r fe_nolulc-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models when land-use predictors are excluded.
+Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
+Also shown is a comparison to a zero effect (solid vertical line).
 Values that do not overlap zero are shaded in red.
 Horizontal bars separate coefficients in distinct predictor categories.
-Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance.", warning=FALSE, echo = FALSE}
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance and correspond with $\\beta$ from Equation 1.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/fe_nolulc-1.pdf")

### 2019-12-07 manuscript/figures.Rmd
coordinate vertical line styles, expanded caption detail

--- 2019-11-27 manuscript/figures.Rmd
@@
 Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
-Also shown is a comparison to a zero effect (dashed line).", warning=FALSE, echo = FALSE}
+Also shown is a comparison to a zero effect (solid vertical line).
+Values that do not overlap zero are shaded in red.
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/re-comparison-1.pdf")
@@
 ```{r fe-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models.
+Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
+Also shown is a comparison to a zero effect (solid vertical line).
 Values that do not overlap zero are shaded in red.
 Horizontal bars separate coefficients in distinct predictor categories.
-Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance.", warning=FALSE, echo = FALSE}
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance and correspond with $\\beta$ from Equation 1.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/fe-1.pdf")
@@
 ```{r re-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models.
-Lines shown are 95% credible intervals with median marked by a filled circle.
-Values that do not overlap the population level estimate are shaded in red.", warning=FALSE, echo = FALSE}
+Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
+Also shown is a comparison to a zero effect (solid vertical line.
+Values that do not overlap the population level effect are shaded in red.
+Coefficient estimates correspond with $\\gamma$ from Equation 1.", warning=FALSE, echo = FALSE}
 knitr::include_graphics("../figures/re-1.pdf")
@@
 
-```{r tn_re_compare-1, fig.cap = "Histograms showing the distribution of Clay and N deposition for the corn sensitive regions compared to all other regions.
+```{r tn_re_compare-1, fig.cap = "Histograms showing the distribution of soil clay content for regions sensitive to watershed land-use (see highlighted credible intervals in Figure 4) relative to all other regions.
 Medians for each group are shown as vertical dashed lines.", warning=FALSE, echo = FALSE}

### 2020-03-02 figures/07_model-selection.Rmd
use non standardized clay values for histogram

@@
 # compare lakes in signif hu4s
-dt        <- readRDS("../data/dt_scaled.rds") %>%
+dt <- readRDS("../data/dt.rds") %>%
   mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
@@
   mutate(median = median(value, na.rm = TRUE))
+
+dt_scaled        <- readRDS("../data/dt_scaled.rds") %>%
+  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
+  tidyr::gather(key = "key", value = "value", 
+                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4) %>%
+  group_by(key, signif_hu4) %>%
+  mutate(median_scaled = median(value, na.rm = TRUE)) %>%
+  rename(value_scaled = value)
+
+dt <- dplyr::left_join(dt, dt_scaled)
 
@@
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  labs(fill = "LULC Sensitive", color = "LULC Sensitive") +
   cowplot::theme_cowplot() +
-  theme(legend.position = 0) +
+  theme(legend.position = c(0.7, 0.8)) +
   theme(rect = element_rect(fill = "transparent"), 
         strip.background = element_rect(fill = "transparent"), 
-        strip.text = element_text(face = "bold")) +
+        strip.text = element_blank()) +
   facet_wrap(~pretty) +
-  xlab("Standardized value")
+  # xlim(c(0, 34)) + 
+  xlab("Clay (percent)")
 

### 2020-03-02 manuscript/appendix.Rmd
specify CDL year
cleanup caption grammar, remove trophic gridlines

@@
 ```{r 02_cdl_key, results='asis', warning=FALSE, echo = FALSE}
-knitr::kable('', col.names = NULL, caption = "CDL category definitions. See code supplement for listing of variables classified as 'ag'")
+knitr::kable('', col.names = NULL, caption = "Category definitions from the 2010 CDL. See code supplement for listing of variables classified as 'ag'")
 ```
@@
 
-```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes in the study extent.
+```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes from Soranno et al.
+(2017) located with our study extent.
 Trophic state based on the chlorophyll critera from Carlson (1996)", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
@@
   geom_rect(aes(fill = `Trophic State`, ymax = ymax, ymin = ymin, xmin = 3, xmax = 4)) +
+  cowplot::theme_cowplot() +
   theme(axis.text.x = element_blank(), 

### 2020-03-02 figures/07_model-selection.Rmd
use hu4 ids in re plot and order by longitude

@@
 
+hu4_key <- dplyr::select(st_drop_geometry(hu4), HUC4, ZoneID, Lon) %>%
+  mutate(hu4vzoneid = gsub("HU4_", "", ZoneID))
+fit_tp$re <- left_join(fit_tp$re, hu4_key, by = "hu4vzoneid") %>%
+  arrange(desc(Lon))
+fit_tp$re$HUC4 <- factor(fit_tp$re$HUC4, levels = fit_tp$re$HUC4)
+
 gg_tp_re <- ggplot(data = fit_tp$re) +
-  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
+  geom_pointrange(aes(x = HUC4, y = `50%`, 
                       ymin = `5%`, ymax = `95%`, color = signif)) +
@@
   theme(rect = element_rect(fill = "transparent")) +
-  ggtitle("TP") + xlab("Zone ID") +
+  ggtitle("TP") + xlab("HUC4 ID") +
   theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
@@
   mutate_at(vars(matches("%")), function(x) x + as.numeric(global_offset))
+fit_tn$re <- left_join(fit_tn$re, hu4_key, by = "hu4vzoneid") %>%
+  arrange(desc(Lon))
+fit_tn$re$HUC4 <- factor(fit_tn$re$HUC4, levels = fit_tn$re$HUC4)
 
@@
   geom_hline(yintercept = as.numeric(global_offset)) +
-  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
+  geom_pointrange(aes(x = HUC4, y = `50%`, 
                       ymin = `5%`, ymax = `95%`, color = signif)) +
@@
   theme(rect = element_rect(fill = "transparent")) +
-  ggtitle("TN") + xlab("Zone ID") +
+  ggtitle("TN") + xlab("HUC4 ID") +
   theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
@@
   cowplot::theme_cowplot() +
-  theme(legend.position = c(0.7, 0.8)) +
+  theme(legend.position = c(0.6, 0.8)) +
   theme(rect = element_rect(fill = "transparent"), 
@@
 
-```{r re}
+```{r re, fig.width=4.25}
 cowplot::plot_grid(
@@
                                     plot.margin = unit(c(0,0,0,0), "cm")), 
-                   rel_widths = c(1, 0.9)), 
+                   rel_widths = c(1, 0.8)), 
 ggplot(data.frame(x = 0, y = 0, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 

### 2020-03-02 manuscript/figures.Rmd
note huc4 ordering in caption
note that regions are huc4

@@
 
-```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC) regions.", warning=FALSE, echo = FALSE, eval=TRUE}
+```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC4) regions.", warning=FALSE, echo = FALSE, eval=TRUE}
 knitr::include_graphics("../figures/11_map-1.pdf")
@@
 ```{r re-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models.
-Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
+Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines) for individual hydrologic units (HUC4s) ordered from top to bottom (west to east).
 Also shown is a comparison to a zero effect (solid vertical line.

### 2020-03-02 manuscript/appendix.Rmd
use log10_x scale

@@
 ggplot(data = dt) + 
-  geom_point(aes(x = log(ag), y = log(tn))) + 
+  geom_point(aes(x = ag, y = tn)) + 
   ylab("log(TN) (ug/L)") +
-  xlab("log(Percent Agriculture)"), 
+  xlab("log(Percent Agriculture)") +
+  scale_x_log10() + scale_y_log10(), 
 ggplot(data = dt) + 
-  geom_point(aes(x = log(ag), y = log(tp))) +
+  geom_point(aes(x = ag, y = tp)) + 
   ylab("log(TP) (ug/L)") +
-  xlab("log(Percent Agriculture)")
+  xlab("log(Percent Agriculture)") +
+  scale_x_log10() + scale_y_log10()
 )

### 2020-03-03 figures/07_model-selection.Rmd
reorder figure 2 entries

@@
 re_global <- dplyr::filter(re_global, term != "rowvcropvpct") %>%
-mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))
+mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
+  mutate(term = factor(term, levels = c("wetlands", "forest", 
+                                        "pasture", "soybeans", "corn", "ag")))
+
+gg_tp <- ggplot(data = dplyr::filter(re_global, response == "tp")) +
+    geom_pointrange(aes(x = term, y = `50%`, 
+                      ymin = `5%`, ymax = `95%`, color = signif)) +
+  scale_color_manual(values = c("black", "red")) +
+  geom_hline(yintercept = 0) +
+  expand_limits(y = c(-0.2, 0.5)) +
+  coord_flip() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        strip.placement = "outside", 
+        strip.background = element_blank(), 
+        panel.background = element_rect(fill = "transparent", color = NA),
+        plot.background = element_rect(fill = "transparent", color = NA), 
+        panel.grid = element_blank(),
+        rect = element_rect(fill = "transparent"), 
+        axis.line = element_line(), 
+        legend.position = "none") +
+  ggtitle("TP") + 
+  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
 
@@
   ggtitle("TN") + 
-  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
-
-gg_tp <- ggplot(data = dplyr::filter(re_global, response == "tp")) +
-    geom_pointrange(aes(x = term, y = `50%`, 
-                      ymin = `5%`, ymax = `95%`, color = signif)) +
-  scale_color_manual(values = c("black", "red")) +
-  geom_hline(yintercept = 0) +
-  expand_limits(y = c(-0.2, 0.5)) +
-  coord_flip() +
-  theme(axis.title.y = element_blank(),
-        axis.title.x = element_blank(),
-        strip.placement = "outside", 
-        strip.background = element_blank(), 
-        panel.background = element_rect(fill = "transparent", color = NA),
-        plot.background = element_rect(fill = "transparent", color = NA), 
-        panel.grid = element_blank(),
-        rect = element_rect(fill = "transparent"), 
-        axis.line = element_line(), 
-        legend.position = "none") +
-  ggtitle("TP") + 
   theme(plot.title = element_text(hjust = 0.5, face = "bold"))

### 2020-03-03 figures/07_model-selection.Rmd
add category labels to figure 2

--- 2020-03-02 figures/07_model-selection.Rmd
@@
 
-```{r re-comparison, fig.width=4}
+```{r re-comparison, fig.width=5}
 re_global <- dplyr::filter(re_global, term != "rowvcropvpct") %>%
-mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))
+mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
+  mutate(term = factor(term, levels = c("wetlands", "forest", 
+                                        "soybeans", "corn", "pasture", "ag")))
+
+gg_tp <- ggplot(data = dplyr::filter(re_global, response == "tp")) +
+    geom_pointrange(aes(x = term, y = `50%`, 
+                      ymin = `5%`, ymax = `95%`, color = signif)) +
+  scale_color_manual(values = c("black", "red")) +
+  geom_hline(yintercept = 0) +
+  expand_limits(y = c(-0.2, 0.5)) +
+  coord_flip() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        strip.placement = "outside", 
+        strip.background = element_blank(), 
+        panel.background = element_rect(fill = "transparent", color = NA),
+        plot.background = element_rect(fill = "transparent", color = NA), 
+        panel.grid = element_blank(),
+        rect = element_rect(fill = "transparent"), 
+        axis.line = element_line(), 
+        legend.position = "none") +
+  ggtitle("TP") + 
+  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
+
+label_key <- data.frame(labels = c("Aggregate", "Granular", "Other"), 
+                        x = c(0, 0, 0), 
+                        y = c(0.62, 0.49, 0.37), 
+                        stringsAsFactors = FALSE)
+gg_labels <- ggplot() + geom_text(data = label_key, 
+                                        aes(x = x, y = y, label = labels), angle = 90) +
+    expand_limits(y = c(0.3, 0.7)) +
+    theme_void()
+gg_tp <- cowplot::plot_grid(gg_labels, 
+                   gg_tp, rel_widths = c(0.3, 1))
 
@@
 
-gg_tp <- ggplot(data = dplyr::filter(re_global, response == "tp")) +
-    geom_pointrange(aes(x = term, y = `50%`, 
-                      ymin = `5%`, ymax = `95%`, color = signif)) +
-  scale_color_manual(values = c("black", "red")) +
-  geom_hline(yintercept = 0) +
-  expand_limits(y = c(-0.2, 0.5)) +
-  coord_flip() +
-  theme(axis.title.y = element_blank(),
-        axis.title.x = element_blank(),
-        strip.placement = "outside", 
-        strip.background = element_blank(), 
-        panel.background = element_rect(fill = "transparent", color = NA),
-        plot.background = element_rect(fill = "transparent", color = NA), 
-        panel.grid = element_blank(),
-        rect = element_rect(fill = "transparent"), 
-        axis.line = element_line(), 
-        legend.position = "none") +
-  ggtitle("TP") + 
-  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
-
 cowplot::plot_grid(
-cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.75)),
+cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.6)),
 ggplot(data.frame(x = 1, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 

### 2020-03-03 manuscript/figures.Rmd
describe elpd in table caption

@@
 knitr::kable('\\includegraphics[width=5in]{"../tables/03_model_summary"}', col.names = NULL, caption = "Diagnostics for each model listed by regionally varying coefficient.
-Table is sorted by decreasing R2 and expected log predictive density.")
+Table is sorted by decreasing $R^2$ and expected log predictive density (ELPD).
+ELPD has a similar interpretation to information criterion measures like AIC.
+Typically models are considered to be different if they are separated by an AIC value of greater than 2, which is equivalent to an ELPD value of -1.")
 ```

### 2020-03-03 manuscript/figures.Rmd
add granularity column to table 1

@@
 ```{r 01_predictors, results='asis', warning=FALSE, echo = FALSE}
-knitr::kable('\\includegraphics[width=5in]{"../tables/01_predictors"}', col.names = NULL, caption = "Medians followed by first and third quantiles of predictor variables for 928 lakes.")
+knitr::kable('\\includegraphics[width=5in]{"../tables/01_predictors"}', col.names = NULL, caption = "Medians followed by first and third quantiles of predictor variables for 928 lakes.
+Also shown is whether each predictor is defined as an aggregate or granular measure of agriculture.")
 ```

### 2020-03-03 tables/01_predictors.Rmd
add granularity column to table 1

@@
   IQR = paste0(q25, " - ", q75))
-dt <- dplyr::select(dt, Variable = pretty, 
-                    Median = q50, Q25 = q25, Q75 = q75)
+dt <- dplyr::select(dt, Variable = pretty, Granularity = granularity,
+                    Median = q50, Q25 = q25, Q75 = q75, category) 
+dt <- dt %>%
+  mutate(Granularity = factor(Granularity, levels = c("Other", "Granular", "Aggregate")), 
+         category = factor(category, levels = c("Land-use cover", "Buffer configuration", "Nutrient inputs", "Nutrient transport", "Lake"))) %>%
+  arrange(desc(Granularity), category) %>%
+  dplyr::select(-category)
 
+unfill_vec <- function(x) {
+  # https://github.com/tidyverse/tidyr/issues/250#issuecomment-344984802
+  same <- x == dplyr::lag(x)
+  ifelse(!is.na(same) & same, NA, x)
+}
+dt$Granularity <- unfill_vec(as.character(dt$Granularity))
+
+options(knitr.kable.NA = " - ")
 knitr::kable(dt, digits = 0, format = "markdown") 

### 2020-03-03 scripts/99_make_predictor_key.R

@@ -22,6 +22,16 @@ pred_key <- data.frame(var = c(
     "Fertilizer N", "Fertilizer P", "P input", 
     "N Deposition",
     "Manure P", "Wheat", "Pasture", "Row-crop Ag"),
+  granularity = c("Other", "Other", "Other", 
+                  "Other", "Other", 
+                  "Granular", "Other", "Aggregate", "Other", "Aggregate",
+                  "Granular", "Granular", 
+                  "Aggregate", "Granular", "Other", "Other", 
+                  "Other", "Granular", "Granular", 
+                  "Other", "Granular", "Granular", 
+                  "Granular", "Granular", "Granular",
+                  "Granular", 
+                  "Granular", "Granular", "Aggregate", "Aggregate"),
                       category = c(
   "Nutrient inputs", "Lake", "Lake", 
   "Nutrient transport", "Nutrient transport", 

### 2020-03-04 figures/08_exploratory_dotplot.Rmd
rm tn and tp from heatmap, closes #16
cleanup correlation heatmap

@@
 dt_sub   <-  dt %>% 
-  dplyr::select(-lagoslakeid) %>%
+  dplyr::select(names(.)[names(.) %in% c(pred_key$var, "tn", "tp")]) %>%
+  # dplyr::select(-lagoslakeid) %>%
   # dplyr::select(tp, tn, lake_area_ha:wheat, 
@@
 dt_tp_hmap            <- dt_tp_hmap %>%
-  dplyr::select(-rowname) %>%
-  mutate_all(abs)
+  dplyr::select(-rowname) # %>%
+  # mutate_all(abs)
 row.names(dt_tp_hmap) <- dt_tp_rows
@@
 pretty_names <- pretty_names[!is.na(pretty_names)]
-row.names(dt_tp_hmap)[which(!is.na(match(row.names(dt_tp_hmap), pred_key$var)))] <- 
-  pretty_names
+row.names(dt_tp_hmap)[
+  which(!is.na(match(row.names(dt_tp_hmap), pred_key$var)))] <- pretty_names
+
+# rm tp and tn also row crop ag and stream-buffer ag
+dt_tp_hmap <- dplyr::select(dt_tp_hmap, -tp, -tn, 
+                            -`Row-crop Ag`, -`Stream-buffer Ag`)
+dt_tp_hmap <- dt_tp_hmap[!(row.names(dt_tp_hmap) %in% 
+                              c("tp", "tn", "Row-crop Ag", "Stream-buffer Ag")),]
+
+# manually sort according to the clustering shown when cluster_rows/cols TRUE
+# see jsta/jsta #15 
+rowcol_order <- c("Manure N", "Manure P", "Fertilizer N", 
+                  "Fertilizer P", "N input", "P input", 
+                  "Max depth", "Watershed-lake ratio",
+                  "N deposition", "Baseflow", "Clay",
+                  "Wetlands", "Pasture", "Precipitation",
+                  "Soil organic carbon", "Wetland potential",
+                  "Buffer natural", "Buffer Ag", "Ag", 
+                  "Soybeans", "Forest", "Corn")
+dt_tp_hmap <- dt_tp_hmap[match(rowcol_order, row.names(dt_tp_hmap)),]
+dt_tp_hmap <- dt_tp_hmap[,match(rowcol_order, names(dt_tp_hmap))]
+
+dt_tp_hmap_abs <- mutate_all(dt_tp_hmap, abs) %>%
+  data.frame()
+row.names(dt_tp_hmap_abs) <- rowcol_order
+pheatmap::pheatmap(
+  t(dt_tp_hmap_abs),
+  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
+                                            "Reds"))(100),
+  cluster_cols = TRUE, cluster_rows = TRUE,
+  na.col = "grey",
+  cellheight = 7)
 
@@
   t(dt_tp_hmap),
-  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
-                                            "Reds"))(100),
+  # color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
+  #                                          "Reds"))(100),
   cluster_cols = TRUE, cluster_rows = TRUE,

### 2020-03-04 scripts/99_make_predictor_key.R

@@ -15,7 +15,7 @@ pred_key <- data.frame(var = c(
     "N deposition", "Max depth", "Watershed-lake ratio", 
     "Baseflow", "Precipitation", 
     "Stream-buffer Ag", "Wetlands", "Ag", "Forest", "Row-crop",
-    "Buffer Ag", "Buffer Natural",
+    "Buffer Ag", "Buffer natural",
     "Non-ag", "N-fixer", "Clay", "Lake area",
     "Wetland potential", "Corn", "Manure N", 
     "Soil organic carbon", "Soybeans", "N input",

### 2020-03-04 figures/08_exploratory_dotplot.Rmd
avoid label and cluster tree cutoff

@@
   na.col = "grey",
-  cellheight = 7)
+  cellheight = 7, cellwidth = 7)
 ```

### 2020-03-04 figures/08_exploratory_dotplot.Rmd
use non abs correlation values

--- 2020-03-04 figures/08_exploratory_dotplot.Rmd
@@
 
-dt_tp_hmap_abs <- mutate_all(dt_tp_hmap, abs) %>%
-  data.frame()
-row.names(dt_tp_hmap_abs) <- rowcol_order
-pheatmap::pheatmap(
-  t(dt_tp_hmap_abs),
-  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
-                                            "Reds"))(100),
-  cluster_cols = TRUE, cluster_rows = TRUE,
-  na.col = "grey",
-  cellheight = 7)
+# dt_tp_hmap_abs <- mutate_all(dt_tp_hmap, abs) %>%
+#   data.frame()
+# row.names(dt_tp_hmap_abs) <- rowcol_order
+# pheatmap::pheatmap(
+#   t(dt_tp_hmap_abs),
+#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
+#                                             "Reds"))(100),
+#   cluster_cols = TRUE, cluster_rows = TRUE,
+#   na.col = "grey",
+#   cellheight = 7)
 
@@
   na.col = "grey",
-  cellheight = 7)
+  cellheight = 8, cellwidth = 8, treeheight_col = 20, treeheight_row = 40)
 ```

### 2020-03-04 manuscript/appendix.Rmd
describe grey diagonals in heatmap

@@
 
-```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients among predictor variables.", warning=FALSE, echo = FALSE, eval=TRUE}
+```{r exploratory_heatmap, fig.cap = "Heatmap showing Pearson correlation coefficients among predictor variables.
+Grey cells denote correlation matrix diagonals.", warning=FALSE, echo = FALSE, eval=TRUE}
 knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")

### 2020-03-04 figures/07_model-selection_nolulc.Rmd
fix cutoff labels

@@
 
-```{r fe_nolulc}
+```{r fe_nolulc, fig.width=7.5}
 cowplot::plot_grid(

### 2020-03-04 manuscript/appendix.Rmd
annotate equations on scatter plot

@@
 
-# fit_tn      <- lm(log(tn) ~ log(ag), data = dt)
-# fit_tn_pred <- data.frame(tn = fit_tn$model$`log(tn)`, 
-#                           tn_pred = fit_tn$fitted.values, 
-#                           stringsAsFactors = FALSE)
+fit_tn      <- lm(log(tn) ~ log(ag), data = dt)
+fit_tn_pred <- data.frame(tn = fit_tn$model$`log(tn)`,
+                          tn_pred = fit_tn$fitted.values,
+                          ag = fit_tn$model$`log(ag)`,
+                          stringsAsFactors = FALSE)
 # ggplot(data = fit_tn_pred) + 
@@
 # 
-# fit_tp      <- lm(log(tp) ~ log(ag), data = dt)
-# fit_tp_pred <- data.frame(tp = fit_tp$model$`log(tp)`, 
-#                           tp_pred = fit_tp$fitted.values, 
-#                           stringsAsFactors = FALSE)
+fit_tp      <- lm(log(tp) ~ log(ag), data = dt)
+fit_tp_pred <- data.frame(tp = fit_tp$model$`log(tp)`,
+                          tp_pred = fit_tp$fitted.values,
+                          ag = fit_tp$model$`log(ag)`,
+                          stringsAsFactors = FALSE)
 # ggplot(data = fit_tp_pred) + 
@@
 
+get_formula <- function(response_var, model){
+  # https://stackoverflow.com/a/26640226/3362993
+  res <- as.formula(
+    paste0(response_var, " ~ ", round(coefficients(model)[1],2), "", 
+      paste(sprintf(" %+.2f*%s ", 
+                    coefficients(model)[-1],  
+                    names(coefficients(model)[-1])), 
+            collapse="")
+    )
+  )
+  paste(res[2], res[3], sep=' ~ ')
+}
+
 cowplot::plot_grid(
@@
   geom_point(aes(x = ag, y = tn)) + 
+  geom_line(data = fit_tn_pred, aes(x = exp(ag), y = exp(tn_pred)), 
+             color = "red") +
+  annotate("text", x = 14, y = 12000, label = get_formula("log(tn)", fit_tn), 
+           size = 2) +
   ylab("log(TN) (ug/L)") +
   xlab("log(Percent Agriculture)") +
-  scale_x_log10() + scale_y_log10(), 
+  scale_x_log10() + scale_y_log10() +
+  theme_cowplot(), 
 ggplot(data = dt) + 
   geom_point(aes(x = ag, y = tp)) + 
+    geom_line(data = fit_tp_pred, aes(x = exp(ag), y = exp(tp_pred)), 
+             color = "red") +
+  annotate("text", x = 14, y = 900, label = get_formula("log(tp)", fit_tp), 
+           size = 2) +
   ylab("log(TP) (ug/L)") +
   xlab("log(Percent Agriculture)") +
-  scale_x_log10() + scale_y_log10()
+  scale_x_log10() + scale_y_log10() +
+  theme_cowplot()
 )

### 2020-03-04 manuscript/appendix.Rmd
resize scatter plot

@@
 
-```{r ag-scatter, fig.cap="Lake nutrient concentrations plotted against percent watershed agriculture.", fig.width = 5, fig.height = 3.2, warning=FALSE, message=FALSE}
+```{r ag-scatter, fig.cap="Lake nutrient concentrations plotted against percent watershed agriculture.", fig.width = 5.5, fig.height = 3, warning=FALSE, message=FALSE}
 dt <- readRDS("../data/dt.rds")

### 2020-03-04 manuscript/figures.Rmd
fix double caption of table 2

--- 2020-03-03 manuscript/figures.Rmd
@@
 - \usepackage{colortbl}
+- \usepackage{caption}
+- \usepackage{float}
 ---
@@
 knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6, dev = c("pdf"))
+knitr::opts_chunk$set(fig.pos = 'H')
 ```
@@
 
-```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC4) regions.", warning=FALSE, echo = FALSE, eval=TRUE}
+```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC4) regions.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
 knitr::include_graphics("../figures/11_map-1.pdf")
@@
 
-```{r 01_predictors, results='asis', warning=FALSE, echo = FALSE}
-knitr::kable('\\includegraphics[width=5in]{"../tables/01_predictors"}', col.names = NULL, caption = "Medians followed by first and third quantiles of predictor variables for 928 lakes.")
-```
-
-\pagebreak
+\begin{center}
+\captionof{table}{Medians followed by first and third quantiles of predictor variables for 928 lakes.
+Also shown is whether each predictor is defined as an aggregate or granular measure of agriculture.}
+\includegraphics{../tables/01_predictors}
+\end{center}
 
 ```{r re-comparison-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN from six candidate models.
-Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
+Values shown are posterior medians (filled circles) and 95\\% credible intervals (solid lines).
 Also shown is a comparison to a zero effect (solid vertical line).
 Values that do not overlap zero are shaded in red.
-Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance.", warning=FALSE, echo = FALSE}
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance.", warning=FALSE, echo = FALSE, out.extra='', fig.align='center'}
 knitr::include_graphics("../figures/re-comparison-1.pdf")
@@
 
-```{r 03_model_summary, results='asis', warning=FALSE, echo = FALSE}
-knitr::kable('\\includegraphics[width=5in]{"../tables/03_model_summary"}', col.names = NULL, caption = "Diagnostics for each model listed by regionally varying coefficient.
+\begin{center}
+\captionof{table}{Diagnostics for each model listed by regionally varying coefficient.
 Table is sorted by decreasing $R^2$ and expected log predictive density (ELPD).
 ELPD has a similar interpretation to information criterion measures like AIC.
-Typically models are considered to be different if they are separated by an AIC value of greater than 2, which is equivalent to an ELPD value of -1.")
-```
+Typically models are considered to be different if they are separated by an AIC value of greater than 2, which is equivalent to an ELPD value of -1.}
+\includegraphics{../tables/03_model_summary}
+\end{center}
 
 ```{r fe-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models.
-Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).
+Values shown are posterior medians (filled circles) and 95\\% credible intervals (solid lines).
 Also shown is a comparison to a zero effect (solid vertical line).
@@
 Horizontal bars separate coefficients in distinct predictor categories.
-Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance and correspond with $\\beta$ from Equation 1.", warning=FALSE, echo = FALSE}
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance and correspond with $\\beta$ from Equation 1.", warning=FALSE, echo = FALSE, out.extra=''}
 knitr::include_graphics("../figures/fe-1.pdf")
@@
 ```{r re-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models.
-Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines) for individual hydrologic units (HUC4s) ordered from top to bottom (west to east).
+Values shown are posterior medians (filled circles) and 95\\% credible intervals (solid lines) for individual hydrologic units (HUC4s) ordered from top to bottom (west to east).
 Also shown is a comparison to a zero effect (solid vertical line.
 Values that do not overlap the population level effect are shaded in red.
-Coefficient estimates correspond with $\\gamma$ from Equation 1.", warning=FALSE, echo = FALSE}
+Coefficient estimates correspond with $\\gamma$ from Equation 1.", warning=FALSE, echo = FALSE, out.extra='', fig.align='center'}
 knitr::include_graphics("../figures/re-1.pdf")
@@
 
-```{r tn_re_hu4-1, fig.cap = "Location of hydrologic regions sensitive to watershed land-use cover corresponding to highlighted credible intervals in Figure 4.", warning=FALSE, echo = FALSE}
+```{r tn_re_hu4-1, fig.cap = "Location of hydrologic regions sensitive to watershed land-use cover corresponding to highlighted credible intervals in Figure 4.", warning=FALSE, echo = FALSE, out.extra='', fig.align='center'}
 knitr::include_graphics("../figures/tn_re_hu4-1.pdf")
@@
 ```{r tn_re_compare-1, fig.cap = "Histograms showing the distribution of soil clay content for regions sensitive to watershed land-use (see highlighted credible intervals in Figure 4) relative to all other regions.
-Medians for each group are shown as vertical dashed lines.", warning=FALSE, echo = FALSE}
+Medians for each group are shown as vertical dashed lines.", warning=FALSE, echo = FALSE, out.extra='', fig.align='center'}
 knitr::include_graphics("../figures/tn_re_compare-1.pdf")

### 2020-03-05 manuscript/figures.Rmd
adjust figure captions

@@
 
-```{r re-comparison-1, fig.cap = "Population level effect of watershed land-use cover on lake TP and TN from six candidate models.
+```{r re-comparison-1, fig.cap = "Population level estimates (i.e.
+slopes, $\\mu_\\gamma$) for the effect of watershed land-use cover on lake TP and TN from six candidate models.
 Values shown are posterior medians (filled circles) and 95\\% credible intervals (solid lines).
@@
 
-```{r fe-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models.
+```{r fe-1, fig.cap = "Global (fixed effect) coefficient values ($\\beta$, for all non-LULC predictors) and population level estimates for the effect of watershed land-use ($\\mu_\\gamma$, LULC) on lake TP and TN for each respective top-ranked model.
+Note that the values for LULC here are identical to their corresponding values in Figure 2.
 Values shown are posterior medians (filled circles) and 95\\% credible intervals (solid lines).
@@
 Horizontal bars separate coefficients in distinct predictor categories.
-Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance and correspond with $\\beta$ from Equation 1.", warning=FALSE, echo = FALSE, out.extra=''}
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance and correspond with $\\beta$ (and $\\mu_\\gamma$ for LULC) from Equation 1.", warning=FALSE, echo = FALSE, out.extra=''}
 knitr::include_graphics("../figures/fe-1.pdf")
@@
 
-```{r re-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models.
-Values shown are posterior medians (filled circles) and 95\\% credible intervals (solid lines) for individual hydrologic units (HUC4s) ordered from top to bottom (west to east).
+```{r re-1, fig.cap = "Effect of watershed land-use ($\\gamma_j$) for individual regions in the top-ranked lake TP and TN models.
+Values shown are posterior medians (filled circles) and 95\\% credible intervals (solid lines) for individual hydrologic units (HUC4s) ordered from top to bottom according to longitude (west to east).
 Also shown is a comparison to a zero effect (solid vertical line.
-Values that do not overlap the population level effect are shaded in red.
-Coefficient estimates correspond with $\\gamma$ from Equation 1.", warning=FALSE, echo = FALSE, out.extra='', fig.align='center'}
+Values that do not overlap the population level effect are shaded in red.", warning=FALSE, echo = FALSE, out.extra='', fig.align='center'}
 knitr::include_graphics("../figures/re-1.pdf")

### 2020-03-06 manuscript/figures.Rmd
fig 6 caption revision

@@
 
-```{r tn_re_compare-1, fig.cap = "Histograms showing the distribution of soil clay content for regions sensitive to watershed land-use (see highlighted credible intervals in Figure 4) relative to all other regions.
+```{r tn_re_compare-1, fig.cap = "Histograms showing the distribution of soil clay content for watersheds in regions sensitive to watershed land-use (see highlighted credible intervals in Figure 4) relative to watersheds all other regions.
 Medians for each group are shown as vertical dashed lines.", warning=FALSE, echo = FALSE, out.extra='', fig.align='center'}

### 2020-03-06 manuscript/appendix.Rmd
adjust figure captions
add tile drainage plot

@@
 ```{r trophic_state, fig.cap="Lake trophic state in our study lakes versus all lakes from Soranno et al.
-(2017) located with our study extent.
+(2017) located within our study extent.
 Trophic state based on the chlorophyll critera from Carlson (1996)", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
@@
 
+```{r tile_drainage_vs_clay, fig.cap = "Scatterplot showing the median clay content of watersheds in our hydrologic regions plotted against percent tile drainage from Nakagaki and Wieczorek (2016).
+Our regions highly sensitive to agriculture land-use from Figure 4 are highlighted.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3}
+# load huc4 clay estimates
+signif_hu4_ids <- c("HU4_56", "HU4_57")
+dt <- readRDS("../data/dt.rds") %>%
+  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
+  dplyr::select(lagoslakeid, hu4_zoneid, clay_pct, signif_hu4) %>%
+  group_by(hu4_zoneid) %>%
+  mutate(median = median(clay_pct, na.rm = TRUE)) %>%
+  distinct(hu4_zoneid, median, signif_hu4)
+
+# compute per huc tile drainage
+# load huc4s
+# study_bbox    <- st_read("data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
+# hu4_focal     <- st_read("data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
+# hu4_focal     <- st_crop(st_transform(hu4_focal, st_crs(study_bbox)), study_bbox)
+# http://dx.doi.org/10.5066/F7W37TDP
+# library(exactextractr)
+# r <- raster("data/SubsurfaceDrainExtentMW_2012.tif")
+# test <- st_cast(hu4_focal, "MULTIPOLYGON")
+# test$tile_drainage <- exact_extract(r, test, "sum")
+# saveRDS(test, "data/tile_drainage.rds")
+test <- readRDS("../data/tile_drainage.rds")
+test2 <- left_join(test, dt, by = c("ZoneID" = "hu4_zoneid"))
+
+# scatter plot clay versus tile drainage highlighting sensitve hucs
+ggplot(data = test2) +
+  geom_point(aes(x = tile_drainage/900, # grid cells are 30x30 = 900
+                 y = median, color = signif_hu4)) +
+  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
+  xlab("Percent tile drainage") + ylab("Median clay content (percent)") +
+  cowplot::theme_cowplot() +
+  theme(legend.position = c(0.6, 0.3), 
+        legend.background = element_rect(fill = "white", color = "black"),
+        legend.text = element_text(size = 10), 
+        legend.title = element_text(size = 11)) +
+  labs(color = "LULC Sensitive")
+```
+
 ```{r coef-summary-table, eval = FALSE}

### 2020-03-11 figures/11_map.Rmd
shrink lake dots

@@
     geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
-    geom_sf(data = ep, size = 0.9) +
+    geom_sf(data = ep, size = 0.5) +
     coord_sf(datum = NA) +

### 2020-03-11 manuscript/appendix.Rmd
cleanup captions

@@
 ```{r tile_drainage_vs_clay, fig.cap = "Scatterplot showing the median clay content of watersheds in our hydrologic regions plotted against percent tile drainage from Nakagaki and Wieczorek (2016).
-Our regions highly sensitive to agriculture land-use from Figure 4 are highlighted.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3}
+The regions that are highly sensitive to agriculture land-use from Figure 4 are highlighted.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3}
 # load huc4 clay estimates

### 2020-03-11 manuscript/figures.Rmd
cleanup captions

@@
 
-```{r re-comparison-1, fig.cap = "Population level estimates (i.e.
-slopes, $\\mu_\\gamma$) for the effect of watershed land-use cover on lake TP and TN from six candidate models.
+```{r re-comparison-1, fig.cap = "Population level slope estimates ($\\mu_\\gamma$) for the effect of watershed land-use cover on lake TP and TN from six candidate models.
 Values shown are posterior medians (filled circles) and 95\\% credible intervals (solid lines).
@@
 
-```{r fe-1, fig.cap = "Global (fixed effect) coefficient values ($\\beta$, for all non-LULC predictors) and population level estimates for the effect of watershed land-use ($\\mu_\\gamma$, LULC) on lake TP and TN for each respective top-ranked model.
+```{r fe-1, fig.cap = "Global (fixed effect) coefficient values ($\\beta$, for all non-LULC predictors) and population level estimates for the effect of watershed land-use ($\\mu_\\gamma$, for LULC) on lake TP and TN for each respective top-ranked model.
 Note that the values for LULC here are identical to their corresponding values in Figure 2.
@@
 Horizontal bars separate coefficients in distinct predictor categories.
-Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance and correspond with $\\beta$ (and $\\mu_\\gamma$ for LULC) from Equation 1.", warning=FALSE, echo = FALSE, out.extra=''}
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance and correspond with $\\beta$ (and $\\mu_\\gamma$ for LULC) from Equation 1.
+Note that the LULC coefficients are identical to their corresponding lines in Figure 2.", warning=FALSE, echo = FALSE, out.extra=''}
 knitr::include_graphics("../figures/fe-1.pdf")

### 2020-03-16 manuscript/appendix.Rmd
create nonlinear clay vs tn plot

@@
            size = 2) +
-  ylab("log(TN) (ug/L)") +
-  xlab("log(Percent Agriculture)") +
+  ylab("TN (ug/L)") +
+  xlab("Percent Agriculture") +
   scale_x_log10() + scale_y_log10() +
@@
            size = 2) +
-  ylab("log(TP) (ug/L)") +
-  xlab("log(Percent Agriculture)") +
+  ylab("TP (ug/L)") +
+  xlab("Percent Agriculture") +
   scale_x_log10() + scale_y_log10() +
@@
 
+```{r clay-nonlinear, fig.cap = "Scatterplot showing the non-linear relationship between watersehd clay content and lake TN concentration.
+Vertical dashed line shows transition between a positive and a negative correlation (r) between the two variables.
+Solid red line shows the fit of a generalized additive model from the mgcv R package.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3}
+# Why was the clay coefficient negative in the TN model?
+# re_brms <- readRDS("data/mcmc/re_brms.rds")
+# re_brms[[8]]$formula
+dt       <- # readRDS("data/dt.rds") %>%
+  readRDS("../data/dt_scaled.rds") %>%
+  dplyr::select(clay_pct, hu12_ppt_mean, hu12_baseflow_mean, 
+                buffer_cultivated_crops, iwsla_ratio, soil_org_carbon,
+                wetlands,
+                maxdepth, ag, tn, lagoslakeid)
+
+test <- readRDS("../data/dt_scaled.rds") %>%
+  dplyr::select(lagoslakeid, clay_pct, tn) %>%
+  left_join(
+    dplyr::select(readRDS("../data/dt.rds"), lagoslakeid, clay_pct, tn), 
+    by = "lagoslakeid") %>%
+  setNames(c("lagoslakeid", "clay_pct_scaled", "tn_scaled", 
+  "clay_pct_raw", "tn_raw")) %>%
+  mutate_all(as.numeric)
+labs_key              <- data.frame(clay_pct_raw = seq(0, 30, length.out = 5))
+fit <- lm(clay_pct_scaled ~ clay_pct_raw, data = test)
+labs_key$clay_pct_scaled <- round(predict(fit, newdata = labs_key), 1)
+
+# https://stats.stackexchange.com/a/35922/49019
+library(mgcViz)
+b <- bamV(tn ~ s(clay_pct, k = 4), data = dt)
+o <- plot(sm(b, 1), nsim = 50) # 50 posterior simulations 
+o + l_fitLine(colour = "red") + l_points(size = 0.8, shape = 19) +
+  geom_vline(xintercept = 0.765, linetype = "dashed") +
+  scale_x_continuous(breaks = labs_key$clay_pct_scaled, 
+                     labels = labs_key$clay_pct_raw, 
+                     limits = c(-2, 3)) +
+  xlab("Clay content (%)") + ylab("log(TN (ug/L))") +
+  annotate("text", x = -1, y = 3.3, label = paste0("r = ", 
+           round(broom::tidy({
+             dplyr::filter(dt, clay_pct < 0.765) %$% cor.test(clay_pct, tn)
+           })$estimate, 3))) +
+  annotate("text", x = 2, y = 3.3, label = paste0("r = ", 
+        round(broom::tidy({
+          dplyr::filter(dt, clay_pct > 0.765) %$% cor.test(clay_pct, tn)
+          })$estimate, 3)))
+```
+
 ```{r coef-summary-table, eval = FALSE}

### 2020-03-16 manuscript/appendix.Rmd
cleanup

@@
 
-```{r clay-nonlinear, fig.cap = "Scatterplot showing the non-linear relationship between watersehd clay content and lake TN concentration.
+```{r clay-nonlinear, fig.cap = "Scatterplot showing the non-linear relationship between watershed clay content and lake TN concentration.
 Vertical dashed line shows transition between a positive and a negative correlation (r) between the two variables.
-Solid red line shows the fit of a generalized additive model from the mgcv R package.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3}
+Solid red line shows the fit of a generalized additive model from the mgcv R package.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3, message=FALSE}
+library(magrittr)
 # Why was the clay coefficient negative in the TN model?

### 2020-03-16 figures/07_model-selection.Rmd
rename buffer category to spatial config

@@
   mutate(category = forcats::fct_recode(category, 
-                                        Buffer = "Buffer configuration", 
+                                        `Spatial\nconfig.` = "Buffer configuration", 
                                         LULC = "Land-use cover")) %>%

### 2020-03-16 manuscript/figures.Rmd
remove repeated sentence

@@
 Horizontal bars separate coefficients in distinct predictor categories.
-Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance and correspond with $\\beta$ (and $\\mu_\\gamma$ for LULC) from Equation 1.
-Note that the LULC coefficients are identical to their corresponding lines in Figure 2.", warning=FALSE, echo = FALSE, out.extra=''}
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance and correspond with $\\beta$ (and $\\mu_\\gamma$ for LULC) from Equation 1.", warning=FALSE, echo = FALSE, out.extra=''}
 knitr::include_graphics("../figures/fe-1.pdf")

### 2020-03-18 figures/07_model-selection.Rmd
adjust figure labels

@@
                         x = c(0, 0, 0), 
-                        y = c(0.62, 0.49, 0.37), 
+                        y = c(0.665, 0.54, 0.37), 
                         stringsAsFactors = FALSE)

### 2020-04-01 manuscript/figures.Rmd
set correct nutrient order in figure captions

@@
 
-```{r re-comparison-1, fig.cap = "Population level slope estimates ($\\mu_\\gamma$) for the effect of watershed land-use cover on lake TP and TN from six candidate models.
+```{r re-comparison-1, fig.cap = "Population level slope estimates ($\\mu_\\gamma$) for the effect of watershed land-use cover on lake TN and TP from six candidate models.
 Values shown are posterior medians (filled circles) and 95\\% credible intervals (solid lines).
@@
 
-```{r fe-1, fig.cap = "Global (fixed effect) coefficient values ($\\beta$, for all non-LULC predictors) and population level estimates for the effect of watershed land-use ($\\mu_\\gamma$, for LULC) on lake TP and TN for each respective top-ranked model.
+```{r fe-1, fig.cap = "Global (fixed effect) coefficient values ($\\beta$, for all non-LULC predictors) and population level estimates for the effect of watershed land-use ($\\mu_\\gamma$, for LULC) on lake TN and TP for each respective top-ranked model.
 Note that the values for LULC here are identical to their corresponding values in Figure 2.
@@
 
-```{r re-1, fig.cap = "Effect of watershed land-use ($\\gamma_j$) for individual regions in the top-ranked lake TP and TN models.
+```{r re-1, fig.cap = "Effect of watershed land-use ($\\gamma_j$) for individual regions in the top-ranked lake N and P models.
 Values shown are posterior medians (filled circles) and 95\\% credible intervals (solid lines) for individual hydrologic units (HUC4s) ordered from top to bottom according to longitude (west to east).

### 2020-04-01 manuscript/appendix.Rmd
caption typo fixes

@@
 ```{r 02_cdl_key, results='asis', warning=FALSE, echo = FALSE}
-knitr::kable('', col.names = NULL, caption = "Category definitions from the 2010 CDL. See code supplement for listing of variables classified as 'ag'")
+knitr::kable('', col.names = NULL, caption = "Category definitions from the 2010 CDL. See code supplement for listing of variables classified as 'ag'.")
 ```
@@
 (2017) located within our study extent.
-Trophic state based on the chlorophyll critera from Carlson (1996)", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
+Trophic state based on the chlorophyll critera from Carlson (1996).", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
 
@@
 
-```{r fe_nolulc-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for best-fit lake TP and TN models when land-use predictors are excluded.
+```{r fe_nolulc-1, fig.cap = "Global (fixed effect) coefficient values and credible intervals for top-ranked lake TP and TN models when land-use predictors are excluded.
 Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines).

### 2020-04-01 manuscript/figures.Rmd
caption typo fixes

@@
 \captionof{table}{Medians followed by first and third quantiles of predictor variables for 928 lakes.
-Also shown is whether each predictor is defined as an aggregate or granular measure of agriculture.}
+Also shown is whether each predictor is defined as an aggregate or granular measure of agriculture or as a non-agriculture (other) predictor.
+Dashed entries for the granularity cateogry indicate an identical categorization as the preceding predictor.}
 \includegraphics{../tables/01_predictors}
@@
 ELPD has a similar interpretation to information criterion measures like AIC.
-Typically models are considered to be different if they are separated by an AIC value of greater than 2, which is equivalent to an ELPD value of -1.}
+Typically models are considered to be different if they are separated by an Akaike information criterion (AIC) value of greater than 2, which is equivalent to an ELPD value of -1.}
 \includegraphics{../tables/03_model_summary}
@@
 Values shown are posterior medians (filled circles) and 95\\% credible intervals (solid lines) for individual hydrologic units (HUC4s) ordered from top to bottom according to longitude (west to east).
-Also shown is a comparison to a zero effect (solid vertical line.
-Values that do not overlap the population level effect are shaded in red.", warning=FALSE, echo = FALSE, out.extra='', fig.align='center'}
+Also shown is a comparison to a zero effect (solid vertical line).
+Values that are different from the population level effect are shaded in red.", warning=FALSE, echo = FALSE, out.extra='', fig.align='center'}
 knitr::include_graphics("../figures/re-1.pdf")

### 2020-04-01 figures/07_model-selection.Rmd
center xaxis labels

@@
   rel_widths = c(1, 0.95)),
-
+cowplot::plot_grid(
+  ggplot() + geom_blank() + theme(panel.background = element_blank()), 
 ggplot(data.frame(x = 1, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
   geom_text(aes(x = x, y = y, label = label)) +
-  theme_void(),
+  theme_void(), rel_widths = c(0.03, 1)),
 ncol = 1, rel_heights = c(1, 0.05))
@@
                                     axis.title.x = element_blank(),
-                                    plot.margin = unit(c(0,0,0,0), "cm")), 
+                                    plot.margin = unit(c(0,0.3,0,0), "cm")), 
                    rel_widths = c(1, 0.8)),
+cowplot::plot_grid(
+  ggplot() + geom_blank() + theme(panel.background = element_blank()),
 ggplot(data.frame(x = 0, y = 0, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
@@
   theme(plot.margin = unit(c(0,0,0,0), "cm")), 
+rel_widths = c(0.15, 1)),
 ncol = 1, rel_heights = c(1, 0.05))
@@
 cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.6)),
-ggplot(data.frame(x = 1, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
+cowplot::plot_grid(
+  ggplot() + geom_blank() + theme(panel.background = element_blank()), 
+ggplot(data.frame(x = 4, y = 1, label = "Standardized coefficients", stringsAsFactors = FALSE)) + 
   geom_text(aes(x = x, y = y, label = label)) +
-  theme_void(),
+  theme_void(), rel_widths = c(0.3, 1)),
 ncol = 1, rel_heights = c(1, 0.05))

### 2020-04-01 figures/08_exploratory_dotplot.Rmd
turn off clustering tree lines

@@
   na.col = "grey",
-  cellheight = 8, cellwidth = 8, treeheight_col = 20, treeheight_row = 40)
+  cellheight = 8, cellwidth = 8, treeheight_col = 0, treeheight_row = 0)
 ```

### 2020-04-01 manuscript/appendix.Rmd
use unlogged ag in scatterplot and percent tile drainage

@@
 
-fit_tn      <- lm(log(tn) ~ log(ag), data = dt)
+fit_tn      <- lm(log(tn) ~ ag, data = dt)
 fit_tn_pred <- data.frame(tn = fit_tn$model$`log(tn)`,
                           tn_pred = fit_tn$fitted.values,
-                          ag = fit_tn$model$`log(ag)`,
+                          ag = fit_tn$model$ag,
                           stringsAsFactors = FALSE)
@@
 # 
-fit_tp      <- lm(log(tp) ~ log(ag), data = dt)
+fit_tp      <- lm(log(tp) ~ ag, data = dt)
 fit_tp_pred <- data.frame(tp = fit_tp$model$`log(tp)`,
                           tp_pred = fit_tp$fitted.values,
-                          ag = fit_tp$model$`log(ag)`,
+                          ag = fit_tp$model$ag,
                           stringsAsFactors = FALSE)
@@
   geom_point(aes(x = ag, y = tn)) + 
-  geom_line(data = fit_tn_pred, aes(x = exp(ag), y = exp(tn_pred)), 
+  geom_line(data = fit_tn_pred, aes(x = ag, y = exp(tn_pred)), 
              color = "red") +
-  annotate("text", x = 14, y = 12000, label = get_formula("log(tn)", fit_tn), 
+  annotate("text", x = 24, y = 12000, label = get_formula("log(tn)", fit_tn), 
            size = 2) +
@@
   xlab("Percent Agriculture") +
-  scale_x_log10() + scale_y_log10() +
+  scale_y_log10() +
   theme_cowplot(), 
@@
   geom_point(aes(x = ag, y = tp)) + 
-    geom_line(data = fit_tp_pred, aes(x = exp(ag), y = exp(tp_pred)), 
+    geom_line(data = fit_tp_pred, aes(x = ag, y = exp(tp_pred)), 
              color = "red") +
-  annotate("text", x = 14, y = 900, label = get_formula("log(tp)", fit_tp), 
+  annotate("text", x = 24, y = 900, label = get_formula("log(tp)", fit_tp), 
            size = 2) +
@@
   xlab("Percent Agriculture") +
-  scale_x_log10() + scale_y_log10() +
+  scale_y_log10() +
   theme_cowplot()
@@
 ```{r tile_drainage_vs_clay, fig.cap = "Scatterplot showing the median clay content of watersheds in our hydrologic regions plotted against percent tile drainage from Nakagaki and Wieczorek (2016).
-The regions that are highly sensitive to agriculture land-use from Figure 4 are highlighted.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3}
+The regions that are highly sensitive to agricultural land-use from Figure 4 are highlighted in red.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3}
 # load huc4 clay estimates
@@
 ggplot(data = test2) +
-  geom_point(aes(x = tile_drainage/900, # grid cells are 30x30 = 900
+  geom_point(aes(x = (tile_drainage/900) * 100, # grid cells are 30x30 = 900
                  y = median, color = signif_hu4)) +
   scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
-  xlab("Percent tile drainage") + ylab("Median clay content (percent)") +
+  xlab("Tile drainage (percent)") + ylab("Median clay content (percent)") +
   cowplot::theme_cowplot() +
-  theme(legend.position = c(0.6, 0.3), 
+  theme(legend.position = "none", 
         legend.background = element_rect(fill = "white", color = "black"),

### 2020-04-02 manuscript/appendix.Rmd
fix cutoff eq

@@
              color = "red") +
-  annotate("text", x = 24, y = 12000, label = get_formula("log(tn)", fit_tn), 
+  annotate("text", x = 29, y = 12000, label = get_formula("log(tn)", fit_tn), 
            size = 2) +
@@
              color = "red") +
-  annotate("text", x = 24, y = 900, label = get_formula("log(tp)", fit_tp), 
+  annotate("text", x = 29, y = 900, label = get_formula("log(tp)", fit_tp), 
            size = 2) +

### 2020-04-02 manuscript/appendix.Rmd
formatting fixes

@@
 ---
-title: "Appendix"
+title: "Appendix S1"
 output:
@@
 - \usepackage{colortbl}
+- \usepackage{setspace, caption}
+- \usepackage{times}
+- \DeclareCaptionFont{blah}{\doublespacing\normalsize\fontseries{n}\fontfamily{ptm}\selectfont}
+- \captionsetup{font=blah}
+- \pagenumbering{gobble}
 ---
 
-\def\figurename{Figure A}
-\def\tablename{Table A}
+\def\figurename{Figure S\hspace{-0.3em}}
+\def\tablename{Table S\hspace{-0.3em}}
 
@@
 \pagebreak
+
+\centering
+# Appendix S1
+
+\begin{flushleft}
+Title: Granular measures of agricultural land-use influence lake nitrogen and phosphorus differently at macroscales.
+
+Authors: Joseph Stachelek, W. Weng, C.C. Carey, A.R. Kemanian, K.M. Cobourn, T. Wagner, K.C. Weathers, P.A. Soranno
+
+Journal: Ecological Applications
+\end{flushleft}
+
+\vspace{6em}
 
@@
 
+\pagebreak
+
 ```{r tile_drainage_vs_clay, fig.cap = "Scatterplot showing the median clay content of watersheds in our hydrologic regions plotted against percent tile drainage from Nakagaki and Wieczorek (2016).
@@
 ```
+
+\pagebreak
 

### 2020-04-02 manuscript/figures.Rmd
formatting fixes

@@
 - \usepackage{colortbl}
-- \usepackage{caption}
+- \usepackage{setspace, caption}
 - \usepackage{float}
+- \usepackage{times}
+- \DeclareCaptionFont{blah}{\doublespacing\normalsize\fontseries{n}\fontfamily{ptm}\selectfont}
+- \captionsetup{font=blah}
+- \setcounter{page}{37}
 ---
@@
 
-```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC4) regions.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
-knitr::include_graphics("../figures/11_map-1.pdf")
-```
-
 \begin{center}
@@
 \end{center}
+
+\pagebreak
+
+\begin{center}
+\captionof{table}{Diagnostics for each model listed by regionally varying coefficient.
+Table is sorted by decreasing $R^2$ and expected log predictive density (ELPD).
+ELPD has a similar interpretation to information criterion measures like AIC.
+Typically models are considered to be different if they are separated by an Akaike information criterion (AIC) value of greater than 2, which is equivalent to an ELPD value of -1.}
+\includegraphics{../tables/03_model_summary}
+\end{center}
+
+\pagebreak
+
+\renewcommand{\listfigurename}{Figure legends}
+\doublespacing
+\renewcommand*\numberline[1]{Figure\,#1:\space}
+\makeatletter
+\renewcommand*\l@figure[2]{\noindent#1\par}
+\makeatother
+\listoffigures
+
+\pagebreak
+
+```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC4) regions.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
+knitr::include_graphics("../figures/11_map-1.pdf")
+```
+
+\pagebreak
 
@@
 
-\begin{center}
-\captionof{table}{Diagnostics for each model listed by regionally varying coefficient.
-Table is sorted by decreasing $R^2$ and expected log predictive density (ELPD).
-ELPD has a similar interpretation to information criterion measures like AIC.
-Typically models are considered to be different if they are separated by an Akaike information criterion (AIC) value of greater than 2, which is equivalent to an ELPD value of -1.}
-\includegraphics{../tables/03_model_summary}
-\end{center}
+\pagebreak
 
@@
 
+\pagebreak
+
 ```{r re-1, fig.cap = "Effect of watershed land-use ($\\gamma_j$) for individual regions in the top-ranked lake N and P models.
@@
 
+\pagebreak
+
 ```{r tn_re_hu4-1, fig.cap = "Location of hydrologic regions sensitive to watershed land-use cover corresponding to highlighted credible intervals in Figure 4.", warning=FALSE, echo = FALSE, out.extra='', fig.align='center'}

### 2020-04-16 figures/07_model-selection.Rmd
avoid overlapping y-axis labels in re fig

@@
 cowplot::plot_grid(
-cowplot::plot_grid(gg_tp_re + theme(axis.title.x = element_blank(), 
+  ggplot() + geom_blank() + theme(panel.background = element_blank()),
+cowplot::plot_grid(
+cowplot::plot_grid(gg_tp_re + theme(axis.text.y = element_text(size = 9),
+                                    axis.title.x = element_blank(), 
                                     plot.margin = unit(c(0,0,0,0), "cm")),
@@
 rel_widths = c(0.15, 1)),
-ncol = 1, rel_heights = c(1, 0.05))
+ncol = 1, rel_heights = c(1, 0.05)), 
+ncol = 2, rel_widths = c(0.05, 1))
 

### 2020-04-17 manuscript/manuscript.Rmd
start of postprint

---
title: Granular measures of agricultural land-use influence lake nitrogen and phosphorus differently at macroscales

# Use letters for affiliations
author:
  - name: Joseph Stachelek
    affiliation: a
  - name: Weizhe Weng
    affiliation: b
  - name: Patricia A. Soranno
    affiliation: a
address:
  - code: a
    address: Department of Fisheries and Wildlife, Michigan State University, 480 Wilson Rd., East Lansing, MI 48824, USA
  - code: b
    address: School of Business, State University of New York College at Geneseo, 1 College Circle, Geneseo, NY 14454, USA

# Optional: line of arbitrary text with additional information.
# Could be used, for example, to mention the bibliographic info in a post-print.
# If not specified, defaults to "This version was compiled on \today"
#date_subtitle: Published in *Journal of Statistical Software*, 2018
date_subtitle: > 
  This is the accepted version of the following article: J. Stachelek et al., Ecological Applications. In Press, which has been published in final form at DOI:  [DOI](https://doi.org).  This article may be used for non-commercial purposes in accordance with Wiley Terms and Conditions for Use of Self-Archived Versions.

# For footer text  TODO(fold into template, allow free form two-authors)
lead_author_surname: Stachelek et al.

# Place eg a DOI URL or CRAN Package URL here
doi_footer: "https://doi.org/10.5281/zenodo.3754916"

# Abstract
abstract: |
  Agricultural land-use is typically associated with high stream nutrient concentrations and increased nutrient loading to lakes. For lakes, evidence for these associations mostly comes from studies on individual lakes or watersheds that relate concentrations of nitrogen (N) or phosphorus (P) to aggregate measures of agricultural land-use, such as the proportion of land used for agriculture in a lake’s watershed. However, at macroscales (i.e., in hundreds to thousands of lakes across large spatial extents), there is high variability around such relationships and it is unclear whether considering more granular (or detailed) agricultural data, such as fertilizer application, planting of specific crops, or the extent of near-stream cropping, would improve prediction and inform understanding of lake nutrient drivers. Furthermore, it is unclear whether lake N and P would have different relationships to such measures and whether these relationships would vary by region, since regional variation has been observed in prior studies using aggregate measures of agriculture. To address these knowledge gaps, we examined relationships between granular measures of agricultural activity and lake total phosphorus (TP) and total nitrogen (TN) concentrations in 928 lakes and their watersheds in the Northeastern and Midwest U.S. using a Bayesian hierarchical modelling approach. We found that both lake TN and TP concentrations were related to these measures of agriculture, especially near-stream agriculture. The relationships between measures of agriculture and lake TN concentrations were more regionally variable than those for TP. Conversely, TP concentrations were more strongly related to lake-specific measures like depth and watershed hydrology relative to TN. Our finding that lake TN and TP concentrations have different relationships with granular measures of agricultural activity has implications for the design of effective and efficient policy approaches to maintain and improve water quality.

# Optional: Acknowledgements
acknowledgements: |
  This work was supported by the U.S. National Science Foundation’s Dynamics of Coupled Natural and Human Systems (CNH) Program (award 1517823) and Macrosystems Biology Program (awards EF-1638679, EF-1638554, EF-1638539, and EF-1638550). PAS was also supported by the USDA National Institute of Food and Agriculture, Hatch project 1013544. ARK supported by Hatch Appropriations under Project #PEN04571 and Accession #1003346. We thank Sarah Collins for early input on the design and motivation for this study. Any use of trade, firm, or product names is for descriptive purposes only and does not imply endorsement by the U.S. Government. Author contributions: JS conceived of the study, built models, analyzed data, and wrote the paper. CCC, ARK, and PAS contributed to the conception of the manuscript and edited the paper. WW, KMC, TW, KCW, and PAS provided interpretation of results and edited the paper.

# Optional: One or more keywords
keywords:
  - agriculture
  - fertilizer
  - lakes
  - manure
  - nitrogen
  - phosphorus
  - water quality

# Paper size for the document, values of letter and a4
papersize: letter

# Font size of the document, values of 9pt (default), 10pt, 11pt and 12pt
fontsize: 9pt

# Optional: Force one-column layout, default is two-column
#one_column: true

# Optional: Enables lineno mode, but only if one_column mode is also true
#lineno: true

# Optional: Enable one-sided layout, default is two-sided
#one_sided: true

# Optional: Enable section numbering, default is unnumbered
#numbersections: true

# Optional: Specify the depth of section number, default is 5
#secnumdepth: 5

# Optional: Skip inserting final break between acknowledgements, default is false
skip_final_break: true

# Optional: Bibliography 
bibliography: lagosag
biblio-style: elsarticle-harv

# Optional: Enable a 'Draft' watermark on the document
#watermark: true

# Customize footer, eg by referencing the vignette
footer_contents: "Agriculture-lake nutrient relationships"

# Produce a pinp document
output: pinp::pinp

# Required: Vignette metadata for inclusion in a package.
vignette: >
  %\VignetteIndexEntry{YourPackage-vignetteentry}
  %\VignetteKeywords{YourPackage, r, anotherkeyword}
  %\VignettePackage{YourPackage}
  %\VignetteEngine{knitr::rmarkdown}
---

## Introduction

Freshwaters are vulnerable to eutrophication in areas of high agricultural land-use and land cover because agricultural activities are associated with high nutrient runoff and loading to groundwater and streams (Allan 2004, Arbuckle and Downing, 2001, Daniel et al. 2010, Taranu et al. 2008). High runoff and loading in these areas is a result of high rates of nutrient input combined with hydrologic modifications that decrease the travel time of these inputs from the land surface to lakes \citep{blannEffectsAgriculturalDrainage2009}. Surprisingly, while some studies have found strong relationships between agricultural land-use and land cover (hereafter referred to as “land-use” or LULC) and lake nutrient concentrations (Arbuckle and Downing 2001, Taranu et al. 2008), others have found more mixed results (Jones et al. 2008), particularly in studies that include many lakes located in multiple regions (Soranno et al. 2015). Further examples of such macroscale studies (see Heffernan et al. 2014) in which lakes are spread across many regions at distances spanning hundreds to thousands of kilometers include Collins et al. (2017) and Read et al. (2015), who found that the strength of agriculture and lake nutrient relationships varied depending on geographic region and lake characteristics.

Mixed results from prior studies may be due to two difficulties in quantifying lake nutrient and agricultural land-use relationships. First, the pathways of nutrients from fields to streams and ultimately to lakes are complex and indirect (Cherry et al. 2008, Heathwaite et al. 2003, King et al. 2005). For example, in order for nitrogen applied as fertilizer to reach a lake, it must be transported to streams or groundwater in excess of microbial denitrification, plant use, and microbial uptake. Then, it must travel, again, often undergoing repeated chemical transformation as it passes through riparian buffers and along stream networks before finally entering the lake (Maranger et al. 2018). Each step of the journey represents an opportunity for those nutrients to be sequestered or removed. Further, overall hydrologic transport is influenced by soil type (Naiman et al. 2010), and topography. Thus, the nutrients that ultimately enter a lake are a function of filtering by the landscape as well as geochemical transformation processes that are difficult to capture at broad scales (Canham et al. 2012, Maranger et al. 2018).

Second, much of our evidence for a connection between agricultural land-use and increased nutrient concentrations comes from studies focusing on a single watershed or on several watersheds within a single geographic region (Capel et al. 2018b, Daniel et al. 2010, Hayes et al. 2015, Renwick et al. 2008). These studies tend to focus on very detailed measures of agricultural activity such as tillage and other practices, nutrient amendments, and their spatial arrangement. However, studies at broader spatial scales (i.e., the macroscale, Heffernan et al. 2014), which aim to provide a more general view of relationships between lake nutrient concentrations and agriculture, tend to focus only on relatively coarse measures of agricultural activity (Fergus et al. 2016, Filstrup et al. 2018, Read et al. 2015, Schmadel et al. 2019). As a result, it is unclear to what extent the mixed results from prior broad-scale studies might be due to the limited use of detailed measures of agricultural activity or simply from regional variation.

There are two ways in which detailed (i.e., granular) measures of agricultural activity may be substituted for their coarse (i.e., aggregate) counterparts. The first is by using granular measures that are recorded in the same locations as their aggregate equivalents but are more descriptive. For example, in broad-scale studies, the proportion of land used for agriculture in a lake watershed is sometimes replaced by separate representations of the land used for pasture and the land used for row-crops (Abell et al. 2011, Collins et al., 2017). The second is by using granular measures that have the same description as their aggregate equivalents, but that are measured in more specific locations. For example, a small number of lake studies have compared the proportion of land used for agriculture in near-stream buffers versus the watershed as a whole (Gemesi et al. 2011, Soranno et al. 2015). Although the term granular can be used in a general sense to describe any detailed agricultural measure, we define the term more narrowly as only those that have a specific aggregate counterpart (Table 1).

Prior use of granular data in broad-scale studies of lake water quality has been limited. For this reason, findings from broad-scale studies may be less useful in applied management settings because coarse (i.e. aggregate) land-use and land cover change metrics have become less widely used policy instruments (Morefield et al. 2016). Instead, recent policy interventions go beyond aggregate measures of agricultural activity to target more specific measures such as implementation of specific farming practices, no-till agriculture, and construction of riparian buffer strips (Capel et al. 2018a, NRC 2010, Yang et al. 2005). Thus, broad-scale studies could be made more relevant for informing policy interventions if they used covariates that have a similar level of granularity to those used in fine-scale studies. For example, implementation of no-till agriculture policies may be better informed by covariates at the granular crop level rather than solely by aggregate covariates like land used for agriculture (Figure S1).

\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth,keepaspectratio]{../tables/01_predictors}
    \captionsetup{labelformat=empty}
    \caption{\textbf{Table 1. } Medians followed by first and third quantiles of predictor variables for 928 lakes. Also shown is whether each predictor is defined as an aggregate or granular measure of agriculture or as a non-agriculture (other) predictor. Dashed entries for the granularity category indicate an identical categorization as the preceding predictor.} \customlabel{table1}{1}     
  \end{center}
\end{figure}

One likely reason that broad-scale studies have rarely used granular agricultural data is that until recently, such data have not been available with corresponding lake nutrient concentration data over large geographic extents. Although a few examples exist of studies connecting granular agricultural data to either stream nitrogen or phosphorus concentrations at the macroscale (Boyer et al. 2002, Bellmore et al. 2018, Metson et al. 2017), most studies have focused on either nitrogen (N) or phosphorus (P) but not on both at the same time (Alexander et al. 2008). Crucially, we are not aware of prior work examining relationships between a multiple granular measures of agricultural activity on either lake N or P concentrations at macroscales.

There are several plausible expectations, which are based on the findings of broad-scale stream studies as well as the findings of fine-scale lake studies, for the type of relationships between such measures and lake nutrient concentrations that may emerge at macroscales. First, we expect that increased nutrient inputs to the land surface as fertilizer and manure will increase lake nutrient concentrations (Bellmore and other 2018, Renwick et al. 2008). Second, we expect that lakes with watersheds that have high soil clay content and high soil organic carbon content will have higher lake nutrient concentrations. This will occur because clay soils tend to have higher rates of surface runoff and have higher organic matter content relative to sandy soils, despite the tendency for higher organic matter content to increase water storage and reduce surface runoff (Capel et al. 2018b). Finally, we expect that lakes with stream networks characterized by extensive near-stream agriculture will have higher nutrient concentrations because there will be less interception of agricultural runoff (Naiman et al. 2010).

Although we can formulate potential expectations for relationships between agricultural activities and lake nutrients at the macroscale by building on the findings of prior studies, several key uncertainties remain. The first key uncertainty is the extent to which lake and watershed characteristics, such as watershed hydrology and soil type, affect relationships between granular measures of agricultural activity and lake nutrient concentrations at the macroscale. For example, macroscale studies have found that lake P concentrations are strongly dependent on lake depth (Collins et al. 2017), but the degree to which granular agricultural data provide additional explanatory power is unknown. Similarly, Abell et al. (2011) found that watershed to lake area ratio (i.e. lake water residence time) was positively related to lake N concentrations after controlling for aggregate measures of agricultural land-use, but it is unknown whether this mediation effect would also affect relationships with more granular measures of agriculture.

The second key uncertainty is the extent to which relationships between granular measures of agricultural activity and lake nutrient concentrations vary regionally. For example, previous macroscale studies on lake nutrient concentrations have found that relationships between lake chlorophyll and nutrient concentrations vary regionally according to hydrologic subregions (Wagner et al. 2011, Qian et al. 2019). Models in which separate relationships (e.g. slopes) are estimated for different regions, such as those used by Wagner et al. (2011), can be used to test differences among regions in the sensitivity to nutrient predictors. Wagner et al. (2011) found that the slope of the chlorophyll to P relationship was notably higher in several of their study regions and found that lakes with high pasture land-use in their watershed were more sensitive to changes in P concentrations (larger, positive slope estimate). They suggest that elevated sensitivity in high pasture regions is due to dual N and P nutrient enrichment associated with this land cover type. Given the findings of this and other studies in stream ecosystems (Alexander et al. 2008), it follows that other relationships in lakes may vary regionally, but whether or not this includes relationships with granular measures of agricultural activity remains unknown.

We addressed the knowledge gaps described above by asking two questions using data from approximately 900 lakes in the Northeastern and Midwestern US: 1) How do granular measures of agricultural activity relate to lake N and P concentrations? And, 2) How do relationships between agricultural activities and lake nutrients vary regionally among hydrologic and climatic regions? To answer these questions, we fit statistical models of lake nutrient concentrations as a function of granular measures of agricultural activity such as the proportion of watershed area land-use of specific crops, and near-stream land-use, as well as fertilizer and manure applications. We also included a variety of lake and watershed characteristics as predictors to account for the influence of other drivers. Finally, our models included a hierarchical component where relationships between watershed land-use and lake nutrient concentrations were allowed to vary among hydrologic subregions to examine potential regional variation in these relationships.

## Methods

### Data description

We analyzed data on lake total nitrogen (TN) and total phosphorus (TP) concentrations from the LAGOS-NE data product (Soranno and Cheruvelil 2017). The LAGOS-NE nutrient data are limited to surface (or “epilimnetic”) samples and were derived from federal, state, tribal, and non-profit agencies, as well as university researchers and citizen scientist data collections (Soranno et al. 2017). We collapsed lake nutrient data to long-term median values computed using all data from the summer stratified period (i.e. 15 June through 15 September) available for each lake between 2000 and 2010. For the lakes that met our selection criteria (see below) the median number of samples per lake was nine (range = 3-94) and the median number of years sampled was four (range = 2-10).

Our first source for granular agricultural information was the 2010 Cropland Data Layer (CDL, USDA 2019), which we used to generate lake watershed and stream buffer estimates of the proportion of land cover due to specific crops such as corn and soybeans. We used the R package cdlTools to access CDL products (Chen 2018). We used the 2010 CDL data because this was the first year of high resolution (30 x 30m) CDL data collection that matched our lake nutrient data collection window. Because the CDL contains detailed coverage for dozens of crops, including rare crops with little to no coverage, we re-categorized CDL data based on Lark et al. (2015) to a more limited set of categories (Table A1).

As a more granular representation of watershed agricultural land use, we measured the proportion of land cover in agricultural and “natural” land-uses in 100-m buffers of lake shorelines and streams for each lake watershed. We chose a 100-m buffer width because this width is inclusive of nearly all “riparian buffers” (Mayer et al. 2007). Here agricultural land-use is defined in the aggregate sense as the proportion of land used for agriculture in a lake’s watershed whereas “natural” land-uses include the sum of all non-agriculture and non-developed CDL classes. We identified the streams associated with each lake using the stream network extraction tool in the nhdR interface e (Stachelek 2019) to the National Hydrography Network (USGS 2019). We compiled soil characteristics for each lake watershed using the Gridded Soil Survey Geographic Database (gSSURGO, USDA 2019) where we used the python package gssurgo (Stachelek 2019) to access gSSURGO  products. One such product was wetland potential, defined as the percentage of the soil grid that meets the criteria for hydric soils formed under conditions of saturation, flooding, or ponding long enough to develop anaerobic conditions but not so long as to be classified as a permanent waterbody (USDA 2019). Finally, we compiled mean annual nutrient inputs via fertilizer and manure to lake watersheds from 1982-2001 using county level data provided by Ruddy et al. (2006). We spatially aligned these county level estimates to lake watershed polygons provided by LAGOS-NE (Soranno and Cheruvelil 2017) using the area-weighted interpolation functions provided by the sf R package (Pebesma 2019). All of our data and data processing code are available at [Zenodo DOI].

### Location information

We restricted the lakes included in the study to those located within the footprint of LAGOS-NE which includes lakes located in 17 Northeastern and Midwest U.S. states (Soranno et al., 2017). We excluded lakes from our analysis if they had a surface area > 400 km2 or a maximum depth > 35 m. These removals resulted in exclusion of approximately 40 lakes which we regarded as outliers that would likely have undue influence on model results because such large and deep lakes are likely to respond differently to enrichment as a result of enhanced stratification. To ensure an adequate comparison between aggregate and granular measures of agriculture, we
further limited lakes in our study to those with at least 10% of the total watershed area devoted to agricultural land-use and those that were sampled at least three times between 2000 and 2010. A total of 928 lakes met these selection criteria (Figure 1). Because we focused on lakes in agricultural watersheds, more than 35  percent of lakes in our study are considered eutrophic to hypereutrophic using chlorophyll a as a diagnostic e versus only 15 percent for all lakes from Soranno et al. (2017) located within our study extent (Figure A3). For the regional terms in our models, we used hydrologic regions at the subbasin (i.e. HUC4) level because this level was small enough to give a sense of overall spatial variation but large enough to encompass sufficient numbers of lakes to estimate within region variance.

\begin{figure}
  \begin{center}
    \includegraphics[width=0.49\textwidth, height=3.5in,keepaspectratio]{../figures/11_map-1}
  \end{center}
  \caption{asdfdd}\label{fig1}
\end{figure}

## References

Here we differ from PNAS and suggest natbib. References will appear in
author-year form. Use `\citet{}`, `\citep{}`, etc as usual.

## Inline R Code

The PNAS sample included a fixed PNG image here, but this document prefers
to show the results and embedding of _R_ code.

```{r figex, fig.width=3, fig.height=3, cache=TRUE, echo=TRUE, fig.cap="Narrow ggplot2 figure"}
library(ggplot2)
ggplot(mtcars, aes(wt, mpg)) +
    geom_point(size=3, aes(colour=factor(cyl))) +
    theme(legend.position="none")
```

Here we use a standard knitr bloc with explicit options for

- figure width and height (`fig.width`, `fig.height`), both set to three inches;
- whether the code is shown (`echo=TRUE`); and
- the caption (`fig.cap`) as shown above.

## Digital Figures

Markdown, Pandoc and LaTeX support `.eps` and `.pdf` files.

Figures and Tables should be labelled and referenced in the standard way
using the `\label{}` and `\ref{}` commands.

The R examples above show how to insert a column-wide
figure. To insert a figure wider than one column, please use the
`\begin{figure*}...\end{figure*}` environment.

One (roundabout) way of doing this is to _not_ actually plot a figure, but to
save it in a file as the following segment shows:

This file is then included via standard LaTeX commands.

## Typeset Code (But Do Not Run It)

We can also just show code.

```r
xx <- faithful[,"eruptions"]
fit <- density(xx)
plot(fit)
```

This simply used a pandoc bloc started and ended by three backticks,
with `r` as the language choice.  Similarly, _many_ other languages
can be typeset directly simply by relying on pandoc.

## Single column equations

Authors may use 1- or 2-column equations in their article, according to
their preference.

To allow an equation to span both columns, options are to use the
`\begin{figure*}...\end{figure*}` environment mentioned above for
figures. The `\begin{widetext}...\end{widetext}` environment as shown
in equation \ref{eqn:example} below is deprecated, but \LaTeX commands
`\onecolumn` and `\twocolumn` work fine.

Please note that this option may run into problems with floats and
footnotes, as mentioned in the [cuted package
documentation](http://texdoc.net/pkg/cuted). In the case of problems
with footnotes, it may be possible to correct the situation using
commands `\footnotemark` and `\footnotetext`.

\begin{equation}
  \begin{aligned}
(x+y)^3&=(x+y)(x+y)^2\\
       &=(x+y)(x^2+2xy+y^2) \\
       &=x^3+3x^2y+3xy^3+x^3. 
       \label{eqn:example} 
  \end{aligned}
\end{equation}

<!-- pandoc writes all tables using longtable, which fails in 2-column mode

  Species                    CBS     CV     G3
  ----------------------- ------ ------ ------
  1\. Acetaldehyde           0.0    0.0    0.0
  2\. Vinyl alcohol          9.1    9.6   13.5
  3\. Hydroxyethylidene     50.8   51.2   54.0

  : Comparison of the fitted potential energy surfaces and ab initio
  benchmark electronic energy calculations

-->

### 2020-04-17 manuscript/manuscript.Rmd
use jsta citation style
finish entering ms text

@@
     affiliation: b
+  - name: Cayelan C. Carey
+    affiliation: c
+  - name: Armen R. Kemanian
+    affiliation: d
+  - name: Kelly M. Cobourn
+    affiliation: e
+  - name: Tyler Wagner
+    affiliation: f
+  - name: Kathleen C. Weathers
+    affiliation: g
   - name: Patricia A. Soranno
     affiliation: a
+
 address:
@@
     address: School of Business, State University of New York College at Geneseo, 1 College Circle, Geneseo, NY 14454, USA
+  - code: c
+    address: Department of Biological Sciences, Virginia Tech, 926 W Campus Dr., Blacksburg, Virginia 24061 USA
+  - code: d
+    address: Department of Plant Science, The Pennsylvania State University, 247 Agricultural Sciences and Industries Bldg., University Park, Pennsylvania 16802 USA
+  - code: e
+    address: Department of Forest Resources and Environmental Conservation, Virginia Tech, 310 W Campus Dr., Blacksburg, Virginia 24061 USA
+  - code: f
+    address: U.S. Geological Survey, Pennsylvania Cooperative Fish and Wildlife Research Unit, The Pennsylvania State University, University Park, Pennsylvania
+  - code: g
+    address: Cary Institute of Ecosystem Studies, 2801 Sharon Tpke., Millbrook, New York 12545 USA
 
@@
 bibliography: lagosag
-biblio-style: elsarticle-harv
+biblio-style: jsta
 
@@
 Further examples of such macroscale studies (see Heffernan et al.
-2014) in which lakes are spread across many regions at distances spanning hundreds to thousands of kilometers include Collins et al.
-(2017) and Read et al.
+2014) in which lakes are spread across many regions at distances spanning hundreds to thousands of kilometers include \citet{collinsLakeNutrientStoichiometry2017} and Read et al.
 (2015), who found that the strength of agriculture and lake nutrient relationships varied depending on geographic region and lake characteristics.
@@
 further limited lakes in our study to those with at least 10% of the total watershed area devoted to agricultural land-use and those that were sampled at least three times between 2000 and 2010.
-A total of 928 lakes met these selection criteria (Figure 1).
+A total of 928 lakes met these selection criteria (Figure \ref{fig1}).
 Because we focused on lakes in agricultural watersheds, more than 35  percent of lakes in our study are considered eutrophic to hypereutrophic using chlorophyll a as a diagnostic e versus only 15 percent for all lakes from Soranno et al.
@@
 
+\setcounter{figure}{0}
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.68\textwidth, height=3.5in,keepaspectratio]{../figures/11_map-1}
+  \end{center}
+  \caption{A) Map of lake locations and B) hydrologic (HUC4) regions.}\label{fig1}
+\end{figure*}
+
+### Model overview
+
+We evaluated the effects of agricultural activities on lake TN and TP concentrations using a Bayesian hierarchical modelling approach.
+A list of lake and watershed covariates with their summary statistics is available in Table 1.
+In the first part of our model evaluation, we compared models that each had only a single measure of watershed land-use along with all remaining non-watershed land-use predictors.
+These non-watershed land-use predictors were included in every fitted model and were defined as measures of near-stream land-use, soil characteristics, and lake and watershed characteristics.
+We took this approach of evaluating one watershed land-use measure at a time for two reasons: 1) because measures of watershed land-use were highly correlated, and 2) because it allowed us to more rigorously test our expectation that granular measures of agriculture provide additional explanatory power beyond that offered by more typical aggregate measures of agriculture.
+In the second part of our model evaluation, we selected the top-ranked watershed land-use model according to our selection criteria for lake N and P (see below) for further inspection of their standardized coefficient values (See Table \ref{table1}).
+Our models were of the form:
+
+\begin{equation}
+\begin{split}
+& y_i = N(\alpha_{j(i)} + \beta_1 * X_{1i}...\beta_n * X_{ni} + \gamma_{1j(i)} * W_{1i} + \gamma_{mj{i}} * W_{mi})\\
+& \binom{\alpha_j}{\gamma_{1j}} \sim MVN\left( \binom{\mu_\alpha}{\mu_{\gamma1}}, \Sigma \right)
+\label{eqn1} 
+\end{split}
+\end{equation}
+
+\noindent where yi is either TN or TP concentration for lake i, and $\beta$ are “global” (i.e.
+fixed effect) coefficients.
+This set of global coefficients included estimates for watershed soil characteristics, near-stream land-use, as well as fertilizer and manure inputs for each lake (Xi).
+Whereas $\beta$ coefficients were estimated as fixed effects, $\gamma$ coefficients and $\alpha$ intercepts were estimated as varying (i.e.
+random) slopes and intercepts respectively among m hydrologic regions j on watershed land-use (Wij).
+Region specific intercepts $\alpha$ and $\gamma$ slopes were assumed to come from a multivariate normal distribution (MVN) where $\mu_\alpha$ and $\mu_{\gamma1}$ are their respective grand mean (i.e., population level) estimates.
+We tested a variety of watershed land-use types for Wij, including both granular and more aggregate measures of agricultural activity.
+Our only aggregate measure of agricultural activity was agricultural land-use whereas we used several granular measures of agricultural activity.
+These included both detailed measures of watershed land-use such as corn and soybean cover as well as more detailed measures of nutrient inputs and near-stream land-use (Table 1).
+We included measures of both N and P inputs in both N and P models because of the possibility for stoichiometric interaction.
+Given our regularization scheme (i.e.
+our use of “horseshoe priors” described below) there was little reason to exclude P inputs from N models (and vice versa) because unless P inputs are strongly related to lake TN concentration, their coefficient will be forced close to zero.
+
+All models had the same set of fixed effect coefficients while each individual model used a single different watershed land-use variable as a random effect.
+This modelling strategy is supported by our view that watershed land-use is an indirect proxy (sensu Burcher et al.
+2007, Hayes et al.
+2015, King et al.
+2005) for other unquantifiable agricultural activities.
+Therefore, we expect the makeup of specific activities represented by this indirect measure to vary regionally.
+This contrasts with other predictor variables e like lake depth, where we have little evidence from prior studies that its effect on lake nutrient concentrations is spatially variable.
+Prior to model fitting, we examined the bivariate relationships between lake nutrient concentrations and all predictor variables using Pearson’s correlation coefficients (Figure A5) to determine the overall structure of the predictor dataset.
+We did not use the results of this exercise for building our model, performing model selection, or variable selection.
+For qualitative analysis of our model results, we classified predictor variables following Collins et al.
+(2017) into categories based on the dominant mechanism affecting lake nutrient concentrations, which includes nutrient inputs, nutrient transport, spatial configuration of land-use in stream buffers (Spatial config.), lake characteristics, and watershed land-use (LULC).
+
+We fit all models in a Bayesian framework using the brms R package interface to the Stan statistical program (Bürkner et al., 2017; Stan Development Team, 2017).
+We used horseshoe shrinkage priors on all fixed effect coefficients to evaluate variable importance (Carvalho et al.
+2010).
+We considered a response variable sensitive to a given predictor if the predictor’s 95% credible interval did not overlap 0.
+We standardized all predictor variables by subtracting the mean of each variable and dividing by their respective standard deviation so that model coefficients could be compared on roughly the same scale.
+As a result, the relative sensitivity of a response variable to a particular predictor is related to the relative magnitude of its coefficient estimate.
+We evaluated model fit of each watershed land-use variable (i.e., each model having one regionally varying coefficient) in two ways.
+First, we computed a Bayesian R2 following the method of Gelman et al.
+(2017) and second, we computed differences in expected log predictive density (ELPD) using the leave-one-out cross e validation routines provided by the loo R package and implemented in brms (Vehtari et al.
+2017).
+The loo package uses leave-one-out cross validation to estimate overall model error by computing O the average error of models iteratively trained on all the data except for a single point.
+ELPD values have a similar interpretation to information criterion measures such as Akaike information criterion (AIC) or Watanabe-Akaike information criterion (WAIC) except that values are on a different scale (Gelman et al.
+2013).
+Typically, models are considered to be different if they are separated by an AIC value of greater than 2 (Anderson and Burnham 2002), which is equivalent to an ELPD value of -1 (Gelman et al.
+2013).
+We report differences in ELPD among models using the notation $\Delta$ELPD.
+We selected the model with the lowest absolute value ELPD as the “top-ranked” model for detailed reporting and discussion as this signifies the model with the lowest leave one out cross-validation error for N and P respectively.
+
+We used the default settings of brms to generate posterior estimates using four chains of 4,000 iterations each with no thinning and discarding the first 1,000 iterations.
+We examined model fits to ensure that all models had acceptable convergence of MCMC chains and had approximately normal model residuals.
+We further tested for spatial correlation among model residuals using the spind R package (Carl et al.
+2018).
+All of our code for model fitting and evaluation is available at [Zenodo DOI].
+
+## Results
+
+### Effects of agriculture on lake nitrogen and phosphorus
+
+Lake characteristics (e.g., maximum depth and watershed to lake area ratio) along with measures of nutrient transport (e.g., baseflow) and near-stream agriculture were significant predictors in all lake N and P models that we fit.
+When we  compared among different models for each nutrient individually, we found that those with agricultural watershed O land-use (in the aggregate sense) were top-ranked (i.e., had the lowest absolute value leave-one-out cross validation score) for models of both TN and TP concentrations (Figure 2, Table 2).
+Although we observed no difference in the specific watershed land-use predictor used in each top-ranked model, we found differences in the extent to which each top-ranked model was substantially different from lower ranked models.
+For example, in the case of P, all models had nearly identical R2 (0.63) and the difference between the top-ranked model and second ranked model was modest ($\Delta$ELPD = 0.41).
+For N models, however, agricultural and corn land-use models had higher R2 (0.58) compared to other models and the difference between the top-ranked and second ranked model was more substantial ($\Delta$ELPD = 2.58, Figure 2, Table 1).
+
 \begin{figure}
   \begin{center}
-    \includegraphics[width=0.49\textwidth, height=3.5in,keepaspectratio]{../figures/11_map-1}
+    \includegraphics[width=0.49\textwidth, height=3.5in,keepaspectratio]{../figures/re-comparison-1}
   \end{center}
-  \caption{asdfdd}\label{fig1}
+  \caption{Population level slope estimates ($\mu_\gamma$) for the effect of watershed land-use cover on lake TN and TP from six candidate models.
+Values shown are posterior medians (filled circles) and 95\% credible intervals (solid lines).
+Also shown is a comparison to a zero effect (solid vertical line).
+Values that do not overlap zero are shaded in red.
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance.}\label{fig2}
 \end{figure}
 
-## References
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.3\textwidth,keepaspectratio]{../tables/03_model_summary}
+    \captionsetup{labelformat=empty}
+    \caption{\textbf{Table 2.
+} Diagnostics for each model listed by regionally varying coefficient.
+Table is sorted by decreasing $R^2$ and expected log predictive density (ELPD).
+ELPD has a similar interpretation to information criterion measures like AIC.
+Typically models are considered to be different if they are separated by an Akaike information criterion (AIC) value of greater than 2, which is equivalent to an ELPD value of -1.} \customlabel{table2}{2}
+  \end{center}
+\end{figure}
 
-Here we differ from PNAS and suggest natbib. References will appear in
-author-year form. Use `\citet{}`, `\citep{}`, etc as usual.
+When we looked more closely at each top-ranked model, we found similarities in the
+types of predictors that contributed significantly to the top-ranked N and P models (Figure 3).
+First, both N and P models included measures of lake characteristics such as maximum depth and watershed to lake area ratio as significant predictors, with the sign of these associated coefficients matching our conventional understanding, in which shallower lakes and lakes with greater hydrologic loads have higher TN and TP concentrations.
+Second, both models included measures of nutrient transport such as baseflow and precipitation, in which lakes with a “flashier” hydrology (i.e., having lower baseflow) where incoming water is primarily from surface runoff rather than from groundwater, had higher TN and TP concentrations.
+Finally, both models indicated that high near-stream agriculture (i.e., a high proportion of the area adjacent to the stream network was in agricultural land-use) was associated with lakes having higher TN and TP concentrations.
+Where N and P models differed was in the effect of soil clay content, in which soils with low clay content were associated with high lake N but had no significant relationship with P.
 
-## Inline R Code
+\setcounter{figure}{2}
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.7\textwidth, height=3.5in,keepaspectratio]{../figures/fe-1}
+  \end{center}
+  \caption{Global (fixed effect) coefficient values ($\beta$, for all non-LULC predictors) and population level estimates for the effect of watershed land-use ($\mu_\gamma$, for LULC) on lake TN and TP for each respective top-ranked model.
+Note that the values for LULC here are identical to their corresponding values in Figure 2.
+Values shown are posterior medians (filled circles) and 95\% credible intervals (solid lines).
+Also shown is a comparison to a zero effect (solid vertical line).
+Values that do not overlap zero are shaded in red.
+Horizontal bars separate coefficients in distinct predictor categories.
+Coefficient estimates are reported relative to standardized predictor variables centered at zero with unit variance and correspond with $\beta$ (and $\mu_\gamma$ for LULC) from Equation 1.}\label{fig3}
+\end{figure*}
 
-The PNAS sample included a fixed PNG image here, but this document prefers
-to show the results and embedding of _R_ code.
+Although top-ranked N and P models shared some similarities in the type of predictors that contributed significantly to each model, the coefficients of these models differed in magnitude, and thus the top-ranked models varied in their sensitivity to specific predictors (Figure 3).
+For example, the top-ranked P model was more sensitive to lake characteristics, whereas the top-ranked N model was more sensitive to watershed land-use.
+Quantitatively, lake TP concentrations were more sensitive to maximum depth ($\beta_{depth}$: median = -0.39, SD = 0.04) compared to lake TN concentrations ($\beta_{depth}$: median = -0.14, SD = 0.04); whereas lake TN concentrations were more sensitive to watershed agriculture land-use ($\beta_{ag}$: median = 0.44, SD = 0.11) compared to lake TP concentrations ($\beta_{ag}$: median = 0.10, SD = 0.08).
+Finally, although we found that near-stream agriculture was associated with both higher TN and TP concentrations (i.e., a source-effect of near-stream agriculture), there was not a significant difference in the magnitude (i.e., sensitivity) of this coefficient between N ($\beta_{bufferag}$: median = 0.16, SD = 0.06) and P ($\beta_{bufferag}$: median = 0.12, SD = 0.06) models.
 
-```{r figex, fig.width=3, fig.height=3, cache=TRUE, echo=TRUE, fig.cap="Narrow ggplot2 figure"}
-library(ggplot2)
-ggplot(mtcars, aes(wt, mpg)) +
-    geom_point(size=3, aes(colour=factor(cyl))) +
-    theme(legend.position="none")
-```
+No predictors in the nutrient input category appeared to be strongly related to either TN or TP concentrations.
+One explanation may be that these variables co-varied with watershed and near-stream land-use variables (Figure A5).
+In an attempt to further investigate this possibility, we fit alternative models excluding all land-use predictors.
+The results show that, at least in the case of N, removing these predictors e caused model variance to be apportioned from watershed and buffer land-use predictors to N input and P fertilizer predictors (Figure A4).
+However, this non-land-use N model had a relatively poor fit (R2 = 0.40) compared to the top-ranked model that included land-use as a predictor (R2 = 0.58).
 
-Here we use a standard knitr bloc with explicit options for
+### Regional variation in agriculture sensitivity
 
-- figure width and height (`fig.width`, `fig.height`), both set to three inches;
-- whether the code is shown (`echo=TRUE`); and
-- the caption (`fig.cap`) as shown above.
+Both TN and TP concentrations were sensitive to measures of watershed land-use as well as near-stream agriculture (Figure 2, Table 1).
+Despite these similarities, we found differences in both the magnitude of these effects and the extent to which we observed regional variation in watershed land-use sensitivity for N and P models (Figure 4).
+For P, there was little evidence that sensitivity to watershed land-use was regionally variable.
+More specifically, the credible intervals for the slope of each individual region overlapped the global slope estimate (Figure 4).
+In contrast, for N we found evidence for regional variation in sensitivity to watershed land-use.
+For this nutrient, the credible intervals for 2 of the 37 regions did not overlap the global estimate (Figure 4).
+These regions were found in parts of Iowa, Minnesota, and Illinois and appear to be more sensitive to watershed land-use – i.e., lake N increases at a faster rate per unit increase in agricultural land-use compared to other regions (Figure 5).
+The median soil clay content of watersheds in these regions was higher than the median across watersheds in all other regions (Figure 6).
+Furthermore, these two regions had a unique combination of both high soil clay content and extensive tile drainage (Figure S6).
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.49\textwidth, height=3.5in,keepaspectratio]{../figures/re-1}
+  \end{center}
+  \caption{Effect of watershed land-use ($\gamma_j$) for individual regions in the top-ranked lake N and P models.
+Values shown are posterior medians (filled circles) and 95\% credible intervals (solid lines) for individual hydrologic units (HUC4s) ordered from top to bottom according to longitude (west to east).
+Also shown is a comparison to a zero effect (solid vertical line).
+Values that are different from the population level effect are shaded in red.}\label{fig4}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.36\textwidth, height=3.5in,keepaspectratio]{../figures/tn_re_hu4-1}
+  \end{center}
+  \caption{Location of hydrologic regions sensitive to watershed land-use cover corresponding to highlighted credible intervals in Figure 4.}\label{fig5}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.38\textwidth, height=3.5in,keepaspectratio]{../figures/tn_re_compare-1}
+  \end{center}
+  \caption{Histograms showing the distribution of soil clay content for watersheds in regions sensitive to watershed land-use (see highlighted credible intervals in Figure 4) relative to watersheds all other regions.
+Medians for each group are shown as vertical dashed lines.}\label{fig6}
+\end{figure}
+
+## Discussion
+
+### Effects of granular measures of agriculture on lake nitrogen and phosphorus
+
+There is substantial unexplained variation around simple linear relationships between aggregate representations of watershed land-use in agriculture and both lake N and P (Figure S2).
+Our study was designed to examine these relationships in greater detail by testing whether more granular measures of agriculture could help explain some of this uncertainty for both N and P, and whether there were regional differences in these relationships.
+In sum, all models for TN and TP concentrations included at least one granular measure of agriculture, but there were also important differences between N and P related to the type of measures that were important to each.
+For example, we found little benefit of increased granularity of description (i.e., where measures are recorded in all the same locations as their aggregate equivalents) but consistent benefit of granular representation of the spatial configuration of land-use in near-stream buffers.
+
+### Spatial configuration
+
+The result showing that lake TN and TP concentrations are sensitive to the spatial configuration of land-use in near-stream buffers is consistent with our expectation and prior research.
+Specifically, our finding that model coefficients on near-stream agriculture (i.e., agricultural land-use in stream buffers) in all N and P models were significant and positive indicates a nutrient-delivery effect of stream buffer agriculture and suggests that the spatial configuration of agriculture with respect to stream buffers has a detectable influence on both lake N and P at macroscales.
+This is consistent with prior studies conducted over more limited spatial extents which examined relationships between lake or stream nutrient concentrations and agricultural land-use in stream buffers (Diebel et al.
+2007, Baker et al.
+2006, Gemesi et al.
+2011, Soranno et al.
+2015).
+In contrast to near-stream agriculture, we found that near-stream “natural” land-use was not significant in either N or P models.
+While we cannot definitively answer why, it may be related to the role that natural buffers play in nutrient cycling for N and P (Alexander et al.
+2008, Canham et al.
+2012).
+In the case of N, natural buffers may reduce stream loading by facilitating denitrification, whereas, in the case of P, natural buffers may trap particulate bound material without necessarily removing it (Mayer et al.
+2007, Naiman 2010).
+An alternative possibility is that we are observing a scale effect whereby the delivery effect of near-stream agriculture is spatially consistent whereas the trapping and removal effects of N and P by natural buffers is more spatially variable (Parn et al.
+2012).
+Finally, we may not have observed a protective effect of natural buffers because natural land-use in buffers is too coarse of a proxy for “riparian buffers” composed of forest or herbaceous vegetation (Mayer et al.
+2007).
+
+### Crop type
+
+We found that for N models, land-use of specific crops was significant, although it was not found in the top-ranked model.
+Specifically, we found that watershed land-use in corn production was a significant predictor in the second-ranked N model (Table 2).
+In the case of P by contrast, neither aggregate nor granular measures of watershed land-use were significant in any models (Figure 2).
+This can be explained by our finding that all watershed land-use metrics had weak relationships with lake P, especially relative to the strong relationships we observed between P and other factors like lake depth, hydrology, and near-stream agricultural land-use.
+Here, our finding is consistent with prior studies in stream ecosystems showing that the influence of hydrology exceeds that of agricultural land-use or anthropogenic P inputs (Metson et al.
+2017).
+
+### Nutrient inputs
+
+None of the nutrient input variables were significant for either N or P models.
+On the surface, this would seem to contradict the findings of prior research such as that of Bellmore et al.
+(2018), who found that stream TN concentrations were more strongly controlled by N input predictors relative to measures of either watershed or near-stream land-use.
+However, our finding has several alternative explanations.
+First, differences between our lake study and the Bellmore et al.
+(2018) stream study may simply point to differences in the controls on stream nitrogen concentrations relative to lake nitrogen concentrations (Allan 2004, Canham et al.
+2012).
+Second, our finding that N and P were insensitive to nutrient input variables may be a result of shared variance between nutrient input variables and watershed land-use.
+This makes sense given that agricultural land-uses and corn land-use in particular are associated with high rates of fertilizer and manure application (Powers 2007).
+To test this explanation, we formulated N models without a watershed land-use term and observed that model variance was transferred from watershed land-use to the nutrient input terms total N input and P fertilizer (Figure S4).
+While the positive coefficient on total N input has a straightforward interpretation, the negative coefficient on P fertilizer is unclear.
+Rather than evidence of a true inverse relationship between P fertilizer and N (or evidence for stoichiometric interaction sensu Paerl et al.
+2016), we interpret the negative coefficient on P fertilizer as evidence of either model misspecification (i.e., model fit was poor compared to the model with land-use because N was very sensitive to land-use) or as evidence of multicollinearity among nutrient input variables (Figure S5).
+Thus, we think that it is likely that the removal of one of the key drivers of N (being land-use) caused model variance to be transferred to nutrient input predictors generally such that the specific highlighting of P fertilizer is a result of noise rather than a true relationship.
+
+### Nutrient transport
+
+An important category of predictors in our models was nutrient transport.
+For example, we found that baseflow was a significant predictor in all N but especially all P models.
+This is consistent with prior research at macroscales showing the sensitivity of lake nutrients to this metric (Collins et al.
+2017).
+In contrast to baseflow, we found that watershed soil clay content was a significant predictor in all N models but not in any P models.
+Furthermore, we found that the coefficient on soil clay content was negative, which was contrary to our expectation, and prior research.
+It seems to suggest a negative correlation between clay content and N.
+However, upon closer inspection, we did not find evidence for such a relationship.
+Instead, we found evidence for a non-linear relationship, which may explain the negative coefficient on clay, whereby clay and TN were positively correlated over most of the range of watershed clay content but were negatively correlated in watersheds with very high soil clay content (> 20%; Figure S7).
+This non-linear relationship may be an artifact of the specific non-random sampling of our lakes whereby the lakes with extremely high soil clay content watersheds happen to have extremely long water residence times leading to extensive removal of N loads due to denitrification (Groffman et al.
+2009).
+Overall, granular measures of agriculture were significant in both N and P models.
+However, the contribution of such measures relative to other non-agricultural predictors was greater for N models (Figure 2, Figure 3).
+One reason why granular measures of agricultural activity had a greater effect on N models may be that variation in N is less effectively captured solely by lake and watershed characteristics owing in part to the more complex nature of transformations in the nitrogen cycle.
+This finding is consistent with that of Collins et al.
+(2017) and Wagner and Schliep (2018) who found that lake depth coefficients were of a much higher magnitude for P relative to N.
+This is expected since depth strongly controls internal P loading (i.e., recycling), which is a dominant control on lake phosphorus dynamics (Sondergaard et al.
+2013).
+
+### Regional variation in agriculture--nutrient relationships
+
+The macroscale nature of our study motivated our second research question examining how relationships between agricultural activities and lake nutrients vary regionally.
+This is because recent research has shown that analyzing macroscale lake datasets without considering the possibility of regionally varying relationships runs the risk of drawing imprecise or incorrect conclusions because it can lump together lakes with fundamentally different responses to a given predictor variable (Qian et al.
+2019).
+Additionally, we looked at this question because prior studies have shown regional variation in the relationship of lake nutrient concentrations to aggregate measures of agriculture (Wagner and Schliep 2018).
+In our study, we found mixed evidence for regional variation in relationships with watershed land-use, depending on the lake nutrient response variable.
+For N, we found evidence for regional variation whereby lakes in two of the 37 regions were more sensitive to changes in agricultural land-use relative to other regions.
+The reasons for this elevated sensitivity are unclear, but one possible reason may be that watersheds in these more sensitive regions had higher median soil clay content than the median soil clay content of watersheds in less sensitive regions (Figure 6).
+Higher soil clay content in particular may ultimately control the nitrogen content of field runoff because it is associated with more direct (i.e., tile) drainage.
+For example, maps produced by Capel et al.
+(2018a) suggest that our more sensitive regions correspond roughly with areas where field exports of nutrients are likely to bypass trapping by riparian buffers.
+As evidence of this association, data from Nakagaki and Wieczorek (2016) indicate that watersheds in these two sensitive regions had a unique combination of high soil clay content and extensive tile drainage (Figure S6).
+For P, we found no evidence for regional variation in its relationship with watershed land-use.
+This finding, that watershed land-use can be modelled as a global (fixed) effect, is consistent with that of Taranu and Gregory-Eaves (2008), who found no statistically significant differences in region-specific relationships between lake P and agricultural land-use.
+However, it is inconsistent with that of Wagner et al.
+(2011), who found regionally variable relationships between lake P and agricultural land-use using a multilevel modelling framework.
+One reason that both our analysis and the Taranu and Gregory-Eaves (2008) study did not observe regional variation in the watershed land-use versus P relationship may be that P is so strongly controlled by lake depth that there is little additional explanatory power offered by including a watershed land-use term.
+In addition, if lake P is controlled primarily by lake depth, which we can assume does not change with time, then our results may explain the finding of Oliver et al.
+(2017) that lake P trends are spatially consistent whereas lake N trends have distinct regional variability.
+
+### Management implications
+
+Knowledge of differences in the drivers of lake N and P can support the design of effective and efficient policy approaches to maintain or improve water quality.
+For instance, our finding of regional variation in the relationship between lake TN concentrations and watershed land-use in agriculture suggests spatial targeting of best management practices (BMPs) to specific regions known to be highly sensitive (Holmes et al.
+2016).
+In addition, our finding of strong relationships between lake TP concentrations and lake characteristic predictors contrasts with the strong relationships we observed between watershed land-use and lake TN.
+Given that watershed land-use, rather than lake characteristics, is a more feasible management target, our results suggest that the cost-effectiveness of BMPs could differ depending on whether the goal is to protect against excess N, P, or both (Paerl et al.
+2016).
+For P, our analysis suggests that nutrient control policies are likely to be especially effective in shallow lakes and lakes with low baseflow (i.e., those with flashier hydrology).
+Conversely, phosphorus control in deeper lakes and reservoirs with long residence times will likely require recovery efforts in addition to prevention efforts due to the long time-scales of stored (i.e., legacy) P (Powers et al.
+2015).
+In contrast to P, our results show that lake TN concentrations are more sensitive to watershed land-use.
+This suggests that policies to enhance the use of BMPs to reduce N inputs to lakes are likely to require a greater degree of stakeholder involvement, possibly through consideration of tradeoffs between land retirement and working lands programs (Capel et al.
+2018a, NRC 2010).
+
+### Future research priorities
+
+Due to a lack of temporally resolved data, our study focused on spatial patterns in sensitivity of lake TN and TP concentrations to measures of agricultural activity and did not examine the possibility that such relationships could be temporally variable.
+A consequence of this was that we assumed that relationships between lake N and P relative to agricultural drivers did not change over our data collection window (2000 - 2010).
+However, there are several instances where time may be important, and these would likely be fruitful areas for future research.
+For example, Lark et al.
+(2015) showed marked conversion of conservation reserve program (CRP) lands to cropland throughout the footprint of our study from 2008 to 2012.
+Such changes in land-use could make it more difficult to quantify lake sensitivity to agriculture if relationships vary through time especially if relationships are subject to threshold effects (Renwick et al.
+2008).
+A more subtle illustration of when time may be important is when field-scale nutrient export is highly dependent on episodic hydrology.
+For example, a number of previous studies have shown that field-scale nutrient export of N is greatest when a series of dry years is followed by a wet spring (Motew et al.
+2017, Strickling and Obenour 2018).
+It might make sense then to organize modeling around whether lake watersheds are generally subject to slowflow, fastflow, or drainflow (Capel et al.
+2018a) nutrient transport rather than solely taking a spatial regionalization approach (i.e., using HUCs).
+Barriers to more detailed temporal approaches include greater demands of spatio-temporally resolved data products.
+Overall, our results point to hydrology predictors like baseflow as an instance where we only have spatially coarse information and development of more granular estimates of watershed hydrology, possibly using the output of hydrology models, would likely improve future research efforts.
+
+## Conclusion
+
+We show that granular measures of agricultural activity are related to both lake N and P and that these relationships are regionally variable for lake N.
+Taken together, our results suggest that lake TP concentrations are more strongly driven by lake characteristics; whereas, lake TN concentrations are more strongly driven by watershed land-use.
+A consequence of our finding is that lake TP concentrations are largely predictable from lake-specific measures such as near-stream land-use, lake depth, and transport metrics like baseflow; whereas, accurate predictions of lake N likely requires not only lake specific information (including granular measures of agriculture) but also consideration of regional context due to complex regional variation of soil characteristics.
+Such differences in lake nutrient model sensitivity to measures of agricultural activity may affect the outcome of policies to enhance water quality depending on whether they focus on lake N or P.
 
@@
 This file is then included via standard LaTeX commands.
-
-## Typeset Code (But Do Not Run It)
-
-We can also just show code.
-
-```r
-xx <- faithful[,"eruptions"]
-fit <- density(xx)
-plot(fit)
-```
-
-This simply used a pandoc bloc started and ended by three backticks,
-with `r` as the language choice.  Similarly, _many_ other languages
-can be typeset directly simply by relying on pandoc.
-
-## Single column equations
-
-Authors may use 1- or 2-column equations in their article, according to
-their preference.
-
-To allow an equation to span both columns, options are to use the
-`\begin{figure*}...\end{figure*}` environment mentioned above for
-figures. The `\begin{widetext}...\end{widetext}` environment as shown
-in equation \ref{eqn:example} below is deprecated, but \LaTeX commands
-`\onecolumn` and `\twocolumn` work fine.
-
-Please note that this option may run into problems with floats and
-footnotes, as mentioned in the [cuted package
-documentation](http://texdoc.net/pkg/cuted). In the case of problems
-with footnotes, it may be possible to correct the situation using
-commands `\footnotemark` and `\footnotetext`.
 

### 2020-04-17 manuscript/manuscript.Rmd
test ref and figure linking

@@
 2015).
-Although the term granular can be used in a general sense to describe any detailed agricultural measure, we define the term more narrowly as only those that have a specific aggregate counterpart (Table 1).
+Although the term granular can be used in a general sense to describe any detailed agricultural measure, we define the term more narrowly as only those that have a specific aggregate counterpart (Table \ref{table1}).
 
@@
 
-\begin{figure}
+\begin{figure}[H]
   \begin{center}
@@
 We evaluated the effects of agricultural activities on lake TN and TP concentrations using a Bayesian hierarchical modelling approach.
-A list of lake and watershed covariates with their summary statistics is available in Table 1.
+A list of lake and watershed covariates with their summary statistics is available in Table \ref{table1}.
 In the first part of our model evaluation, we compared models that each had only a single measure of watershed land-use along with all remaining non-watershed land-use predictors.
@@
 Our only aggregate measure of agricultural activity was agricultural land-use whereas we used several granular measures of agricultural activity.
-These included both detailed measures of watershed land-use such as corn and soybean cover as well as more detailed measures of nutrient inputs and near-stream land-use (Table 1).
+These included both detailed measures of watershed land-use such as corn and soybean cover as well as more detailed measures of nutrient inputs and near-stream land-use (Table \ref{table1}).
 We included measures of both N and P inputs in both N and P models because of the possibility for stoichiometric interaction.
@@
 For example, in the case of P, all models had nearly identical R2 (0.63) and the difference between the top-ranked model and second ranked model was modest ($\Delta$ELPD = 0.41).
-For N models, however, agricultural and corn land-use models had higher R2 (0.58) compared to other models and the difference between the top-ranked and second ranked model was more substantial ($\Delta$ELPD = 2.58, Figure 2, Table 1).
+For N models, however, agricultural and corn land-use models had higher R2 (0.58) compared to other models and the difference between the top-ranked and second ranked model was more substantial ($\Delta$ELPD = 2.58, Figure 2, Table \ref{table1}).
 
@@
 
-Both TN and TP concentrations were sensitive to measures of watershed land-use as well as near-stream agriculture (Figure 2, Table 1).
+Both TN and TP concentrations were sensitive to measures of watershed land-use as well as near-stream agriculture (Figure 2, Table \ref{table1}).
 Despite these similarities, we found differences in both the magnitude of these effects and the extent to which we observed regional variation in watershed land-use sensitivity for N and P models (Figure 4).

### 2020-04-17 manuscript/manuscript.Rmd
center equation

@@
 Here agricultural land-use is defined in the aggregate sense as the proportion of land used for agriculture in a lake’s watershed whereas “natural” land-uses include the sum of all non-agriculture and non-developed CDL classes.
-We identified the streams associated with each lake using the stream network extraction tool in the nhdR interface e (Stachelek 2019) to the National Hydrography Network (USGS 2019).
+We identified the streams associated with each lake using the stream network extraction tool in the nhdR interface (Stachelek 2019) to the National Hydrography Network (USGS 2019).
 We compiled soil characteristics for each lake watershed using the Gridded Soil Survey Geographic Database (gSSURGO, USDA 2019) where we used the python package gssurgo (Stachelek 2019) to access gSSURGO  products.
@@
 \begin{equation}
-\begin{split}
-& y_i = N(\alpha_{j(i)} + \beta_1 * X_{1i}...\beta_n * X_{ni} + \gamma_{1j(i)} * W_{1i} + \gamma_{mj{i}} * W_{mi})\\
+\begin{aligned}
+y_i = N(\alpha_{j(i)} + \beta_1 &* X_{1i}...\beta_n * X_{ni} + \gamma_{1j(i)} * W_{1i} + \gamma_{mj{i}} * W_{mi})\\
 & \binom{\alpha_j}{\gamma_{1j}} \sim MVN\left( \binom{\mu_\alpha}{\mu_{\gamma1}}, \Sigma \right)
 \label{eqn1} 
-\end{split}
+\end{aligned}
 \end{equation}

### 2020-04-17 manuscript/manuscript.Rmd
all figures, tables added, bib cites added through intro

@@
 
-Freshwaters are vulnerable to eutrophication in areas of high agricultural land-use and land cover because agricultural activities are associated with high nutrient runoff and loading to groundwater and streams (Allan 2004, Arbuckle and Downing, 2001, Daniel et al.
-2010, Taranu et al.
-2008).
+Freshwaters are vulnerable to eutrophication in areas of high agricultural land-use and land cover because agricultural activities are associated with high nutrient runoff and loading to groundwater and streams \citep{allanLandscapesRiverscapesInfluence2004,arbuckleInfluenceWatershedLand2001,danielInfluencesSpatialScale2010,taranuQuantifyingRelationshipsPhosphorus2008}.
 High runoff and loading in these areas is a result of high rates of nutrient input combined with hydrologic modifications that decrease the travel time of these inputs from the land surface to lakes \citep{blannEffectsAgriculturalDrainage2009}.
-Surprisingly, while some studies have found strong relationships between agricultural land-use and land cover (hereafter referred to as “land-use” or LULC) and lake nutrient concentrations (Arbuckle and Downing 2001, Taranu et al.
-2008), others have found more mixed results (Jones et al.
-2008), particularly in studies that include many lakes located in multiple regions (Soranno et al.
-2015).
-Further examples of such macroscale studies (see Heffernan et al.
-2014) in which lakes are spread across many regions at distances spanning hundreds to thousands of kilometers include \citet{collinsLakeNutrientStoichiometry2017} and Read et al.
-(2015), who found that the strength of agriculture and lake nutrient relationships varied depending on geographic region and lake characteristics.
+Surprisingly, while some studies have found strong relationships between agricultural land-use and land cover (hereafter referred to as “land-use” or LULC) and lake nutrient concentrations \citep{arbuckleInfluenceWatershedLand2001,downingPredictingCyanobacteriaDominance2001,taranuQuantifyingRelationshipsPhosphorus2008}, others have found more mixed results \citep{jonesRoleLandCover2008}, particularly in studies that include many lakes located in multiple regions \citep{sorannoEffectsLandUse2015}.
+Further examples of such macroscale studies (see \citealt{heffernanMacrosystemsEcologyUnderstanding2014}) in which lakes are spread across many regions at distances spanning hundreds to thousands of kilometers include \citet{collinsLakeNutrientStoichiometry2017} and \citet[]{readImportanceLakespecificCharacteristics2015}, who found that the strength of agriculture and lake nutrient relationships varied depending on geographic region and lake characteristics.
 
 Mixed results from prior studies may be due to two difficulties in quantifying lake nutrient and agricultural land-use relationships.
-First, the pathways of nutrients from fields to streams and ultimately to lakes are complex and indirect (Cherry et al.
-2008, Heathwaite et al.
-2003, King et al.
-2005).
+First, the pathways of nutrients from fields to streams and ultimately to lakes are complex and indirect \citep{cherryAssessingEffectivenessActions2008,heathwaitePhosphorusIndicatorsTool2003,kingSpatialConsiderationsLinking2005}.
 For example, in order for nitrogen applied as fertilizer to reach a lake, it must be transported to streams or groundwater in excess of microbial denitrification, plant use, and microbial uptake.
-Then, it must travel, again, often undergoing repeated chemical transformation as it passes through riparian buffers and along stream networks before finally entering the lake (Maranger et al.
-2018).
+Then, it must travel, again, often undergoing repeated chemical transformation as it passes through riparian buffers and along stream networks before finally entering the lake \Citep{marangerStoichiometryCarbonNitrogen2018}.
 Each step of the journey represents an opportunity for those nutrients to be sequestered or removed.
-Further, overall hydrologic transport is influenced by soil type (Naiman et al.
-2010), and topography.
-Thus, the nutrients that ultimately enter a lake are a function of filtering by the landscape as well as geochemical transformation processes that are difficult to capture at broad scales (Canham et al.
-2012, Maranger et al.
-2018).
+Further, overall hydrologic transport is influenced by soil type \citep{naiman2010riparia}, and topography.
+Thus, the nutrients that ultimately enter a lake are a function of filtering by the landscape as well as geochemical transformation processes that are difficult to capture at broad scales \citep{canhamNitrogenDepositionLake2012,marangerStoichiometryCarbonNitrogen2018}.
 
-Second, much of our evidence for a connection between agricultural land-use and increased nutrient concentrations comes from studies focusing on a single watershed or on several watersheds within a single geographic region (Capel et al.
-2018b, Daniel et al.
-2010, Hayes et al.
-2015, Renwick et al.
-2008).
+Second, much of our evidence for a connection between agricultural land-use and increased nutrient concentrations comes from studies focusing on a single watershed or on several watersheds within a single geographic region \citep{capelpauldAgricultureRiverRuns2018,danielInfluencesSpatialScale2010, hayesClimateLandUse2015, renwickWaterQualityTrends2008}.
 These studies tend to focus on very detailed measures of agricultural activity such as tillage and other practices, nutrient amendments, and their spatial arrangement.
-However, studies at broader spatial scales (i.e., the macroscale, Heffernan et al.
-2014), which aim to provide a more general view of relationships between lake nutrient concentrations and agriculture, tend to focus only on relatively coarse measures of agricultural activity (Fergus et al.
-2016, Filstrup et al.
-2018, Read et al.
-2015, Schmadel et al.
-2019).
+However, studies at broader spatial scales (i.e., the macroscale, \citealt{heffernanMacrosystemsEcologyUnderstanding2014}, which aim to provide a more general view of relationships between lake nutrient concentrations and agriculture, tend to focus only on relatively coarse measures of agricultural activity \citep{filstrupEvidenceRegionalNitrogen2018,readImportanceLakespecificCharacteristics2015,schmadelSmallPondsHeadwater2019}.
 As a result, it is unclear to what extent the mixed results from prior broad-scale studies might be due to the limited use of detailed measures of agricultural activity or simply from regional variation.
@@
 The first is by using granular measures that are recorded in the same locations as their aggregate equivalents but are more descriptive.
-For example, in broad-scale studies, the proportion of land used for agriculture in a lake watershed is sometimes replaced by separate representations of the land used for pasture and the land used for row-crops (Abell et al.
-2011, Collins et al., 2017).
+For example, in broad-scale studies, the proportion of land used for agriculture in a lake watershed is sometimes replaced by separate representations of the land used for pasture and the land used for row-crops \citep{abellRelationshipsLandUse2011,collinsLakeNutrientStoichiometry2017}.
 The second is by using granular measures that have the same description as their aggregate equivalents, but that are measured in more specific locations.
-For example, a small number of lake studies have compared the proportion of land used for agriculture in near-stream buffers versus the watershed as a whole (Gemesi et al.
-2011, Soranno et al.
-2015).
+For example, a small number of lake studies have compared the proportion of land used for agriculture in near-stream buffers versus the watershed as a whole \citep{gemesiEffectsWatershedConfiguration2011,sorannoEffectsLandUse2015}.
 Although the term granular can be used in a general sense to describe any detailed agricultural measure, we define the term more narrowly as only those that have a specific aggregate counterpart (Table \ref{table1}).
@@
 For this reason, findings from broad-scale studies may be less useful in applied management settings because coarse (i.e.
-aggregate) land-use and land cover change metrics have become less widely used policy instruments (Morefield et al.
-2016).
-Instead, recent policy interventions go beyond aggregate measures of agricultural activity to target more specific measures such as implementation of specific farming practices, no-till agriculture, and construction of riparian buffer strips (Capel et al.
-2018a, NRC 2010, Yang et al.
-2005).
+aggregate) land-use and land cover change metrics have become less widely used policy instruments \citep{morefieldGrasslandsWetlandsAgriculture2016}.
+Instead, recent policy interventions go beyond aggregate measures of agricultural activity to target more specific measures such as implementation of specific farming practices, no-till agriculture, and construction of riparian buffer strips \citep{capelConceptualFrameworkEffectively2018, nrcSustainableAgriculturalSystems2010,yangSpatialTargetingConservation2005}.
 Thus, broad-scale studies could be made more relevant for informing policy interventions if they used covariates that have a similar level of granularity to those used in fine-scale studies.
@@
 One likely reason that broad-scale studies have rarely used granular agricultural data is that until recently, such data have not been available with corresponding lake nutrient concentration data over large geographic extents.
-Although a few examples exist of studies connecting granular agricultural data to either stream nitrogen or phosphorus concentrations at the macroscale (Boyer et al.
-2002, Bellmore et al.
-2018, Metson et al.
-2017), most studies have focused on either nitrogen (N) or phosphorus (P) but not on both at the same time (Alexander et al.
-2008).
+Although a few examples exist of studies connecting granular agricultural data to either stream nitrogen or phosphorus concentrations at the macroscale \citep{boyerAnthropogenicNitrogenSources2002,bellmoreNitrogenInputsDrive2018,metsonLinkingTerrestrialPhosphorus2017}, most studies have focused on either nitrogen (N) or phosphorus (P) but not on both at the same time \citep{alexanderDifferencesPhosphorusNitrogen2008}.
 Crucially, we are not aware of prior work examining relationships between a multiple granular measures of agricultural activity on either lake N or P concentrations at macroscales.
@@
 There are several plausible expectations, which are based on the findings of broad-scale stream studies as well as the findings of fine-scale lake studies, for the type of relationships between such measures and lake nutrient concentrations that may emerge at macroscales.
-First, we expect that increased nutrient inputs to the land surface as fertilizer and manure will increase lake nutrient concentrations (Bellmore and other 2018, Renwick et al.
-2008).
+First, we expect that increased nutrient inputs to the land surface as fertilizer and manure will increase lake nutrient concentrations \citep{bellmoreNitrogenInputsDrive2018,renwickWaterQualityTrends2008}.
 Second, we expect that lakes with watersheds that have high soil clay content and high soil organic carbon content will have higher lake nutrient concentrations.
-This will occur because clay soils tend to have higher rates of surface runoff and have higher organic matter content relative to sandy soils, despite the tendency for higher organic matter content to increase water storage and reduce surface runoff (Capel et al.
-2018b).
-Finally, we expect that lakes with stream networks characterized by extensive near-stream agriculture will have higher nutrient concentrations because there will be less interception of agricultural runoff (Naiman et al.
-2010).
+This will occur because clay soils tend to have higher rates of surface runoff and have higher organic matter content relative to sandy soils, despite the tendency for higher organic matter content to increase water storage and reduce surface runoff \citep{capelpauldAgricultureRiverRuns2018}.
+Finally, we expect that lakes with stream networks characterized by extensive near-stream agriculture will have higher nutrient concentrations because there will be less interception of agricultural runoff \citep{naiman2010riparia}.
 
@@
 The first key uncertainty is the extent to which lake and watershed characteristics, such as watershed hydrology and soil type, affect relationships between granular measures of agricultural activity and lake nutrient concentrations at the macroscale.
-For example, macroscale studies have found that lake P concentrations are strongly dependent on lake depth (Collins et al.
-2017), but the degree to which granular agricultural data provide additional explanatory power is unknown.
-Similarly, Abell et al.
-(2011) found that watershed to lake area ratio (i.e.
+For example, macroscale studies have found that lake P concentrations are strongly dependent on lake depth \citep{collinsLakeNutrientStoichiometry2017}, but the degree to which granular agricultural data provide additional explanatory power is unknown.
+Similarly, \citet{abellRelationshipsLandUse2011} found that watershed to lake area ratio (i.e.
 lake water residence time) was positively related to lake N concentrations after controlling for aggregate measures of agricultural land-use, but it is unknown whether this mediation effect would also affect relationships with more granular measures of agriculture.
@@
 The second key uncertainty is the extent to which relationships between granular measures of agricultural activity and lake nutrient concentrations vary regionally.
-For example, previous macroscale studies on lake nutrient concentrations have found that relationships between lake chlorophyll and nutrient concentrations vary regionally according to hydrologic subregions (Wagner et al.
-2011, Qian et al.
-2019).
+For example, previous macroscale studies on lake nutrient concentrations have found that relationships between lake chlorophyll and nutrient concentrations vary regionally according to hydrologic subregions \citep{wagnerLandscapeDriversRegional2011,qianImplicationsSimpsonParadox2019}.
 Models in which separate relationships (e.g.
-slopes) are estimated for different regions, such as those used by Wagner et al.
-(2011), can be used to test differences among regions in the sensitivity to nutrient predictors.
-Wagner et al.
-(2011) found that the slope of the chlorophyll to P relationship was notably higher in several of their study regions and found that lakes with high pasture land-use in their watershed were more sensitive to changes in P concentrations (larger, positive slope estimate).
+slopes) are estimated for different regions, such as those used by \citet{wagnerLandscapeDriversRegional2011}, can be used to test differences among regions in the sensitivity to nutrient predictors.
+\citet{wagnerLandscapeDriversRegional2011} found that the slope of the chlorophyll to P relationship was notably higher in several of their study regions and found that lakes with high pasture land-use in their watershed were more sensitive to changes in P concentrations (larger, positive slope estimate).
 They suggest that elevated sensitivity in high pasture regions is due to dual N and P nutrient enrichment associated with this land cover type.
-Given the findings of this and other studies in stream ecosystems (Alexander et al.
-2008), it follows that other relationships in lakes may vary regionally, but whether or not this includes relationships with granular measures of agricultural activity remains unknown.
+Given the findings of this and other studies in stream ecosystems \citep{alexanderDifferencesPhosphorusNitrogen2008}, it follows that other relationships in lakes may vary regionally, but whether or not this includes relationships with granular measures of agricultural activity remains unknown.
 
@@
 Such differences in lake nutrient model sensitivity to measures of agricultural activity may affect the outcome of policies to enhance water quality depending on whether they focus on lake N or P.
-
-## Digital Figures
-
-Markdown, Pandoc and LaTeX support `.eps` and `.pdf` files.
-
-Figures and Tables should be labelled and referenced in the standard way
-using the `\label{}` and `\ref{}` commands.
-
-The R examples above show how to insert a column-wide
-figure. To insert a figure wider than one column, please use the
-`\begin{figure*}...\end{figure*}` environment.
-
-One (roundabout) way of doing this is to _not_ actually plot a figure, but to
-save it in a file as the following segment shows:
-
-This file is then included via standard LaTeX commands.
-
-\begin{equation}
-  \begin{aligned}
-(x+y)^3&=(x+y)(x+y)^2\\
-       &=(x+y)(x^2+2xy+y^2) \\
-       &=x^3+3x^2y+3xy^3+x^3. 
-       \label{eqn:example} 
-  \end{aligned}
-\end{equation}
-
-<!-- pandoc writes all tables using longtable, which fails in 2-column mode
-
-  Species                    CBS     CV     G3
-  ----------------------- ------ ------ ------
-  1\. Acetaldehyde           0.0    0.0    0.0
-  2\. Vinyl alcohol          9.1    9.6   13.5
-  3\. Hydroxyethylidene     50.8   51.2   54.0
-
-  : Comparison of the fitted potential energy surfaces and ab initio
-  benchmark electronic energy calculations
-
--->

### 2020-04-17 manuscript/manuscript.Rmd
add inline cite links up to discussion

@@
 PAS was also supported by the USDA National Institute of Food and Agriculture, Hatch project 1013544.
-ARK supported by Hatch Appropriations under Project #PEN04571 and Accession #1003346.
+ARK was supported by Hatch Appropriations under Project #PEN04571 and Accession #1003346.
 We thank Sarah Collins for early input on the design and motivation for this study.
@@
 
-We analyzed data on lake total nitrogen (TN) and total phosphorus (TP) concentrations from the LAGOS-NE data product (Soranno and Cheruvelil 2017).
-The LAGOS-NE nutrient data are limited to surface (or “epilimnetic”) samples and were derived from federal, state, tribal, and non-profit agencies, as well as university researchers and citizen scientist data collections (Soranno et al.
-2017).
+We analyzed data on lake total nitrogen (TN) and total phosphorus (TP) concentrations from the LAGOS-NE data product \citep{soranno2017lagos}.
+The LAGOS-NE nutrient data are limited to surface (or “epilimnetic”) samples and were derived from federal, state, tribal, and non-profit agencies, as well as university researchers and citizen scientist data collections \citep{sorannoLAGOSNEMultiscaledGeospatial2017}.
 We collapsed lake nutrient data to long-term median values computed using all data from the summer stratified period (i.e.
@@
 
-Our first source for granular agricultural information was the 2010 Cropland Data Layer (CDL, USDA 2019), which we used to generate lake watershed and stream buffer estimates of the proportion of land cover due to specific crops such as corn and soybeans.
-We used the R package cdlTools to access CDL products (Chen 2018).
+Our first source for granular agricultural information was the 2010 Cropland Data Layer (CDL, \citealt{usda-nassNationalAgriculturalStatistics2019}), which we used to generate lake watershed and stream buffer estimates of the proportion of land cover due to specific crops such as corn and soybeans.
+We used the R package cdlTools to access CDL products \citep{chenToolsDownloadWork2018}.
 We used the 2010 CDL data because this was the first year of high resolution (30 x 30m) CDL data collection that matched our lake nutrient data collection window.
-Because the CDL contains detailed coverage for dozens of crops, including rare crops with little to no coverage, we re-categorized CDL data based on Lark et al.
-(2015) to a more limited set of categories (Table A1).
+Because the CDL contains detailed coverage for dozens of crops, including rare crops with little to no coverage, we re-categorized CDL data based on \citet{larkCroplandExpansionOutpaces2015} to a more limited set of categories (Table A1).
 
 As a more granular representation of watershed agricultural land use, we measured the proportion of land cover in agricultural and “natural” land-uses in 100-m buffers of lake shorelines and streams for each lake watershed.
-We chose a 100-m buffer width because this width is inclusive of nearly all “riparian buffers” (Mayer et al.
-2007).
+We chose a 100-m buffer width because this width is inclusive of nearly all “riparian buffers” \citep{mayerMetaAnalysisNitrogenRemoval2007}.
 Here agricultural land-use is defined in the aggregate sense as the proportion of land used for agriculture in a lake’s watershed whereas “natural” land-uses include the sum of all non-agriculture and non-developed CDL classes.
-We identified the streams associated with each lake using the stream network extraction tool in the nhdR interface (Stachelek 2019) to the National Hydrography Network (USGS 2019).
-We compiled soil characteristics for each lake watershed using the Gridded Soil Survey Geographic Database (gSSURGO, USDA 2019) where we used the python package gssurgo (Stachelek 2019) to access gSSURGO  products.
-One such product was wetland potential, defined as the percentage of the soil grid that meets the criteria for hydric soils formed under conditions of saturation, flooding, or ponding long enough to develop anaerobic conditions but not so long as to be classified as a permanent waterbody (USDA 2019).
-Finally, we compiled mean annual nutrient inputs via fertilizer and manure to lake watersheds from 1982-2001 using county level data provided by Ruddy et al.
-(2006).
-We spatially aligned these county level estimates to lake watershed polygons provided by LAGOS-NE (Soranno and Cheruvelil 2017) using the area-weighted interpolation functions provided by the sf R package (Pebesma 2019).
-All of our data and data processing code are available at [Zenodo DOI].
+We identified the streams associated with each lake using the stream network extraction tool in the nhdR interface \citep{stachelekNhdRToolsWorking2019} to the National Hydrography Network \citep{usgsNationalHydrographyDataset2019}.
+We compiled soil characteristics for each lake watershed using the Gridded Soil Survey Geographic Database (gSSURGO, \citealt{soil2016gridded}) where we used the python package gssurgo \citep{stachelekGssurgoPythonToolbox2019} to access gSSURGO  products.
+One such product was wetland potential, defined as the percentage of the soil grid that meets the criteria for hydric soils formed under conditions of saturation, flooding, or ponding long enough to develop anaerobic conditions but not so long as to be classified as a permanent waterbody \citep{soil2016gridded}.
+Finally, we compiled mean annual nutrient inputs via fertilizer and manure to lake watersheds from 1982-2001 using county level data provided by \citet{ruddy2006county}.
+We spatially aligned these county level estimates to lake watershed polygons provided by LAGOS-NE \citep{LAGOSgis} using the area-weighted interpolation functions provided by the sf R package \citep{pebesma2018}.
+All of our data and data processing code are available at \href{https://doi.org/10.5281/zenodo.3754916}{doi:10.5281/zenodo.3754916}.
 
@@
 We restricted the lakes included in the study to those located within the footprint of LAGOS-NE which includes lakes located in 17 Northeastern and Midwest U.S.
-states (Soranno et al., 2017).
+states \citep{sorannoLAGOSNEMultiscaledGeospatial2017}.
 We excluded lakes from our analysis if they had a surface area > 400 km2 or a maximum depth > 35 m.
@@
 A total of 928 lakes met these selection criteria (Figure \ref{fig1}).
-Because we focused on lakes in agricultural watersheds, more than 35  percent of lakes in our study are considered eutrophic to hypereutrophic using chlorophyll a as a diagnostic e versus only 15 percent for all lakes from Soranno et al.
-(2017) located within our study extent (Figure A3).
+Because we focused on lakes in agricultural watersheds, more than 35  percent of lakes in our study are considered eutrophic to hypereutrophic using chlorophyll a as a diagnostic versus only 15 percent for all lakes from \citet{sorannoLAGOSNEMultiscaledGeospatial2017} located within our study extent (Figure A3).
 For the regional terms in our models, we used hydrologic regions at the subbasin (i.e.
@@
 All models had the same set of fixed effect coefficients while each individual model used a single different watershed land-use variable as a random effect.
-This modelling strategy is supported by our view that watershed land-use is an indirect proxy (sensu Burcher et al.
-2007, Hayes et al.
-2015, King et al.
-2005) for other unquantifiable agricultural activities.
+This modelling strategy is supported by our view that watershed land-use is an indirect proxy (sensu \citealt{burcherLandcoverCascadeRelationships2007,hayesClimateLandUse2015,kingSpatialConsiderationsLinking2005}) for other unquantifiable agricultural activities.
 Therefore, we expect the makeup of specific activities represented by this indirect measure to vary regionally.
@@
 We did not use the results of this exercise for building our model, performing model selection, or variable selection.
-For qualitative analysis of our model results, we classified predictor variables following Collins et al.
-(2017) into categories based on the dominant mechanism affecting lake nutrient concentrations, which includes nutrient inputs, nutrient transport, spatial configuration of land-use in stream buffers (Spatial config.), lake characteristics, and watershed land-use (LULC).
+For qualitative analysis of our model results, we classified predictor variables following \citet{collinsLakeNutrientStoichiometry2017} into categories based on the dominant mechanism affecting lake nutrient concentrations, which includes nutrient inputs, nutrient transport, spatial configuration of land-use in stream buffers (Spatial config.), lake characteristics, and watershed land-use (LULC).
 
-We fit all models in a Bayesian framework using the brms R package interface to the Stan statistical program (Bürkner et al., 2017; Stan Development Team, 2017).
-We used horseshoe shrinkage priors on all fixed effect coefficients to evaluate variable importance (Carvalho et al.
-2010).
+We fit all models in a Bayesian framework using the brms R package interface to the Stan statistical program \citep{burkner2017brms, stan2017}.
+We used horseshoe shrinkage priors on all fixed effect coefficients to evaluate variable importance \citep{carvalhoHorseshoeEstimatorSparse2010}.
 We considered a response variable sensitive to a given predictor if the predictor’s 95% credible interval did not overlap 0.
@@
 We evaluated model fit of each watershed land-use variable (i.e., each model having one regionally varying coefficient) in two ways.
-First, we computed a Bayesian R2 following the method of Gelman et al.
-(2017) and second, we computed differences in expected log predictive density (ELPD) using the leave-one-out cross e validation routines provided by the loo R package and implemented in brms (Vehtari et al.
-2017).
+First, we computed a Bayesian $R^2$ following the method of \citet{gelmanRsquaredBayesianRegression2017} and second, we computed differences in expected log predictive density (ELPD) using the leave-one-out cross e validation routines provided by the loo R package and implemented in brms \citep{vehtari2017practical}.
 The loo package uses leave-one-out cross validation to estimate overall model error by computing O the average error of models iteratively trained on all the data except for a single point.
-ELPD values have a similar interpretation to information criterion measures such as Akaike information criterion (AIC) or Watanabe-Akaike information criterion (WAIC) except that values are on a different scale (Gelman et al.
-2013).
-Typically, models are considered to be different if they are separated by an AIC value of greater than 2 (Anderson and Burnham 2002), which is equivalent to an ELPD value of -1 (Gelman et al.
-2013).
+ELPD values have a similar interpretation to information criterion measures such as Akaike information criterion (AIC) or Watanabe-Akaike information criterion (WAIC) except that values are on a different scale \citep{gelmanUnderstandingPredictiveInformation2013}.
+Typically, models are considered to be different if they are separated by an AIC value of greater than 2 \citep{andersonAvoidingPitfallsWhen2002}, which is equivalent to an ELPD value of -1 \citep{gelmanUnderstandingPredictiveInformation2013}.
 We report differences in ELPD among models using the notation $\Delta$ELPD.
@@
 We examined model fits to ensure that all models had acceptable convergence of MCMC chains and had approximately normal model residuals.
-We further tested for spatial correlation among model residuals using the spind R package (Carl et al.
-2018).
-All of our code for model fitting and evaluation is available at [Zenodo DOI].
+We further tested for spatial correlation among model residuals using the spind R package \citep{carlSpindPackageAccount2018}.
+All of our code for model fitting and evaluation is available at \href{https://doi.org/10.5281/zenodo.3754916}{doi:10.5281/zenodo.3754916}.
 
@@
 Although we observed no difference in the specific watershed land-use predictor used in each top-ranked model, we found differences in the extent to which each top-ranked model was substantially different from lower ranked models.
-For example, in the case of P, all models had nearly identical R2 (0.63) and the difference between the top-ranked model and second ranked model was modest ($\Delta$ELPD = 0.41).
-For N models, however, agricultural and corn land-use models had higher R2 (0.58) compared to other models and the difference between the top-ranked and second ranked model was more substantial ($\Delta$ELPD = 2.58, Figure 2, Table \ref{table1}).
+For example, in the case of P, all models had nearly identical $R^2$ (0.63) and the difference between the top-ranked model and second ranked model was modest ($\Delta$ELPD = 0.41).
+For N models, however, agricultural and corn land-use models had higher $R^2$ (0.58) compared to other models and the difference between the top-ranked and second ranked model was more substantial ($\Delta$ELPD = 2.58, Figure 2, Table \ref{table1}).
 
@@
 The results show that, at least in the case of N, removing these predictors e caused model variance to be apportioned from watershed and buffer land-use predictors to N input and P fertilizer predictors (Figure A4).
-However, this non-land-use N model had a relatively poor fit (R2 = 0.40) compared to the top-ranked model that included land-use as a predictor (R2 = 0.58).
+However, this non-land-use N model had a relatively poor fit ($R^2$ = 0.40) compared to the top-ranked model that included land-use as a predictor ($R^2$ = 0.58).
 

### 2020-04-17 manuscript/manuscript.Rmd
finish inline linking and typo fixes

@@
 Our first source for granular agricultural information was the 2010 Cropland Data Layer (CDL, \citealt{usda-nassNationalAgriculturalStatistics2019}), which we used to generate lake watershed and stream buffer estimates of the proportion of land cover due to specific crops such as corn and soybeans.
-We used the R package cdlTools to access CDL products \citep{chenToolsDownloadWork2018}.
+We used the R package `cdlTools` to access CDL products \citep{chenToolsDownloadWork2018}.
 We used the 2010 CDL data because this was the first year of high resolution (30 x 30m) CDL data collection that matched our lake nutrient data collection window.
@@
 Here agricultural land-use is defined in the aggregate sense as the proportion of land used for agriculture in a lake’s watershed whereas “natural” land-uses include the sum of all non-agriculture and non-developed CDL classes.
-We identified the streams associated with each lake using the stream network extraction tool in the nhdR interface \citep{stachelekNhdRToolsWorking2019} to the National Hydrography Network \citep{usgsNationalHydrographyDataset2019}.
-We compiled soil characteristics for each lake watershed using the Gridded Soil Survey Geographic Database (gSSURGO, \citealt{soil2016gridded}) where we used the python package gssurgo \citep{stachelekGssurgoPythonToolbox2019} to access gSSURGO  products.
+We identified the streams associated with each lake using the stream network extraction tool in the `nhdR` interface \citep{stachelekNhdRToolsWorking2019} to the National Hydrography Network \citep{usgsNationalHydrographyDataset2019}.
+We compiled soil characteristics for each lake watershed using the Gridded Soil Survey Geographic Database (gSSURGO, \citealt{soil2016gridded}) where we used the python package `gssurgo` \citep{stachelekGssurgoPythonToolbox2019} to access gSSURGO  products.
 One such product was wetland potential, defined as the percentage of the soil grid that meets the criteria for hydric soils formed under conditions of saturation, flooding, or ponding long enough to develop anaerobic conditions but not so long as to be classified as a permanent waterbody \citep{soil2016gridded}.
 Finally, we compiled mean annual nutrient inputs via fertilizer and manure to lake watersheds from 1982-2001 using county level data provided by \citet{ruddy2006county}.
-We spatially aligned these county level estimates to lake watershed polygons provided by LAGOS-NE \citep{LAGOSgis} using the area-weighted interpolation functions provided by the sf R package \citep{pebesma2018}.
+We spatially aligned these county level estimates to lake watershed polygons provided by LAGOS-NE \citep{LAGOSgis} using the area-weighted interpolation functions provided by the `sf` R package \citep{pebesma2018}.
 All of our data and data processing code are available at \href{https://doi.org/10.5281/zenodo.3754916}{doi:10.5281/zenodo.3754916}.
@@
 states \citep{sorannoLAGOSNEMultiscaledGeospatial2017}.
-We excluded lakes from our analysis if they had a surface area > 400 km2 or a maximum depth > 35 m.
+We excluded lakes from our analysis if they had a surface area > 400 $km^2$ or a maximum depth > 35 m.
 These removals resulted in exclusion of approximately 40 lakes which we regarded as outliers that would likely have undue influence on model results because such large and deep lakes are likely to respond differently to enrichment as a result of enhanced stratification.
@@
 fixed effect) coefficients.
-This set of global coefficients included estimates for watershed soil characteristics, near-stream land-use, as well as fertilizer and manure inputs for each lake (Xi).
+This set of global coefficients included estimates for watershed soil characteristics, near-stream land-use, as well as fertilizer and manure inputs for each lake ($X_i$).
 Whereas $\beta$ coefficients were estimated as fixed effects, $\gamma$ coefficients and $\alpha$ intercepts were estimated as varying (i.e.
-random) slopes and intercepts respectively among m hydrologic regions j on watershed land-use (Wij).
+random) slopes and intercepts respectively among m hydrologic regions j on watershed land-use ($W_{ij}$).
 Region specific intercepts $\alpha$ and $\gamma$ slopes were assumed to come from a multivariate normal distribution (MVN) where $\mu_\alpha$ and $\mu_{\gamma1}$ are their respective grand mean (i.e., population level) estimates.
-We tested a variety of watershed land-use types for Wij, including both granular and more aggregate measures of agricultural activity.
+We tested a variety of watershed land-use types for $W_{ij}$, including both granular and more aggregate measures of agricultural activity.
 Our only aggregate measure of agricultural activity was agricultural land-use whereas we used several granular measures of agricultural activity.
@@
 
-We fit all models in a Bayesian framework using the brms R package interface to the Stan statistical program \citep{burkner2017brms, stan2017}.
+We fit all models in a Bayesian framework using the `brms` R package interface to the Stan statistical program \citep{burkner2017brms, stan2017}.
 We used horseshoe shrinkage priors on all fixed effect coefficients to evaluate variable importance \citep{carvalhoHorseshoeEstimatorSparse2010}.
@@
 We evaluated model fit of each watershed land-use variable (i.e., each model having one regionally varying coefficient) in two ways.
-First, we computed a Bayesian $R^2$ following the method of \citet{gelmanRsquaredBayesianRegression2017} and second, we computed differences in expected log predictive density (ELPD) using the leave-one-out cross e validation routines provided by the loo R package and implemented in brms \citep{vehtari2017practical}.
-The loo package uses leave-one-out cross validation to estimate overall model error by computing O the average error of models iteratively trained on all the data except for a single point.
+First, we computed a Bayesian $R^2$ following the method of \citet{gelmanRsquaredBayesianRegression2017} and second, we computed differences in expected log predictive density (ELPD) using the leave-one-out cross e validation routines provided by the `loo` R package and implemented in brms \citep{vehtari2017practical}.
+The `loo` package uses leave-one-out cross validation to estimate overall model error by computing the average error of models iteratively trained on all the data except for a single point.
 ELPD values have a similar interpretation to information criterion measures such as Akaike information criterion (AIC) or Watanabe-Akaike information criterion (WAIC) except that values are on a different scale \citep{gelmanUnderstandingPredictiveInformation2013}.
@@
 We examined model fits to ensure that all models had acceptable convergence of MCMC chains and had approximately normal model residuals.
-We further tested for spatial correlation among model residuals using the spind R package \citep{carlSpindPackageAccount2018}.
+We further tested for spatial correlation among model residuals using the `spind` R package \citep{carlSpindPackageAccount2018}.
 All of our code for model fitting and evaluation is available at \href{https://doi.org/10.5281/zenodo.3754916}{doi:10.5281/zenodo.3754916}.
@@
 Lake characteristics (e.g., maximum depth and watershed to lake area ratio) along with measures of nutrient transport (e.g., baseflow) and near-stream agriculture were significant predictors in all lake N and P models that we fit.
-When we  compared among different models for each nutrient individually, we found that those with agricultural watershed O land-use (in the aggregate sense) were top-ranked (i.e., had the lowest absolute value leave-one-out cross validation score) for models of both TN and TP concentrations (Figure 2, Table 2).
+When we  compared among different models for each nutrient individually, we found that those with agricultural watershed land-use (in the aggregate sense) were top-ranked (i.e., had the lowest absolute value leave-one-out cross validation score) for models of both TN and TP concentrations (Figure \ref{fig2, Table \ref{table2}).
 Although we observed no difference in the specific watershed land-use predictor used in each top-ranked model, we found differences in the extent to which each top-ranked model was substantially different from lower ranked models.
 For example, in the case of P, all models had nearly identical $R^2$ (0.63) and the difference between the top-ranked model and second ranked model was modest ($\Delta$ELPD = 0.41).
-For N models, however, agricultural and corn land-use models had higher $R^2$ (0.58) compared to other models and the difference between the top-ranked and second ranked model was more substantial ($\Delta$ELPD = 2.58, Figure 2, Table \ref{table1}).
+For N models, however, agricultural and corn land-use models had higher $R^2$ (0.58) compared to other models and the difference between the top-ranked and second ranked model was more substantial ($\Delta$ELPD = 2.58, Figure \ref{fig2}, Table \ref{table1}).
 
@@
 When we looked more closely at each top-ranked model, we found similarities in the
-types of predictors that contributed significantly to the top-ranked N and P models (Figure 3).
+types of predictors that contributed significantly to the top-ranked N and P models (Figure \ref{fig3}).
 First, both N and P models included measures of lake characteristics such as maximum depth and watershed to lake area ratio as significant predictors, with the sign of these associated coefficients matching our conventional understanding, in which shallower lakes and lakes with greater hydrologic loads have higher TN and TP concentrations.
@@
 
-Although top-ranked N and P models shared some similarities in the type of predictors that contributed significantly to each model, the coefficients of these models differed in magnitude, and thus the top-ranked models varied in their sensitivity to specific predictors (Figure 3).
+Although top-ranked N and P models shared some similarities in the type of predictors that contributed significantly to each model, the coefficients of these models differed in magnitude, and thus the top-ranked models varied in their sensitivity to specific predictors (Figure \ref{fig3}).
 For example, the top-ranked P model was more sensitive to lake characteristics, whereas the top-ranked N model was more sensitive to watershed land-use.
@@
 In an attempt to further investigate this possibility, we fit alternative models excluding all land-use predictors.
-The results show that, at least in the case of N, removing these predictors e caused model variance to be apportioned from watershed and buffer land-use predictors to N input and P fertilizer predictors (Figure A4).
+The results show that, at least in the case of N, removing these predictors caused model variance to be apportioned from watershed and buffer land-use predictors to N input and P fertilizer predictors (Figure A4).
 However, this non-land-use N model had a relatively poor fit ($R^2$ = 0.40) compared to the top-ranked model that included land-use as a predictor ($R^2$ = 0.58).
@@
 
-Both TN and TP concentrations were sensitive to measures of watershed land-use as well as near-stream agriculture (Figure 2, Table \ref{table1}).
-Despite these similarities, we found differences in both the magnitude of these effects and the extent to which we observed regional variation in watershed land-use sensitivity for N and P models (Figure 4).
+Both TN and TP concentrations were sensitive to measures of watershed land-use as well as near-stream agriculture (Figure \ref{fig2}, Table \ref{table1}).
+Despite these similarities, we found differences in both the magnitude of these effects and the extent to which we observed regional variation in watershed land-use sensitivity for N and P models (Figure \ref{fig4}).
 For P, there was little evidence that sensitivity to watershed land-use was regionally variable.
-More specifically, the credible intervals for the slope of each individual region overlapped the global slope estimate (Figure 4).
+More specifically, the credible intervals for the slope of each individual region overlapped the global slope estimate (Figure \ref{fig4}).
 In contrast, for N we found evidence for regional variation in sensitivity to watershed land-use.
-For this nutrient, the credible intervals for 2 of the 37 regions did not overlap the global estimate (Figure 4).
-These regions were found in parts of Iowa, Minnesota, and Illinois and appear to be more sensitive to watershed land-use – i.e., lake N increases at a faster rate per unit increase in agricultural land-use compared to other regions (Figure 5).
-The median soil clay content of watersheds in these regions was higher than the median across watersheds in all other regions (Figure 6).
+For this nutrient, the credible intervals for 2 of the 37 regions did not overlap the global estimate (Figure \ref{fig4}).
+These regions were found in parts of Iowa, Minnesota, and Illinois and appear to be more sensitive to watershed land-use – i.e., lake N increases at a faster rate per unit increase in agricultural land-use compared to other regions (Figure \ref{fig5}).
+The median soil clay content of watersheds in these regions was higher than the median across watersheds in all other regions (Figure \ref{fig6}).
 Furthermore, these two regions had a unique combination of both high soil clay content and extensive tile drainage (Figure S6).
@@
 Specifically, our finding that model coefficients on near-stream agriculture (i.e., agricultural land-use in stream buffers) in all N and P models were significant and positive indicates a nutrient-delivery effect of stream buffer agriculture and suggests that the spatial configuration of agriculture with respect to stream buffers has a detectable influence on both lake N and P at macroscales.
-This is consistent with prior studies conducted over more limited spatial extents which examined relationships between lake or stream nutrient concentrations and agricultural land-use in stream buffers (Diebel et al.
-2007, Baker et al.
-2006, Gemesi et al.
-2011, Soranno et al.
-2015).
+This is consistent with prior studies conducted over more limited spatial extents which examined relationships between lake or stream nutrient concentrations and agricultural land-use in stream buffers \citep{diebelLandscapePlanningAgricultural2009, bakerImprovedMethodsQuantifying2006,gemesiEffectsWatershedConfiguration2011, sorannoEffectsLandUse2015}.
 In contrast to near-stream agriculture, we found that near-stream “natural” land-use was not significant in either N or P models.
-While we cannot definitively answer why, it may be related to the role that natural buffers play in nutrient cycling for N and P (Alexander et al.
-2008, Canham et al.
-2012).
-In the case of N, natural buffers may reduce stream loading by facilitating denitrification, whereas, in the case of P, natural buffers may trap particulate bound material without necessarily removing it (Mayer et al.
-2007, Naiman 2010).
-An alternative possibility is that we are observing a scale effect whereby the delivery effect of near-stream agriculture is spatially consistent whereas the trapping and removal effects of N and P by natural buffers is more spatially variable (Parn et al.
-2012).
-Finally, we may not have observed a protective effect of natural buffers because natural land-use in buffers is too coarse of a proxy for “riparian buffers” composed of forest or herbaceous vegetation (Mayer et al.
-2007).
+While we cannot definitively answer why, it may be related to the role that natural buffers play in nutrient cycling for N and P \citep{alexanderDifferencesPhosphorusNitrogen2008,canhamNitrogenDepositionLake2012}.
+In the case of N, natural buffers may reduce stream loading by facilitating denitrification, whereas, in the case of P, natural buffers may trap particulate bound material without necessarily removing it \citep{mayerMetaAnalysisNitrogenRemoval2007,naiman2010riparia}.
+An alternative possibility is that we are observing a scale effect whereby the delivery effect of near-stream agriculture is spatially consistent whereas the trapping and removal effects of N and P by natural buffers is more spatially variable \citep{parnIndicatorsNutrientsTransport2012}.
+Finally, we may not have observed a protective effect of natural buffers because natural land-use in buffers is too coarse of a proxy for “riparian buffers” composed of forest or herbaceous vegetation \citep{mayerMetaAnalysisNitrogenRemoval2007}.
 
@@
 We found that for N models, land-use of specific crops was significant, although it was not found in the top-ranked model.
-Specifically, we found that watershed land-use in corn production was a significant predictor in the second-ranked N model (Table 2).
-In the case of P by contrast, neither aggregate nor granular measures of watershed land-use were significant in any models (Figure 2).
+Specifically, we found that watershed land-use in corn production was a significant predictor in the second-ranked N model (Table \ref{table2}).
+In the case of P by contrast, neither aggregate nor granular measures of watershed land-use were significant in any models (Figure \ref{fig2}).
 This can be explained by our finding that all watershed land-use metrics had weak relationships with lake P, especially relative to the strong relationships we observed between P and other factors like lake depth, hydrology, and near-stream agricultural land-use.
-Here, our finding is consistent with prior studies in stream ecosystems showing that the influence of hydrology exceeds that of agricultural land-use or anthropogenic P inputs (Metson et al.
-2017).
+Here, our finding is consistent with prior studies in stream ecosystems showing that the influence of hydrology exceeds that of agricultural land-use or anthropogenic P inputs \citep{metsonLinkingTerrestrialPhosphorus2017}.
 
@@
 None of the nutrient input variables were significant for either N or P models.
-On the surface, this would seem to contradict the findings of prior research such as that of Bellmore et al.
-(2018), who found that stream TN concentrations were more strongly controlled by N input predictors relative to measures of either watershed or near-stream land-use.
+On the surface, this would seem to contradict the findings of prior research such as that of \citet{bellmoreNitrogenInputsDrive2018}, who found that stream TN concentrations were more strongly controlled by N input predictors relative to measures of either watershed or near-stream land-use.
 However, our finding has several alternative explanations.
-First, differences between our lake study and the Bellmore et al.
-(2018) stream study may simply point to differences in the controls on stream nitrogen concentrations relative to lake nitrogen concentrations (Allan 2004, Canham et al.
-2012).
+First, differences between our lake study and the \citet{bellmoreNitrogenInputsDrive2018} stream study may simply point to differences in the controls on stream nitrogen concentrations relative to lake nitrogen concentrations \citep{allanLandscapesRiverscapesInfluence2004,canhamNitrogenDepositionLake2012}.
 Second, our finding that N and P were insensitive to nutrient input variables may be a result of shared variance between nutrient input variables and watershed land-use.
-This makes sense given that agricultural land-uses and corn land-use in particular are associated with high rates of fertilizer and manure application (Powers 2007).
+This makes sense given that agricultural land-uses and corn land-use in particular are associated with high rates of fertilizer and manure application \citep{powersNutrientLoadsSurface2007}.
 To test this explanation, we formulated N models without a watershed land-use term and observed that model variance was transferred from watershed land-use to the nutrient input terms total N input and P fertilizer (Figure S4).
 While the positive coefficient on total N input has a straightforward interpretation, the negative coefficient on P fertilizer is unclear.
-Rather than evidence of a true inverse relationship between P fertilizer and N (or evidence for stoichiometric interaction sensu Paerl et al.
-2016), we interpret the negative coefficient on P fertilizer as evidence of either model misspecification (i.e., model fit was poor compared to the model with land-use because N was very sensitive to land-use) or as evidence of multicollinearity among nutrient input variables (Figure S5).
+Rather than evidence of a true inverse relationship between P fertilizer and N (or evidence for stoichiometric interaction sensu \citealt{paerlItTakesTwo2016}, we interpret the negative coefficient on P fertilizer as evidence of either model misspecification (i.e., model fit was poor compared to the model with land-use because N was very sensitive to land-use) or as evidence of multicollinearity among nutrient input variables (Figure S5).
 Thus, we think that it is likely that the removal of one of the key drivers of N (being land-use) caused model variance to be transferred to nutrient input predictors generally such that the specific highlighting of P fertilizer is a result of noise rather than a true relationship.
@@
 For example, we found that baseflow was a significant predictor in all N but especially all P models.
-This is consistent with prior research at macroscales showing the sensitivity of lake nutrients to this metric (Collins et al.
-2017).
+This is consistent with prior research at macroscales showing the sensitivity of lake nutrients to this metric \citep{collinsLakeNutrientStoichiometry2017}.
 In contrast to baseflow, we found that watershed soil clay content was a significant predictor in all N models but not in any P models.
@@
 Instead, we found evidence for a non-linear relationship, which may explain the negative coefficient on clay, whereby clay and TN were positively correlated over most of the range of watershed clay content but were negatively correlated in watersheds with very high soil clay content (> 20%; Figure S7).
-This non-linear relationship may be an artifact of the specific non-random sampling of our lakes whereby the lakes with extremely high soil clay content watersheds happen to have extremely long water residence times leading to extensive removal of N loads due to denitrification (Groffman et al.
-2009).
+This non-linear relationship may be an artifact of the specific non-random sampling of our lakes whereby the lakes with extremely high soil clay content watersheds happen to have extremely long water residence times leading to extensive removal of N loads due to denitrification \citep{groffmanChallengesIncorporatingSpatially2009}.
 Overall, granular measures of agriculture were significant in both N and P models.
-However, the contribution of such measures relative to other non-agricultural predictors was greater for N models (Figure 2, Figure 3).
+However, the contribution of such measures relative to other non-agricultural predictors was greater for N models (Figure \ref{fig2}, Figure \ref{fig3}).
 One reason why granular measures of agricultural activity had a greater effect on N models may be that variation in N is less effectively captured solely by lake and watershed characteristics owing in part to the more complex nature of transformations in the nitrogen cycle.
-This finding is consistent with that of Collins et al.
-(2017) and Wagner and Schliep (2018) who found that lake depth coefficients were of a much higher magnitude for P relative to N.
-This is expected since depth strongly controls internal P loading (i.e., recycling), which is a dominant control on lake phosphorus dynamics (Sondergaard et al.
-2013).
+This finding is consistent with that of \citet{collinsLakeNutrientStoichiometry2017} and \citet{wagnerCombiningNutrientProductivity2018} who found that lake depth coefficients were of a much higher magnitude for P relative to N.
+This is expected since depth strongly controls internal P loading (i.e., recycling), which is a dominant control on lake phosphorus dynamics \citep{sondergaardPersistentInternalPhosphorus2013}.
 
@@
 The macroscale nature of our study motivated our second research question examining how relationships between agricultural activities and lake nutrients vary regionally.
-This is because recent research has shown that analyzing macroscale lake datasets without considering the possibility of regionally varying relationships runs the risk of drawing imprecise or incorrect conclusions because it can lump together lakes with fundamentally different responses to a given predictor variable (Qian et al.
-2019).
-Additionally, we looked at this question because prior studies have shown regional variation in the relationship of lake nutrient concentrations to aggregate measures of agriculture (Wagner and Schliep 2018).
+This is because recent research has shown that analyzing macroscale lake datasets without considering the possibility of regionally varying relationships runs the risk of drawing imprecise or incorrect conclusions because it can lump together lakes with fundamentally different responses to a given predictor variable \citep{qianImplicationsSimpsonParadox2019}.
+Additionally, we looked at this question because prior studies have shown regional variation in the relationship of lake nutrient concentrations to aggregate measures of agriculture \citep{wagnerCombiningNutrientProductivity2018}.
+
 In our study, we found mixed evidence for regional variation in relationships with watershed land-use, depending on the lake nutrient response variable.
 For N, we found evidence for regional variation whereby lakes in two of the 37 regions were more sensitive to changes in agricultural land-use relative to other regions.
-The reasons for this elevated sensitivity are unclear, but one possible reason may be that watersheds in these more sensitive regions had higher median soil clay content than the median soil clay content of watersheds in less sensitive regions (Figure 6).
+The reasons for this elevated sensitivity are unclear, but one possible reason may be that watersheds in these more sensitive regions had higher median soil clay content than the median soil clay content of watersheds in less sensitive regions (Figure \ref{fig6}).
 Higher soil clay content in particular may ultimately control the nitrogen content of field runoff because it is associated with more direct (i.e., tile) drainage.
-For example, maps produced by Capel et al.
-(2018a) suggest that our more sensitive regions correspond roughly with areas where field exports of nutrients are likely to bypass trapping by riparian buffers.
-As evidence of this association, data from Nakagaki and Wieczorek (2016) indicate that watersheds in these two sensitive regions had a unique combination of high soil clay content and extensive tile drainage (Figure S6).
+For example, maps produced by \citet{capelConceptualFrameworkEffectively2018} suggest that our more sensitive regions correspond roughly with areas where field exports of nutrients are likely to bypass trapping by riparian buffers.
+As evidence of this association, data from \citet{nakagaki2016estimates} indicate that watersheds in these two sensitive regions had a unique combination of high soil clay content and extensive tile drainage (Figure S6).
 For P, we found no evidence for regional variation in its relationship with watershed land-use.
-This finding, that watershed land-use can be modelled as a global (fixed) effect, is consistent with that of Taranu and Gregory-Eaves (2008), who found no statistically significant differences in region-specific relationships between lake P and agricultural land-use.
-However, it is inconsistent with that of Wagner et al.
-(2011), who found regionally variable relationships between lake P and agricultural land-use using a multilevel modelling framework.
-One reason that both our analysis and the Taranu and Gregory-Eaves (2008) study did not observe regional variation in the watershed land-use versus P relationship may be that P is so strongly controlled by lake depth that there is little additional explanatory power offered by including a watershed land-use term.
-In addition, if lake P is controlled primarily by lake depth, which we can assume does not change with time, then our results may explain the finding of Oliver et al.
-(2017) that lake P trends are spatially consistent whereas lake N trends have distinct regional variability.
+This finding, that watershed land-use can be modelled as a global (fixed) effect, is consistent with that of \citet{taranuQuantifyingRelationshipsPhosphorus2008}, who found no statistically significant differences in region-specific relationships between lake P and agricultural land-use.
+However, it is inconsistent with that of \citet{wagnerLandscapeDriversRegional2011}, who found regionally variable relationships between lake P and agricultural land-use using a multilevel modelling framework.
+One reason that both our analysis and the \citet{taranuQuantifyingRelationshipsPhosphorus2008} study did not observe regional variation in the watershed land-use versus P relationship may be that P is so strongly controlled by lake depth that there is little additional explanatory power offered by including a watershed land-use term.
+In addition, if lake P is controlled primarily by lake depth, which we can assume does not change with time, then our results may explain the finding of \citet{oliverUnexpectedStasisChanging2017} that lake P trends are spatially consistent whereas lake N trends have distinct regional variability.
 
@@
 Knowledge of differences in the drivers of lake N and P can support the design of effective and efficient policy approaches to maintain or improve water quality.
-For instance, our finding of regional variation in the relationship between lake TN concentrations and watershed land-use in agriculture suggests spatial targeting of best management practices (BMPs) to specific regions known to be highly sensitive (Holmes et al.
-2016).
+For instance, our finding of regional variation in the relationship between lake TN concentrations and watershed land-use in agriculture suggests spatial targeting of best management practices (BMPs) to specific regions known to be highly sensitive \citep{holmesEffectsBestManagement2016}.
 In addition, our finding of strong relationships between lake TP concentrations and lake characteristic predictors contrasts with the strong relationships we observed between watershed land-use and lake TN.
-Given that watershed land-use, rather than lake characteristics, is a more feasible management target, our results suggest that the cost-effectiveness of BMPs could differ depending on whether the goal is to protect against excess N, P, or both (Paerl et al.
-2016).
+Given that watershed land-use, rather than lake characteristics, is a more feasible management target, our results suggest that the cost-effectiveness of BMPs could differ depending on whether the goal is to protect against excess N, P, or both \citep{paerlItTakesTwo2016}.
 For P, our analysis suggests that nutrient control policies are likely to be especially effective in shallow lakes and lakes with low baseflow (i.e., those with flashier hydrology).
-Conversely, phosphorus control in deeper lakes and reservoirs with long residence times will likely require recovery efforts in addition to prevention efforts due to the long time-scales of stored (i.e., legacy) P (Powers et al.
-2015).
+Conversely, phosphorus control in deeper lakes and reservoirs with long residence times will likely require recovery efforts in addition to prevention efforts due to the long time-scales of stored (i.e., legacy) P \citep{powersControlNitrogenPhosphorus2015}.
 In contrast to P, our results show that lake TN concentrations are more sensitive to watershed land-use.
-This suggests that policies to enhance the use of BMPs to reduce N inputs to lakes are likely to require a greater degree of stakeholder involvement, possibly through consideration of tradeoffs between land retirement and working lands programs (Capel et al.
-2018a, NRC 2010).
+This suggests that policies to enhance the use of BMPs to reduce N inputs to lakes are likely to require a greater degree of stakeholder involvement, possibly through consideration of tradeoffs between land retirement and working lands programs \citep{capelConceptualFrameworkEffectively2018,nrcSustainableAgriculturalSystems2010}.
 
@@
 However, there are several instances where time may be important, and these would likely be fruitful areas for future research.
-For example, Lark et al.
-(2015) showed marked conversion of conservation reserve program (CRP) lands to cropland throughout the footprint of our study from 2008 to 2012.
-Such changes in land-use could make it more difficult to quantify lake sensitivity to agriculture if relationships vary through time especially if relationships are subject to threshold effects (Renwick et al.
-2008).
+For example, \citet{larkCroplandExpansionOutpaces2015} showed marked conversion of conservation reserve program (CRP) lands to cropland throughout the footprint of our study from 2008 to 2012.
+Such changes in land-use could make it more difficult to quantify lake sensitivity to agriculture if relationships vary through time especially if relationships are subject to threshold effects \citep{renwickWaterQualityTrends2008}.
 A more subtle illustration of when time may be important is when field-scale nutrient export is highly dependent on episodic hydrology.
-For example, a number of previous studies have shown that field-scale nutrient export of N is greatest when a series of dry years is followed by a wet spring (Motew et al.
-2017, Strickling and Obenour 2018).
-It might make sense then to organize modeling around whether lake watersheds are generally subject to slowflow, fastflow, or drainflow (Capel et al.
-2018a) nutrient transport rather than solely taking a spatial regionalization approach (i.e., using HUCs).
+For example, a number of previous studies have shown that field-scale nutrient export of N is greatest when a series of dry years is followed by a wet spring \citep{motewInfluenceLegacyLake2017,stricklingLeveragingSpatialTemporal2018}.
+It might make sense then to organize modeling around whether lake watersheds are generally subject to slowflow, fastflow, or drainflow \citep{capelConceptualFrameworkEffectively2018} nutrient transport rather than solely taking a spatial regionalization approach (i.e., using HUCs).
 Barriers to more detailed temporal approaches include greater demands of spatio-temporally resolved data products.

### 2020-04-17 scripts/00_get_usgs.R
rm unnesessary calls to the jsta package

@@ -17,7 +17,7 @@ ofile <- paste0(sfile, "x")
 
 if(!file.exists(ofile)){
   # convert xls to xlsx
-  jsta::get_if_not_exists("https://pubs.usgs.gov/sir/2006/5012/excel/Nutrient_Inputs_1982-2001jan06.xls", sfile, overwrite = FALSE)
+  get_if_not_exists("https://pubs.usgs.gov/sir/2006/5012/excel/Nutrient_Inputs_1982-2001jan06.xls", sfile, overwrite = FALSE)
   writexl::write_xlsx(readxl::read_excel(sfile), ofile)
 
   # # file.exists(sfile)

### 2020-04-17 scripts/99_utils.R

@@ -471,3 +471,23 @@ get_r2 <- function(x){
   x$R2 <- res
   x
 }
+
+# jsta::pdf_table
+pdf_table <- function(x, out_name = "test.pdf"){
+  if(is.data.frame(x)){
+    pdf(file = out_name)
+    # Only fits 25 rows of data. Warn if greater?
+    gridExtra::grid.table(x, rows = rep("", nrow(x)))
+    dev.off()
+  }
+  if(is.character(x)){
+    zz <- file("test.md", "w")
+    sink(zz)
+    cat("\\pagenumbering{gobble}")
+    print(x)
+    sink()
+    close(zz)
+    system(paste0("pandoc -s test.md -o ", out_name))
+    unlink("test.md")
+  }
+}

### 2020-04-19 tables/01_predictors.Rmd
add latex table placeholders

@@
 knitr::kable(dt, digits = 0, format = "markdown") 
+# knitr::kable(dt, format = 'latex', align = c("lllll"))
 #%>%

### 2020-04-19 tables/03_model_summary.Rmd
add latex table placeholders

@@
                row.names = FALSE)
+# knitr::kable(digits = 2, format = 'latex', align = c("lllll"), row.names = FALSE)
 ```

### 2020-04-19 manuscript/manuscript.Rmd
print face package names

@@
 We evaluated model fit of each watershed land-use variable (i.e., each model having one regionally varying coefficient) in two ways.
-First, we computed a Bayesian $R^2$ following the method of \citet{gelmanRsquaredBayesianRegression2017} and second, we computed differences in expected log predictive density (ELPD) using the leave-one-out cross e validation routines provided by the `loo` R package and implemented in brms \citep{vehtari2017practical}.
+First, we computed a Bayesian $R^2$ following the method of \citet{gelmanRsquaredBayesianRegression2017} and second, we computed differences in expected log predictive density (ELPD) using the leave-one-out cross e validation routines provided by the `loo` R package and implemented in `brms` \citep{vehtari2017practical}.
 The `loo` package uses leave-one-out cross validation to estimate overall model error by computing the average error of models iteratively trained on all the data except for a single point.
@@
 
-We used the default settings of brms to generate posterior estimates using four chains of 4,000 iterations each with no thinning and discarding the first 1,000 iterations.
+We used the default settings of `brms` to generate posterior estimates using four chains of 4,000 iterations each with no thinning and discarding the first 1,000 iterations.
 We examined model fits to ensure that all models had acceptable convergence of MCMC chains and had approximately normal model residuals.

### 2020-04-21 manuscript/manuscript.Rmd
add missing paragraph break
fix misreferenced table and supplement fig prefixs

@@
 We used the 2010 CDL data because this was the first year of high resolution (30 x 30m) CDL data collection that matched our lake nutrient data collection window.
-Because the CDL contains detailed coverage for dozens of crops, including rare crops with little to no coverage, we re-categorized CDL data based on \citet{larkCroplandExpansionOutpaces2015} to a more limited set of categories (Table A1).
+Because the CDL contains detailed coverage for dozens of crops, including rare crops with little to no coverage, we re-categorized CDL data based on \citet{larkCroplandExpansionOutpaces2015} to a more limited set of categories (Table S1).
 
@@
 For example, in the case of P, all models had nearly identical $R^2$ (0.63) and the difference between the top-ranked model and second ranked model was modest ($\Delta$ELPD = 0.41).
-For N models, however, agricultural and corn land-use models had higher $R^2$ (0.58) compared to other models and the difference between the top-ranked and second ranked model was more substantial ($\Delta$ELPD = 2.58, Figure \ref{fig2}, Table \ref{table1}).
+For N models, however, agricultural and corn land-use models had higher $R^2$ (0.58) compared to other models and the difference between the top-ranked and second ranked model was more substantial ($\Delta$ELPD = 2.58, Figure \ref{fig2}, Table \ref{table2}).
 
@@
 
-Both TN and TP concentrations were sensitive to measures of watershed land-use as well as near-stream agriculture (Figure \ref{fig2}, Table \ref{table1}).
+Both TN and TP concentrations were sensitive to measures of watershed land-use as well as near-stream agriculture (Figure \ref{fig2}, Table \ref{table2}).
 Despite these similarities, we found differences in both the magnitude of these effects and the extent to which we observed regional variation in watershed land-use sensitivity for N and P models (Figure \ref{fig4}).
@@
 As evidence of this association, data from \citet{nakagaki2016estimates} indicate that watersheds in these two sensitive regions had a unique combination of high soil clay content and extensive tile drainage (Figure S6).
+
 For P, we found no evidence for regional variation in its relationship with watershed land-use.

### 2020-04-21 scripts/99_utils.R
rm some unnecessary pkgs

@@ -21,12 +21,10 @@ library(stringr)
 suppressMessages(library(cowplot))
 suppressWarnings(library(mapview))
 library(broom)
-suppressMessages(library(ggsn))
 suppressMessages(library(nhdR))
 library(FedData)
 suppressMessages(library(raster))
 library(progress)
-suppressMessages(library(smoothr))
 library(assertr)
 suppressMessages(library(HydroData)) # install_github("mikejohnson51/HydroData")
 suppressMessages(library(kableExtra))

### 2020-04-21 manuscript/appendix.Rmd
link to code supplement
fix carlson ref

@@
 ```{r 02_cdl_key, results='asis', warning=FALSE, echo = FALSE}
-knitr::kable('', col.names = NULL, caption = "Category definitions from the 2010 CDL. See code supplement for listing of variables classified as 'ag'.")
+knitr::kable('', col.names = NULL, caption = "Category definitions from the 2010 CDL. See code supplement for listing of variables classified as 'ag' (https://doi.org/10.5281/zenodo.3754916).")
 ```
@@
 (2017) located within our study extent.
-Trophic state based on the chlorophyll critera from Carlson (1996).", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
+Trophic state based on the chlorophyll criteria from Carlson and Simpson (1996).", fig.width = 4, fig.height = 3.2, warning=FALSE, message=FALSE}
 

### 2020-04-22 manuscript/appendix.Rmd
note that lagos-gis cannot be symlinked

@@
 
-# compute per huc tile drainage
-# load huc4s
-# study_bbox    <- st_read("data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
-# hu4_focal     <- st_read("data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
-# hu4_focal     <- st_crop(st_transform(hu4_focal, st_crs(study_bbox)), study_bbox)
-# http://dx.doi.org/10.5066/F7W37TDP
-# library(exactextractr)
-# r <- raster("data/SubsurfaceDrainExtentMW_2012.tif")
-# test <- st_cast(hu4_focal, "MULTIPOLYGON")
-# test$tile_drainage <- exact_extract(r, test, "sum")
-# saveRDS(test, "data/tile_drainage.rds")
 test  <- readRDS("../data/tile_drainage.rds")

### 2020-04-22 scripts/00_get_tile_drainage.R
add tile_drainage getting to make

@@ -1,0 +1,13 @@
+source("scripts/99_utils.R")
+
+# compute per huc tile drainage
+# load huc4s
+study_bbox    <- st_read("data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
+hu4_focal     <- st_read("data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
+hu4_focal     <- st_crop(st_transform(hu4_focal, st_crs(study_bbox)), study_bbox)
+# http://dx.doi.org/10.5066/F7W37TDP
+library(exactextractr)
+r <- raster("data/SubsurfaceDrainExtentMW_2012.tif")
+test <- st_cast(hu4_focal, "MULTIPOLYGON")
+test$tile_drainage <- exact_extract(r, test, "sum")
+saveRDS(test, "data/tile_drainage.rds")

### 2020-04-23 figures/07_model-selection.Rmd
select correct bbox layer

@@
 # setwd("figures")
-study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
+study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[1,]
 states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)

### 2020-04-23 figures/11_map.Rmd
select correct bbox layer

@@
 # study_bbox    <- cl$study_bbox
-study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
+study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[1,]
 ep            <- st_read("../data/gis.gpkg", "ep", quiet = TRUE)

### 2020-07-23 manuscript/manuscript.Rmd
stash accepted/preprint version of ms

@@
 # If not specified, defaults to "This version was compiled on \today"
-#date_subtitle: Published in *Journal of Statistical Software*, 2018
 date_subtitle: > 
@@
 Stachelek et al., Ecological Applications.
-In Press, which has been published in final form at DOI:  [DOI](https://doi.org).
+2020, which has been published in final form at DOI:  [10.1002/eap.2187](https://doi.org/10.1002/eap.2187).
 This article may be used for non-commercial purposes in accordance with Wiley Terms and Conditions for Use of Self-Archived Versions.
